### 2015-02-18 papers/fittest14/paper.tex
adding previous papers

\documentclass[runningheads,a4paper]{llncs}

\usepackage{mathtools}
\usepackage{rotating}
\usepackage{longtable}
\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage{url}
\usepackage{amsmath}
\usepackage{algorithm2e}
\usepackage{xspace}
\usepackage{cite}
\usepackage{microtype}
\usepackage{booktabs}
\usepackage{color}
\usepackage{colortbl}
\usepackage{tabularx}
\usepackage[usenames,dvipsnames,table]{xcolor}
\usepackage{ctable}

\usepackage[pdftex]{hyperref}
\hypersetup{colorlinks,% 
citecolor=black,% 
filecolor=black,% 
linkcolor=black,% 
urlcolor=black 
}

\setupctable{botcap, captionskip = 0.5ex}

\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

\newcommand{\EVOSUITE}{{\sc EvoSuite}\xspace}
\newcommand{\MUTEST}{{\sc $\mu$Test}\xspace}
\newcommand{\CS}{{\sc SF100}\xspace}

\begin{document}

\mainmatter
\title{EvoSuite at the Second \\ Unit Testing Tool Competition}
\author{Gordon Fraser\inst{1} \and Andrea Arcuri\inst{2}}
%
\institute{University of Sheffield\\
Dep. of Computer Science, Sheffield, UK\\
\email{gordon.fraser@sheffield.ac.uk},\\
\and
Simula Research Laboratory\\
P.O. Box 134, 1325 Lysaker, Norway\\
\email{arcuri@simula.no}
}

\maketitle

\begin{abstract}
  \EVOSUITE is a mature research prototype implementing a search-based
  approach to unit test generation for Java classes. It has been
  successfully run on a variety of different Java projects in the
  past, and after winning the first instance of the unit testing tool
  competition at SBST'13, it has also taken part in the second
  run. This paper reports on the obstacles and challenges encountered
  during the latter competition.

\keywords{automated unit testing, search-based testing, competition}
\end{abstract}

\section{Introduction}

The \EVOSUITE test generation tool is a mature research prototype that
automatically generates unit test suites for given Java classes. The
first experiments with \EVOSUITE were reported in~\cite{FrA11b}, and
it has since been applied to a range of different projects and
domains~\cite{GoA_TSE12,FrA12b}, leading to various improvements over
time. 
In the first unit test competition organised at the SBST'13 workshop~\cite{sbst2013},
\EVOSUITE obtained the highest score among the participating tools~\cite{evosuiteAtSbst2013}.

Besides the obvious research challenge of achieving high coverage, the
challenges in building a tool like \EVOSUITE often lie in practical
issues imposed by the Java language, and the nature of real code. For
example, often the structure of code is trivial in terms of the
complexity of the branching conditions, yet difficult for a testing
tool as the code has complex environmental dependencies, such as files
and databases~\cite{FrA13a}. These findings are once more confirmed by
the results of the second unit testing tool competition.
%, following that was run
%after the first one~\cite{evosuiteAtSbst2013}.  
In this paper, we analyze the major obstacles \EVOSUITE encountered in
this second competition by focusing on classes where the coverage is
particularly low.

\section{About \EVOSUITE}

\EVOSUITE is a tool that automatically produces unit test suites for
Java classes with the aim to maximize code coverage. As input it
requires only the bytecode of the class under test as well as its
dependencies. This is provided automatically when using the
Eclipse-frontend to interact with \EVOSUITE, and on the command-line
it amounts to setting a classpath and specifying the target class name
as a command-line parameter.

\begin{table}[t] %[!h]
\centering
    \renewcommand{\arraystretch}{1.2}

    \begin{tabular}{|l|p{5cm}|}
      \hline
      \multicolumn{2}{|l|}{{\bf Prerequisites}} \\
      \hline
  Static or dynamic &  Dynamic testing at the Java class level\\
  Software Type &  Java classes\\
  Lifecycle phase&  Unit testing for Java programs\\
  Environment&  All Java development environments \\
  Knowledge required & JUnit unit testing for Java\\
  Experience required &  Basic unit testing knowledge\\
     \hline
      \multicolumn{2}{|l|}{{\bf Input and Output of the tool}} \\
      \hline
 Input & Bytecode of the target class and dependencies \\
    \hline
Output&  JUnit test cases (version 3 or 4)\\

      \hline
      \multicolumn{2}{|l|}{{\bf Operation}} \\
      \hline
  Interaction &  Through the command line\\
  User guidance &  manual verification of assertions for functional faults\\
  Source of information &  http://www.evosuite.org \\
  Maturity&  Mature research prototype, under development\\
  Technology behind the tool & Search-based testing / whole test suite generation\\
    \hline
      \multicolumn{2}{|l|}{{\bf Obtaining the tool and information}} \\
      \hline
License & GNU General Public License V3\\
Cost & Open source\\
Support & None \\
    \hline
    \hline
      \multicolumn{2}{|l|}{{\bf Empirical evidence about the tool}} \\
      \hline
  Effectiveness and Scalability & See~\cite{GoA_TSE12,FrA12b}. \\
    \hline
    \end{tabular}
%
\vspace{0.4cm}
	\caption{Description of \EVOSUITE}\label{tool-description}
\end{table}

\EVOSUITE applies a search-based approach, where a genetic algorithm
optimizes whole test suites towards a chosen target criterion (e.g.,
branch coverage by default). The advantage of this approach is that it
is not negatively affected by infeasible goals and its performance
does not depend on the order in which testing goals are considered, as
has been demonstrated in the past~\cite{GoA_TSE12}. To increase the
performance further, \EVOSUITE integrates dynamic symbolic execution
(DSE) in a hybrid approach~\cite{evoISSRE113}, where primitive values
(e.g., numbers or strings) are optimized using a constraint
solver. However, due to the experimental nature of this feature it was
not activated during the competition.

The search-based optimization in \EVOSUITE results in a set of
sequences of method calls that maximizes coverage, yet these sequences
are not yet usable as unit test cases --- at least not for human
consumption. In order to make it easier to understand and use the test
cases produced, \EVOSUITE applies a range of post-processing steps to
produce sets of small and concise unit tests. The final step of this
post-processing consists of adding test assertions, i.e., statements
that check the outcome of the test. As \EVOSUITE only requires the
bytecode as input and such bytecode often does not include formal specifications, 
the assertions
produced will reflect observed behavior, rather than the intended
behavior. Consequently, the test cases are intended either as
regression tests, or serve as starting point for a human tester, who
can manually revise the assertions in order to determine
failures~\cite{10.1109/TSE.2011.93}. However, \EVOSUITE is also able
to automatically detect certain classes of bugs which are independent
of a specification; for example, undeclared exceptions or violations
of assertions in the code~\cite{emse13_oracle}.

Table \ref{tool-description} describes \EVOSUITE in terms of the
template used in the unit testing tool competition.

\section{Configuration for the Competition Entry}

Even though several new features have been developed for \EVOSUITE
(e.g., DSE integration~\cite{evoISSRE113}) since the last competition,
we did not include any for the competition entry, as the risk of
reducing the score due to immature code would be too high. One notable
new feature we did include because it is now enabled by default is
support for Java Generics~\cite{evoGenerics13}. Besides this, the
version of \EVOSUITE used in the competition is largely the same as in
the first round in terms of features, yet has seen many revisions to
fix individual problems or bugs.

We used the same configuration as for the first unit testing
competition without any changes. This means that \EVOSUITE was
configured to optimize for weak mutation testing, with three minutes
time for the search per class. Minimization was deactivated to reduce
the test generation time, and \EVOSUITE was configured to include all
possible assertions in the tests (rather than the default of
minimizing the assertions using mutation
analysis~\cite{10.1109/TSE.2011.93}). For all other parameters,
\EVOSUITE was configured to its default parameter
settings~\cite{arcuri2013parameter}.

\section{Results and Problems}

%\resizebox{\textwidth}{!}{%
{\tiny
\ctable[nostar, pos = t!, doinside=\rowcolors{3}{white}{gray!25},
  label = table:results, caption = {\normalfont \EVOSUITE results on the benchmark classes}
]{lllrr@{\hfill}rr@{\hfill}rrr}{}{ %
%\scalebox{0.5}{
%\begin{table}[h!]
%\centering
%\begin{tabular}{lllrrrrr}
  \FL
{\bf No.} & 
{\bf Class} & 
{\bf Project} & 
{\bf LOC} & 
{\bf NBD} & 
\multicolumn{2}{c}{\bf Time (min)}
&
\multicolumn{3}{c}{\bf Coverage}
 \NN
& & & & & 
{\bf Gen} & 
{\bf Exec} & 
{\bf Instr.} & 
{\bf Branch } & 
{\bf Mutation}
\ML

%Cyclo  &  LOC  &  TLOC & TASS
1 &SearchException & Hibernate & 15 & 1 &                                                3.23    &   0.00    &   0.00      &      0.00       &     0.00  \NN                      
2 &Version & Hibernate & 12 & 1 &                                                        3.74    &   0.01    &   60.00     &      0.00       &     0.00  \NN
3 &BackendFactory & Hibernate & 72 & 2 &                                                 4.53    &   0.02    &   27.71     &      6.25       &     40.95 \NN
4 &FlushLuceneWork & Hibernate & 26 & 2 &                                                3.22    &   0.03    &   89.74     &      100.00     &     75.00 \NN
5 &OptimizeLuceneWork & Hibernate & 26 & 2 &                                             3.22    &   0.03    &   89.74     &      100.00     &     75.00 \NN
6 &LoggerFactory & Hibernate & 14 & 1 &                                                  7.75    &   0.01    &   17.41     &      0.00       &     0.00  \NN
7 &LoggerHelper & Hibernate & 17 & 1 &                                                   3.73    &   0.01    &   87.50     &      0.00       &     33.33 \NN
8 &OAuthConfig & Scribe                             & 63 & 3 &                           3.21    &   0.05    &   91.14     &      100.00     &     100.00\NN
9 &OAuthRequest & Scribe                            & 36 & 2 &                           3.15    &   0.03    &   100.00    &      100.00     &     80.00 \NN
10&ParameterList & Scribe                           & 95 & 3 &                           3.19    &   0.06    &   99.60     &      96.83      &     81.99 \NN
11&Request & Scribe                                 & 213 & 2 &                          3.19    &   0.11    &   64.45     &      40.91      &     37.21 \NN
12&Response & Scribe                                & 72 & 2 &                           3.14    &   0.01    &   1.77      &      0.00       &     0.00  \NN
13&Token & Scribe                                   & 64 & 2 &                           3.17    &   0.08    &   100.00    &      94.64      &     90.91 \NN
14&Verifier & Scribe                                & 15 & 1 &                           3.13    &   0.01    &   100.00    &      0.00       &     50.00 \NN
15&ExceptionDiagnosis & Twitter4j                   & 73 & 4 &                           3.27    &   0.07    &   98.30     &      91.27      &     60.00 \NN
16&GeoQuery & Twitter4j                             & 126 & 2 &                          3.30    &   0.18    &   100.00    &      95.83      &     81.86 \NN
17&OEmbedRequest & Twitter4j                        & 147 & 2 &                          3.30    &   0.17    &   95.47     &      88.36      &     57.14 \NN
18&Paging & Twitter4j                               & 171 & 3 &                          3.24    &   0.14    &   93.91     &      91.27      &     68.76 \NN
19&TwitterBaseImpl & Twitter4j                      & 328 & 5 &                          6.73    &   0.04    &   9.16      &      6.16       &     3.54  \NN
20&TwitterException & Twitter4j                     & 237 & 4 &                          3.40    &   0.24    &   78.15     &      70.12      &     17.56 \NN
21&TwitterImpl & Twitter4j                          & 1187 & 3 &                         2.75    &   0.06    &   1.11      &      3.90       &     0.36  \NN
22&AsyncHttpClient & Async Http Client                    & 296 & 5 &                    9.02    &   0.00    &   0.00      &      0.00       &     0.00  \NN
23&AsyncHttpClientConfig & Async Http Client              & 621 & 2 &                    8.71    &   0.11    &   39.76     &      27.62      &     32.34 \NN
24&FluentCaseInsensitiveStringsMap & Async Http Client    & 292 & 4 &                    3.35    &   0.24    &   74.62     &      67.25      &     68.69 \NN
25&FluentStringsMap & Async Http Client                   & 240 & 4 &                    3.31    &   0.24    &   72.77     &      67.11      &     65.95 \NN
26&Realm & Async Http Client                              & 481 & 3 &                    3.43    &   0.28    &   92.98     &      64.65      &     70.09 \NN
27&RequestBuilderBase & Async Http Client                 & 544 & 6 &                    8.59    &   0.09    &   23.76     &      21.31      &     16.83 \NN
28&SimpleAsyncHttpClient & Async Http Client              & 610 & 3 &                    2.70    &   0.00    &   0.00      &      0.00       &     0.00  \NN
29&AttributeHelper & GData Java Client              & 344 & 4 &                          3.45    &   0.22    &   85.90     &      80.49      &     59.07 \NN
30&DateTime & GData Java Client                     & 264 & 5 &                          3.30    &   0.19    &   78.97     &      67.55      &     56.59 \NN
31&Kind & GData Java Client                         & 189 & 5 &                          3.36    &   0.06    &   53.31     &      43.83      &     46.27 \NN
32&Link & GData Java Client                         & 190 & 4 &                          3.79    &   0.17    &   62.98     &      59.46      &     36.43 \NN
33&OtherContent & GData Java Client                 & 179 & 4 &                          4.37    &   0.09    &   46.85     &      37.01      &     36.07 \NN
34&OutOfLineContent & GData Java Client             & 102 & 4 &                          4.13    &   0.15    &   83.55     &      81.12      &     67.26 \NN
35&Source & GData Java Client                       & 324 & 4 &                          3.47    &   0.23    &   42.59     &      30.84      &     33.04 \NN
36&CharMatcher & Guava                              & 824 & 4 &                          6.96    &   0.07    &   70.86     &      65.00      &     47.73 \NN
37&Joiner & Guava                                   & 222 & 3 &                          3.30    &   0.09    &   84.40     &      90.06      &     77.20 \NN
38&Objects & Guava                                  & 130 & 4 &                          3.24    &   0.12    &   96.20     &      79.37      &     96.14 \NN
39&Predicates & Guava                               & 379 & 3 &                          3.31    &   0.13    &   36.99     &      19.35      &     22.63 \NN
40&SmallCharMatcher & Guava                         & 92 & 4 &                           3.22    &   0.02    &   55.77     &      30.77      &     26.79 \NN
41&Splitter & Guava                                 & 266 & 4 &                          3.24    &   0.11    &   93.74     &      87.91      &     82.89 \NN
42&Suppliers & Guava                                & 172 & 4 &                          3.18    &   0.04    &   30.03     &      21.43      &     27.60 \NN
43&CategoryDescendantsIterator & JWPL               & 103 & 4 &                          3.18    &   0.01    &   8.24      &      0.00       &     0.00  \NN
44&CycleHandler & JWPL                              & 71 & 4 &                           3.09    &   0.01    &   21.41     &      20.71      &     27.73 \NN
45&Page & JWPL                                      & 351 & 4 &                          2.81    &   0.01    &   0.64      &      2.00       &     1.90  \NN
46&PageIterator & JWPL                              & 182 & 7 &                          3.14    &   0.05    &   46.55     &      40.82      &     34.23 \NN
47&PageQueryIterable & JWPL                         & 131 & 3 &                          2.62    &   0.03    &   14.93     &      7.31       &     0.00  \NN
48&Title & JWPL                                     & 79 & 2 &                           3.16    &   0.03    &   76.01     &      76.79      &     92.86 \NN
49&WikipediaInfo & JWPL                             & 222 & 6 &                          3.19    &   0.07    &   10.78     &      10.29      &     12.58 \NN
50&AbstractLoader & eclipse-cs                      & 77 & 3 &                           3.30    &   0.01    &   77.00     &      50.00      &     18.57 \NN
51&AnnotationUtility & eclipse-cs                   & 78 & 4 &                           3.24    &   0.10    &   58.11     &      54.29      &     46.75 \NN
52&AutomaticBean & eclipse-cs                       & 178 & 4 &                          4.45    &   0.02    &   49.45     &      29.59      &     13.29 \NN
53&FileContents & eclipse-cs                        & 161 & 4 &                          3.35    &   0.10    &   59.57     &      53.30      &     50.29 \NN
54&FileText & eclipse-cs                            & 184 & 4 &                          3.43    &   0.09    &   48.53     &      45.60      &     55.93 \NN
55&ScopeUtils & eclipse-cs                          & 189 & 4 &                          6.15    &   0.04    &   48.73     &      33.29      &     10.07 \NN
56&Utils & eclipse-cs                               & 160 & 4 &                          3.49    &   0.13    &   55.75     &      78.02      &     65.31 \NN
57&AbstractInstance & JMLL                          & 136 & 2 &                          3.69    &   0.08    &   87.06     &      67.86      &     68.08 \NN
58&Complex & JMLL                                   & 53 & 1 &                           3.18    &   0.08    &   100.00    &      0.00       &     47.93 \NN
59&DefaultDataset & JMLL                            & 152 & 3 &                          3.30    &   0.10    &   95.04     &      97.14      &     60.60 \NN
60&DenseInstance & JMLL                             & 155 & 3 &                          4.07    &   0.15    &   98.84     &      98.66      &     76.73 \NN
61&Fold & JMLL                                      & 201 & 2 &                          3.26    &   0.16    &   87.56     &      82.86      &     80.36 \NN
62&SparseInstance & JMLL                            & 191 & 3 &                          3.32    &   0.16    &   98.17     &      87.50      &     72.90 \NN
63&ARFFHandler & JMLL                               & 51 & 6 &                           3.15    &   0.01    &   0.00      &      0.00       &     0.00  \LL
%\bottomrule
%\end{tabular}
%\end{table}
%\caption{The CUTs that constitute the benchmark}\label{benchmark-classes}
} }

Coverage results achieved by \EVOSUITE are listed in Table~\ref{table:results}. On the 63 classes of the benchmark used in the competition, \EVOSUITE
produced an average instruction coverage of 59.9\%, average branch
coverage of 48.63\%, and average mutation score of 43.8\%. These
results are in line with our expectations based on recent
experimentation~\cite{FrA12b}.

For each class it produced on average 12.3 test cases. For the entire
benchmark of 63 classes, \EVOSUITE took on average 4 hours for test
generation, which means that \EVOSUITE spent an additional 51 seconds
per class on the up-front analysis of the classpath as well as the
post-processing after the search.

In the following discussion, we
%As a detailed discussion of the results on all 63 classes is not
%possible due to space restrictions, we 
focus on some interesting cases where \EVOSUITE achieved no or very
little ($<2\%$) coverage or mutation score.

{\bf Trivial classes: } Class 1 ({\it SearchException}) is a trivial
class with only 15 lines of code, and it seems surprising that
\EVOSUITE achieved 0\% coverage here. The reason for this bad result
is that the class consists of four constructors that do nothing but
calling the constructor of the superclass, and as a result there are
no statements for which \EVOSUITE produced any mutants, and there are
no branching instructions. While the standard branch coverage
criterion in \EVOSUITE also enforces that each method is executed at
least once, the weak mutation testing criterion we used in the
competition did not do so at the time of the competition, and so
\EVOSUITE produced no tests.

{\bf Classpath dependent behavior: } Class 2 ({\it Version}) is
another trivial class, yet the reason for the bad result do not lie in
\EVOSUITE, but rather the frontend of \EVOSUITE we built to interface
with the competition infrastructure. When setting up the classpath for
\EVOSUITE, our competition frontend unnecessarily included the source
directory of the unit under test in the classpath. In the competition
setup there are compiled versions of the classes in the source
directory as well as a dedicated target path; unfortunately, they
differ: Method {\it getVersionString} returns ``[WORKING]'' in the
class in the source directory, whereas the deployed version of the
class is changed to return ``[0.4.4-SNAPSHOT]''. As \EVOSUITE's
assertions were expecting ``[WORKING]'', resulting tests failed and
were not considered for mutation analysis.

{\bf Nondeterministic code: } Class 30 ({\it DateTime}) makes use of
the current system time, such that automatically generated assertions
may refer to the time of test execution. If this happens, then the
tests will fail, and will not be considered for mutation
analysis. This is a known issue, and \EVOSUITE overcomes it by using
bytecode instrumentation that replaces nondeterministic
calls. However, as the PIT mutation testing tool used in the
competition is not able to handle JUnit tests with this kind of
instrumentation, we had to deactivate it. \EVOSUITE does compile and
execute tests as a last step to comment out any failing assertions;
yet in this case there were assertions dependent on the seconds of the
current time, and so this verification step was too quick to notice
the failing assertions.

{\bf Environmental dependencies: } One of the largest problems in unit
testing remains the handling of environmental dependencies. For
example, most classes in the JWPL project (43--49) depend on a valid
instance of a {\it Wikipedia} class, which in turn depends on a valid
{\it DatabaseConfiguration}. As another example, class 63
(ARFFHandler) consists of only one method (and one wrapper for that
method) that receives a file as parameter, and then tries to parse
this file.

%12. Response Scribe: 54 mutants, but must be some other problem.

{\bf Complex classes: } The benchmark included large classes, most
notably class 21 ({\it TwitterImpl}): This class has 1,187 lines of
code, and \EVOSUITE produced 2,453 mutants for it. That on its own
would not be a challenge for \EVOSUITE; however, test execution on
this class turns out to be very slow, and can lead to excessive memory
consumption. To prevent out of memory exceptions from occurring and
crashing \EVOSUITE, \EVOSUITE cancels test generation when the Java
garbage collector fails to free sufficient memory. This happened not
only in this class, but also several others (19, 23, 43, 44, 45, 47,
49). Running \EVOSUITE with more memory would have likely resulted in
higher coverage on these classes.

%22. AsyncHttpClient: Slow (few statements executed) and timeout -
%master killed client in most cases.

%28. SimpleAsyncHttpClient: Error during setup
%(java.lang.ExceptionInInitializerError during call tree
%initialisation).

%43: CategoryDescendantsIterator: Compile errors - complains that
%de.fau.cs.osr.utils is missing. The test does not actually include
%that, but the SUT! Is the classpath correct?

%44 CycleHandler - same problem

%45 Page - same problem

%46 PageIterator - same problem

%47 PageQueryIterable - same problem

%49 WikipediaInfo - same problem

%63 ARFFHandler: No performance problem, but EvoSuite can't produce
%tests, so probably some error in generating an object.

\section{Conclusions}

With an overall score of 205.26, \EVOSUITE achieved the highest score
of all tools in the competition. The score calculated for manual
testing is 210.45 --- a very close call. This means that \EVOSUITE is
achieving almost human-competitive results in terms of the
effectiveness of the resulting test suites. Potentially, just by
fixing some of the errors in \EVOSUITE or its competition frontend the
resulting score could be higher than 210, even without adding new
features. We are confident that some of the experimental features will
further increase this once the required level of robustness has been
achieved.

\section*{Acknowledgements}
This project has been funded by a Google
Focused Research Award on ``Test Amplification'' and the Norwegian
Research Council.

\bibliographystyle{splncs03}
\bibliography{../papers}

\end{document}

### 2015-02-18 papers/sbst13/paper_sbst13.tex
adding previous papers

%--------1---------2---------3---------4---------5---------6---------7
%
% Competition paper
% SBST 2013
% Page limit: 4 pages
%

%\documentclass[10pt, conference, compsocconf]{IEEEtran}
\documentclass[10pt,conference,compsocconf]{IEEEtran}

%\documentclass[times, 10pt,twocolumn]{article} 
%\usepackage{latex8}
%\usepackage{times}
\usepackage{amsfonts}
\usepackage[latin1]{inputenc}
\usepackage[english]{babel}
\usepackage{listings}
\usepackage{algorithmic}
\usepackage{float}
\usepackage{cite}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{subfigure}
\usepackage{hyperref}
\usepackage{color}
\usepackage[usenames,dvipsnames,table]{xcolor}
\usepackage{soul}
\usepackage{xspace}
\usepackage{boxedminipage}
\usepackage{alltt}
\usepackage{multirow}
\usepackage{paralist}
\usepackage{amsmath}

\floatstyle{ruled}
\newfloat{algorithm}{tbp}{loa}
\floatname{algorithm}{Algorithm}

\newtheorem{definition}{Definition}

 %krams hinter fontadjust ist neu
  \definecolor{lightgrey}{rgb}{0.90,0.90,0.90}
\lstset{escapeinside={(*}{*)}}
  \lstloadlanguages{java}
 \lstdefinelanguage{pseudocode}
  {morekeywords={if, else, initialize, return, for, each, in, global, new}
   }
  \lstset{
    tabsize=2,
    mathescape=true,
    escapeinside={(*}{*)},
    captionpos=t,
    framerule=0pt,
    backgroundcolor=\color{lightgrey},
    basicstyle=\footnotesize\ttfamily,
    keywordstyle=\footnotesize\bfseries,
    numbers=none,
    numberstyle=\tiny,
    numbersep=1pt,
    fontadjust,
    breaklines=true,
    breakatwhitespace=false
  }

\def\svn$I#1: #2 #3 #4 #5 #6 ${\def\svnrev{#3}\def\svndate{#4}\def\svndoc{#2}}
\svn$Id: icst11.tex 21983 2011-01-07 16:22:58Z fraser $

\hypersetup{
colorlinks=true,
urlcolor=rltblue,
linkcolor=rltred,
citecolor=rltgreen,
bookmarksnumbered=true,
pdftitle={EvoSuite at the SBST 2013 Tool Competition},
pdfauthor={Gordon Fraser and Andrea Arcuri},
pdfsubject={Test case generation},
pdfkeywords={Test case generation, unit testing, test
  oracles, assertions, search based testing}
}

\definecolor{rltred}{rgb}{0.5,0,0}
\definecolor{rltgreen}{rgb}{0,0.5,0}
\definecolor{rltblue}{rgb}{0,0,0.5}
\definecolor{ScarletRed}{rgb}{0.80,0.00,0.00}

% in draft mode we put \remarks into the margins and do other stuff
% set to \draftfalse for 
\newif\ifdraft
\draftfalse

\ifdraft
	\marginparwidth=1.3cm
	\marginparsep=5pt
	\newcommand\remark[1]{%
		\mymarginpar{\raggedright\hbadness=10000\tiny\it #1\par}}
\else
	\newcommand\remark[1]	{}
\fi

\ifdraft
	\overfullrule3pt
\fi

% We use \FIXME for located problems (``defect'')
\newcommand{\FIXME}[1]{\remark{FIXME: #1}}
\newcommand\parremark[1]	{\par\textbf{REMARK:} #1\par}

\newcommand{\gordon}[1]{\textcolor{blue}{\sf\small\textbf{Gordon:} #1}}
\newcommand{\andrea}[1]{\textcolor{ScarletRed}{\sf\small\textbf{Andrea:} #1}}

% \mathid is used to denote identifiers and slots in formulas
\newcommand{\mathid}[1]{\text{\rmfamily\textit{#1}}}

% But usually, we shall use \|name| instead.
\def\|#1|{\mathid{#1}}

% \codeid is used to denote computer code identifiers
\newcommand{\codeid}[1]{\texttt{#1}}

% But usually, we shall use \<name> instead.
\def\<#1>{\codeid{#1}}

% Our results
\newenvironment{result}%
{\smallskip
\noindent
\let\emph=\textbf
\begin{boxedminipage}{\columnwidth}\begin{center}\em}%
{\end{center}\end{boxedminipage}%
\smallskip
}

\newcommand{\JodaTime}{Joda-Time\xspace}  % That's how they write themselves -- AZ

\newcommand{\EVOSUITE}{{\sc EvoSuite}\xspace}
\newcommand{\MUTEST}{{\sc $\mu$Test}\xspace}
\newcommand{\CS}{{\sc SF100}\xspace}

% TODO marker
\newcommand{\TODO}[1]{\sethlcolor{yellow}\textbf{\textcolor{ScarletRed}{\hl{TODO: #1}}}\xspace}

\DeclareMathSymbol{,}{\mathpunct}{letters}{"3B}
\DeclareMathSymbol{,}{\mathord}{letters}{"3B}
\DeclareMathSymbol{\decimal}{\mathord}{letters}{"3A}
%%%"

%\documentstyle[times,art10,twocolumn,latex8]{article}

%------------------------------------------------------------------------- 
% take the % away on next line to produce the final camera-ready version 
%\pagestyle{empty}

%------------------------------------------------------------------------- 
\begin{document}

%\title{Unit Testing Tool competition: Results for EvoSuite}
\title{EvoSuite at the SBST 2013 Tool Competition}

\author{
\IEEEauthorblockN{Gordon Fraser}
\IEEEauthorblockA{University of Sheffield\\
Sheffield, UK\\
gordon.fraser@sheffield.ac.uk}\\
\and
\IEEEauthorblockN{Andrea Arcuri}
\IEEEauthorblockA{Certus Software V\&V Center at Simula Research Laboratory\\
P.O. Box 134, 1325 Lysaker, Norway\\
arcuri@simula.no}
%\and
%\IEEEauthorblockN{Jeremias R\"{o}{\ss}ler}
%\IEEEauthorblockA{Saarland University -- Computer Science\\
%Saarbr\"ucken, Germany\\
%roessler@cs.uni-saarland.de}
}

\maketitle
%\thispagestyle{empty}

\begin{abstract}
  \EVOSUITE is a mature research prototype that automatically
  generates unit tests for Java code.  This paper summarizes the
  results and experiences in participating at the unit testing
  competition held at SBST 2013, where \EVOSUITE ranked first with a
  score of $156.95$.
\end{abstract}

\begin{IEEEkeywords}
  test case generation; search-based testing; testing classes;
  search-based software engineering
\end{IEEEkeywords}

%------------------------------------------------------------------------- 
\section{Introduction}

This paper describes the results of applying the \EVOSUITE test
generation tool~\cite{FrA11c} to the benchmark used in the tool
competition at the International Workshop on Search-Based Software
Testing (SBST) 2013.  Details on the competition and the benchmark can
be found in~\cite{sbst2013}. In this competition, \EVOSUITE ranked
first with a score of $156.95$.

%------------------------------------------------------------------------- 
\section{About \EVOSUITE}

\begin{table}[!h]
\renewcommand{\arraystretch}{1.3}
\caption{Classification of the \EVOSUITE unit test generation tool.}\label{tool-description}
\begin{tabular}{|l|p{5cm}|}
  \hline
  \multicolumn{2}{|l|}{Prerequisites} \\
  \hline
  Static or dynamic &  Dynamic testing at the Java class level\\
  Software Type &  Java classes\\
  Lifecycle phase&  Unit testing for Java programs\\
  Environment&  All Java development environments \\
  Knowledge required & JUnit unit testing for Java\\
  Experience required &  Basic unit testing knowledge\\
 \hline
  \multicolumn{2}{|l|}{Input and Output of the tool} \\
  \hline
 Input & Bytecode of the target class and dependencies \\
\hline
Output&  JUnit test cases (version 3 or 4)\\

  \hline
  \multicolumn{2}{|l|}{Operation} \\
  \hline
  Interaction &  Through the command line\\
  User guidance &  manual verification of assertions for functional faults\\
  Source of information &  http://www.evosuite.org \\
  Maturity&  Mature research prototype, under development\\
  Technology behind the tool & Search-based testing / whole test suite generation\\
\hline
  \multicolumn{2}{|l|}{Obtaining the tool and information} \\
  \hline
License & GNU General Public License V3\\
Cost & Open source\\
Support & None \\
\hline
\hline
  \multicolumn{2}{|l|}{Does there exist empirical evidence about} \\
  \hline
  Effectiveness and Scalability & See~\cite{GoA_TSE12,FrA12b}. \\
%Completeness & \\
%Effectiveness & \\
%Efficiency & \\
%Defect types & \\
%Scalability & \\
%Comprehensibility & \\
%Learnability & \\
%Subjective satisfaction & \\
%Other & \\
\hline
\end{tabular}\vspace{-1em}
\end{table}

%------------------------------------------------------------------------- 
\subsection{Whole Test Suite Generation}

\EVOSUITE automatically generates JUnit test cases for a given
class. It requires only the bytecode of the class under test and its
dependencies as input. \EVOSUITE is based on search-based testing, and
uses a Genetic Algorithm (GA) to evolve a population of candidate test
suites with respect to a choice of code coverage criteria.

This \emph{whole test suite generation} approach~\cite{GoA_TSE12} is a
key novelty of \EVOSUITE compared to other tools, and represents an
effective counter-measure to the problem of infeasible coverage
goals. When targeting individual goals one at a time, any resources
spent on an infeasible goal are per definition wasted, whereas the
search in \EVOSUITE is not adversely affected by the number of
infeasible goals~\cite{GoA_TSE12}. Our past experiments have shown
that this approach leads to significantly higher coverage than
targeting individual goals.

The search population in \EVOSUITE's GA is initialized with small
random test suites, which are successively evolved using crossover and
mutation. The number of tests and their length is variable, such that
the evolution will automatically lead to a suitable size of test suite
for the criterion at hand. This variability in length requires
bloat-control techniques to counter the problem of population
bloat~\cite{GoA11}. \EVOSUITE incorporates seeding
strategies~\cite{FrA12a} that boost coverage, even in the case of string
dependencies.

The default coverage criterion used by \EVOSUITE is branch coverage,
but there is also rudimentary support for dataflow and mutation
testing, and other coverage criteria could be integrated by encoding
them as fitness functions.

Before presenting test cases to the user, \EVOSUITE applies a range of
post-processing steps. Test cases are minimized, constants are
inlined, individual values can be minimized, and assertions can be
added to the test cases.

\subsection{Efficient Assertion Generation}

A key challenge in automated white-box testing is given by the human
oracle problem: Unless a test case reveals a generic fault such as an
undeclared exception, a tester manually needs to assess the test
outcome to decide whether a fault has been found. In unit testing of
object-oriented code, the oracle problem amounts to adding test
assertions to the unit tests. Because any given JUnit test case offers
a potentially large choice of assertions, \EVOSUITE determines which
of all the possible assertions for a given test case are good at
detecting faults. This is based on mutation
analysis~\cite{10.1109/TSE.2011.93}: \EVOSUITE first determines which
assertions can reveal mutations of the bytecode, and then uses a
heuristic to calculate a minimal set of assertions to detect all
mutants that the test can reveal. However, these assertions reflect
the currently implemented behaviour. This means that they can
immediately be used for regression testing, but to determine whether
there is a fault in the current version of the CUT the developer needs
to inspect and verify each of these assertions.

\subsection{Safe Test Execution}

To evaluate the fitness of a test suite, the GA in \EVOSUITE executes
all tests using instrumentation that collects the necessary data. The
test execution may have undesired side-effects, for example if the
class under test or the sequence of calls \EVOSUITE generated to
satisfy the dependencies access the filesystem. For example, when
running experiments on the 100 randomly selected projects of the \CS
corpus of classes~\cite{FrA12b} we observed creation of files with
random filenames and even deletion of entire directories. To prevent
such undesired actions, \EVOSUITE uses a custom security manager to
restrict test execution to a sandbox environment. Furthermore, to
restrict execution of GUI related code that may cause windows and
other GUI elements showing up during the search, \EVOSUITE is run in
\emph{headless} mode, such that no GUI elements will be shown.

%------------------------------------------------------------------------- 
\section{Configuration for the Competition Entry}

\EVOSUITE supports several coverage criteria, and many other
configuration options. Most of these configuration options are set to
reasonable defaults based on our studies on parameter
tuning~\cite{ArF11}, and we argue that in most cases a user should not
be required to change low-level parameters that would require an
understanding of the underlying techniques. However, it is reasonable
to assume that a user will know how long he or she is prepared to wait
for the results, and which test criterion the generated test cases
should satisfy. As branch coverage may be a weak criterion, in
particular if classes consist of many small methods with trivial
control flow, we chose \emph{weak mutation testing} as target
criterion. \EVOSUITE uses bytecode instrumentation to create a
meta-mutant for the class under test, and can then activate individual
mutants using a parameter. A mutant is weakly killed if it leads to an
immediate state change. Furthermore, we arbitrarily chose three
minutes as timeout for the search. This is based on our past
experience, where 10 minutes for a class in all but very complex
examples is more than enough time, whereas two minutes for non-trivial
classes with many mutants may easily be insufficient time. Given more
than three minutes would likely have resulted in higher coverage.

Considering that the score calculation in the SBST competition does
not directly include the test suite size or length (only in terms of
execution time), we deactivated the test minimization in \EVOSUITE, as
it will take significantly more time to minimize a test suite than can
be gained during execution. Furthermore, for the same reason we
deactivated assertion filtering, such that the resulting test cases
include all possible assertions.

%------------------------------------------------------------------------- 
\section{Benchmark results}

\begin{table*}[t]
  \centering
  \caption{\label{table:results}Detailed results of \EVOSUITE on the SBST benchmark classes.}
  \scriptsize
  \begin{tabular}{l rrrrrr} \toprule
Class & Generation Time & Execution Time  & Tests & Line Coverage & Branch
Coverage & Mutation Score \\ 
%Class & \multicolumn{2}{c}{ Time} & Tests & Line Coverage & Branch
%Coverage & Mutation Score \\ 
%& Generation & Execution & & & & \\
\midrule

\input{results.tex}
\midrule
Average & 186.3 & 0.05 & 9.06 & 0.61 & 0.58 & 0.13\\
\bottomrule
  \end{tabular}
\end{table*}

The results of \EVOSUITE on the benchmark classes are listed in
Table~\ref{table:results}. On average, \EVOSUITE achieved 61.4\% line
coverage, 57.6\% branch coverage\footnote{Using Cobertura's definition
  of branch coverage, which only counts conditional statements, not
  edges in the CFG.}, and 13.3\% mutation score. On average, \EVOSUITE
produced 9 tests per class, and it took an average of 186 per class to
do so (with \EVOSUITE configured to 3 minutes per class).

While the results on code coverage are in line with our expectations
from past experiments (e.g.,~\cite{FrA12b}), the mutation scores are
surprisingly low. A closer inspection of this unexpected result
revealed several issues in assertion generation, which are well known
in principle. The common problem is these cases is that the assertions
produced by \EVOSUITE do not hold upon test re-execution, and tests
with failing assertions are excluded from mutation analysis.

\subsection{Low Mutation Scores}

The first issue becomes apparent when considering the overall low
mutation scores on Joda Time classes, which are contrary to previous
results (e.g., \cite{10.1109/TSE.2011.93}). One reason for this is
that assertions in Joda Time tend to reflect the time during test
generation. For example, an instance of a time object based on the
current system time will include this time in its \<toString>
representation, and any successive test runs will fail, unless they
happen to be executed at the same time. \EVOSUITE in theory overcomes
this issue by instrumenting the bytecode such that all calls to
\<System.currentTimeMillis> and related methods are replaced with
custom calls that allow for deterministic test execution. However, to
enable this during JUnit test execution requires bytecode
instrumentation also at runtime. As this was not supported by the SBST
contest infrastructure, we deactivated this feature in \EVOSUITE.

The second issue we observed is related to static initializers, and is
an issue that is long known in test
generation~\cite{Csallner2004}. To make sure that test cases
are independent, all static initializers would need to be reset before
every single test execution. As this poses a significant overhead,
\EVOSUITE creates executable copies of the static initializer for each
class, removing assignments of \<final> fields. However, we
deactivated this feature in \EVOSUITE for the competition for
performance reasons, which possibly led to higher coverage, but
apparently to lower mutation scores.

\subsection{Classes with Low Coverage}

Besides the generally low mutation scores, we see nine classes on
which \EVOSUITE achieved 0\% coverage in
Table~\ref{table:results}. The classes {\it XlsSheetIterator} and {\it
  XlsxSheetIterator} both take a {\it URL} as input, which \EVOSUITE
produced using calls like {\it
  ClassLoader.getSystemResource("")}. However, the resulting URL
encodes the current directory during test generation and results in
assertions like
\begin{lstlisting}
assertEquals("/home/evosuite/", uRL0.getPath());
\end{lstlisting}
These assertions fail when executed during analysis in a different
directory, and consequently all tests for these classes fail even
before an instance of the target class has been produced, thus leading
to 0\% coverage. This problem would not have occurred if we had not
deactivated assertion minimization -- the problematic assertions are
unrelated to the class under test, and would have immediately been removed in normal operation.

The classes {\it net.sourceforge.barbecue.Barcode} and {\it
  LinearBarcode} are both GUI components extending {\it
  java.awt.Component} and cannot be initialised in \EVOSUITE in
headless mode and with activated sandbox.

{\it org.apache.commons.lang3.BooleanUtils} revealed a bug in
\EVOSUITE related to multi-dimensional arrays, which unfortunately led
to \EVOSUITE crashing on this class in all runs, even though the class
itself would be easily covered by \EVOSUITE. Similarly, the problem on
{\it org.joda.time.DurationField} is related to a bug in \EVOSUITE in
how it handles test generation for abstract classes.

{\it org.joda.time.field.MillisDurationField} is a tricky case: The
class has only a private constructor and thus cannot be constructed by
\EVOSUITE directly. There is one public static instance of the class,
but it is declared as its supertype:
\begin{lstlisting}
public static final DurationField INSTANCE = new MillisDurationField();
\end{lstlisting}
If \EVOSUITE would be left running long enough, then eventually it
would also try and assign this {\it INSTANCE} object, discovering that
it actually is a {\it MillisDurationField} instance. However, this did
not happen in the three minutes given for the competition.

Finally, the classes {\it BuddhistChronology}, {\it
  GregorianChronology}, and {\it DateTimeFormatterBuilder} are working
fine in our own experiments, so the reason for the 0\% coverage in the
competition is currently not clear to us; possibly this is related to
compile errors or failures in the produced JUnit tests. A further
possible contributing factor is that tests requiring the \EVOSUITE
security manager (e.g., when trying to access a file), then the
resulting JUnit test case spawns a new thread to execute the code
using the \EVOSUITE security manager. As this construct is not
supported by Javalanche, we automatically removed all such tests, thus
potentially reducing the coverage.

We also note that {\it org.joda.time.Chronology} achieves low coverage
(only 10.5\% line coverage). This is an interesting case, as much of
this class is contained in methods tagged as deprecated. By default,
\EVOSUITE does not attempt to cover deprecated code, although
deprecated code seems to be considered for coverage and mutation
analysis. However, \EVOSUITE can be configured to also cover
deprecated code.

%------------------------------------------------------------------------- 
\section{Conclusions}

The road to practically usable unit test generators is long,
and we are by far not there yet. The SBST competition has provided an
invaluable incentive to work on the robustness of \EVOSUITE, which in
writing research papers is usually not rewarded. The participation in
this competition has brought \EVOSUITE a big step closer to being
useful in practice, and it has helped us to identify areas where
future work is necessary to improve \EVOSUITE further.

To learn more about \EVOSUITE, visit our Web site:
\begin{center}
%\url{http://evosuite.org/}
\texttt{http://www.evosuite.org}
\end{center}

%------------------------------------------------------------------------- 
\noindent
\textbf{Acknowledgments.}  This project has been funded a Google
Focused Research Award on ``Test Amplification''. Andrea Arcuri is
funded by the Norwegian Research Council.

%------------------------------------------------------------------------- 
%\def\IEEEbibitemsep{5pt plus 1pt}
\def\IEEEbibitemsep{6pt}

\bibliographystyle{IEEEtranS}
\bibliography{../papers}

\end{document}

### 2015-02-18 papers/sbst15/paper_sbst15.tex
working on paper for SBST'15, based on SBST'13

--- 2015-02-18 papers/sbst13/paper_sbst13.tex
@@
   }
-
-\def\svn$I#1: #2 #3 #4 #5 #6 ${\def\svnrev{#3}\def\svndate{#4}\def\svndoc{#2}}
-\svn$Id: icst11.tex 21983 2011-01-07 16:22:58Z fraser $
 
@@
 %\title{Unit Testing Tool competition: Results for EvoSuite}
-\title{EvoSuite at the SBST 2013 Tool Competition}
+\title{EvoSuite at the SBST 2015 Tool Competition}
 
@@
 \IEEEauthorblockA{University of Sheffield\\
-Sheffield, UK\\
-gordon.fraser@sheffield.ac.uk}\\
+Sheffield, UK}\\
+%gordon.fraser@sheffield.ac.uk}\\
 \and
 \IEEEauthorblockN{Andrea Arcuri}
-\IEEEauthorblockA{Certus Software V\&V Center at Simula Research Laboratory\\
-P.O. Box 134, 1325 Lysaker, Norway\\
-arcuri@simula.no}
+\IEEEauthorblockA{Scienta, Norway\\
+and University of Luxembourg}\\
+%arcuri@simula.no}
 %\and
@@
 \begin{abstract}
-  \EVOSUITE is a mature research prototype that automatically
-  generates unit tests for Java code.  This paper summarizes the
-  results and experiences in participating at the unit testing
-  competition held at SBST 2013, where \EVOSUITE ranked first with a
-  score of $156.95$.
+  \EVOSUITE is a mature research prototype that automatically generates unit tests for Java code. 
+  This paper summarizes the results and experiences in participating at the third unit testing competition held at SBST 2015,
+  where \EVOSUITE ranked second with a $190.6$ score.
 \end{abstract}
@@
 competition at the International Workshop on Search-Based Software
-Testing (SBST) 2013.  Details on the competition and the benchmark can
-be found in~\cite{sbst2013}. In this competition, \EVOSUITE ranked
-first with a score of $156.95$.
+Testing (SBST) 2015.  Details on the competition and the benchmark can
+be found in~\cite{sbst2015}. In this competition, \EVOSUITE ranked
+second with a score of $190.6$.
 

### 2015-02-19 papers/sbst15/paper_sbst15.tex
adding result table

@@
 %------------------------------------------------------------------------- 
-\subsection{Whole Test Suite Generation}
-
-\EVOSUITE automatically generates JUnit test cases for a given
-class. It requires only the bytecode of the class under test and its
-dependencies as input. \EVOSUITE is based on search-based testing, and
-uses a Genetic Algorithm (GA) to evolve a population of candidate test
-suites with respect to a choice of code coverage criteria.
-
-This \emph{whole test suite generation} approach~\cite{GoA_TSE12} is a
-key novelty of \EVOSUITE compared to other tools, and represents an
-effective counter-measure to the problem of infeasible coverage
-goals. When targeting individual goals one at a time, any resources
-spent on an infeasible goal are per definition wasted, whereas the
-search in \EVOSUITE is not adversely affected by the number of
-infeasible goals~\cite{GoA_TSE12}. Our past experiments have shown
-that this approach leads to significantly higher coverage than
-targeting individual goals.
-
-The search population in \EVOSUITE's GA is initialized with small
-random test suites, which are successively evolved using crossover and
-mutation. The number of tests and their length is variable, such that
-the evolution will automatically lead to a suitable size of test suite
-for the criterion at hand. This variability in length requires
-bloat-control techniques to counter the problem of population
-bloat~\cite{GoA11}. \EVOSUITE incorporates seeding
-strategies~\cite{FrA12a} that boost coverage, even in the case of string
-dependencies.
-
-The default coverage criterion used by \EVOSUITE is branch coverage,
-but there is also rudimentary support for dataflow and mutation
-testing, and other coverage criteria could be integrated by encoding
-them as fitness functions.
-
-Before presenting test cases to the user, \EVOSUITE applies a range of
-post-processing steps. Test cases are minimized, constants are
-inlined, individual values can be minimized, and assertions can be
-added to the test cases.
-
-\subsection{Efficient Assertion Generation}
-
-A key challenge in automated white-box testing is given by the human
-oracle problem: Unless a test case reveals a generic fault such as an
-undeclared exception, a tester manually needs to assess the test
-outcome to decide whether a fault has been found. In unit testing of
-object-oriented code, the oracle problem amounts to adding test
-assertions to the unit tests. Because any given JUnit test case offers
-a potentially large choice of assertions, \EVOSUITE determines which
-of all the possible assertions for a given test case are good at
-detecting faults. This is based on mutation
-analysis~\cite{10.1109/TSE.2011.93}: \EVOSUITE first determines which
-assertions can reveal mutations of the bytecode, and then uses a
-heuristic to calculate a minimal set of assertions to detect all
-mutants that the test can reveal. However, these assertions reflect
-the currently implemented behaviour. This means that they can
-immediately be used for regression testing, but to determine whether
-there is a fault in the current version of the CUT the developer needs
-to inspect and verify each of these assertions.
-
-\subsection{Safe Test Execution}
-
-To evaluate the fitness of a test suite, the GA in \EVOSUITE executes
-all tests using instrumentation that collects the necessary data. The
-test execution may have undesired side-effects, for example if the
-class under test or the sequence of calls \EVOSUITE generated to
-satisfy the dependencies access the filesystem. For example, when
-running experiments on the 100 randomly selected projects of the \CS
-corpus of classes~\cite{FrA12b} we observed creation of files with
-random filenames and even deletion of entire directories. To prevent
-such undesired actions, \EVOSUITE uses a custom security manager to
-restrict test execution to a sandbox environment. Furthermore, to
-restrict execution of GUI related code that may cause windows and
-other GUI elements showing up during the search, \EVOSUITE is run in
-\emph{headless} mode, such that no GUI elements will be shown.
-
-%------------------------------------------------------------------------- 
-\section{Configuration for the Competition Entry}
-
-\EVOSUITE supports several coverage criteria, and many other
-configuration options. Most of these configuration options are set to
-reasonable defaults based on our studies on parameter
-tuning~\cite{ArF11}, and we argue that in most cases a user should not
-be required to change low-level parameters that would require an
-understanding of the underlying techniques. However, it is reasonable
-to assume that a user will know how long he or she is prepared to wait
-for the results, and which test criterion the generated test cases
-should satisfy. As branch coverage may be a weak criterion, in
-particular if classes consist of many small methods with trivial
-control flow, we chose \emph{weak mutation testing} as target
-criterion. \EVOSUITE uses bytecode instrumentation to create a
-meta-mutant for the class under test, and can then activate individual
-mutants using a parameter. A mutant is weakly killed if it leads to an
-immediate state change. Furthermore, we arbitrarily chose three
-minutes as timeout for the search. This is based on our past
-experience, where 10 minutes for a class in all but very complex
-examples is more than enough time, whereas two minutes for non-trivial
-classes with many mutants may easily be insufficient time. Given more
-than three minutes would likely have resulted in higher coverage.
-
-Considering that the score calculation in the SBST competition does
-not directly include the test suite size or length (only in terms of
-execution time), we deactivated the test minimization in \EVOSUITE, as
-it will take significantly more time to minimize a test suite than can
-be gained during execution. Furthermore, for the same reason we
-deactivated assertion filtering, such that the resulting test cases
-include all possible assertions.
-
-%------------------------------------------------------------------------- 
 \section{Benchmark results}
@@
   \begin{tabular}{l rrrrrr} \toprule
-Class & Generation Time & Execution Time  & Tests & Line Coverage & Branch
-Coverage & Mutation Score \\ 
+Class &  JUnit Files &   Generation Time & Execution Time   & \% Line Coverage & \% Branch Coverage & \% Mutation Score \\  
+% Class & Generation Time & Execution Time  & Tests & Line Coverage & Branch Coverage & Mutation Score \\ 
 %Class & \multicolumn{2}{c}{ Time} & Tests & Line Coverage & Branch
@@
 \midrule
-
 \input{results.tex}
 \midrule
-Average & 186.3 & 0.05 & 9.06 & 0.61 & 0.58 & 0.13\\
+Average & & 371.58 & 2.10 & 55.36 & 47.19 & 41.02\\
 \bottomrule
@@
 
+%average per class generation time:                 371.581857 seconds
+%average per class execution time:                  2.103966 seconds
+%average per class instruction coverage:            54.495767 %
+%average per class line coverage:                   55.368111 %
+%average per class branch coverage:                 47.192896 %
+%average per class method coverage:                 59.628209 %
+%average per class mutation coverage:               41.024248 %
+
 The results of \EVOSUITE on the benchmark classes are listed in
-Table~\ref{table:results}. On average, \EVOSUITE achieved 61.4\% line
-coverage, 57.6\% branch coverage\footnote{Using Cobertura's definition
+Table~\ref{table:results}. On average, \EVOSUITE achieved TODO line
+coverage,TODO branch coverage\footnote{Using Cobertura's definition
   of branch coverage, which only counts conditional statements, not
-  edges in the CFG.}, and 13.3\% mutation score. On average, \EVOSUITE
-produced 9 tests per class, and it took an average of 186 per class to
+  edges in the CFG.}, and TODO mutation score. On average, \EVOSUITE
+produced TODO tests per class, and it took an average of TODO per class to
 do so (with \EVOSUITE configured to 3 minutes per class).
-
-While the results on code coverage are in line with our expectations
-from past experiments (e.g.,~\cite{FrA12b}), the mutation scores are
-surprisingly low. A closer inspection of this unexpected result
-revealed several issues in assertion generation, which are well known
-in principle. The common problem is these cases is that the assertions
-produced by \EVOSUITE do not hold upon test re-execution, and tests
-with failing assertions are excluded from mutation analysis.
-
-\subsection{Low Mutation Scores}
-
-The first issue becomes apparent when considering the overall low
-mutation scores on Joda Time classes, which are contrary to previous
-results (e.g., \cite{10.1109/TSE.2011.93}). One reason for this is
-that assertions in Joda Time tend to reflect the time during test
-generation. For example, an instance of a time object based on the
-current system time will include this time in its \<toString>
-representation, and any successive test runs will fail, unless they
-happen to be executed at the same time. \EVOSUITE in theory overcomes
-this issue by instrumenting the bytecode such that all calls to
-\<System.currentTimeMillis> and related methods are replaced with
-custom calls that allow for deterministic test execution. However, to
-enable this during JUnit test execution requires bytecode
-instrumentation also at runtime. As this was not supported by the SBST
-contest infrastructure, we deactivated this feature in \EVOSUITE.
-
-The second issue we observed is related to static initializers, and is
-an issue that is long known in test
-generation~\cite{Csallner2004}. To make sure that test cases
-are independent, all static initializers would need to be reset before
-every single test execution. As this poses a significant overhead,
-\EVOSUITE creates executable copies of the static initializer for each
-class, removing assignments of \<final> fields. However, we
-deactivated this feature in \EVOSUITE for the competition for
-performance reasons, which possibly led to higher coverage, but
-apparently to lower mutation scores.
 
@@
 
-Besides the generally low mutation scores, we see nine classes on
-which \EVOSUITE achieved 0\% coverage in
-Table~\ref{table:results}. The classes {\it XlsSheetIterator} and {\it
-  XlsxSheetIterator} both take a {\it URL} as input, which \EVOSUITE
-produced using calls like {\it
-  ClassLoader.getSystemResource("")}. However, the resulting URL
-encodes the current directory during test generation and results in
-assertions like
-\begin{lstlisting}
-assertEquals("/home/evosuite/", uRL0.getPath());
-\end{lstlisting}
-These assertions fail when executed during analysis in a different
-directory, and consequently all tests for these classes fail even
-before an instance of the target class has been produced, thus leading
-to 0\% coverage. This problem would not have occurred if we had not
-deactivated assertion minimization -- the problematic assertions are
-unrelated to the class under test, and would have immediately been removed in normal operation.
-
-The classes {\it net.sourceforge.barbecue.Barcode} and {\it
-  LinearBarcode} are both GUI components extending {\it
-  java.awt.Component} and cannot be initialised in \EVOSUITE in
-headless mode and with activated sandbox.
-
-{\it org.apache.commons.lang3.BooleanUtils} revealed a bug in
-\EVOSUITE related to multi-dimensional arrays, which unfortunately led
-to \EVOSUITE crashing on this class in all runs, even though the class
-itself would be easily covered by \EVOSUITE. Similarly, the problem on
-{\it org.joda.time.DurationField} is related to a bug in \EVOSUITE in
-how it handles test generation for abstract classes.
-
-{\it org.joda.time.field.MillisDurationField} is a tricky case: The
-class has only a private constructor and thus cannot be constructed by
-\EVOSUITE directly. There is one public static instance of the class,
-but it is declared as its supertype:
-\begin{lstlisting}
-public static final DurationField INSTANCE = new MillisDurationField();
-\end{lstlisting}
-If \EVOSUITE would be left running long enough, then eventually it
-would also try and assign this {\it INSTANCE} object, discovering that
-it actually is a {\it MillisDurationField} instance. However, this did
-not happen in the three minutes given for the competition.
-
-Finally, the classes {\it BuddhistChronology}, {\it
-  GregorianChronology}, and {\it DateTimeFormatterBuilder} are working
-fine in our own experiments, so the reason for the 0\% coverage in the
-competition is currently not clear to us; possibly this is related to
-compile errors or failures in the produced JUnit tests. A further
-possible contributing factor is that tests requiring the \EVOSUITE
-security manager (e.g., when trying to access a file), then the
-resulting JUnit test case spawns a new thread to execute the code
-using the \EVOSUITE security manager. As this construct is not
-supported by Javalanche, we automatically removed all such tests, thus
-potentially reducing the coverage.
-
-We also note that {\it org.joda.time.Chronology} achieves low coverage
-(only 10.5\% line coverage). This is an interesting case, as much of
-this class is contained in methods tagged as deprecated. By default,
-\EVOSUITE does not attempt to cover deprecated code, although
-deprecated code seems to be considered for coverage and mutation
-analysis. However, \EVOSUITE can be configured to also cover
-deprecated code.
-
 %------------------------------------------------------------------------- 
 \section{Conclusions}
-
-The road to practically usable unit test generators is long,
-and we are by far not there yet. The SBST competition has provided an
-invaluable incentive to work on the robustness of \EVOSUITE, which in
-writing research papers is usually not rewarded. The participation in
-this competition has brought \EVOSUITE a big step closer to being
-useful in practice, and it has helped us to identify areas where
-future work is necessary to improve \EVOSUITE further.
 
@@
 %-------------------------------------------------------------------------
-\noindent
-\textbf{Acknowledgments.}  This project has been funded a Google
-Focused Research Award on ``Test Amplification''. Andrea Arcuri is
-funded by the Norwegian Research Council.
+
+%\noindent
+%\textbf{Acknowledgments.}
 
@@
 \bibliographystyle{IEEEtranS}
-\bibliography{../papers}
+\bibliography{papers}
 

### 2015-02-19 papers/sbst15/results.tex
adding result table

com.google.gdata.data.AttributeHelper                     &         1.00    &   9.94    &   0.03    &   92.56      &     92.89      &     62.50 \\
com.google.gdata.data.DateTime                            &         1.00    &   3.62    &   0.02    &   83.31      &     71.67      &     86.25 \\        
com.google.gdata.data.Kind                                &         1.00    &   4.03    &   0.04    &   57.07      &     48.86      &     46.74  \\         
com.google.gdata.data.Link                                &         1.00    &   11.17   &   0.08    &   74.94      &     72.75      &     63.06  \\        
com.google.gdata.data.OtherContent                        &         1.00    &   3.60    &   0.04    &   56.46      &     49.24      &     64.58  \\          
com.google.gdata.data.OutOfLineContent                    &         1.00    &   8.96    &   0.04    &   89.75      &     85.12      &     29.17  \\          
com.google.gdata.data.Source                              &         1.00    &   10.43   &   0.05    &   64.37      &     63.07      &     16.23  \\          
net.sf.javaml.core.AbstractInstance                       &         1.00    &   3.31    &   0.02    &   13.28      &     5.36       &     0.00  \\           
net.sf.javaml.core.Complex                                &         1.00    &   0.28    &   0.02    &   100.00     &     0.00       &     100.00   \\        
net.sf.javaml.core.DefaultDataset                         &         1.00    &   3.87    &   0.02    &   95.31      &     97.50      &     57.80   \\         
net.sf.javaml.core.DenseInstance                          &         1.00    &   3.92    &   0.02    &   98.87      &     100.00     &     100.00   \\        
net.sf.javaml.core.Fold                                   &         1.00    &   4.74    &   0.02    &   91.44      &     96.67      &     79.17   \\         
net.sf.javaml.core.SparseInstance                         &         1.00    &   3.06    &   0.02    &   98.37      &     87.50      &     97.06   \\         
net.sf.javaml.tools.data.ARFFHandler                      &         1.00    &   2.47    &   0.02    &   75.42      &     70.83      &     48.15    \\        
twitter4j.ExceptionDiagnosis                              &         1.00    &   3.81    &   0.01    &   0.00       &     0.00       &     0.00    \\         
twitter4j.GeoQuery                                        &         1.00    &   3.80    &   0.01    &   0.00       &     0.00       &     0.00    \\         
twitter4j.OEmbedRequest                                   &         1.00    &   4.47    &   0.01    &   0.00       &     0.00       &     0.00   \\          
twitter4j.Paging                                          &         1.00    &   3.35    &   0.01    &   0.00       &     0.00       &     0.00   \\          
twitter4j.TwitterBaseImpl                                 &         1.00    &   11.48   &   0.01    &   0.00       &     0.00       &    0.00    \\         
twitter4j.TwitterException                                &         1.00    &   5.12    &   0.01    &   0.00       &     0.00       &     0.00   \\          
twitter4j.TwitterImpl                                     &         1.00    &   16.35   &   0.01    &   0.00       &     0.00       &     0.00    \\         
com.puppycrawl.tools.checkstyle.api.AbstractLoader        &         1.00    &   2.28    &   0.03    &   77.00      &     50.00      &     30.00   \\         
com.puppycrawl.tools.checkstyle.api.AnnotationUtility     &         1.00    &   3.02    &   0.02    &   53.74      &     50.00      &     40.91   \\         
com.puppycrawl.tools.checkstyle.api.AutomaticBean         &         1.00    &   2.75    &   0.04    &   67.50      &     50.00      &     18.60   \\         
com.puppycrawl.tools.checkstyle.api.FileContents          &         1.00    &   5.50    &   0.03    &   97.08      &     91.67      &     80.67    \\        
com.puppycrawl.tools.checkstyle.api.FileText              &         1.00    &   2.94    &   0.03    &   88.62      &     85.26      &     91.84   \\         
com.puppycrawl.tools.checkstyle.api.ScopeUtils            &         1.00    &   14.16   &   0.09    &   72.63      &     50.33      &     24.04   \\         
com.puppycrawl.tools.checkstyle.api.Utils                 &         1.00    &   3.35    &   0.03    &   93.99      &     92.31      &     90.48   \\         
com.google.common.base.CharMatcher                        &         0.00    &   31.32   &   0.00    &   0.00       &     0.00       &     0.00   \\          
com.google.common.base.Joiner                             &         1.00    &   3.37    &   0.03    &   86.52      &     97.10      &     79.79   \\         
com.google.common.base.Objects                            &         1.00    &   2.63    &   0.03    &   98.13      &     95.37      &     94.59    \\        
com.google.common.base.Predicates                         &         1.00    &   4.16    &   0.02    &   44.39      &     21.88      &     30.68   \\         
com.google.common.base.SmallCharMatcher                   &         1.00    &   4.06    &   0.02    &   97.60      &     92.31      &     0.00    \\         
com.google.common.base.Splitter                           &         1.00    &   4.88    &   0.02    &   94.35      &     91.35      &     76.56   \\         
com.google.common.base.Suppliers                          &         1.00    &   3.07    &   0.02    &   60.38      &     58.33      &     56.06   \\         
org.hibernate.search.SearchException                      &         1.00    &   0.26    &   0.01    &   0.00       &     0.00       &     0.00   \\          
org.hibernate.search.Version                              &         1.00    &   0.24    &   0.01    &   0.00       &     0.00       &     0.00   \\          
org.hibernate.search.backend.BackendFactory               &         1.00    &   7.65    &   0.01    &   0.00       &     0.00       &     0.00   \\          
org.hibernate.search.backend.FlushLuceneWork              &         1.00    &   2.28    &   0.01    &   0.00       &     0.00       &     0.00   \\          
org.hibernate.search.backend.OptimizeLuceneWork           &         1.00    &   2.28    &   0.01    &   0.00       &     0.00       &     0.00   \\          
org.hibernate.search.util.logging.impl.LoggerFactory      &         1.00    &   0.27    &   0.01    &   0.00       &     0.00       &     0.00   \\          
org.hibernate.search.util.logging.impl.LoggerHelper       &         1.00    &   0.25    &   0.01    &   0.00       &     0.00       &     0.00   \\          
de.tudarmstadt.ukp.wikipedia.api.CategoryDescendantsIterator &       1.00   &    2.51   &    0.05   &    8.24      &      0.00       &     0.00   \\          
de.tudarmstadt.ukp.wikipedia.api.CycleHandler             &         0.00    &   32.02   &   0.00    &   0.00       &     0.00        &    0.00    \\         
de.tudarmstadt.ukp.wikipedia.api.Page                     &         1.00    &   2.75    &   0.06    &   1.49       &     6.00        &    2.67    \\         
de.tudarmstadt.ukp.wikipedia.api.PageIterator             &         1.00    &   3.76    &   0.06    &   47.72      &     46.83       &    38.54    \\        
de.tudarmstadt.ukp.wikipedia.api.PageQueryIterable        &         1.00    &   3.01    &   0.05    &   18.57      &     9.30        &    0.00    \\         
de.tudarmstadt.ukp.wikipedia.api.Title                    &         1.00    &   2.98    &   0.02    &   89.51      &     83.33       &    98.81   \\         
de.tudarmstadt.ukp.wikipedia.api.WikipediaInfo            &         0.00    &   32.02   &   0.00    &   0.00       &     0.00        &    0.00    \\         
org.asynchttpclient.AsyncHttpClient                       &         1.00    &   6.81    &   0.05    &   67.51      &     63.89       &    63.08   \\         
org.asynchttpclient.AsyncHttpClientConfig                 &         1.00    &   10.24   &   0.06    &   93.73      &     61.11       &    83.03   \\         
org.asynchttpclient.FluentCaseInsensitiveStringsMap       &         1.00    &   5.59    &   0.02    &   98.72      &     95.13       &    87.21   \\         
org.asynchttpclient.FluentStringsMap                      &         1.00    &   4.00    &   0.02    &   98.76      &     94.38       &    86.05   \\         
org.asynchttpclient.Realm                                 &         1.00    &   8.00    &   0.02    &   97.55      &     95.20       &    89.93    \\        
org.asynchttpclient.RequestBuilderBase                    &         1.00    &   8.06    &   0.03    &   93.96      &     89.89       &    43.05   \\         
org.asynchttpclient.SimpleAsyncHttpClient                 &         0.50    &   31.34   &   0.60    &   32.64      &     20.77       &    0.00    \\         
org.scribe.model.OAuthConfig                              &         1.00    &   0.58    &   0.02    &   100.00     &     100.00      &    100.00   \\        
org.scribe.model.OAuthRequest                             &         1.00    &   3.49    &   0.02    &   100.00     &     100.00      &    80.00   \\         
org.scribe.model.ParameterList                            &         1.00    &   2.65    &   0.02    &   99.61      &     99.07       &    91.30    \\        
org.scribe.model.Request                                  &         1.00    &   3.18    &   0.02    &   62.15      &     40.91       &    28.68   \\         
org.scribe.model.Response                                 &         0.00    &   2.20    &   0.00    &   0.00       &     0.00        &    0.00   \\          
org.scribe.model.Token                                    &         1.00    &   2.35    &   0.02    &   100.00     &     100.00      &    77.27   \\         
org.scribe.model.Verifier                                 &         1.00    &   0.12    &   0.02    &   100.00     &     0.00        &    50.00    \\

### 2015-02-19 papers/sbst15/paper_sbst15.tex
starting discussion

@@
   \caption{\label{table:results}Detailed results of \EVOSUITE on the SBST benchmark classes.}
-  \scriptsize
+  %\scriptsize
+\resizebox{0.9\textwidth}{!}{  
   \begin{tabular}{l rrrrrr} \toprule
@@
   \end{tabular}
+}
 \end{table*}
@@
 
-\subsection{Classes with Low Coverage}
+\subsection{Classes with No Coverage}
+
+Out of 63 CUTs, \EVOSUITE did not manage to obtain any coverage for 18 classes, i.e. 28\% 
+of the total.
+For 14 of them (the 7 in the twitter4j and the 7 in the hibernate projects), this is due
+to a mismatch in libraries on the classpath. 
+In particular, \EVOSUITE does bytecode instrumentation using the ASM library.
+However, the projects of the CUTs had their own (older) version of ASM.
+This leads to errors like: ``java.lang.IncompatibleClassChangeError: 
+class org.objectweb.asm.tree.ClassNode has interface org.objectweb.asm.ClassVisitor as super class''.
+Note: \EVOSUITE can handle its own dependencies as CUTs, i.e. by using customized classloaders, 
+but only during the search phase.
+In the generated JUnit files, those have dependencies to ASM, as we do bytecode instrumentation
+even there (e.g., to support environment testing based on mock objects [TODO]).
+So, \EVOSUITE does generate tests for those 14 classes, but then all those tests fails due to
+that thrown exception.
+An easy solution would be to ship \EVOSUITE with its own ASM version using a 
+different package name (e.g., by using the JarJar tool\footnote{https://code.google.com/p/jarjar/}).
+
+For the other 4 classes, \EVOSUITE failed to generate any test. These are
+\<CharMatcher>, \<CycleHandler>, \<WikipediaInfo> and \<Response>.
+
+TODO
+
+There are also cases of low coverage (e.g., less than 30\%).
+For example, if look at line coverage, then 
+we have \<Page> with 1.49\%, \<AbstractInstance> with 13.28\%, \<CategoryDescendantsIterator> with 8.24\%
+and \<PageQueryIterable> with 18.57\%.
+
+TODO
 

### 2015-02-19 papers/sbst15/results.tex
starting discussion

@@
 net.sf.javaml.tools.data.ARFFHandler                      &         1.00    &   2.47    &   0.02    &   75.42      &     70.83      &     48.15    \\        
-twitter4j.ExceptionDiagnosis                              &         1.00    &   3.81    &   0.01    &   0.00       &     0.00       &     0.00    \\         
-twitter4j.GeoQuery                                        &         1.00    &   3.80    &   0.01    &   0.00       &     0.00       &     0.00    \\         
-twitter4j.OEmbedRequest                                   &         1.00    &   4.47    &   0.01    &   0.00       &     0.00       &     0.00   \\          
-twitter4j.Paging                                          &         1.00    &   3.35    &   0.01    &   0.00       &     0.00       &     0.00   \\          
-twitter4j.TwitterBaseImpl                                 &         1.00    &   11.48   &   0.01    &   0.00       &     0.00       &    0.00    \\         
-twitter4j.TwitterException                                &         1.00    &   5.12    &   0.01    &   0.00       &     0.00       &     0.00   \\          
-twitter4j.TwitterImpl                                     &         1.00    &   16.35   &   0.01    &   0.00       &     0.00       &     0.00    \\         
+\rowcolor{lightgrey} twitter4j.ExceptionDiagnosis                              &         1.00    &   3.81    &   0.01    &   0.00       &     0.00       &     0.00    \\         
+\rowcolor{lightgrey} twitter4j.GeoQuery                                        &         1.00    &   3.80    &   0.01    &   0.00       &     0.00       &     0.00    \\         
+\rowcolor{lightgrey} twitter4j.OEmbedRequest                                   &         1.00    &   4.47    &   0.01    &   0.00       &     0.00       &     0.00   \\          
+\rowcolor{lightgrey} twitter4j.Paging                                          &         1.00    &   3.35    &   0.01    &   0.00       &     0.00       &     0.00   \\          
+\rowcolor{lightgrey} twitter4j.TwitterBaseImpl                                 &         1.00    &   11.48   &   0.01    &   0.00       &     0.00       &    0.00    \\         
+\rowcolor{lightgrey} twitter4j.TwitterException                                &         1.00    &   5.12    &   0.01    &   0.00       &     0.00       &     0.00   \\          
+\rowcolor{lightgrey} twitter4j.TwitterImpl                                     &         1.00    &   16.35   &   0.01    &   0.00       &     0.00       &     0.00    \\         
 com.puppycrawl.tools.checkstyle.api.AbstractLoader        &         1.00    &   2.28    &   0.03    &   77.00      &     50.00      &     30.00   \\         
@@
 com.puppycrawl.tools.checkstyle.api.Utils                 &         1.00    &   3.35    &   0.03    &   93.99      &     92.31      &     90.48   \\         
-com.google.common.base.CharMatcher                        &         0.00    &   31.32   &   0.00    &   0.00       &     0.00       &     0.00   \\          
+\rowcolor{lightgrey} com.google.common.base.CharMatcher                        &         0.00    &   31.32   &   0.00    &   0.00       &     0.00       &     0.00   \\          
 com.google.common.base.Joiner                             &         1.00    &   3.37    &   0.03    &   86.52      &     97.10      &     79.79   \\         
@@
 com.google.common.base.Suppliers                          &         1.00    &   3.07    &   0.02    &   60.38      &     58.33      &     56.06   \\         
-org.hibernate.search.SearchException                      &         1.00    &   0.26    &   0.01    &   0.00       &     0.00       &     0.00   \\          
-org.hibernate.search.Version                              &         1.00    &   0.24    &   0.01    &   0.00       &     0.00       &     0.00   \\          
-org.hibernate.search.backend.BackendFactory               &         1.00    &   7.65    &   0.01    &   0.00       &     0.00       &     0.00   \\          
-org.hibernate.search.backend.FlushLuceneWork              &         1.00    &   2.28    &   0.01    &   0.00       &     0.00       &     0.00   \\          
-org.hibernate.search.backend.OptimizeLuceneWork           &         1.00    &   2.28    &   0.01    &   0.00       &     0.00       &     0.00   \\          
-org.hibernate.search.util.logging.impl.LoggerFactory      &         1.00    &   0.27    &   0.01    &   0.00       &     0.00       &     0.00   \\          
-org.hibernate.search.util.logging.impl.LoggerHelper       &         1.00    &   0.25    &   0.01    &   0.00       &     0.00       &     0.00   \\          
+\rowcolor{lightgrey} org.hibernate.search.SearchException                      &         1.00    &   0.26    &   0.01    &   0.00       &     0.00       &     0.00   \\          
+\rowcolor{lightgrey} org.hibernate.search.Version                              &         1.00    &   0.24    &   0.01    &   0.00       &     0.00       &     0.00   \\          
+\rowcolor{lightgrey} org.hibernate.search.backend.BackendFactory               &         1.00    &   7.65    &   0.01    &   0.00       &     0.00       &     0.00   \\          
+\rowcolor{lightgrey} org.hibernate.search.backend.FlushLuceneWork              &         1.00    &   2.28    &   0.01    &   0.00       &     0.00       &     0.00   \\          
+\rowcolor{lightgrey} org.hibernate.search.backend.OptimizeLuceneWork           &         1.00    &   2.28    &   0.01    &   0.00       &     0.00       &     0.00   \\          
+\rowcolor{lightgrey} org.hibernate.search.util.logging.impl.LoggerFactory      &         1.00    &   0.27    &   0.01    &   0.00       &     0.00       &     0.00   \\          
+\rowcolor{lightgrey} org.hibernate.search.util.logging.impl.LoggerHelper       &         1.00    &   0.25    &   0.01    &   0.00       &     0.00       &     0.00   \\          
 de.tudarmstadt.ukp.wikipedia.api.CategoryDescendantsIterator &       1.00   &    2.51   &    0.05   &    8.24      &      0.00       &     0.00   \\          
-de.tudarmstadt.ukp.wikipedia.api.CycleHandler             &         0.00    &   32.02   &   0.00    &   0.00       &     0.00        &    0.00    \\         
+\rowcolor{lightgrey} de.tudarmstadt.ukp.wikipedia.api.CycleHandler             &         0.00    &   32.02   &   0.00    &   0.00       &     0.00        &    0.00    \\         
 de.tudarmstadt.ukp.wikipedia.api.Page                     &         1.00    &   2.75    &   0.06    &   1.49       &     6.00        &    2.67    \\         
@@
 de.tudarmstadt.ukp.wikipedia.api.Title                    &         1.00    &   2.98    &   0.02    &   89.51      &     83.33       &    98.81   \\         
-de.tudarmstadt.ukp.wikipedia.api.WikipediaInfo            &         0.00    &   32.02   &   0.00    &   0.00       &     0.00        &    0.00    \\         
+\rowcolor{lightgrey} de.tudarmstadt.ukp.wikipedia.api.WikipediaInfo            &         0.00    &   32.02   &   0.00    &   0.00       &     0.00        &    0.00    \\         
 org.asynchttpclient.AsyncHttpClient                       &         1.00    &   6.81    &   0.05    &   67.51      &     63.89       &    63.08   \\         
@@
 org.scribe.model.Request                                  &         1.00    &   3.18    &   0.02    &   62.15      &     40.91       &    28.68   \\         
-org.scribe.model.Response                                 &         0.00    &   2.20    &   0.00    &   0.00       &     0.00        &    0.00   \\          
+\rowcolor{lightgrey} org.scribe.model.Response                                 &         0.00    &   2.20    &   0.00    &   0.00       &     0.00        &    0.00   \\          
 org.scribe.model.Token                                    &         1.00    &   2.35    &   0.02    &   100.00     &     100.00      &    77.27   \\         

### 2015-02-19 papers/sbst15/paper_sbst15.tex
adding EvoSuite description

@@
   \hline
-  Interaction &  Through the command line\\
+  Interaction &  Through the command line, and Eclipse plugin\\
   User guidance &  manual verification of assertions for functional faults\\
@@
   \hline
-  Effectiveness and Scalability & See~\cite{GoA_TSE12,FrA12b}. \\
+  Effectiveness and Scalability & See~\cite{GoA_TSE12,fraser2014large}. \\
 %Completeness & \\
@@
 \end{table}
+
+\EVOSUITE~\cite{FrA11c,GoA_TSE12} automatically generates test suites
+for Java classes, targeting branch coverage and other coverage
+criteria (e.g., mutation testing~\cite{emse14_mutation}). \EVOSUITE
+works at the Java bytecode level, i.e., it does not require source
+code. It is fully automated and requires no manually written test
+drivers or parameterized unit tests.  For example, when \EVOSUITE is
+used from its Eclipse plugin, a user
+just needs to select a class, and tests are generated with a mouse-click.
+
+\EVOSUITE has been evaluated on millions of lines of Java code~\cite{fraser2014large}, both open-source
+code and close-source code provided by one of our industrial partners. 
+In the previous two editions
+of the unit testing tool
+competition, \EVOSUITE arrived first~\cite{evosuiteAtSbst2013,evosuiteAtFittest2013}.
+
+\EVOSUITE uses an evolutionary approach to derive these test suites: A
+genetic algorithm evolves candidate individuals (chromosomes) using
+operators inspired by natural evolution (e.g., selection, crossover
+and mutation), such that iteratively better solutions with respect to
+the optimization target (e.g., branch coverage) are produced.  For
+details on this test generation approach we refer to~\cite{GoA_TSE12}.
+To improve performance further, we are investigating several
+extensions to \EVOSUITE. 
+For example, \EVOSUITE can employ dynamic
+symbolic execution~\cite{evoISSRE113} 
+and memetic algorithms~\cite{fraser2014memetic}
+to handle the cases in which our genetic algorithm may struggle.
+
+As the generated unit tests are meant for human consumption~\cite{fraser2013does}, \EVOSUITE
+applies various post-processing steps to improve readability (e.g.,
+minimising) and adds test assertions that capture the current
+behavior of the tested classes. To select the most effective
+assertions, \EVOSUITE uses mutation
+analysis~\cite{10.1109/TSE.2011.93}. 
+\EVOSUITE can also be used to automatically find faults in the CUTs~\cite{emse13_oracle}, e.g undeclared
+thrown exceptions and broken code contracts.
+ For more details on the tool and
+its abilities we refer to~\cite{FrA11c}, and for more implementation
+details we refer to~\cite{FrA13a}.
 

### 2015-02-19 papers/sbst15/paper_sbst15.tex
first complete draft

@@
   \centering
-  \caption{\label{table:results}Detailed results of \EVOSUITE on the SBST benchmark classes.}
+  \caption{\label{table:results}Detailed results of \EVOSUITE on the SBST benchmark classes. Time is expressed in minutes.}
   %\scriptsize
@@
 \midrule
-Average & & 371.58 & 2.10 & 55.36 & 47.19 & 41.02\\
+Average & & 6.19 & 0.03 & 55.36 & 47.19 & 41.02\\
 \bottomrule
@@
 In the generated JUnit files, those have dependencies to ASM, as we do bytecode instrumentation
-even there (e.g., to support environment testing based on mock objects [TODO]).
+even there (e.g., to support environment testing based on mock objects~\cite{arcuri2014automated}).
 So, \EVOSUITE does generate tests for those 14 classes, but then all those tests fails due to
@@
 \<CharMatcher>, \<CycleHandler>, \<WikipediaInfo> and \<Response>.
-
-TODO
-
-There are also cases of low coverage (e.g., less than 30\%).
+There are also a further 4 cases of low coverage (e.g., less than 30\%).
 For example, if look at line coverage, then 
@@
 and \<PageQueryIterable> with 18.57\%.
-
-TODO
+To improve \EVOSUITE, it will be important to understand why that was the case.
 
@@
 \section{Conclusions}
+
+With an overall score of $190.6$, \EVOSUITE achieved the second highest score of all tools in
+the competition. The score calculated for best testing is $203.7$:  a very close
+call. 
+In particular, due to a configuration issue in the classpath of the target projects,
+\EVOSUITE could had been run only on 7 out of 9 of the projects used as benchmark.
+That is an easily fixed issue that would lead to even higher scores.
 

### 2015-02-21 papers/sbst15/paper_sbst15.tex
Editing paper

@@
 \begin{abstract}
-  \EVOSUITE is a mature research prototype that automatically generates unit tests for Java code. 
-  This paper summarizes the results and experiences in participating at the third unit testing competition held at SBST 2015,
-  where \EVOSUITE ranked second with a $190.6$ score.
+  \EVOSUITE is a mature research prototype that automatically
+  generates unit tests for Java code.  This paper summarizes the
+  results and experiences in participating at the third unit testing
+  competition held at SBST 2015. An unfortunate issue of conflicting
+  dependency versions in two out of the nine projects used in the
+  benchmark reduced \EVOSUITE's overall score to $190.6$, and thus the
+  second rank.
 \end{abstract}
@@
 
-\EVOSUITE has been evaluated on millions of lines of Java code~\cite{fraser2014large}, both open-source
-code and close-source code provided by one of our industrial partners. 
-In the previous two editions
-of the unit testing tool
-competition, \EVOSUITE arrived first~\cite{evosuiteAtSbst2013,evosuiteAtFittest2013}.
+\EVOSUITE has been evaluated on millions of lines of Java
+code~\cite{fraser2014large}, both open-source code and close-source
+code provided by one of our industrial partners.  In the previous two
+editions of the unit testing tool competition, \EVOSUITE ranked
+first~\cite{evosuiteAtSbst2013,evosuiteAtFittest2013}.
 
@@
 
-As the generated unit tests are meant for human consumption~\cite{fraser2013does}, \EVOSUITE
-applies various post-processing steps to improve readability (e.g.,
-minimising) and adds test assertions that capture the current
-behavior of the tested classes. To select the most effective
-assertions, \EVOSUITE uses mutation
-analysis~\cite{10.1109/TSE.2011.93}. 
-\EVOSUITE can also be used to automatically find faults in the CUTs~\cite{emse13_oracle}, e.g undeclared
-thrown exceptions and broken code contracts.
- For more details on the tool and
-its abilities we refer to~\cite{FrA11c}, and for more implementation
-details we refer to~\cite{FrA13a}.
+As the generated unit tests are meant for human
+consumption~\cite{fraser2013does}, \EVOSUITE applies various
+post-processing steps to improve readability (e.g., minimising) and
+adds test assertions that capture the current behavior of the tested
+classes. To select the most effective assertions, \EVOSUITE uses
+mutation analysis~\cite{10.1109/TSE.2011.93}.  \EVOSUITE can also be
+used to automatically find faults in the CUTs~\cite{emse13_oracle},
+e.g., undeclared thrown exceptions and broken code contracts.  For
+more details on the tool and its abilities we refer to~\cite{FrA11c},
+and for more implementation details we refer to~\cite{FrA13a}.
+
+%------------------------------------------------------------------------- 
+\section{Competition Setup}
+
+We configured \EVOSUITE to use a dynamic timeout of maximum 10 minutes
+for the search, with an earlier stop if the fitness value did not
+increase for two minutes. The fitness function to drive the genetic
+algorithm was based on a combination of line coverage, branch
+coverage, and weak mutation testing. We enabled the post-processing
+step of test minimization, but to reduce the time spent we included
+all assertions rather than filtering them with mutation
+analysis~\cite{10.1109/TSE.2011.93}. In practice, this may not result
+in the most readable or maintainable test cases, but neither of these
+two attributes is measured by the SBST contest metric.
 
@@
 produced TODO tests per class, and it took an average of TODO per class to
-do so (with \EVOSUITE configured to 3 minutes per class).
+do so.
+% (with \EVOSUITE configured to 3 minutes per class).
 
-\subsection{Classes with No Coverage}
+\subsection{Issues Encountered}
 
-Out of 63 CUTs, \EVOSUITE did not manage to obtain any coverage for 18 classes, i.e. 28\% 
-of the total.
-For 14 of them (the 7 in the twitter4j and the 7 in the hibernate projects), this is due
-to a mismatch in libraries on the classpath. 
-In particular, \EVOSUITE does bytecode instrumentation using the ASM library.
-However, the projects of the CUTs had their own (older) version of ASM.
-This leads to errors like: ``java.lang.IncompatibleClassChangeError: 
-class org.objectweb.asm.tree.ClassNode has interface org.objectweb.asm.ClassVisitor as super class''.
-Note: \EVOSUITE can handle its own dependencies as CUTs, i.e. by using customized classloaders, 
-but only during the search phase.
-In the generated JUnit files, those have dependencies to ASM, as we do bytecode instrumentation
-even there (e.g., to support environment testing based on mock objects~\cite{arcuri2014automated}).
-So, \EVOSUITE does generate tests for those 14 classes, but then all those tests fails due to
-that thrown exception.
-An easy solution would be to ship \EVOSUITE with its own ASM version using a 
-different package name (e.g., by using the JarJar tool\footnote{https://code.google.com/p/jarjar/}).
+% CharMatcher: Timeout
+% CycleHandler, WikipediaInfo: Infinite loop in generic resolving
+% Response requires java.net.HttpURLConnection
 
-For the other 4 classes, \EVOSUITE failed to generate any test. These are
-\<CharMatcher>, \<CycleHandler>, \<WikipediaInfo> and \<Response>.
-There are also a further 4 cases of low coverage (e.g., less than 30\%).
-For example, if look at line coverage, then 
-we have \<Page> with 1.49\%, \<AbstractInstance> with 13.28\%, \<CategoryDescendantsIterator> with 8.24\%
-and \<PageQueryIterable> with 18.57\%.
-To improve \EVOSUITE, it will be important to understand why that was the case.
+Out of 63 CUTs, \EVOSUITE did not manage to obtain any coverage for 18
+classes, i.e., 28\% of all classes.  For 14 of them (the 7 in the
+twitter4j and the 7 in the hibernate projects), this is due to a
+mismatch in libraries on the classpath.  In particular, \EVOSUITE does
+bytecode instrumentation using the ASM library.  However, the projects
+of the CUTs had their own (older) version of ASM.  This leads to
+errors like: ``java.lang.IncompatibleClassChangeError: class
+org.objectweb.asm.tree.ClassNode has interface
+org.objectweb.asm.ClassVisitor as super class''.  Note: \EVOSUITE can
+handle its own dependencies as CUTs, i.e., by using customized
+classloaders, but only during the search phase.  In the generated
+JUnit files, those have dependencies to ASM, as we do bytecode
+instrumentation even there (e.g., to support environment testing based
+on mock objects~\cite{arcuri2014automated}).  So, \EVOSUITE does
+generate tests for those 14 classes, but then all those tests fails
+due to that thrown exception.  An easy solution would be to ship
+\EVOSUITE with its own ASM version using a different package name
+(e.g., by using the JarJar
+tool\footnote{https://code.google.com/p/jarjar/}).
+%
+If we had handled this issue properly before the competition, this
+would have changed the result: Excluding classes from the twitter4j
+and hibernate, the overall score of \EVOSUITE would be 191.584,
+whereas GRT would have a score of 164.464. Consequently, this issue
+clearly is the main factor affecting \EVOSUITE's overall result.
+
+For the other four classes with 0\% coverage, \EVOSUITE failed to
+generate any tests. For \<CharMatcher>, the issue is an issue in how
+\EVOSUITE handled timeouts, which resulted in \EVOSUITE's master
+process killing the client process before tests were written to
+disk. For \<CycleHandler> and \<WikipediaInfo>, \EVOSUITE ran into an
+issue when trying to resolve the generic type parameters of some
+dependency classes. This issue could be avoided by omitting generic
+type parameters, as the Java compiler would only issue warnings about
+such missing parameters. However, as \EVOSUITE is aiming to produce
+readable tests, we feel it is important to properly handle Java
+Generics. Finally, for \<Response> the constructor requires a
+parameter of type \<java.net.HttpURLConnection>, which is an abstract
+class without concrete subclasses. As \EVOSUITE does not produce stubs
+automatically, it therefore failed to instantiate \<Response> objects.
+
+There are also a further 4 cases of low coverage (e.g., less than
+30\%).  For example, if look at line coverage, then we have \<Page>
+with 1.49\%, \<AbstractInstance> with 13.28\%,
+\<CategoryDescendantsIterator> with 8.24\% and \<PageQueryIterable>
+with 18.57\%.
+
+TODO: Will look into these four.
+
+%To improve \EVOSUITE, it will be important to
+%understand why that was the case.
 
@@
 
-With an overall score of $190.6$, \EVOSUITE achieved the second highest score of all tools in
-the competition. The score calculated for best testing is $203.7$:  a very close
-call. 
-In particular, due to a configuration issue in the classpath of the target projects,
-\EVOSUITE could had been run only on 7 out of 9 of the projects used as benchmark.
-That is an easily fixed issue that would lead to even higher scores.
+With an overall score of $190.6$, \EVOSUITE achieved the second
+highest score of all tools in the competition. The score calculated
+for the best tool is $203.7$: a very close call.  In particular, if
+considering only projects without a configuration issue in the
+classpath of the target projects, \EVOSUITE would have scored first
+with a score of $191.6$.
+%
+%due to
+%a configuration issue in the classpath of the target projects,
+%\EVOSUITE could had been run only on 7 out of 9 of the projects used
+%as benchmark.  
+The underlying issue can be easily fixed for future runs of the
+competition.
+% issue that would lead to even
+%higher scores.
 

### 2015-02-21 papers/sbst15/paper_sbst15.tex
Paper editing

@@
   generates unit tests for Java code.  This paper summarizes the
-  results and experiences in participating at the third unit testing
-  competition held at SBST 2015. An unfortunate issue of conflicting
-  dependency versions in two out of the nine projects used in the
-  benchmark reduced \EVOSUITE's overall score to $190.6$, and thus the
-  second rank.
+  results and experiences of \EVOSUITE's participation at the third
+  unit testing competition at SBST 2015. An unfortunate issue of
+  conflicting dependency versions in two out of the nine benchmark
+  projects reduced \EVOSUITE's overall score to $190.6$, leading to
+  the overall second rank.
 \end{abstract}
@@
 competition at the International Workshop on Search-Based Software
-Testing (SBST) 2015.  Details on the competition and the benchmark can
-be found in~\cite{sbst2015}. In this competition, \EVOSUITE ranked
+Testing (SBST) 2015.  Details about the competition and the benchmark
+can be found in~\cite{sbst2015}. In this competition, \EVOSUITE ranked
 second with a score of $190.6$.
@@
 mutation analysis~\cite{10.1109/TSE.2011.93}.  \EVOSUITE can also be
-used to automatically find faults in the CUTs~\cite{emse13_oracle},
-e.g., undeclared thrown exceptions and broken code contracts.  For
-more details on the tool and its abilities we refer to~\cite{FrA11c},
-and for more implementation details we refer to~\cite{FrA13a}.
+used to automatically find faults such as undeclared thrown exceptions
+and broken code contracts~\cite{emse13_oracle}.  For more details on
+the tool and its abilities we refer to~\cite{FrA11c}, and for more
+implementation details we refer to~\cite{FrA13a}.
 
@@
 We configured \EVOSUITE to use a dynamic timeout of maximum 10 minutes
-for the search, with an earlier stop if the fitness value did not
-increase for two minutes. The fitness function to drive the genetic
-algorithm was based on a combination of line coverage, branch
-coverage, and weak mutation testing. We enabled the post-processing
-step of test minimization, but to reduce the time spent we included
-all assertions rather than filtering them with mutation
-analysis~\cite{10.1109/TSE.2011.93}. In practice, this may not result
-in the most readable or maintainable test cases, but neither of these
-two attributes is measured by the SBST contest metric.
+per class for the search, with an earlier stop if the fitness value
+did not increase for two minutes. The fitness function to drive the
+genetic algorithm was based on a combination of line coverage, branch
+coverage, and weak mutation testing~\cite{emse14_mutation}. We enabled
+the post-processing step of test minimization, but to reduce the time
+spent we included all assertions rather than filtering them with
+mutation analysis~\cite{10.1109/TSE.2011.93}. In practice, this may
+not result in the most readable or maintainable test cases, but
+neither of these two attributes is measured by the SBST contest
+metric.
 
@@
 
-Out of 63 CUTs, \EVOSUITE did not manage to obtain any coverage for 18
-classes, i.e., 28\% of all classes.  For 14 of them (the 7 in the
-twitter4j and the 7 in the hibernate projects), this is due to a
-mismatch in libraries on the classpath.  In particular, \EVOSUITE does
-bytecode instrumentation using the ASM library.  However, the projects
-of the CUTs had their own (older) version of ASM.  This leads to
-errors like: ``java.lang.IncompatibleClassChangeError: class
+Out of 63 classes under test (CUTs), \EVOSUITE did not manage to
+obtain any coverage for 18, i.e., 28\% of all classes.  For 14 of them
+(seven in the twitter4j project and seven in the hibernate project),
+this is due to a mismatch in libraries on the classpath.  In
+particular, \EVOSUITE does bytecode instrumentation using the ASM
+library (currently using version 5.0.3).  However, the projects of the
+CUTs had their own (older) version of ASM; for example Twitter4J has
+an indirect dependency to ASM 3.2.
+
+Because the API of ASM has changed over different versions, this leads
+to errors like: ``java.lang.IncompatibleClassChangeError: class
 org.objectweb.asm.tree.ClassNode has interface
 org.objectweb.asm.ClassVisitor as super class''.  Note: \EVOSUITE can
-handle its own dependencies as CUTs, i.e., by using customized
-classloaders, but only during the search phase.  In the generated
-JUnit files, those have dependencies to ASM, as we do bytecode
-instrumentation even there (e.g., to support environment testing based
-on mock objects~\cite{arcuri2014automated}).  So, \EVOSUITE does
-generate tests for those 14 classes, but then all those tests fails
-due to that thrown exception.  An easy solution would be to ship
+be applied to its own library dependencies through its use of
+customized classloaders. However, bytecode instrumentation is also
+performed in the generated JUnit files (e.g., to support environment
+testing based on mock objects~\cite{arcuri2014automated}), which leads
+to a runtime dependency to ASM. Consequently, \EVOSUITE generates
+tests for those 14 classes, but then all these tests fail due to the
+above mentioned exception.  An easy solution would be to ship
 \EVOSUITE with its own ASM version using a different package name
@@
 If we had handled this issue properly before the competition, this
-would have changed the result: Excluding classes from the twitter4j
+would have changed the outcome: Excluding classes from the twitter4j
 and hibernate, the overall score of \EVOSUITE would be 191.584,
-whereas GRT would have a score of 164.464. Consequently, this issue
-clearly is the main factor affecting \EVOSUITE's overall result.
+whereas the first ranked tool (GRT) would have a score of
+164.464. Consequently, this issue clearly is the main factor affecting
+\EVOSUITE's overall result.
 
 For the other four classes with 0\% coverage, \EVOSUITE failed to
-generate any tests. For \<CharMatcher>, the issue is an issue in how
-\EVOSUITE handled timeouts, which resulted in \EVOSUITE's master
-process killing the client process before tests were written to
-disk. For \<CycleHandler> and \<WikipediaInfo>, \EVOSUITE ran into an
-issue when trying to resolve the generic type parameters of some
-dependency classes. This issue could be avoided by omitting generic
-type parameters, as the Java compiler would only issue warnings about
-such missing parameters. However, as \EVOSUITE is aiming to produce
+generate any tests for other reasons. For \<CharMatcher>, the issue is
+an issue in how \EVOSUITE handled timeouts, which resulted in
+\EVOSUITE's master process killing the client process before tests
+were written to disk. For \<CycleHandler> and \<WikipediaInfo>,
+\EVOSUITE ran into an issue when trying to resolve the generic type
+parameters of some dependency classes; this also affects \<Page> with
+1.49\% coverage. This issue could be avoided by omitting generic type
+parameters, as the Java compiler would only issue warnings about such
+missing parameters. However, as \EVOSUITE is aiming to produce
 readable tests, we feel it is important to properly handle Java
@@
 
-There are also a further 4 cases of low coverage (e.g., less than
-30\%).  For example, if look at line coverage, then we have \<Page>
-with 1.49\%, \<AbstractInstance> with 13.28\%,
-\<CategoryDescendantsIterator> with 8.24\% and \<PageQueryIterable>
-with 18.57\%.
+%There are also a further 4 cases of low coverage (e.g., less than
+%30\%).  For example, if look at line coverage, then we have \<Page>
+%with 1.49\%, \<AbstractInstance> with 13.28\%,
+%\<CategoryDescendantsIterator> with 8.24\% and \<PageQueryIterable>
+%with 18.57\%.
 
-TODO: Will look into these four.
+%TODO: Will look into these four.
 

### 2015-02-22 papers/sbst15/paper_sbst15.tex
minor paper editing

@@
 The results of \EVOSUITE on the benchmark classes are listed in
-Table~\ref{table:results}. On average, \EVOSUITE achieved TODO line
-coverage,TODO branch coverage\footnote{Using Cobertura's definition
+Table~\ref{table:results}. On average, \EVOSUITE achieved 55.36\% line
+coverage, 47.19\% branch coverage\footnote{Using Cobertura's definition
   of branch coverage, which only counts conditional statements, not
-  edges in the CFG.}, and TODO mutation score. On average, \EVOSUITE
-produced TODO tests per class, and it took an average of TODO per class to
-do so.
+  edges in the CFG.}, and 41.02\% mutation score. 
+%On average, \EVOSUITE
+%produced TODO tests per class, and it took an average of TODO per class to
+%do so.
 % (with \EVOSUITE configured to 3 minutes per class).
+On average, \EVOSUITE took 6 minutes and 11 seconds per class to generate test cases. 
+The generated test suites take on average 2.1 seconds to run per class.
 
@@
 For the other four classes with 0\% coverage, \EVOSUITE failed to
-generate any tests for other reasons. For \<CharMatcher>, the issue is
+generate any tests for other reasons. For \<CharMatcher>, there was 
 an issue in how \EVOSUITE handled timeouts, which resulted in

### 2016-02-16 papers/sbst16/paper_sbst16.tex
draft for SBST 16 competition

--- 2015-02-21 papers/sbst15/paper_sbst15.tex
@@
 bookmarksnumbered=true,
-pdftitle={EvoSuite at the SBST 2013 Tool Competition},
+pdftitle={EvoSuite at the SBST 2016 Tool Competition},
 pdfauthor={Gordon Fraser and Andrea Arcuri},
@@
 %\title{Unit Testing Tool competition: Results for EvoSuite}
-\title{EvoSuite at the SBST 2015 Tool Competition}
+\title{EvoSuite at the SBST 2016 Tool Competition}
 
@@
 \begin{abstract}
-  \EVOSUITE is a mature research prototype that automatically
+  \EVOSUITE is a search-based tool that automatically
   generates unit tests for Java code.  This paper summarizes the
-  results and experiences in participating at the third unit testing
-  competition held at SBST 2015. An unfortunate issue of conflicting
-  dependency versions in two out of the nine projects used in the
-  benchmark reduced \EVOSUITE's overall score to $190.6$, and thus the
-  second rank.
+  results and experiences of \EVOSUITE's participation at the fourth
+  unit testing competition at SBST 2016. 
 \end{abstract}
@@
 competition at the International Workshop on Search-Based Software
-Testing (SBST) 2015.  Details on the competition and the benchmark can
-be found in~\cite{sbst2015}. In this competition, \EVOSUITE ranked
-second with a score of $190.6$.
+Testing (SBST) 2016.  Details about the competition and the benchmark
+can be found in []. 
+In this competition, \EVOSUITE ranked [] with a score of [].
 
@@
   \hline
-  Interaction &  Through the command line, and Eclipse plugin\\
+  Interaction &  Through the command line, and plugins for IntelliJ, Maven and Eclipse\\
   User guidance &  manual verification of assertions for functional faults\\
@@
   \hline
-License & GNU General Public License V3\\
+License & Lesser GPL V.3\\
 Cost & Open source\\
@@
 drivers or parameterized unit tests.  For example, when \EVOSUITE is
-used from its Eclipse plugin, a user
+used from its Eclipse and IntelliJ plugins, a user
 just needs to select a class, and tests are generated with a mouse-click.
@@
 code~\cite{fraser2014large}, both open-source code and close-source
-code provided by one of our industrial partners.  In the previous two
+code provided by one of our industrial partners.  In the first two
 editions of the unit testing tool competition, \EVOSUITE ranked
-first~\cite{evosuiteAtSbst2013,evosuiteAtFittest2013}.
+first~\cite{evosuiteAtSbst2013,evosuiteAtFittest2013}, whereas it
+ranked second in the third one [].
 
@@
 details on this test generation approach we refer to~\cite{GoA_TSE12}.
-To improve performance further, we are investigating several
-extensions to \EVOSUITE. 
-For example, \EVOSUITE can employ dynamic
-symbolic execution~\cite{evoISSRE113} 
-and memetic algorithms~\cite{fraser2014memetic}
-to handle the cases in which our genetic algorithm may struggle.
+%To improve performance further, we are investigating several
+%extensions to \EVOSUITE. 
+%For example, \EVOSUITE can employ dynamic
+%symbolic execution~\cite{evoISSRE113} 
+%and memetic algorithms~\cite{fraser2014memetic}
+%to handle the cases in which our genetic algorithm may struggle.
 
@@
 
-We configured \EVOSUITE to use a dynamic timeout of maximum 10 minutes
-for the search, with an earlier stop if the fitness value did not
-increase for two minutes. The fitness function to drive the genetic
-algorithm was based on a combination of line coverage, branch
-coverage, and weak mutation testing. We enabled the post-processing
-step of test minimization, but to reduce the time spent we included
-all assertions rather than filtering them with mutation
-analysis~\cite{10.1109/TSE.2011.93}. In practice, this may not result
-in the most readable or maintainable test cases, but neither of these
-two attributes is measured by the SBST contest metric.
+%We configured \EVOSUITE to use a dynamic timeout of maximum 10 minutes
+%per class for the search, with an earlier stop if the fitness value
+%did not increase for two minutes. The fitness function to drive the
+%genetic algorithm was based on a combination of line coverage, branch
+%coverage, and weak mutation testing~\cite{emse14_mutation}. We enabled
+%the post-processing step of test minimization, but to reduce the time
+%spent we included all assertions rather than filtering them with
+%mutation analysis~\cite{10.1109/TSE.2011.93}. In practice, this may
+%not result in the most readable or maintainable test cases, but
+%neither of these two attributes is measured by the SBST contest
+%metric.
 
@@
 Class &  JUnit Files &   Generation Time & Execution Time   & \% Line Coverage & \% Branch Coverage & \% Mutation Score \\  
-% Class & Generation Time & Execution Time  & Tests & Line Coverage & Branch Coverage & Mutation Score \\ 
-%Class & \multicolumn{2}{c}{ Time} & Tests & Line Coverage & Branch
-%Coverage & Mutation Score \\ 
-%& Generation & Execution & & & & \\
 \midrule
-\input{results.tex}
+%\input{results.tex}
 \midrule
-Average & & 6.19 & 0.03 & 55.36 & 47.19 & 41.02\\
+%Average & & 6.19 & 0.03 & 55.36 & 47.19 & 41.02\\
 \bottomrule
@@
 
-%average per class generation time:                 371.581857 seconds
-%average per class execution time:                  2.103966 seconds
-%average per class instruction coverage:            54.495767 %
-%average per class line coverage:                   55.368111 %
-%average per class branch coverage:                 47.192896 %
-%average per class method coverage:                 59.628209 %
-%average per class mutation coverage:               41.024248 %
-
 The results of \EVOSUITE on the benchmark classes are listed in
-Table~\ref{table:results}. On average, \EVOSUITE achieved TODO line
-coverage,TODO branch coverage\footnote{Using Cobertura's definition
+Table~\ref{table:results}. On average, \EVOSUITE achieved []\% line
+coverage, []\% branch coverage\footnote{Using Cobertura's definition
   of branch coverage, which only counts conditional statements, not
-  edges in the CFG.}, and TODO mutation score. On average, \EVOSUITE
-produced TODO tests per class, and it took an average of TODO per class to
-do so.
-% (with \EVOSUITE configured to 3 minutes per class).
+  edges in the CFG.}, and []\% mutation score.
 
@@
 
-% CharMatcher: Timeout
-% CycleHandler, WikipediaInfo: Infinite loop in generic resolving
-% Response requires java.net.HttpURLConnection
-
-Out of 63 CUTs, \EVOSUITE did not manage to obtain any coverage for 18
-classes, i.e., 28\% of all classes.  For 14 of them (the 7 in the
-twitter4j and the 7 in the hibernate projects), this is due to a
-mismatch in libraries on the classpath.  In particular, \EVOSUITE does
-bytecode instrumentation using the ASM library.  However, the projects
-of the CUTs had their own (older) version of ASM.  This leads to
-errors like: ``java.lang.IncompatibleClassChangeError: class
-org.objectweb.asm.tree.ClassNode has interface
-org.objectweb.asm.ClassVisitor as super class''.  Note: \EVOSUITE can
-handle its own dependencies as CUTs, i.e., by using customized
-classloaders, but only during the search phase.  In the generated
-JUnit files, those have dependencies to ASM, as we do bytecode
-instrumentation even there (e.g., to support environment testing based
-on mock objects~\cite{arcuri2014automated}).  So, \EVOSUITE does
-generate tests for those 14 classes, but then all those tests fails
-due to that thrown exception.  An easy solution would be to ship
-\EVOSUITE with its own ASM version using a different package name
-(e.g., by using the JarJar
-tool\footnote{https://code.google.com/p/jarjar/}).
-%
-If we had handled this issue properly before the competition, this
-would have changed the result: Excluding classes from the twitter4j
-and hibernate, the overall score of \EVOSUITE would be 191.584,
-whereas GRT would have a score of 164.464. Consequently, this issue
-clearly is the main factor affecting \EVOSUITE's overall result.
-
-For the other four classes with 0\% coverage, \EVOSUITE failed to
-generate any tests. For \<CharMatcher>, the issue is an issue in how
-\EVOSUITE handled timeouts, which resulted in \EVOSUITE's master
-process killing the client process before tests were written to
-disk. For \<CycleHandler> and \<WikipediaInfo>, \EVOSUITE ran into an
-issue when trying to resolve the generic type parameters of some
-dependency classes. This issue could be avoided by omitting generic
-type parameters, as the Java compiler would only issue warnings about
-such missing parameters. However, as \EVOSUITE is aiming to produce
-readable tests, we feel it is important to properly handle Java
-Generics. Finally, for \<Response> the constructor requires a
-parameter of type \<java.net.HttpURLConnection>, which is an abstract
-class without concrete subclasses. As \EVOSUITE does not produce stubs
-automatically, it therefore failed to instantiate \<Response> objects.
-
-There are also a further 4 cases of low coverage (e.g., less than
-30\%).  For example, if look at line coverage, then we have \<Page>
-with 1.49\%, \<AbstractInstance> with 13.28\%,
-\<CategoryDescendantsIterator> with 8.24\% and \<PageQueryIterable>
-with 18.57\%.
-
-TODO: Will look into these four.
-
-%To improve \EVOSUITE, it will be important to
-%understand why that was the case.
+[]
 
@@
 
-With an overall score of $190.6$, \EVOSUITE achieved the second
-highest score of all tools in the competition. The score calculated
-for the best tool is $203.7$: a very close call.  In particular, if
-considering only projects without a configuration issue in the
-classpath of the target projects, \EVOSUITE would have scored first
-with a score of $191.6$.
-%
-%due to
-%a configuration issue in the classpath of the target projects,
-%\EVOSUITE could had been run only on 7 out of 9 of the projects used
-%as benchmark.  
-The underlying issue can be easily fixed for future runs of the
-competition.
-% issue that would lead to even
-%higher scores.
+With an overall score of [], \EVOSUITE achieved the []
+ score of all tools in the competition.
 
@@
 %\noindent
-%\textbf{Acknowledgments.}
+\textbf{Acknowledgments.}
 

### 2016-02-18 papers/sbst16/paper_sbst16.tex
Update paper

@@
 
-%We configured \EVOSUITE to use a dynamic timeout of maximum 10 minutes
-%per class for the search, with an earlier stop if the fitness value
-%did not increase for two minutes. The fitness function to drive the
-%genetic algorithm was based on a combination of line coverage, branch
-%coverage, and weak mutation testing~\cite{emse14_mutation}. We enabled
-%the post-processing step of test minimization, but to reduce the time
-%spent we included all assertions rather than filtering them with
-%mutation analysis~\cite{10.1109/TSE.2011.93}. In practice, this may
-%not result in the most readable or maintainable test cases, but
-%neither of these two attributes is measured by the SBST contest
-%metric.
+\EVOSUITE can be configured to target different coverage criteria. The
+fitness function to drive the genetic algorithm was based on a
+combination of several criteria~\cite{rojas2015combining} (e.g., line
+coverage, branch coverage, branch coverage by direct method
+invocation, weak mutation testing, output coverage, exception
+coverage). \EVOSUITE now by default uses an archive of
+solutions~\cite{emse_archive}, which means that throughout the search,
+whenever a new coverage goal is satisfied, the corresponding test is
+stored in the archive, and this goal is no longer targeted by the
+fitness function. We enabled the post-processing step of test
+minimization, but to reduce the time spent we included all assertions
+rather than filtering them with mutation
+analysis~\cite{10.1109/TSE.2011.93}. The use of all assertions has
+effects on readability and the chances of obtaining flaky
+tests. However, as readability is not measured by the SBST contest
+metric, and many of the improvements to \EVOSUITE since the last
+competition target flaky tests we deemed this not a problem.
+
+In contrast to previous instances of the competition, the test
+generation tools this time received a time budget as input, and then
+had to generate tests within that time. \EVOSUITE uses a combination
+of different timeouts for its individual phases (e.g., initialization,
+search, minimization, assertion generation, compilation check, removal
+of flaky tests), which created the challenge of distributing the
+overall budget onto these phases. We used a simple approach where 50\%
+of the time was allocated to the search, whereas the other half of the
+time was distributed equally to the remaining phases. If any of the
+phases used more time than allocated, which can for example happen if
+test executions take long or lead to timeouts, then phases for which
+there is no time left are skipped. For example, if there is no time
+left for minimization, then the raw test suite as generated by the
+search is returned.
 
@@
 
-[]
+Following recent experiments on
+Defects4J~\cite{shamshiri2015automatically} that revealed general
+issues in unit test generation, \EVOSUITE now includes assertions on
+the source of exceptions, similar to commercial tools like Agitar
+One~\cite{agitarone}. However, there were several instances in the
+competition where these assertions lead to flaky tests. For example,
+the following is an excerpt from a test for the Defects4J bug Lang-41,
+generated by \EVOSUITE:
+
+\begin{lstlisting}
+@Test(timeout = 4000)
+public void test19()  throws Throwable  {
+ Class<Double> class0 = Double.class;
+ String string0 = ClassUtils.getPackageName(class0);
+ try { 
+   ClassUtils.getClass(string0);
+   fail("Expecting exception: ClassNotFoundException"); 
+ } catch(ClassNotFoundException e) {
+   assertThrownBy("java.net.URLClassLoader", e);
+ }
+}
+\end{lstlisting}
+
+While compiling and executing this test with JUnit works without
+problems, the mutation analysis step of the competition used Ant to
+run the tests; Ant uses a complex setup of classloaders that
+eventually leads to the \texttt{assertThrownBy} in the above example
+to fail, as the source of the exception is a different one.
 
@@
 
+Many thanks to all the contributors to \EVOSUITE.
+
 %------------------------------------------------------------------------- 

### 2016-02-21 papers/sbst16/mainTable.tex
added table

\begin{tabular}{ l rrrr rrrr}\toprule 
 Class &  \multicolumn{4}{c}{Branch Coverage}  &  \multicolumn{4}{c}{Fault Detection} \\ 
 & 60s & 120s & 240s & 480s & 60s & 120s & 240s & 480s \\ 
\midrule 
com.google.javascript.jscomp.CheckGlobalThis &  3.4\% &  20.9\% &  20.5\% &  26.5\% &  0.0\% &  0.0\% &  0.0\% &  8.3\%\\ 
com.google.javascript.jscomp.CollapseProperties &  2.6\% &  3.6\% &  5.3\% &  6.5\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
com.google.javascript.jscomp.ControlFlowAnalysis &  1.1\% &  1.4\% &  20.4\% &  25.9\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
com.google.javascript.jscomp.ExploitAssigns &  0.0\% &  2.5\% &  22.3\% &  25.7\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
com.google.javascript.jscomp.PeepholeFoldConstants &  0.2\% &  0.2\% &  5.0\% &  6.5\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
com.google.javascript.jscomp.PeepholeSubstituteAlternateSyntax &  3.6\% &  4.7\% &  6.8\% &  9.6\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
com.google.javascript.jscomp.ReferenceCollectingCallback &  5.8\% &  9.0\% &  20.6\% &  26.3\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
com.google.javascript.jscomp.ScopedAliases &  0.0\% &  5.6\% &  11.3\% &  11.8\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
com.google.javascript.jscomp.parsing.JsDocInfoParser &  11.3\% &  12.4\% &  16.5\% &  24.6\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
com.google.javascript.rhino.jstype.RecordType &  0.0\% &  0.0\% &  63.7\% &  75.7\% &  0.0\% &  0.0\% &  16.7\% &  0.0\%\\ 
org.apache.commons.lang.ClassUtils &  61.3\% &  65.6\% &  67.7\% &  59.2\% &  100.0\% &  100.0\% &  100.0\% &  100.0\%\\ 
org.apache.commons.lang.LocaleUtils &  75.0\% &  70.8\% &  66.4\% &  70.1\% &  83.3\% &  100.0\% &  100.0\% &  100.0\%\\ 
org.apache.commons.lang.math.NumberUtils &  64.1\% &  65.9\% &  73.4\% &  77.7\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
org.apache.commons.lang.text.ExtendedMessageFormat &  32.0\% &  37.9\% &  41.6\% &  54.4\% &  100.0\% &  100.0\% &  100.0\% &  100.0\%\\ 
org.apache.commons.lang.text.StrBuilder &  66.6\% &  72.2\% &  78.3\% &  82.6\% &  33.3\% &  38.9\% &  55.6\% &  61.1\%\\ 
org.apache.commons.lang.time.DateUtils &  56.6\% &  81.3\% &  87.9\% &  93.6\% &  33.3\% &  16.7\% &  83.3\% &  100.0\%\\ 
org.apache.commons.lang.time.DurationFormatUtils &  78.8\% &  82.6\% &  80.2\% &  90.1\% &  0.0\% &  0.0\% &  0.0\% &  16.7\%\\ 
org.apache.commons.lang.time.FastDateFormat &  63.2\% &  43.4\% &  73.8\% &  73.0\% &  0.0\% &  0.0\% &  0.0\% &  16.7\%\\ 
org.apache.commons.lang3.ArrayUtils &  61.5\% &  66.5\% &  72.2\% &  75.1\% &  16.7\% &  0.0\% &  0.0\% &  33.3\%\\ 
org.apache.commons.lang3.ClassUtils &  60.9\% &  61.0\% &  66.7\% &  59.9\% &  100.0\% &  100.0\% &  100.0\% &  83.3\%\\ 
org.apache.commons.lang3.math.NumberUtils &  67.1\% &  70.8\% &  76.0\% &  80.0\% &  16.7\% &  0.0\% &  83.3\% &  83.3\%\\ 
org.apache.commons.lang3.text.translate.NumericEntityUnescaper &  6.2\% &  27.1\% &  51.0\% &  79.2\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
org.apache.commons.math.distribution.NormalDistributionImpl &  77.8\% &  77.8\% &  77.8\% &  77.8\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
org.apache.commons.math.fraction.Fraction &  94.1\% &  95.9\% &  97.4\% &  98.5\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
org.apache.commons.math.fraction.ProperFractionFormat &  46.5\% &  70.2\% &  76.3\% &  70.2\% &  0.0\% &  0.0\% &  16.7\% &  0.0\%\\ 
org.apache.commons.math.geometry.euclidean.threed.Rotation &  45.5\% &  59.0\% &  88.7\% &  91.5\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
org.apache.commons.math.ode.AbstractIntegrator &  49.6\% &  50.7\% &  58.3\% &  64.5\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
org.apache.commons.math.ode.nonstiff.EmbeddedRungeKuttaIntegrator &  39.2\% &  36.1\% &  69.1\% &  71.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
org.apache.commons.math.optimization.MultiStartUnivariateRealOptimizer &  81.9\% &  90.7\% &  86.8\% &  97.1\% &  100.0\% &  100.0\% &  100.0\% &  100.0\%\\ 
org.apache.commons.math.optimization.general.LevenbergMarquardtOptimizer &  22.7\% &  27.6\% &  55.0\% &  64.8\% &  0.0\% &  66.7\% &  66.7\% &  83.3\%\\ 
org.apache.commons.math.optimization.linear.SimplexTableau &  2.2\% &  74.8\% &  86.9\% &  96.1\% &  0.0\% &  0.0\% &  16.7\% &  0.0\%\\ 
org.apache.commons.math.util.MathUtils &  78.9\% &  80.4\% &  83.5\% &  85.9\% &  0.0\% &  16.7\% &  0.0\% &  16.7\%\\ 
org.apache.commons.math.util.MultidimensionalCounter &  94.3\% &  95.8\% &  98.4\% &  98.4\% &  16.7\% &  16.7\% &  83.3\% &  100.0\%\\ 
org.apache.commons.math3.distribution.HypergeometricDistribution &  96.8\% &  96.2\% &  98.7\% &  99.4\% &  0.0\% &  16.7\% &  0.0\% &  0.0\%\\ 
org.apache.commons.math3.linear.RectangularCholeskyDecomposition &  58.3\% &  70.2\% &  73.2\% &  91.1\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
org.apache.commons.math3.ode.AbstractIntegrator &  29.6\% &  39.4\% &  59.2\% &  63.8\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
org.apache.commons.math3.optimization.direct.CMAESOptimizer &  69.3\% &  72.0\% &  69.3\% &  71.3\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
org.jfree.chart.axis.Axis &  37.5\% &  56.9\% &  63.2\% &  57.1\% &  0.0\% &  0.0\% &  16.7\% &  0.0\%\\ 
org.jfree.chart.plot.MultiplePiePlot &  48.0\% &  53.4\% &  55.6\% &  45.8\% &  16.7\% &  16.7\% &  0.0\% &  0.0\%\\ 
org.jfree.chart.plot.ValueMarker &  87.5\% &  87.5\% &  87.5\% &  75.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
org.jfree.chart.plot.XYPlot &  29.5\% &  32.5\% &  41.6\% &  47.6\% &  16.7\% &  0.0\% &  100.0\% &  100.0\%\\ 
org.jfree.chart.renderer.GrayPaintScale &  100.0\% &  100.0\% &  100.0\% &  100.0\% &  100.0\% &  33.3\% &  50.0\% &  66.7\%\\ 
org.jfree.chart.renderer.category.AbstractCategoryItemRenderer &  22.6\% &  26.4\% &  39.9\% &  45.7\% &  0.0\% &  0.0\% &  16.7\% &  0.0\%\\ 
org.jfree.chart.renderer.category.MinMaxCategoryRenderer &  30.7\% &  36.6\% &  34.8\% &  26.2\% &  0.0\% &  83.3\% &  50.0\% &  66.7\%\\ 
org.jfree.chart.renderer.category.StatisticalBarRenderer &  8.3\% &  8.9\% &  10.0\% &  16.5\% &  0.0\% &  0.0\% &  50.0\% &  50.0\%\\ 
org.jfree.chart.util.ShapeList &  37.5\% &  49.0\% &  49.0\% &  50.0\% &  83.3\% &  100.0\% &  83.3\% &  100.0\%\\ 
org.jfree.chart.util.ShapeUtilities &  58.0\% &  82.8\% &  57.3\% &  76.6\% &  50.0\% &  100.0\% &  66.7\% &  83.3\%\\ 
org.jfree.data.category.DefaultIntervalCategoryDataset &  74.6\% &  78.1\% &  80.1\% &  85.0\% &  100.0\% &  100.0\% &  100.0\% &  100.0\%\\ 
org.jfree.data.general.DatasetUtilities &  0.0\% &  15.9\% &  62.2\% &  66.9\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
org.jfree.data.time.TimePeriodValues &  38.3\% &  89.2\% &  95.4\% &  98.5\% &  0.0\% &  16.7\% &  50.0\% &  66.7\%\\ 
org.jfree.data.time.TimeSeries &  57.6\% &  69.6\% &  79.3\% &  86.4\% &  33.3\% &  44.4\% &  44.4\% &  50.0\%\\ 
org.joda.time.DateTimeZone &  69.9\% &  71.6\% &  73.4\% &  77.6\% &  33.3\% &  50.0\% &  33.3\% &  50.0\%\\ 
org.joda.time.MutableDateTime &  79.6\% &  84.4\% &  90.5\% &  96.8\% &  100.0\% &  50.0\% &  33.3\% &  16.7\%\\ 
org.joda.time.Partial &  55.5\% &  61.0\% &  87.1\% &  93.6\% &  16.7\% &  0.0\% &  50.0\% &  33.3\%\\ 
org.joda.time.Period &  81.0\% &  84.4\% &  90.6\% &  93.2\% &  33.3\% &  50.0\% &  83.3\% &  100.0\%\\ 
org.joda.time.base.BaseSingleFieldPeriod &  87.3\% &  90.6\% &  86.6\% &  92.4\% &  0.0\% &  0.0\% &  16.7\% &  16.7\%\\ 
org.joda.time.format.DateTimeFormatter &  84.1\% &  80.3\% &  84.1\% &  87.5\% &  33.3\% &  16.7\% &  16.7\% &  0.0\%\\ 
org.joda.time.format.DateTimeFormatterBuilder &  25.3\% &  25.5\% &  52.6\% &  60.9\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
org.joda.time.format.PeriodFormatterBuilder &  29.0\% &  31.0\% &  44.6\% &  54.5\% &  0.0\% &  0.0\% &  0.0\% &  16.7\%\\ 
org.joda.time.tz.ZoneInfoCompiler &  25.9\% &  27.9\% &  40.2\% &  30.7\% &  100.0\% &  100.0\% &  100.0\% &  66.7\%\\ 
\bottomrule 
\end{tabular}

### 2016-02-21 papers/sbst16/r_files/analyze.R

@@ -1,0 +1,48 @@
+#tool,benchmark,class,run,preparationTime,generationTime,executionTime,testcaseNumber,
+#uncompilableNumber,brokenTests,failTests,linesTotal,linesCovered,linesCoverageRatio,
+#conditionsTotal,conditionsCovered,conditionsCoverageRatio,mutantsTotal,mutantsCovered,mutantsCoverageRatio,
+#mutantsKilled,mutantsKillRatio,mutantsAlive,timeBudget,totalTestClasses
+
+
+FILE = "../data/single_transcript.csv";
+
+mainTable <- function(){
+
+	dt <- read.csv(FILE,header=T)
+
+	TABLE = paste("../mainTable.tex",sep="")
+	unlink(TABLE)
+	sink(TABLE, append=TRUE, split=TRUE)
+
+	cat("\\begin{tabular}{ l rrrr rrrr}\\toprule","\n")
+	cat(" Class &  \\multicolumn{4}{c}{Branch Coverage}  &  \\multicolumn{4}{c}{Fault Detection} \\\\ \n")
+	cat(" & 60s & 120s & 240s & 480s & 60s & 120s & 240s & 480s \\\\ \n" )
+	cat("\\midrule","\n")
+
+	classes = sort(unique(dt$class))
+	times = sort(unique(dt$timeBudget))
+
+	for(class in classes){
+
+		mask = dt$tool=="evosuite" & dt$class==class
+
+		cat(class)
+
+		for(t in times){
+			cov = dt$conditionsCoverageRatio[mask & dt$timeBudget==t]
+			cat(" & ", paste(formatC(mean(cov),digits=1,format="f"),"\\%",sep=""))
+		}
+
+		for(t in times){
+			fails = dt$failTests[mask & dt$timeBudget==t]
+			ratio = sum(fails>0) / length(fails)
+			cat(" & ", paste(formatC(100*mean(ratio),digits=1,format="f"),"\\%",sep=""))
+		}
+		cat("\\\\ \n")
+	}
+
+	cat("\\bottomrule","\n")
+	cat("\\end{tabular}","\n")
+
+	sink()
+}

### 2016-02-21 papers/sbst16/coverageTable.tex
Update tables and paper

\begin{tabular}{ ll rrrr rrrr}\toprule 
 Defects4J ID & Class &  \multicolumn{4}{c}{Line Coverage}  &  \multicolumn{4}{c}{Branch Coverage} \\ 
 & & 60s & 120s & 240s & 480s & 60s & 120s & 240s & 480s \\ 
\midrule 
Chart-1 &  org.jfree.chart.renderer.category.AbstractCategoryItemRenderer &  34.5\% &  36.8\% &  51.0\% &  56.2\% &  22.6\% &  26.4\% &  39.9\% &  45.7\%\\ 
Chart-11 &  org.jfree.chart.util.ShapeUtilities &  81.0\% &  92.1\% &  62.1\% &  79.4\% &  58.0\% &  82.8\% &  57.3\% &  76.6\%\\ 
Chart-12 &  org.jfree.chart.plot.MultiplePiePlot &  54.2\% &  62.0\% &  64.9\% &  51.3\% &  48.0\% &  53.4\% &  55.6\% &  45.8\%\\ 
Chart-16 &  org.jfree.data.category.DefaultIntervalCategoryDataset &  81.8\% &  82.7\% &  85.2\% &  88.2\% &  74.6\% &  78.1\% &  80.1\% &  85.0\%\\ 
Chart-17 &  org.jfree.data.time.TimeSeries &  69.2\% &  83.0\% &  87.3\% &  89.5\% &  58.9\% &  74.3\% &  80.9\% &  84.5\%\\ 
Chart-2 &  org.jfree.data.general.DatasetUtilities &  0.0\% &  18.0\% &  67.2\% &  71.4\% &  0.0\% &  15.9\% &  62.2\% &  66.9\%\\ 
Chart-20 &  org.jfree.chart.plot.ValueMarker &  95.5\% &  95.5\% &  95.5\% &  80.3\% &  87.5\% &  87.5\% &  87.5\% &  75.0\%\\ 
Chart-23 &  org.jfree.chart.renderer.category.MinMaxCategoryRenderer &  41.6\% &  44.2\% &  43.1\% &  30.8\% &  30.7\% &  36.6\% &  34.8\% &  26.2\%\\ 
Chart-24 &  org.jfree.chart.renderer.GrayPaintScale &  100.0\% &  100.0\% &  100.0\% &  100.0\% &  100.0\% &  100.0\% &  100.0\% &  100.0\%\\ 
Chart-25 &  org.jfree.chart.renderer.category.StatisticalBarRenderer &  13.1\% &  13.4\% &  18.4\% &  26.8\% &  8.3\% &  8.9\% &  10.0\% &  16.5\%\\ 
Chart-26 &  org.jfree.chart.axis.Axis &  54.6\% &  63.7\% &  73.5\% &  65.7\% &  37.5\% &  56.9\% &  63.2\% &  57.1\%\\ 
Chart-3 &  org.jfree.data.time.TimeSeries &  77.5\% &  78.8\% &  90.3\% &  93.2\% &  60.5\% &  64.7\% &  81.4\% &  87.5\%\\ 
Chart-4 &  org.jfree.chart.plot.XYPlot &  45.5\% &  48.1\% &  55.9\% &  60.8\% &  29.5\% &  32.5\% &  41.6\% &  47.6\%\\ 
Chart-6 &  org.jfree.chart.util.ShapeList &  51.0\% &  54.9\% &  55.4\% &  55.4\% &  37.5\% &  49.0\% &  49.0\% &  50.0\%\\ 
Chart-7 &  org.jfree.data.time.TimePeriodValues &  58.6\% &  95.3\% &  97.0\% &  98.1\% &  38.3\% &  89.2\% &  95.4\% &  98.5\%\\ 
Chart-9 &  org.jfree.data.time.TimeSeries &  65.8\% &  79.8\% &  83.6\% &  92.3\% &  53.3\% &  69.8\% &  75.6\% &  87.0\%\\ 
Closure-100 &  com.google.javascript.jscomp.CheckGlobalThis &  24.4\% &  42.6\% &  40.7\% &  51.1\% &  3.6\% &  21.7\% &  21.1\% &  29.2\%\\ 
Closure-124 &  com.google.javascript.jscomp.ExploitAssigns &  9.5\% &  12.8\% &  36.7\% &  39.9\% &  0.0\% &  2.5\% &  22.3\% &  25.7\%\\ 
Closure-130 &  com.google.javascript.jscomp.CollapseProperties &  9.1\% &  11.3\% &  13.1\% &  15.4\% &  2.6\% &  3.6\% &  5.3\% &  6.5\%\\ 
Closure-132 &  com.google.javascript.jscomp.PeepholeSubstituteAlternateSyntax &  9.8\% &  13.4\% &  11.3\% &  14.1\% &  3.1\% &  4.8\% &  6.3\% &  8.4\%\\ 
Closure-14 &  com.google.javascript.jscomp.ControlFlowAnalysis &  9.4\% &  10.5\% &  31.9\% &  37.6\% &  1.1\% &  1.4\% &  20.4\% &  25.9\%\\ 
Closure-16 &  com.google.javascript.jscomp.ScopedAliases &  12.4\% &  18.3\% &  24.2\% &  24.2\% &  0.0\% &  5.6\% &  11.3\% &  11.8\%\\ 
Closure-20 &  com.google.javascript.jscomp.PeepholeSubstituteAlternateSyntax &  11.0\% &  12.8\% &  12.7\% &  17.9\% &  4.0\% &  4.7\% &  7.2\% &  10.8\%\\ 
Closure-46 &  com.google.javascript.rhino.jstype.RecordType &  2.3\% &  2.3\% &  75.6\% &  91.1\% &  0.0\% &  0.0\% &  63.7\% &  75.7\%\\ 
Closure-68 &  com.google.javascript.jscomp.parsing.JsDocInfoParser &  16.6\% &  17.4\% &  22.9\% &  33.5\% &  11.3\% &  12.4\% &  16.5\% &  24.6\%\\ 
Closure-74 &  com.google.javascript.jscomp.PeepholeFoldConstants &  5.6\% &  5.8\% &  8.9\% &  10.9\% &  0.2\% &  0.2\% &  5.0\% &  6.5\%\\ 
Closure-98 &  com.google.javascript.jscomp.ReferenceCollectingCallback &  29.2\% &  35.3\% &  57.3\% &  63.0\% &  5.8\% &  9.0\% &  20.6\% &  26.3\%\\ 
Closure-99 &  com.google.javascript.jscomp.CheckGlobalThis &  24.4\% &  43.3\% &  42.6\% &  48.5\% &  3.2\% &  20.2\% &  19.9\% &  23.9\%\\ 
Lang-28 &  org.apache.commons.lang3.text.translate.NumericEntityUnescaper &  12.0\% &  23.3\% &  47.3\% &  75.3\% &  6.2\% &  27.1\% &  51.0\% &  79.2\%\\ 
Lang-33 &  org.apache.commons.lang3.ClassUtils &  80.7\% &  81.9\% &  84.6\% &  77.0\% &  60.9\% &  61.0\% &  66.7\% &  59.9\%\\ 
Lang-36 &  org.apache.commons.lang3.math.NumberUtils &  83.9\% &  86.2\% &  90.3\% &  92.1\% &  67.1\% &  70.8\% &  76.0\% &  80.0\%\\ 
Lang-37 &  org.apache.commons.lang3.ArrayUtils &  78.6\% &  83.5\% &  88.1\% &  90.1\% &  61.5\% &  66.5\% &  72.2\% &  75.1\%\\ 
Lang-41 &  org.apache.commons.lang.ClassUtils &  81.4\% &  84.8\% &  86.1\% &  76.2\% &  61.3\% &  65.6\% &  67.7\% &  59.2\%\\ 
Lang-43 &  org.apache.commons.lang.text.ExtendedMessageFormat &  49.6\% &  54.1\% &  53.3\% &  62.9\% &  32.0\% &  37.9\% &  41.6\% &  54.4\%\\ 
Lang-47 &  org.apache.commons.lang.text.StrBuilder &  75.7\% &  82.0\% &  86.2\% &  90.6\% &  63.8\% &  72.3\% &  78.7\% &  84.6\%\\ 
Lang-50 &  org.apache.commons.lang.time.FastDateFormat &  80.4\% &  53.6\% &  85.1\% &  86.3\% &  63.2\% &  43.4\% &  73.8\% &  73.0\%\\ 
Lang-57 &  org.apache.commons.lang.LocaleUtils &  86.2\% &  86.4\% &  84.0\% &  85.7\% &  75.0\% &  70.8\% &  66.4\% &  70.1\%\\ 
Lang-58 &  org.apache.commons.lang.math.NumberUtils &  79.4\% &  82.3\% &  86.3\% &  89.8\% &  64.1\% &  65.9\% &  73.4\% &  77.7\%\\ 
Lang-59 &  org.apache.commons.lang.text.StrBuilder &  78.5\% &  79.9\% &  86.0\% &  89.3\% &  68.8\% &  71.4\% &  79.1\% &  82.0\%\\ 
Lang-60 &  org.apache.commons.lang.text.StrBuilder &  77.3\% &  80.9\% &  85.5\% &  88.6\% &  67.2\% &  72.9\% &  77.0\% &  81.3\%\\ 
Lang-63 &  org.apache.commons.lang.time.DurationFormatUtils &  81.1\% &  84.8\% &  82.6\% &  92.1\% &  78.8\% &  82.6\% &  80.2\% &  90.1\%\\ 
Lang-65 &  org.apache.commons.lang.time.DateUtils &  72.5\% &  89.3\% &  94.1\% &  97.5\% &  56.6\% &  81.3\% &  87.9\% &  93.6\%\\ 
Math-103 &  org.apache.commons.math.distribution.NormalDistributionImpl &  85.7\% &  85.7\% &  85.7\% &  85.7\% &  77.8\% &  77.8\% &  77.8\% &  77.8\%\\ 
Math-106 &  org.apache.commons.math.fraction.ProperFractionFormat &  63.5\% &  80.2\% &  85.4\% &  79.9\% &  46.5\% &  70.2\% &  76.3\% &  70.2\%\\ 
Math-18 &  org.apache.commons.math3.optimization.direct.CMAESOptimizer &  85.7\% &  86.1\% &  82.3\% &  84.2\% &  71.0\% &  72.2\% &  66.7\% &  69.6\%\\ 
Math-2 &  org.apache.commons.math3.distribution.HypergeometricDistribution &  98.5\% &  98.2\% &  99.7\% &  99.5\% &  96.8\% &  96.2\% &  98.7\% &  99.4\%\\ 
Math-20 &  org.apache.commons.math3.optimization.direct.CMAESOptimizer &  85.4\% &  87.3\% &  86.7\% &  87.3\% &  67.7\% &  71.8\% &  71.9\% &  72.9\%\\ 
Math-21 &  org.apache.commons.math3.linear.RectangularCholeskyDecomposition &  58.5\% &  69.7\% &  73.3\% &  91.5\% &  58.3\% &  70.2\% &  73.2\% &  91.1\%\\ 
Math-39 &  org.apache.commons.math.ode.nonstiff.EmbeddedRungeKuttaIntegrator &  74.4\% &  67.1\% &  89.5\% &  90.9\% &  39.2\% &  36.1\% &  69.1\% &  71.0\%\\ 
Math-44 &  org.apache.commons.math.ode.AbstractIntegrator &  63.1\% &  62.6\% &  68.2\% &  73.3\% &  49.6\% &  50.7\% &  58.3\% &  64.5\%\\ 
Math-52 &  org.apache.commons.math.geometry.euclidean.threed.Rotation &  72.9\% &  81.3\% &  97.0\% &  98.7\% &  45.5\% &  59.0\% &  88.7\% &  91.5\%\\ 
Math-56 &  org.apache.commons.math.util.MultidimensionalCounter &  97.9\% &  99.3\% &  99.8\% &  99.8\% &  94.3\% &  95.8\% &  98.4\% &  98.4\%\\ 
Math-64 &  org.apache.commons.math.optimization.general.LevenbergMarquardtOptimizer &  35.8\% &  40.9\% &  66.5\% &  76.9\% &  22.7\% &  27.6\% &  55.0\% &  64.8\%\\ 
Math-67 &  org.apache.commons.math.optimization.MultiStartUnivariateRealOptimizer &  87.6\% &  88.7\% &  86.9\% &  90.0\% &  81.9\% &  90.7\% &  86.8\% &  97.1\%\\ 
Math-7 &  org.apache.commons.math3.ode.AbstractIntegrator &  50.0\% &  58.9\% &  74.7\% &  77.6\% &  29.6\% &  39.4\% &  59.2\% &  63.8\%\\ 
Math-88 &  org.apache.commons.math.optimization.linear.SimplexTableau &  8.4\% &  84.0\% &  94.3\% &  96.1\% &  2.2\% &  74.8\% &  86.9\% &  96.1\%\\ 
Math-91 &  org.apache.commons.math.fraction.Fraction &  96.5\% &  97.2\% &  97.5\% &  97.9\% &  94.1\% &  95.9\% &  97.4\% &  98.5\%\\ 
Math-93 &  org.apache.commons.math.util.MathUtils &  81.6\% &  84.1\% &  86.0\% &  87.5\% &  78.9\% &  80.4\% &  83.5\% &  85.9\%\\ 
Time-10 &  org.joda.time.base.BaseSingleFieldPeriod &  91.4\% &  91.4\% &  88.6\% &  91.2\% &  87.3\% &  90.6\% &  86.6\% &  92.4\%\\ 
Time-11 &  org.joda.time.tz.ZoneInfoCompiler &  30.7\% &  32.5\% &  46.3\% &  34.0\% &  25.9\% &  27.9\% &  40.2\% &  30.7\%\\ 
Time-13 &  org.joda.time.format.PeriodFormatterBuilder &  49.8\% &  52.7\% &  65.5\% &  72.7\% &  29.0\% &  31.0\% &  44.6\% &  54.5\%\\ 
Time-20 &  org.joda.time.format.DateTimeFormatterBuilder &  35.3\% &  36.5\% &  68.5\% &  77.0\% &  25.3\% &  25.5\% &  52.6\% &  60.9\%\\ 
Time-23 &  org.joda.time.DateTimeZone &  83.6\% &  83.9\% &  84.0\% &  85.4\% &  71.5\% &  72.7\% &  73.9\% &  77.5\%\\ 
Time-3 &  org.joda.time.MutableDateTime &  87.4\% &  91.0\% &  93.6\% &  95.4\% &  79.6\% &  84.4\% &  90.5\% &  96.8\%\\ 
Time-4 &  org.joda.time.Partial &  72.5\% &  77.0\% &  93.5\% &  97.8\% &  55.5\% &  61.0\% &  87.1\% &  93.6\%\\ 
Time-5 &  org.joda.time.Period &  96.7\% &  97.3\% &  98.4\% &  98.9\% &  81.0\% &  84.4\% &  90.6\% &  93.2\%\\ 
Time-7 &  org.joda.time.format.DateTimeFormatter &  87.3\% &  86.8\% &  90.1\% &  91.7\% &  84.1\% &  80.3\% &  84.1\% &  87.5\%\\ 
Time-8 &  org.joda.time.DateTimeZone &  81.3\% &  81.4\% &  82.8\% &  84.8\% &  68.3\% &  70.4\% &  72.9\% &  77.7\%\\ 
\midrule 
Average &  &  58.3\% &  63.7\% &  71.1\% &  73.9\% &  46.6\% &  53.5\% &  61.7\% &  65.6\%\\ 
\bottomrule 
\end{tabular}

### 2016-02-21 papers/sbst16/faultTable.tex
Update tables and paper

\begin{tabular}{ ll rrrr rrrr}\toprule 
 Defects4J ID & Class &  \multicolumn{4}{c}{Mutation Score}  &  \multicolumn{4}{c}{Fault Detection} \\ 
 & & 60s & 120s & 240s & 480s & 60s & 120s & 240s & 480s \\ 
\midrule 
Chart-1 &  org.jfree.chart.renderer.category.AbstractCategoryItemRenderer &  11.3\% &  12.2\% &  17.4\% &  22.4\% &  0.0\% &  0.0\% &  16.7\% &  0.0\%\\ 
Chart-11 &  org.jfree.chart.util.ShapeUtilities &  13.4\% &  28.0\% &  18.9\% &  25.4\% &  50.0\% &  100.0\% &  66.7\% &  83.3\%\\ 
Chart-12 &  org.jfree.chart.plot.MultiplePiePlot &  10.8\% &  19.6\% &  20.3\% &  17.7\% &  16.7\% &  16.7\% &  0.0\% &  0.0\%\\ 
Chart-16 &  org.jfree.data.category.DefaultIntervalCategoryDataset &  47.3\% &  48.6\% &  52.7\% &  55.4\% &  100.0\% &  100.0\% &  100.0\% &  100.0\%\\ 
Chart-17 &  org.jfree.data.time.TimeSeries &  27.9\% &  32.7\% &  39.0\% &  42.4\% &  100.0\% &  100.0\% &  100.0\% &  100.0\%\\ 
Chart-2 &  org.jfree.data.general.DatasetUtilities &  0.0\% &  7.3\% &  43.4\% &  49.9\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
Chart-20 &  org.jfree.chart.plot.ValueMarker &  81.8\% &  81.8\% &  81.8\% &  69.7\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
Chart-23 &  org.jfree.chart.renderer.category.MinMaxCategoryRenderer &  3.4\% &  8.4\% &  6.9\% &  6.3\% &  0.0\% &  83.3\% &  50.0\% &  66.7\%\\ 
Chart-24 &  org.jfree.chart.renderer.GrayPaintScale &  91.9\% &  65.3\% &  73.4\% &  82.9\% &  100.0\% &  33.3\% &  50.0\% &  66.7\%\\ 
Chart-25 &  org.jfree.chart.renderer.category.StatisticalBarRenderer &  0.3\% &  1.9\% &  2.4\% &  2.3\% &  0.0\% &  0.0\% &  50.0\% &  50.0\%\\ 
Chart-26 &  org.jfree.chart.axis.Axis &  5.7\% &  17.1\% &  19.8\% &  17.5\% &  0.0\% &  0.0\% &  16.7\% &  0.0\%\\ 
Chart-3 &  org.jfree.data.time.TimeSeries &  28.0\% &  33.8\% &  44.9\% &  47.8\% &  0.0\% &  16.7\% &  33.3\% &  50.0\%\\ 
Chart-4 &  org.jfree.chart.plot.XYPlot &  17.3\% &  17.2\% &  19.8\% &  36.6\% &  16.7\% &  0.0\% &  100.0\% &  100.0\%\\ 
Chart-6 &  org.jfree.chart.util.ShapeList &  15.5\% &  23.8\% &  19.0\% &  20.2\% &  83.3\% &  100.0\% &  83.3\% &  100.0\%\\ 
Chart-7 &  org.jfree.data.time.TimePeriodValues &  21.7\% &  63.9\% &  67.3\% &  61.2\% &  0.0\% &  16.7\% &  50.0\% &  66.7\%\\ 
Chart-9 &  org.jfree.data.time.TimeSeries &  23.0\% &  31.5\% &  36.2\% &  44.1\% &  0.0\% &  16.7\% &  0.0\% &  0.0\%\\ 
Closure-100 &  com.google.javascript.jscomp.CheckGlobalThis &  8.2\% &  18.2\% &  20.6\% &  23.6\% &  0.0\% &  0.0\% &  0.0\% &  16.7\%\\ 
Closure-124 &  com.google.javascript.jscomp.ExploitAssigns &  1.4\% &  2.5\% &  15.1\% &  16.9\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
Closure-130 &  com.google.javascript.jscomp.CollapseProperties &  0.0\% &  0.4\% &  0.7\% &  1.3\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
Closure-132 &  com.google.javascript.jscomp.PeepholeSubstituteAlternateSyntax &  3.5\% &  8.8\% &  7.4\% &  13.7\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
Closure-14 &  com.google.javascript.jscomp.ControlFlowAnalysis &  2.7\% &  3.6\% &  20.0\% &  26.3\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
Closure-16 &  com.google.javascript.jscomp.ScopedAliases &  0.0\% &  4.0\% &  5.6\% &  4.4\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
Closure-20 &  com.google.javascript.jscomp.PeepholeSubstituteAlternateSyntax &  3.9\% &  8.5\% &  10.0\% &  13.4\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
Closure-46 &  com.google.javascript.rhino.jstype.RecordType &  0.0\% &  0.0\% &  37.4\% &  43.1\% &  0.0\% &  0.0\% &  16.7\% &  0.0\%\\ 
Closure-68 &  com.google.javascript.jscomp.parsing.JsDocInfoParser &  3.7\% &  4.4\% &  9.3\% &  13.5\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
Closure-74 &  com.google.javascript.jscomp.PeepholeFoldConstants &  1.9\% &  2.0\% &  2.5\% &  3.2\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
Closure-98 &  com.google.javascript.jscomp.ReferenceCollectingCallback &  8.3\% &  9.1\% &  22.4\% &  27.6\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
Closure-99 &  com.google.javascript.jscomp.CheckGlobalThis &  7.0\% &  17.0\% &  18.2\% &  21.1\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
Lang-28 &  org.apache.commons.lang3.text.translate.NumericEntityUnescaper &  8.3\% &  17.7\% &  24.2\% &  49.8\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
Lang-33 &  org.apache.commons.lang3.ClassUtils &  36.2\% &  39.4\% &  43.7\% &  38.1\% &  100.0\% &  100.0\% &  100.0\% &  83.3\%\\ 
Lang-36 &  org.apache.commons.lang3.math.NumberUtils &  27.1\% &  36.2\% &  38.7\% &  41.8\% &  16.7\% &  0.0\% &  83.3\% &  83.3\%\\ 
Lang-37 &  org.apache.commons.lang3.ArrayUtils &  24.4\% &  35.0\% &  56.6\% &  58.2\% &  16.7\% &  0.0\% &  0.0\% &  33.3\%\\ 
Lang-41 &  org.apache.commons.lang.ClassUtils &  39.1\% &  44.2\% &  46.5\% &  36.8\% &  100.0\% &  100.0\% &  100.0\% &  100.0\%\\ 
Lang-43 &  org.apache.commons.lang.text.ExtendedMessageFormat &  12.4\% &  16.6\% &  19.4\% &  25.8\% &  100.0\% &  100.0\% &  100.0\% &  100.0\%\\ 
Lang-47 &  org.apache.commons.lang.text.StrBuilder &  23.2\% &  32.2\% &  44.0\% &  54.6\% &  66.7\% &  66.7\% &  66.7\% &  83.3\%\\ 
Lang-50 &  org.apache.commons.lang.time.FastDateFormat &  19.2\% &  22.9\% &  50.8\% &  56.5\% &  0.0\% &  0.0\% &  0.0\% &  16.7\%\\ 
Lang-57 &  org.apache.commons.lang.LocaleUtils &  40.5\% &  39.2\% &  37.7\% &  38.4\% &  83.3\% &  100.0\% &  100.0\% &  100.0\%\\ 
Lang-58 &  org.apache.commons.lang.math.NumberUtils &  21.1\% &  33.3\% &  37.6\% &  42.5\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
Lang-59 &  org.apache.commons.lang.text.StrBuilder &  25.3\% &  31.1\% &  44.8\% &  49.9\% &  16.7\% &  33.3\% &  83.3\% &  66.7\%\\ 
Lang-60 &  org.apache.commons.lang.text.StrBuilder &  23.8\% &  34.0\% &  44.9\% &  48.6\% &  16.7\% &  16.7\% &  16.7\% &  33.3\%\\ 
Lang-63 &  org.apache.commons.lang.time.DurationFormatUtils &  13.6\% &  20.4\% &  20.8\% &  25.5\% &  0.0\% &  0.0\% &  0.0\% &  16.7\%\\ 
Lang-65 &  org.apache.commons.lang.time.DateUtils &  28.1\% &  35.7\% &  51.9\% &  55.3\% &  33.3\% &  16.7\% &  83.3\% &  100.0\%\\ 
Math-103 &  org.apache.commons.math.distribution.NormalDistributionImpl &  63.0\% &  62.8\% &  63.7\% &  63.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
Math-106 &  org.apache.commons.math.fraction.ProperFractionFormat &  25.0\% &  32.2\% &  40.9\% &  35.1\% &  0.0\% &  0.0\% &  16.7\% &  0.0\%\\ 
Math-18 &  org.apache.commons.math3.optimization.direct.CMAESOptimizer &  29.9\% &  29.0\% &  26.5\% &  26.5\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
Math-2 &  org.apache.commons.math3.distribution.HypergeometricDistribution &  39.3\% &  84.8\% &  89.5\% &  90.8\% &  0.0\% &  16.7\% &  0.0\% &  0.0\%\\ 
Math-20 &  org.apache.commons.math3.optimization.direct.CMAESOptimizer &  33.1\% &  35.9\% &  28.7\% &  27.3\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
Math-21 &  org.apache.commons.math3.linear.RectangularCholeskyDecomposition &  23.7\% &  32.5\% &  28.1\% &  44.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
Math-39 &  org.apache.commons.math.ode.nonstiff.EmbeddedRungeKuttaIntegrator &  20.7\% &  17.2\% &  30.3\% &  35.6\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
Math-44 &  org.apache.commons.math.ode.AbstractIntegrator &  35.0\% &  32.6\% &  35.0\% &  41.4\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
Math-52 &  org.apache.commons.math.geometry.euclidean.threed.Rotation &  52.8\% &  58.8\% &  79.5\% &  82.8\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
Math-56 &  org.apache.commons.math.util.MultidimensionalCounter &  48.8\% &  56.2\% &  74.3\% &  74.4\% &  16.7\% &  16.7\% &  83.3\% &  100.0\%\\ 
Math-64 &  org.apache.commons.math.optimization.general.LevenbergMarquardtOptimizer &  5.7\% &  5.9\% &  16.4\% &  24.0\% &  0.0\% &  66.7\% &  66.7\% &  83.3\%\\ 
Math-67 &  org.apache.commons.math.optimization.MultiStartUnivariateRealOptimizer &  36.2\% &  52.2\% &  47.4\% &  59.4\% &  100.0\% &  100.0\% &  100.0\% &  100.0\%\\ 
Math-7 &  org.apache.commons.math3.ode.AbstractIntegrator &  26.2\% &  32.5\% &  33.1\% &  31.5\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
Math-88 &  org.apache.commons.math.optimization.linear.SimplexTableau &  0.5\% &  41.6\% &  52.8\% &  57.1\% &  0.0\% &  0.0\% &  16.7\% &  0.0\%\\ 
Math-91 &  org.apache.commons.math.fraction.Fraction &  58.7\% &  69.1\% &  70.8\% &  70.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
Math-93 &  org.apache.commons.math.util.MathUtils &  24.6\% &  46.0\% &  65.7\% &  68.8\% &  0.0\% &  16.7\% &  0.0\% &  16.7\%\\ 
Time-10 &  org.joda.time.base.BaseSingleFieldPeriod &  46.3\% &  63.3\% &  59.6\% &  63.4\% &  0.0\% &  0.0\% &  16.7\% &  16.7\%\\ 
Time-11 &  org.joda.time.tz.ZoneInfoCompiler &  11.4\% &  15.7\% &  19.4\% &  14.6\% &  100.0\% &  100.0\% &  100.0\% &  66.7\%\\ 
Time-13 &  org.joda.time.format.PeriodFormatterBuilder &  11.9\% &  16.8\% &  25.1\% &  30.9\% &  0.0\% &  0.0\% &  0.0\% &  16.7\%\\ 
Time-20 &  org.joda.time.format.DateTimeFormatterBuilder &  9.3\% &  11.2\% &  27.7\% &  39.4\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
Time-23 &  org.joda.time.DateTimeZone &  40.4\% &  49.3\% &  50.2\% &  51.7\% &  0.0\% &  16.7\% &  0.0\% &  0.0\%\\ 
Time-3 &  org.joda.time.MutableDateTime &  35.4\% &  47.6\% &  55.9\% &  57.6\% &  100.0\% &  50.0\% &  33.3\% &  16.7\%\\ 
Time-4 &  org.joda.time.Partial &  29.6\% &  38.7\% &  67.9\% &  73.9\% &  16.7\% &  0.0\% &  50.0\% &  33.3\%\\ 
Time-5 &  org.joda.time.Period &  25.1\% &  45.1\% &  73.4\% &  82.2\% &  33.3\% &  50.0\% &  83.3\% &  100.0\%\\ 
Time-7 &  org.joda.time.format.DateTimeFormatter &  39.6\% &  46.1\% &  54.6\% &  59.3\% &  33.3\% &  16.7\% &  16.7\% &  0.0\%\\ 
Time-8 &  org.joda.time.DateTimeZone &  33.8\% &  47.6\% &  51.6\% &  53.8\% &  66.7\% &  83.3\% &  66.7\% &  100.0\%\\ 
\midrule 
Average &  &  23.4\% &  30.6\% &  37.7\% &  41.0\% &  21.8\% &  24.3\% &  31.1\% &  33.3\%\\ 
\bottomrule 
\end{tabular}

### 2016-02-21 papers/sbst16/paper_sbst16.tex
added table
luxembourg grant ack
Update tables and paper

@@
 
+% \begin{table*}[t]
+%   \centering
+%   \caption{\label{table:results}Detailed results of \EVOSUITE on the SBST benchmark classes.}
+% \resizebox{0.9\textwidth}{!}{  
+% \input{mainTable.tex}
+% }	
+% \end{table*}
+
 \begin{table*}[t]
   \centering
-  \caption{\label{table:results}Detailed results of \EVOSUITE on the SBST benchmark classes. Time is expressed in minutes.}
-  %\scriptsize
+  \caption{\label{table:coverage_results}Detailed coverage results of \EVOSUITE on the SBST benchmark classes.}
 \resizebox{0.9\textwidth}{!}{  
-  \begin{tabular}{l rrrrrr} \toprule
-Class &  JUnit Files &   Generation Time & Execution Time   & \% Line Coverage & \% Branch Coverage & \% Mutation Score \\  
-\midrule
-%\input{results.tex}
-\midrule
-%Average & & 6.19 & 0.03 & 55.36 & 47.19 & 41.02\\
-\bottomrule
-  \end{tabular}
+\input{coverageTable.tex}
 }
@@
 
-The results of \EVOSUITE on the benchmark classes are listed in
-Table~\ref{table:results}. On average, \EVOSUITE achieved []\% line
-coverage, []\% branch coverage\footnote{Using Cobertura's definition
-  of branch coverage, which only counts conditional statements, not
-  edges in the CFG.}, and []\% mutation score.
+\begin{table*}[t]
+  \centering
+  \caption{\label{table:fault_results}Detailed fault detection results of \EVOSUITE on the SBST benchmark classes.}
+\resizebox{0.9\textwidth}{!}{  
+\input{faultTable.tex}
+}	
+\end{table*}
 
-\subsection{Issues Encountered}
+The coverage results (line coverage and branch coverage) achieved by
+\EVOSUITE on the benchmark classes are listed in
+Table~\ref{table:coverage_results}. Coverage is generally in the
+expected range, with clear increases for higher time budgets. Coverage
+on several of the benchmarks from Closure is low, which matches
+previous findings~\cite{shamshiri2015automatically}.
 
-Following recent experiments on
-Defects4J~\cite{shamshiri2015automatically} that revealed general
-issues in unit test generation, \EVOSUITE now includes assertions on
-the source of exceptions, similar to commercial tools like Agitar
-One~\cite{agitarone}. However, there were several instances in the
-competition where these assertions lead to flaky tests. For example,
-the following is an excerpt from a test for the Defects4J bug Lang-41,
-generated by \EVOSUITE:
+Results in terms of mutation scores and fault detection ratio (i.e.,
+how many of the runs had at least one failing test on the
+corresponding bug) are showing in
+Table~\ref{table:fault_results}. Again the Closure results are
+generally worse than those of other projects, both in terms of
+mutation score and ratio of fault detection.
+
+On average, \EVOSUITE generated 0.14 flaky tests per run, a value that
+is significantly lower than that of any of the competing tools. This
+is due to extensive efforts to isolate \EVOSUITE tests from the
+execution environment~\cite{arcuri2014automated}. A few of these flaky
+tests were introduced by recent changes to \EVOSUITE following
+experiments on Defects4J~\cite{shamshiri2015automatically}: \EVOSUITE
+now includes assertions on the source of exceptions, similar to
+commercial tools like Agitar One~\cite{agitarone}. Unfortunately,
+there were several instances in the competition where these assertions
+lead to flaky tests. For example, the following is an excerpt from a
+test for the Defects4J bug Lang-41, generated by \EVOSUITE:
 
@@
 
+There are 15 runs in total where \EVOSUITE did not produce any test
+suites; these are only for higher time budgets (240s, 480s). The
+majority of these runs are due to \EVOSUITE not terminating before the
+hard timeout of the competition infrastructure. This may happen, for
+example, when test execution on the class under test takes long (e.g.,
+timeouts), and when resetting the static state of the classes under
+test takes a long time. However, this number is still lower than the
+number of erroneous runs compared to other tools, and in the remaining
+1617 runs of the competition \EVOSUITE terminated in time and produced
+at least two tests. In 13 of these, \EVOSUITE produced a test suite
+with a compile error.
+
 %------------------------------------------------------------------------- 
@@
 
-With an overall score of [], \EVOSUITE achieved the []
- score of all tools in the competition.
+With an overall score of 1126.7, \EVOSUITE achieved the highest score
+of all tools in the competition.
 
@@
 Many thanks to all the contributors to \EVOSUITE.
+This project has been funded by 
+%the EPSRC project ``EXOGEN'' (EP/K030353/1), a Google Focused Research Award on ``Test
+%Amplification'', and by 
+the National Research Fund, Luxembourg (FNR/P10/03).
 

### 2016-02-22 papers/sbst16/paper_sbst16.tex
minor

@@
   results and experiences of \EVOSUITE's participation at the fourth
-  unit testing competition at SBST 2016. 
+  unit testing competition at SBST 2016, where \EVOSUITE achieved the
+  highest overall score. 
 \end{abstract}
@@
 Testing (SBST) 2016.  Details about the competition and the benchmark
-can be found in []. 
-In this competition, \EVOSUITE ranked [] with a score of [].
+can be found in [TODO]. 
+In this competition, \EVOSUITE achieved a 1126.7 overall score, which was the highest among
+the competing tools.
 
@@
 first~\cite{evosuiteAtSbst2013,evosuiteAtFittest2013}, whereas it
-ranked second in the third one [].
+ranked second in the third one.
 
@@
 metric, and many of the improvements to \EVOSUITE since the last
-competition target flaky tests we deemed this not a problem.
+competition target flaky tests, we deemed this not a problem.
 
@@
 at least two tests. In 13 of these, \EVOSUITE produced a test suite
-with a compile error.
+with a compilation error.
 

### 2016-02-22 papers/sbst16/paper_sbst16.tex
last pass

@@
 Testing (SBST) 2016.  Details about the competition and the benchmark
-can be found in [TODO]. 
+can be found in~\cite{sbst16competition}. 
 In this competition, \EVOSUITE achieved a 1126.7 overall score, which was the highest among
@@
 now includes assertions on the source of exceptions, similar to
-commercial tools like Agitar One~\cite{agitarone}. Unfortunately,
-there were several instances in the competition where these assertions
+commercial tools like Agitar One. %~\cite{agitarone}. 
+Unfortunately, there were several instances in the competition where these assertions
 lead to flaky tests. For example, the following is an excerpt from a
@@
 %\noindent
-\textbf{Acknowledgments.}
-
-Many thanks to all the contributors to \EVOSUITE.
+\textbf{Acknowledgments:} Many thanks to all the contributors to \EVOSUITE.
 This project has been funded by 

### 2016-02-29 papers/sbst16/paper_sbst16.tex
Update
ACM format for CR

@@
 %\documentclass[10pt, conference, compsocconf]{IEEEtran}
-\documentclass[10pt,conference,compsocconf]{IEEEtran}
+%\documentclass[10pt,conference,compsocconf]{IEEEtran}
+\documentclass{sig-alternate}
 
@@
 \usepackage{subfigure}
-\usepackage{hyperref}
+%\usepackage{hyperref}
 \usepackage{color}
 \usepackage[usenames,dvipsnames,table]{xcolor}
-\usepackage{soul}
+%\usepackage{soul}
 \usepackage{xspace}
@@
 \usepackage{amsmath}
+\usepackage{balance}
 
@@
     backgroundcolor=\color{lightgrey},
-    basicstyle=\footnotesize\ttfamily,
+    basicstyle=\scriptsize\ttfamily,
     keywordstyle=\footnotesize\bfseries,
@@
 
-\hypersetup{
-colorlinks=true,
-urlcolor=rltblue,
-linkcolor=rltred,
-citecolor=rltgreen,
-bookmarksnumbered=true,
-pdftitle={EvoSuite at the SBST 2016 Tool Competition},
-pdfauthor={Gordon Fraser and Andrea Arcuri},
-pdfsubject={Test case generation},
-pdfkeywords={Test case generation, unit testing, test
-  oracles, assertions, search based testing}
-}
+% \hypersetup{
+% colorlinks=true,
+% urlcolor=rltblue,
+% linkcolor=rltred,
+% citecolor=rltgreen,
+% bookmarksnumbered=true,
+% pdftitle={EvoSuite at the SBST 2016 Tool Competition},
+% pdfauthor={Gordon Fraser and Andrea Arcuri},
+% pdfsubject={Test case generation},
+% pdfkeywords={Test case generation, unit testing, test
+%   oracles, assertions, search based testing}
+% }
 
@@
 
+\CopyrightYear{2016} 
+\setcopyright{rightsretained} 
+\conferenceinfo{ICSE '16}{May 16-17 2016, Austin, TX, USA} 
+\isbn{978-1-4503-4166-0/16/05}
+\doi{http://dx.doi.org/10.1145/2897010.2897020}
+
 %------------------------------------------------------------------------- 
@@
 
+%
+
 %\title{Unit Testing Tool competition: Results for EvoSuite}
@@
 
+\numberofauthors{2}
 \author{
-\IEEEauthorblockN{Gordon Fraser}
-\IEEEauthorblockA{University of Sheffield\\
-Sheffield, UK}\\
-%gordon.fraser@sheffield.ac.uk}\\
-\and
-\IEEEauthorblockN{Andrea Arcuri}
-\IEEEauthorblockA{Scienta, Norway\\
-and University of Luxembourg}\\
-%arcuri@simula.no}
-%\and
-%\IEEEauthorblockN{Jeremias R\"{o}{\ss}ler}
-%\IEEEauthorblockA{Saarland University -- Computer Science\\
-%Saarbr\"ucken, Germany\\
-%roessler@cs.uni-saarland.de}
+\alignauthor
+Gordon Fraser\\
+       \affaddr{University of Sheffield}\\
+%       \affaddr{Dep. of Computer Science}\\
+       \affaddr{Sheffield, UK}
+\alignauthor
+ Andrea Arcuri \\
+       \affaddr{Scienta, Norway}\\
+       \affaddr{and University of Luxembourg}\\
+%      \affaddr{P.O. Box 134, 1325 Lysaker, Norway}\\
+%       \email{arcuri@simula.no}
 }
@@
 
-\begin{IEEEkeywords}
-  test case generation; search-based testing; testing classes;
-  search-based software engineering
-\end{IEEEkeywords}
+\begin{CCSXML}
+<ccs2012>
+<concept>
+<concept_id>10011007.10011074.10011099.10011102.10011103</concept_id>
+<concept_desc>Software and its engineering~Software testing and debugging</concept_desc>
+<concept_significance>500</concept_significance>
+</concept>
+<concept>
+<concept_id>10011007.10011074.10011784</concept_id>
+<concept_desc>Software and its engineering~Search-based software engineering</concept_desc>
+<concept_significance>500</concept_significance>
+</concept>
+<concept>
+<concept_id>10011007.10011006.10011073</concept_id>
+<concept_desc>Software and its engineering~Software maintenance tools</concept_desc>
+<concept_significance>300</concept_significance>
+</concept>
+</ccs2012>
+\end{CCSXML}
+
+\ccsdesc[500]{Software and its engineering~Software testing and debugging}
+\ccsdesc[500]{Software and its engineering~Search-based software engineering}
+
+%
+%  Use this command to print the description
+%
+\printccsdesc
+
+\keywords{test case generation; search-based testing; testing classes;
+  search-based software engineering}
 
@@
 %------------------------------------------------------------------------- 
-\section{About \EVOSUITE}
+\section{About EvoSuite}
 
@@
 \renewcommand{\arraystretch}{1.3}
-\caption{Classification of the \EVOSUITE unit test generation tool.}\label{tool-description}
+\caption{Classification of the \EVOSUITE unit test generation
+  tool.}\label{tool-description}
+\resizebox{1.0\columnwidth}{!}{  
 \begin{tabular}{|l|p{5cm}|}
@@
 \end{tabular}\vspace{-1em}
+}
 \end{table}
@@
 and broken code contracts~\cite{emse13_oracle}.  For more details on
-the tool and its abilities we refer to~\cite{FrA11c}, and for more
-implementation details we refer to~\cite{FrA13a}.
+the tool and its abilities we refer to~\cite{FrA11c,FrA13a}.
 
@@
   \caption{\label{table:coverage_results}Detailed coverage results of \EVOSUITE on the SBST benchmark classes.}
-\resizebox{0.9\textwidth}{!}{  
+\resizebox{0.8\textwidth}{!}{  
 \input{coverageTable.tex}
@@
   \caption{\label{table:fault_results}Detailed fault detection results of \EVOSUITE on the SBST benchmark classes.}
-\resizebox{0.9\textwidth}{!}{  
+\resizebox{0.8\textwidth}{!}{  
 \input{faultTable.tex}
@@
 test for the Defects4J bug Lang-41, generated by \EVOSUITE:
+\vspace{1em}
 
@@
 %\def\IEEEbibitemsep{5pt plus 1pt}
-\def\IEEEbibitemsep{6pt}
+%\def\IEEEbibitemsep{6pt}
 
@@
 \bibliography{papers}
+\balance
 

### 2017-02-17 papers/sbst17/paper_sbst17.tex
SBST17 draft

--- 2016-02-29 papers/sbst16/paper_sbst16.tex
@@
 %\documentclass[10pt,conference,compsocconf]{IEEEtran}
-\documentclass{sig-alternate}
+\documentclass[10pt,conference]{IEEEtran}
 
@@
 
-\CopyrightYear{2016} 
-\setcopyright{rightsretained} 
-\conferenceinfo{ICSE '16}{May 16-17 2016, Austin, TX, USA} 
-\isbn{978-1-4503-4166-0/16/05}
-\doi{http://dx.doi.org/10.1145/2897010.2897020}
-
 %------------------------------------------------------------------------- 
@@
 %\title{Unit Testing Tool competition: Results for EvoSuite}
-\title{EvoSuite at the SBST 2016 Tool Competition}
+\title{EvoSuite at the SBST 2017 Tool Competition}
 
-\numberofauthors{2}
-\author{
-\alignauthor
-Gordon Fraser\\
-       \affaddr{University of Sheffield}\\
-%       \affaddr{Dep. of Computer Science}\\
-       \affaddr{Sheffield, UK}
-\alignauthor
- Andrea Arcuri \\
-       \affaddr{Scienta, Norway}\\
-       \affaddr{and University of Luxembourg}\\
-%      \affaddr{P.O. Box 134, 1325 Lysaker, Norway}\\
-%       \email{arcuri@simula.no}
-}
+\author{\IEEEauthorblockN{Authors}}
 
@@
 \end{abstract}
-
-\begin{CCSXML}
-<ccs2012>
-<concept>
-<concept_id>10011007.10011074.10011099.10011102.10011103</concept_id>
-<concept_desc>Software and its engineering~Software testing and debugging</concept_desc>
-<concept_significance>500</concept_significance>
-</concept>
-<concept>
-<concept_id>10011007.10011074.10011784</concept_id>
-<concept_desc>Software and its engineering~Search-based software engineering</concept_desc>
-<concept_significance>500</concept_significance>
-</concept>
-<concept>
-<concept_id>10011007.10011006.10011073</concept_id>
-<concept_desc>Software and its engineering~Software maintenance tools</concept_desc>
-<concept_significance>300</concept_significance>
-</concept>
-</ccs2012>
-\end{CCSXML}
-
-\ccsdesc[500]{Software and its engineering~Software testing and debugging}
-\ccsdesc[500]{Software and its engineering~Search-based software engineering}
-
-%
-%  Use this command to print the description
-%
-\printccsdesc
-
-\keywords{test case generation; search-based testing; testing classes;
-  search-based software engineering}
 
@@
 \resizebox{0.8\textwidth}{!}{  
-\input{coverageTable.tex}
+%\input{coverageTable.tex}
 }
@@
 \resizebox{0.8\textwidth}{!}{  
-\input{faultTable.tex}
+%\input{faultTable.tex}
 }	
@@
 \end{document}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% End:

### 2017-02-18 papers/sbst17/paper_sbst17.tex
Update for SBST17

@@
 \begin{abstract}
-  \EVOSUITE is a search-based tool that automatically
-  generates unit tests for Java code.  This paper summarizes the
-  results and experiences of \EVOSUITE's participation at the fourth
-  unit testing competition at SBST 2016, where \EVOSUITE achieved the
-  highest overall score. 
+  \EVOSUITE is a search-based tool that automatically generates unit
+  tests for Java code.  This paper summarizes the results and
+  experiences of \EVOSUITE's participation at the fifth unit testing
+  competition at SBST 2017, where \EVOSUITE achieved the highest
+  overall score.
 \end{abstract}
@@
 \section{Introduction}
-
-This paper describes the results of applying the \EVOSUITE test
-generation tool~\cite{FrA11c} to the benchmark used in the tool
+The annual unit test generation competition aims to drive and evaluate
+progress on unit test generation tools. In the 5th instance of the
 competition at the International Workshop on Search-Based Software
-Testing (SBST) 2016.  Details about the competition and the benchmark
-can be found in~\cite{sbst16competition}. 
-In this competition, \EVOSUITE achieved a 1126.7 overall score, which was the highest among
-the competing tools.
+Testing (SBST) 2017, four tools competed on a set of open source Java
+classes. This paper describes the results of applying the \EVOSUITE
+test generation tool~\cite{FrA11c} in this competition. Details about
+the procedure of the competition, the technical framework, and the
+benchmark classes can be found in~\cite{sbst17competition}.  In this
+competition, \EVOSUITE achieved a 1457.3 overall score, which was the
+highest among the competing tools.
 

### 2017-02-18 papers/sbst17/paper_sbst17.tex
Some text describing setup

@@
 \hline
-Output&  JUnit test cases (version 3 or 4)\\
+Output&  JUnit 4 test cases\\
 
@@
 
-\EVOSUITE~\cite{FrA11c,GoA_TSE12} automatically generates test suites
-for Java classes, targeting branch coverage and other coverage
-criteria (e.g., mutation testing~\cite{emse14_mutation}). \EVOSUITE
-works at the Java bytecode level, i.e., it does not require source
-code. It is fully automated and requires no manually written test
-drivers or parameterized unit tests.  For example, when \EVOSUITE is
-used from its Eclipse and IntelliJ plugins, a user
-just needs to select a class, and tests are generated with a mouse-click.
+\EVOSUITE~\cite{FrA11c} is a search-based tool~\cite{GoA_TSE12} that
+uses a genetic algorithm to automatically generate test suites for
+Java classes. Given the name of a target class and the full Java
+classpath (i.e., where to find the compiled bytecode of the class
+under test and all its dependencies), \EVOSUITE automatically produces
+a set of JUnit test cases that maximise the achieved code
+coverage. \EVOSUITE can be used on the command line, or through
+plugins for popular development tools such as IntelliJ, Eclipse, or Maven~\cite{ICST16_Tool}.
 
-\EVOSUITE has been evaluated on millions of lines of Java
-code~\cite{fraser2014large}, both open-source code and close-source
-code provided by one of our industrial partners.  In the first two
-editions of the unit testing tool competition, \EVOSUITE ranked
-first~\cite{evosuiteAtSbst2013,evosuiteAtFittest2013}, whereas it
-ranked second in the third one.
+The underlying genetic algorithm uses test suites as representation
+(chromosomes). Each test suite consists of a variable number of test
+cases, each of which is represented as a variable length sequence of
+Java statements (e.g., calls on the class under test). A population of
+randomly generated individuals is evolved using suitable search
+operators (e.g., selection, crossover and mutation), such that
+iteratively better solutions with respect to the optimisation target
+are produced. The optimisation target is to maximise code coverage. To
+achieve this, the fitness function uses standard heuristics such as
+the branch distance; see~\cite{GoA_TSE12} for more details. \EVOSUITE
+can be configured to optimise for multiple coverage criteria at the
+same time, and the default configuration combines branch coverage with
+mutation testing~\cite{emse14_mutation} and other basic
+criteria~\cite{rojas2015combining}. Once the search is completed,
+\EVOSUITE applies various optimisations to improve the readability of
+the generated tests. For example, tests are minimised, and a
+minimised set of effective test assertions is selected using mutation
+analysis~\cite{10.1109/TSE.2011.93}. For more details on the tool and
+its abilities we refer to~\cite{FrA11c,FrA13a}.
 
-\EVOSUITE uses an evolutionary approach to derive these test suites: A
-genetic algorithm evolves candidate individuals (chromosomes) using
-operators inspired by natural evolution (e.g., selection, crossover
-and mutation), such that iteratively better solutions with respect to
-the optimization target (e.g., branch coverage) are produced.  For
-details on this test generation approach we refer to~\cite{GoA_TSE12}.
+The effectiveness of \EVOSUITE has been evaluated on open source as
+well as industrial software in terms of code
+coverage~\cite{fraser2014large,emse_archive}, fault finding
+effectiveness~\cite{shamshiri2015automatically,moein2017}, and effects
+on developer productivity~\cite{TOSEM_userstudy,ISSTA15_Study}.
+
+In the first two and the fourth editions of the unit testing tool
+competition, \EVOSUITE ranked
+first~\cite{evosuiteAtSbst2013,evosuiteAtFittest2013,evosuiteAtSbst2016},
+whereas it ranked second in the third one.
+
 %To improve performance further, we are investigating several
@@
 
-As the generated unit tests are meant for human
-consumption~\cite{fraser2013does}, \EVOSUITE applies various
-post-processing steps to improve readability (e.g., minimising) and
-adds test assertions that capture the current behavior of the tested
-classes. To select the most effective assertions, \EVOSUITE uses
-mutation analysis~\cite{10.1109/TSE.2011.93}.  \EVOSUITE can also be
-used to automatically find faults such as undeclared thrown exceptions
-and broken code contracts~\cite{emse13_oracle}.  For more details on
-the tool and its abilities we refer to~\cite{FrA11c,FrA13a}.
-
 %------------------------------------------------------------------------- 
@@
 
-\EVOSUITE can be configured to target different coverage criteria. The
-fitness function to drive the genetic algorithm was based on a
-combination of several criteria~\cite{rojas2015combining} (e.g., line
-coverage, branch coverage, branch coverage by direct method
-invocation, weak mutation testing, output coverage, exception
-coverage). \EVOSUITE now by default uses an archive of
-solutions~\cite{emse_archive}, which means that throughout the search,
-whenever a new coverage goal is satisfied, the corresponding test is
-stored in the archive, and this goal is no longer targeted by the
-fitness function. We enabled the post-processing step of test
-minimization, but to reduce the time spent we included all assertions
+The configuration of \EVOSUITE for the competition is largely based on
+its default values, since these have been tuned
+extensively~\cite{arcuri2013parameter}. We used the default set of
+coverage criteria~\cite{rojas2015combining} (e.g., line coverage,
+branch coverage, branch coverage by direct method invocation, weak
+mutation testing, output coverage, exception coverage). The use of an
+archive of solutions~\cite{emse_archive}, which iteratively removes
+covered goals from the fitness function and stores the corresponding
+test cases is now enabled by default in \EVOSUITE.
+
+A new feature in \EVOSUITE is the use of Mockito mock
+classes~\cite{ICST_Mocking17}. After a certain percentage of the
+search budget has passed, \EVOSUITE starts considering the use of mock
+objects instead of real classes. Only branches that cannot be covered
+without mocks will result in tests with mock objects in the end. We
+further added frequency based weighting to constants for
+seeding~\cite{sakti2015instance}, and included extensions to support
+Java Enterprise Edition features~\cite{arcuri2016java}. Besides these
+changes, several bug fixes were applied since the last instance of the
+competition, in particular in relation to non-determinism and flaky
+tests~\cite{ase14_environment}.
+
+Like in previous instances of the competition, we enabled the
+post-processing step of test minimisation (but not for efficiency
+reasons, but because minimised tests are less likely to break). To
+reduce the overall time of test generation we included all assertions
 rather than filtering them with mutation
-analysis~\cite{10.1109/TSE.2011.93}. The use of all assertions has
-effects on readability and the chances of obtaining flaky
-tests. However, as readability is not measured by the SBST contest
-metric, and many of the improvements to \EVOSUITE since the last
-competition target flaky tests, we deemed this not a problem.
+analysis~\cite{10.1109/TSE.2011.93}, which is a computationally
+expensive process. The use of all assertions has a negative impact on
+readability, but this is not evaluated as part of the SBST contest.
 
-In contrast to previous instances of the competition, the test
-generation tools this time received a time budget as input, and then
-had to generate tests within that time. \EVOSUITE uses a combination
-of different timeouts for its individual phases (e.g., initialization,
+Like in the 2016 competition, tools were called with different time
+budgets. We used the same strategy as for the previous
+competition~\cite{evosuiteAtSbst2016} to distribute the overall time
+budget onto the different phases of \EVOSUITE (e.g., initialization,
 search, minimization, assertion generation, compilation check, removal
-of flaky tests), which created the challenge of distributing the
-overall budget onto these phases. We used a simple approach where 50\%
-of the time was allocated to the search, whereas the other half of the
-time was distributed equally to the remaining phases. If any of the
-phases used more time than allocated, which can for example happen if
-test executions take long or lead to timeouts, then phases for which
-there is no time left are skipped. For example, if there is no time
-left for minimization, then the raw test suite as generated by the
-search is returned.
+of flaky tests). That is, 50\% of the time was allocated to the
+search, and the rest was distributed equally to the remaining
+phases.
 

### 2017-02-18 papers/sbst17/mainTable.tex
Update scripts and add some tables

\begin{tabular}{ l rrrrrrr rrrrrrrr}\toprule 
 Benchmark &  \multicolumn{7}{c}{Branch Coverage} &  \multicolumn{7}{c}{Mutation Score}\\ 
 & 10s & 30s & 60s & 120s & 240s & 300s & 480s & 10s & 30s & 60s & 120s & 240s & 300s & 480s \\ 
\midrule 
BCEL-1 &  14.0\% &  0.0\% &  18.0\% &  36.6\% &  17.2\% &  0.0\% &  0.0\% &  5.9\% &  0.0\% &  14.9\% &  18.6\% &  16.8\% &  0.0\% &  0.0\%\\ 
BCEL-10 &  1.4\% &  1.4\% &  41.2\% &  45.8\% &  71.3\% &  76.4\% &  77.3\% &  1.3\% &  1.3\% &  35.6\% &  39.6\% &  62.2\% &  68.9\% &  65.3\%\\ 
BCEL-2 &  1.1\% &  1.3\% &  1.5\% &  1.9\% &  2.0\% &  2.4\% &  2.1\% &  0.4\% &  0.4\% &  0.7\% &  1.1\% &  1.2\% &  1.5\% &  1.5\%\\ 
BCEL-3 &  57.9\% &  63.8\% &  65.7\% &  73.3\% &  78.6\% &  79.8\% &  52.9\% &  33.9\% &  38.2\% &  29.4\% &  43.6\% &  44.4\% &  49.7\% &  53.6\%\\ 
BCEL-4 &  62.4\% &  66.2\% &  74.3\% &  80.2\% &  81.0\% &  82.6\% &  84.6\% &  46.3\% &  45.8\% &  58.2\% &  55.9\% &  59.9\% &  62.1\% &  81.9\%\\ 
BCEL-5 &  6.9\% &  6.9\% &  16.7\% &  55.1\% &  53.7\% &  31.9\% &  51.9\% &  4.8\% &  3.9\% &  17.4\% &  50.2\% &  50.7\% &  32.4\% &  48.3\%\\ 
BCEL-6 &  55.6\% &  54.9\% &  59.9\% &  66.7\% &  68.5\% &  68.5\% &  68.5\% &  56.7\% &  55.3\% &  66.0\% &  69.3\% &  76.7\% &  76.0\% &  78.0\%\\ 
BCEL-7 &  57.8\% &  63.7\% &  37.8\% &  63.7\% &  65.2\% &  21.5\% &  71.9\% &  38.1\% &  43.7\% &  27.8\% &  49.2\% &  65.1\% &  14.3\% &  50.8\%\\ 
BCEL-8 &  37.5\% &  37.5\% &  93.1\% &  93.1\% &  97.2\% &  93.1\% &  94.4\% &  21.9\% &  21.9\% &  91.7\% &  93.8\% &  94.8\% &  92.7\% &  94.8\%\\ 
BCEL-9 &  0.0\% &  0.0\% &  36.9\% &  0.0\% &  23.1\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  33.3\% &  0.0\% &  17.5\% &  0.0\% &  0.0\%\\ 
FREEHEP-1 &  83.6\% &  83.6\% &  87.4\% &  89.1\% &  92.5\% &  93.4\% &  93.4\% &  21.8\% &  23.3\% &  38.8\% &  37.4\% &  40.2\% &  38.2\% &  37.9\%\\ 
FREEHEP-10 &  48.6\% &  67.6\% &  82.4\% &  95.4\% &  94.0\% &  95.8\% &  95.8\% &  22.0\% &  22.9\% &  69.9\% &  77.4\% &  72.6\% &  78.3\% &  77.1\%\\ 
FREEHEP-2 &  0.0\% &  0.0\% &  64.2\% &  95.4\% &  96.1\% &  96.8\% &  96.5\% &  0.0\% &  0.0\% &  4.0\% &  7.1\% &  7.4\% &  7.6\% &  7.1\%\\ 
FREEHEP-3 &  0.0\% &  0.0\% &  48.1\% &  74.8\% &  86.7\% &  81.7\% &  87.1\% &  0.0\% &  0.0\% &  11.1\% &  14.4\% &  16.2\% &  19.2\% &  21.5\%\\ 
FREEHEP-4 &  13.2\% &  50.8\% &  49.2\% &  62.4\% &  79.4\% &  70.9\% &  84.7\% &  4.2\% &  18.0\% &  17.5\% &  24.7\% &  31.7\% &  28.9\% &  34.4\%\\ 
FREEHEP-5 &  32.1\% &  32.7\% &  59.1\% &  68.5\% &  67.3\% &  72.4\% &  75.2\% &  17.8\% &  21.5\% &  46.2\% &  52.3\% &  53.3\% &  53.3\% &  56.3\%\\ 
FREEHEP-6 &  0.0\% &  0.0\% &  86.4\% &  87.7\% &  88.3\% &  89.5\% &  89.5\% &  0.0\% &  0.0\% &  38.0\% &  46.7\% &  50.0\% &  41.3\% &  46.0\%\\ 
FREEHEP-7 &  54.2\% &  55.6\% &  85.4\% &  93.1\% &  94.4\% &  99.3\% &  93.8\% &  14.2\% &  14.2\% &  42.8\% &  51.2\% &  61.4\% &  47.5\% &  45.9\%\\ 
FREEHEP-8 &  25.9\% &  28.2\% &  58.8\% &  82.4\% &  81.0\% &  86.1\% &  91.2\% &  1.0\% &  2.4\% &  10.2\% &  51.8\% &  54.3\% &  43.1\% &  65.9\%\\ 
FREEHEP-9 &  1.4\% &  1.4\% &  13.1\% &  22.5\% &  49.1\% &  29.7\% &  33.8\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  16.7\% &  15.8\% &  16.2\%\\ 
GSON-1 &  0.0\% &  0.0\% &  46.3\% &  68.5\% &  70.4\% &  70.4\% &  70.4\% &  0.0\% &  0.0\% &  45.4\% &  63.0\% &  65.7\% &  65.7\% &  63.9\%\\ 
GSON-10 &  43.9\% &  45.1\% &  63.0\% &  62.2\% &  61.8\% &  62.2\% &  62.2\% &  22.9\% &  22.1\% &  54.5\% &  53.2\% &  52.4\% &  53.7\% &  55.4\%\\ 
GSON-2 &  3.3\% &  9.6\% &  25.5\% &  32.4\% &  36.7\% &  37.1\% &  39.6\% &  2.8\% &  8.1\% &  26.4\% &  34.1\% &  36.4\% &  37.2\% &  42.1\%\\ 
GSON-3 &  60.8\% &  54.6\% &  76.7\% &  80.4\% &  82.9\% &  85.4\% &  88.3\% &  46.7\% &  47.9\% &  78.9\% &  78.2\% &  82.4\% &  83.5\% &  77.8\%\\ 
GSON-4 &  3.1\% &  2.4\% &  13.1\% &  18.9\% &  27.5\% &  41.7\% &  46.8\% &  0.4\% &  0.6\% &  8.7\% &  12.8\% &  19.5\% &  17.2\% &  34.2\%\\ 
GSON-5 &  16.0\% &  21.8\% &  30.7\% &  32.7\% &  38.7\% &  40.4\% &  50.7\% &  17.7\% &  22.0\% &  32.8\% &  33.6\% &  37.7\% &  40.3\% &  44.3\%\\ 
GSON-6 &  17.4\% &  24.4\% &  63.6\% &  86.4\% &  86.4\% &  91.9\% &  91.9\% &  15.3\% &  19.6\% &  51.9\% &  72.0\% &  61.8\% &  74.2\% &  76.6\%\\ 
GSON-7 &  42.1\% &  43.0\% &  78.1\% &  82.5\% &  83.3\% &  82.5\% &  81.6\% &  71.3\% &  72.0\% &  90.0\% &  92.0\% &  92.7\% &  91.3\% &  91.3\%\\ 
GSON-9 &  32.8\% &  40.0\% &  51.1\% &  53.9\% &  46.7\% &  40.0\% &  48.3\% &  17.4\% &  27.4\% &  63.7\% &  64.7\% &  58.7\% &  53.7\% &  60.2\%\\ 
IMAGE-1 &  21.3\% &  27.8\% &  44.6\% &  55.4\% &  53.3\% &  49.8\% &  57.0\% &  7.5\% &  19.9\% &  18.4\% &  21.5\% &  28.0\% &  32.1\% &  36.4\%\\ 
IMAGE-2 &  65.0\% &  70.0\% &  78.9\% &  88.3\% &  87.8\% &  91.7\% &  96.1\% &  21.2\% &  20.8\% &  56.6\% &  62.8\% &  72.2\% &  72.6\% &  72.9\%\\ 
IMAGE-3 &  27.8\% &  29.0\% &  24.9\% &  28.5\% &  26.8\% &  39.0\% &  44.4\% &  8.6\% &  8.6\% &  9.2\% &  9.7\% &  14.4\% &  18.1\% &  21.4\%\\ 
IMAGE-4 &  33.6\% &  35.8\% &  47.3\% &  75.9\% &  79.4\% &  77.9\% &  77.9\% &  16.7\% &  17.4\% &  38.0\% &  63.4\% &  55.4\% &  64.1\% &  71.4\%\\ 
JXPATH-1 &  62.4\% &  65.4\% &  73.5\% &  76.8\% &  77.5\% &  76.8\% &  77.4\% &  41.3\% &  38.5\% &  50.3\% &  68.0\% &  68.3\% &  66.7\% &  67.2\%\\ 
JXPATH-10 &  17.6\% &  23.9\% &  35.5\% &  22.3\% &  52.2\% &  48.2\% &  48.0\% &  12.7\% &  15.4\% &  24.2\% &  19.0\% &  39.6\% &  35.4\% &  42.6\%\\ 
JXPATH-2 &  59.7\% &  67.1\% &  69.0\% &  74.4\% &  70.9\% &  77.9\% &  73.6\% &  40.9\% &  44.3\% &  50.8\% &  65.2\% &  62.5\% &  68.2\% &  62.9\%\\ 
JXPATH-3 &  73.4\% &  83.3\% &  79.7\% &  82.8\% &  83.3\% &  87.0\% &  90.1\% &  28.6\% &  39.5\% &  70.1\% &  86.4\% &  84.4\% &  93.2\% &  89.1\%\\ 
JXPATH-4 &  76.8\% &  78.1\% &  80.1\% &  83.0\% &  85.3\% &  89.5\% &  87.6\% &  68.5\% &  68.1\% &  71.4\% &  75.0\% &  78.3\% &  82.6\% &  83.7\%\\ 
JXPATH-5 &  66.0\% &  73.3\% &  82.7\% &  86.7\% &  88.0\% &  88.7\% &  93.3\% &  31.0\% &  31.0\% &  75.4\% &  89.7\% &  88.1\% &  90.5\% &  95.2\%\\ 
JXPATH-6 &  0.0\% &  0.0\% &  0.0\% &  48.6\% &  84.8\% &  83.3\% &  83.3\% &  0.0\% &  0.0\% &  0.0\% &  51.3\% &  82.7\% &  86.7\% &  78.7\%\\ 
JXPATH-7 &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
JXPATH-8 &  38.9\% &  40.2\% &  52.0\% &  52.4\% &  63.6\% &  60.4\% &  67.3\% &  22.1\% &  21.3\% &  39.7\% &  42.8\% &  53.5\% &  49.6\% &  56.6\%\\ 
JXPATH-9 &  9.5\% &  11.9\% &  45.9\% &  91.2\% &  85.4\% &  88.1\% &  91.8\% &  1.1\% &  3.3\% &  26.8\% &  59.8\% &  55.7\% &  54.4\% &  63.1\%\\ 
LA4J-1 &  36.2\% &  68.5\% &  73.5\% &  77.2\% &  77.5\% &  87.0\% &  79.9\% &  23.9\% &  47.1\% &  55.6\% &  55.9\% &  64.7\% &  74.5\% &  55.9\%\\ 
LA4J-10 &  31.8\% &  83.3\% &  90.9\% &  92.4\% &  92.4\% &  92.4\% &  92.4\% &  5.7\% &  22.6\% &  49.1\% &  70.4\% &  77.4\% &  69.2\% &  69.2\%\\ 
LA4J-2 &  10.7\% &  19.4\% &  19.8\% &  79.1\% &  81.4\% &  76.0\% &  78.1\% &  1.0\% &  2.2\% &  4.7\% &  14.8\% &  10.2\% &  17.0\% &  17.8\%\\ 
LA4J-3 &  0.0\% &  15.6\% &  0.0\% &  17.1\% &  38.9\% &  0.0\% &  20.3\% &  0.0\% &  10.8\% &  0.0\% &  10.5\% &  27.1\% &  0.0\% &  7.1\%\\ 
LA4J-4 &  0.0\% &  49.5\% &  71.7\% &  68.2\% &  71.7\% &  77.8\% &  80.8\% &  0.0\% &  33.1\% &  48.9\% &  52.3\% &  53.0\% &  43.9\% &  58.4\%\\ 
LA4J-5 &  0.0\% &  23.5\% &  32.6\% &  42.3\% &  54.4\% &  52.0\% &  44.4\% &  0.0\% &  14.9\% &  20.5\% &  24.1\% &  34.1\% &  20.3\% &  27.2\%\\ 
LA4J-6 &  13.3\% &  61.7\% &  70.0\% &  93.3\% &  95.0\% &  93.3\% &  91.7\% &  4.6\% &  16.7\% &  26.9\% &  78.7\% &  67.6\% &  63.0\% &  67.6\%\\ 
LA4J-7 &  0.0\% &  7.5\% &  0.0\% &  21.7\% &  0.0\% &  0.0\% &  21.9\% &  0.0\% &  6.1\% &  0.0\% &  17.6\% &  0.0\% &  0.0\% &  17.1\%\\ 
LA4J-8 &  32.4\% &  59.8\% &  74.0\% &  75.5\% &  80.9\% &  77.0\% &  77.9\% &  34.2\% &  58.5\% &  69.1\% &  72.7\% &  82.7\% &  78.8\% &  75.5\%\\ 
LA4J-9 &  15.0\% &  39.8\% &  67.4\% &  78.5\% &  77.0\% &  84.8\% &  93.1\% &  0.4\% &  5.6\% &  16.6\% &  24.2\% &  28.0\% &  29.4\% &  22.8\%\\ 
OKHTTP-1 &  4.2\% &  6.4\% &  5.9\% &  8.7\% &  14.4\% &  17.8\% &  16.8\% &  2.2\% &  3.4\% &  4.9\% &  6.5\% &  10.5\% &  8.0\% &  10.5\%\\ 
OKHTTP-2 &  33.3\% &  33.3\% &  33.3\% &  50.0\% &  50.0\% &  33.3\% &  50.0\% &  36.3\% &  38.2\% &  32.4\% &  48.0\% &  49.0\% &  32.4\% &  50.0\%\\ 
OKHTTP-3 &  70.7\% &  75.3\% &  75.8\% &  77.3\% &  74.7\% &  76.8\% &  76.3\% &  36.2\% &  37.6\% &  67.6\% &  69.5\% &  68.1\% &  68.5\% &  68.1\%\\ 
OKHTTP-4 &  29.6\% &  33.9\% &  54.8\% &  53.8\% &  55.9\% &  56.5\% &  58.6\% &  14.1\% &  17.4\% &  46.9\% &  54.5\% &  55.4\% &  55.9\% &  55.9\%\\ 
OKHTTP-5 &  0.0\% &  0.0\% &  3.6\% &  11.1\% &  23.8\% &  12.7\% &  33.3\% &  0.0\% &  0.0\% &  5.0\% &  12.0\% &  19.0\% &  11.8\% &  29.3\%\\ 
OKHTTP-6 &  54.8\% &  72.9\% &  77.6\% &  76.2\% &  83.3\% &  83.3\% &  83.8\% &  9.6\% &  15.3\% &  79.7\% &  75.7\% &  80.2\% &  83.6\% &  81.9\%\\ 
OKHTTP-7 &  27.6\% &  36.5\% &  24.0\% &  39.6\% &  42.7\% &  26.0\% &  46.4\% &  10.1\% &  12.2\% &  11.6\% &  28.6\% &  34.4\% &  12.7\% &  28.0\%\\ 
OKHTTP-8 &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
RE2J-1 &  30.4\% &  50.7\% &  49.2\% &  51.4\% &  60.0\% &  60.5\% &  65.3\% &  19.7\% &  33.2\% &  32.0\% &  34.3\% &  43.8\% &  42.9\% &  39.9\%\\ 
RE2J-2 &  9.2\% &  73.8\% &  77.7\% &  92.0\% &  94.0\% &  95.2\% &  96.4\% &  3.9\% &  32.4\% &  36.6\% &  67.3\% &  69.6\% &  65.7\% &  71.6\%\\ 
RE2J-3 &  1.8\% &  1.8\% &  36.9\% &  48.8\% &  48.8\% &  50.0\% &  57.7\% &  3.4\% &  3.4\% &  23.0\% &  41.4\% &  43.7\% &  43.7\% &  48.9\%\\ 
RE2J-4 &  81.2\% &  85.1\% &  93.1\% &  94.8\% &  95.1\% &  95.5\% &  96.9\% &  27.6\% &  27.1\% &  91.5\% &  91.2\% &  92.0\% &  89.5\% &  84.6\%\\ 
RE2J-5 &  11.0\% &  22.7\% &  57.3\% &  61.2\% &  65.9\% &  58.0\% &  80.4\% &  2.9\% &  3.9\% &  31.1\% &  34.6\% &  36.9\% &  29.4\% &  42.7\%\\ 
RE2J-6 &  0.0\% &  0.0\% &  55.1\% &  56.7\% &  83.7\% &  84.3\% &  86.8\% &  0.0\% &  0.0\% &  42.0\% &  51.0\% &  69.2\% &  68.9\% &  66.3\%\\ 
RE2J-7 &  15.4\% &  39.2\% &  40.3\% &  53.2\% &  48.2\% &  31.4\% &  51.5\% &  5.9\% &  17.0\% &  15.4\% &  40.1\% &  39.2\% &  27.5\% &  47.8\%\\ 
RE2J-8 &  59.2\% &  90.8\% &  89.5\% &  92.9\% &  91.5\% &  92.9\% &  93.2\% &  26.7\% &  44.1\% &  67.7\% &  75.6\% &  81.0\% &  75.6\% &  81.2\%\\ 
\midrule 
Average  &  27.4\% &  36.4\% &  50.9\% &  60.6\% &  64.6\% &  62.3\% &  66.5\% &  15.3\% &  19.8\% &  36.5\% &  45.7\% &  49.6\% &  46.6\% &  50.7\%\\ 
\bottomrule 
\end{tabular}

### 2017-02-18 papers/sbst17/paper_sbst17.tex
Update scripts and add some tables

@@
 
+\begin{table*}[t]
+  \centering
+  \caption{\label{table:results}Detailed results of \EVOSUITE on the SBST benchmark classes.}
+\resizebox{\textwidth}{!}{  
+\input{mainTable.tex}
+}	
+\end{table*}
+
 % \begin{table*}[t]
 %   \centering
-%   \caption{\label{table:results}Detailed results of \EVOSUITE on the SBST benchmark classes.}
-% \resizebox{0.9\textwidth}{!}{  
-% \input{mainTable.tex}
+%   \caption{\label{table:coverage_results}Detailed coverage results of \EVOSUITE on the SBST benchmark classes.}
+% \resizebox{0.8\textwidth}{!}{  
+% \input{coverageTable.tex}
 % }
@@
 
-\begin{table*}[t]
-  \centering
-  \caption{\label{table:coverage_results}Detailed coverage results of \EVOSUITE on the SBST benchmark classes.}
-\resizebox{0.8\textwidth}{!}{  
-%\input{coverageTable.tex}
-}
-\end{table*}
-
-\begin{table*}[t]
-  \centering
-  \caption{\label{table:fault_results}Detailed fault detection results of \EVOSUITE on the SBST benchmark classes.}
-\resizebox{0.8\textwidth}{!}{  
-%\input{faultTable.tex}
-}	
-\end{table*}
+% \begin{table*}[t]
+%   \centering
+%   \caption{\label{table:fault_results}Detailed fault detection results of \EVOSUITE on the SBST benchmark classes.}
+% \resizebox{0.8\textwidth}{!}{  
+% \input{faultTable.tex}
+% }	
+% \end{table*}
 

### 2017-02-18 papers/sbst17/r_files/analyze.R

@@ -3,7 +3,6 @@
 #conditionsTotal,conditionsCovered,conditionsCoverageRatio,mutantsTotal,mutantsCovered,mutantsCoverageRatio,
 #mutantsKilled,mutantsKillRatio,mutantsAlive,timeBudget,totalTestClasses
 
-cols = c("character","character","character","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric", "numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric")
 FILE = "../data/single_transcript.csv";
 
 mainTable <- function(){
@@ -14,10 +13,11 @@ mainTable <- function(){
 	unlink(TABLE)
 	sink(TABLE, append=TRUE, split=TRUE)
 
-	cat("\\begin{tabular}{ l rrrr rrrr}\\toprule","\n")
-	cat(" Benchmark &  \\multicolumn{4}{c}{Branch Coverage}  &  \\multicolumn{4}{c}{Fault Detection} \\\\ \n")
-	cat(" & 60s & 120s & 240s & 480s & 60s & 120s & 240s & 480s \\\\ \n" )
+	cat("\\begin{tabular}{ l rrrrrrr rrrrrrrr}\\toprule","\n")
+	cat(" Benchmark &  \\multicolumn{7}{c}{Branch Coverage} &  \\multicolumn{7}{c}{Mutation Score}\\\\ \n")
+	cat(" & 10s & 30s & 60s & 120s & 240s & 300s & 480s & 10s & 30s & 60s & 120s & 240s & 300s & 480s \\\\ \n" )
 	cat("\\midrule","\n")
+
 
 	classes = sort(unique(dt$class))
 	times = sort(unique(dt$timeBudget))
@@ -36,21 +36,32 @@ mainTable <- function(){
 			cov = dt$conditionsCoverageRatio[mask & dt$timeBudget==t]
 			cat(" & ", paste(formatC(mean(cov),digits=1,format="f"),"\\%",sep=""))
 		}
-
-		for(t in times){
-			fails = dt$failTests[mask & dt$timeBudget==t]
-			ratio = sum(fails>0) / length(fails)
-			cat(" & ", paste(formatC(100*mean(ratio),digits=1,format="f"),"\\%",sep=""))
+                for(t in times){
+			cov = dt$mutantsKillRatio[mask & dt$timeBudget==t]
[…]

### 2017-02-20 papers/sbst17/mainTable.tex
overall results

@@
 \midrule 
-BCEL-1 &  14.0\% &  0.0\% &  18.0\% &  36.6\% &  17.2\% &  0.0\% &  0.0\% &  5.9\% &  0.0\% &  14.9\% &  18.6\% &  16.8\% &  0.0\% &  0.0\%\\ 
+BCEL-1 & 14.0\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 18.0\% & 36.6\% & 17.2\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 5.9\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 14.9\% & 18.6\% & 16.8\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\%\\
 BCEL-10 & 1.4\% & 1.4\% & 41.2\% & 45.8\% & 71.3\% & 76.4\% & 77.3\% & 1.3\% & 1.3\% & 35.6\% & 39.6\% & 62.2\% & 68.9\% & 65.3\%\\ 
@@
 BCEL-8 & 37.5\% & 37.5\% & 93.1\% & 93.1\% & 97.2\% & 93.1\% & 94.4\% & 21.9\% & 21.9\% & 91.7\% & 93.8\% & 94.8\% & 92.7\% & 94.8\%\\ 
-BCEL-9 &  0.0\% &  0.0\% &  36.9\% &  0.0\% &  23.1\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  33.3\% &  0.0\% &  17.5\% &  0.0\% &  0.0\%\\ 
+BCEL-9 & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 36.9\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 23.1\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 33.3\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 17.5\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\%\\
 FREEHEP-1 & 83.6\% & 83.6\% & 87.4\% & 89.1\% & 92.5\% & 93.4\% & 93.4\% & 21.8\% & 23.3\% & 38.8\% & 37.4\% & 40.2\% & 38.2\% & 37.9\%\\ 
 FREEHEP-10 & 48.6\% & 67.6\% & 82.4\% & 95.4\% & 94.0\% & 95.8\% & 95.8\% & 22.0\% & 22.9\% & 69.9\% & 77.4\% & 72.6\% & 78.3\% & 77.1\%\\ 
-FREEHEP-2 &  0.0\% &  0.0\% &  64.2\% &  95.4\% &  96.1\% &  96.8\% &  96.5\% &  0.0\% &  0.0\% &  4.0\% &  7.1\% &  7.4\% &  7.6\% &  7.1\%\\ 
-FREEHEP-3 &  0.0\% &  0.0\% &  48.1\% &  74.8\% &  86.7\% &  81.7\% &  87.1\% &  0.0\% &  0.0\% &  11.1\% &  14.4\% &  16.2\% &  19.2\% &  21.5\%\\ 
+FREEHEP-2 & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 64.2\% & 95.4\% & 96.1\% & 96.8\% & 96.5\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 4.0\% & 7.1\% & 7.4\% & 7.6\% & 7.1\%\\
+FREEHEP-3 & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 48.1\% & 74.8\% & 86.7\% & 81.7\% & 87.1\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 11.1\% & 14.4\% & 16.2\% & 19.2\% & 21.5\%\\
 FREEHEP-4 & 13.2\% & 50.8\% & 49.2\% & 62.4\% & 79.4\% & 70.9\% & 84.7\% & 4.2\% & 18.0\% & 17.5\% & 24.7\% & 31.7\% & 28.9\% & 34.4\%\\ 
 FREEHEP-5 & 32.1\% & 32.7\% & 59.1\% & 68.5\% & 67.3\% & 72.4\% & 75.2\% & 17.8\% & 21.5\% & 46.2\% & 52.3\% & 53.3\% & 53.3\% & 56.3\%\\ 
-FREEHEP-6 &  0.0\% &  0.0\% &  86.4\% &  87.7\% &  88.3\% &  89.5\% &  89.5\% &  0.0\% &  0.0\% &  38.0\% &  46.7\% &  50.0\% &  41.3\% &  46.0\%\\ 
+FREEHEP-6 & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 86.4\% & 87.7\% & 88.3\% & 89.5\% & 89.5\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 38.0\% & 46.7\% & 50.0\% & 41.3\% & 46.0\%\\
 FREEHEP-7 & 54.2\% & 55.6\% & 85.4\% & 93.1\% & 94.4\% & 99.3\% & 93.8\% & 14.2\% & 14.2\% & 42.8\% & 51.2\% & 61.4\% & 47.5\% & 45.9\%\\ 
 FREEHEP-8 & 25.9\% & 28.2\% & 58.8\% & 82.4\% & 81.0\% & 86.1\% & 91.2\% & 1.0\% & 2.4\% & 10.2\% & 51.8\% & 54.3\% & 43.1\% & 65.9\%\\ 
-FREEHEP-9 &  1.4\% &  1.4\% &  13.1\% &  22.5\% &  49.1\% &  29.7\% &  33.8\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  16.7\% &  15.8\% &  16.2\%\\ 
-GSON-1 &  0.0\% &  0.0\% &  46.3\% &  68.5\% &  70.4\% &  70.4\% &  70.4\% &  0.0\% &  0.0\% &  45.4\% &  63.0\% &  65.7\% &  65.7\% &  63.9\%\\ 
+FREEHEP-9 & 1.4\% & 1.4\% & 13.1\% & 22.5\% & 49.1\% & 29.7\% & 33.8\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 16.7\% & 15.8\% & 16.2\%\\
+GSON-1 & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 46.3\% & 68.5\% & 70.4\% & 70.4\% & 70.4\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 45.4\% & 63.0\% & 65.7\% & 65.7\% & 63.9\%\\
 GSON-10 & 43.9\% & 45.1\% & 63.0\% & 62.2\% & 61.8\% & 62.2\% & 62.2\% & 22.9\% & 22.1\% & 54.5\% & 53.2\% & 52.4\% & 53.7\% & 55.4\%\\ 
@@
 JXPATH-5 & 66.0\% & 73.3\% & 82.7\% & 86.7\% & 88.0\% & 88.7\% & 93.3\% & 31.0\% & 31.0\% & 75.4\% & 89.7\% & 88.1\% & 90.5\% & 95.2\%\\ 
-JXPATH-6 &  0.0\% &  0.0\% &  0.0\% &  48.6\% &  84.8\% &  83.3\% &  83.3\% &  0.0\% &  0.0\% &  0.0\% &  51.3\% &  82.7\% &  86.7\% &  78.7\%\\ 
-JXPATH-7 &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
+JXPATH-6 & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 48.6\% & 84.8\% & 83.3\% & 83.3\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 51.3\% & 82.7\% & 86.7\% & 78.7\%\\
+JXPATH-7 & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\%\\
 JXPATH-8 & 38.9\% & 40.2\% & 52.0\% & 52.4\% & 63.6\% & 60.4\% & 67.3\% & 22.1\% & 21.3\% & 39.7\% & 42.8\% & 53.5\% & 49.6\% & 56.6\%\\ 
@@
 LA4J-2 & 10.7\% & 19.4\% & 19.8\% & 79.1\% & 81.4\% & 76.0\% & 78.1\% & 1.0\% & 2.2\% & 4.7\% & 14.8\% & 10.2\% & 17.0\% & 17.8\%\\ 
-LA4J-3 &  0.0\% &  15.6\% &  0.0\% &  17.1\% &  38.9\% &  0.0\% &  20.3\% &  0.0\% &  10.8\% &  0.0\% &  10.5\% &  27.1\% &  0.0\% &  7.1\%\\ 
-LA4J-4 &  0.0\% &  49.5\% &  71.7\% &  68.2\% &  71.7\% &  77.8\% &  80.8\% &  0.0\% &  33.1\% &  48.9\% &  52.3\% &  53.0\% &  43.9\% &  58.4\%\\ 
-LA4J-5 &  0.0\% &  23.5\% &  32.6\% &  42.3\% &  54.4\% &  52.0\% &  44.4\% &  0.0\% &  14.9\% &  20.5\% &  24.1\% &  34.1\% &  20.3\% &  27.2\%\\ 
+LA4J-3 & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 15.6\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 17.1\% & 38.9\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 20.3\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 10.8\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 10.5\% & 27.1\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 7.1\%\\
+LA4J-4 & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 49.5\% & 71.7\% & 68.2\% & 71.7\% & 77.8\% & 80.8\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 33.1\% & 48.9\% & 52.3\% & 53.0\% & 43.9\% & 58.4\%\\
+LA4J-5 & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 23.5\% & 32.6\% & 42.3\% & 54.4\% & 52.0\% & 44.4\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 14.9\% & 20.5\% & 24.1\% & 34.1\% & 20.3\% & 27.2\%\\
 LA4J-6 & 13.3\% & 61.7\% & 70.0\% & 93.3\% & 95.0\% & 93.3\% & 91.7\% & 4.6\% & 16.7\% & 26.9\% & 78.7\% & 67.6\% & 63.0\% & 67.6\%\\ 
-LA4J-7 &  0.0\% &  7.5\% &  0.0\% &  21.7\% &  0.0\% &  0.0\% &  21.9\% &  0.0\% &  6.1\% &  0.0\% &  17.6\% &  0.0\% &  0.0\% &  17.1\%\\ 
+LA4J-7 & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 7.5\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 21.7\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 21.9\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 6.1\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 17.6\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 17.1\%\\
 LA4J-8 & 32.4\% & 59.8\% & 74.0\% & 75.5\% & 80.9\% & 77.0\% & 77.9\% & 34.2\% & 58.5\% & 69.1\% & 72.7\% & 82.7\% & 78.8\% & 75.5\%\\ 
@@
 OKHTTP-4 & 29.6\% & 33.9\% & 54.8\% & 53.8\% & 55.9\% & 56.5\% & 58.6\% & 14.1\% & 17.4\% & 46.9\% & 54.5\% & 55.4\% & 55.9\% & 55.9\%\\ 
-OKHTTP-5 &  0.0\% &  0.0\% &  3.6\% &  11.1\% &  23.8\% &  12.7\% &  33.3\% &  0.0\% &  0.0\% &  5.0\% &  12.0\% &  19.0\% &  11.8\% &  29.3\%\\ 
+OKHTTP-5 & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 3.6\% & 11.1\% & 23.8\% & 12.7\% & 33.3\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 5.0\% & 12.0\% & 19.0\% & 11.8\% & 29.3\%\\
 OKHTTP-6 & 54.8\% & 72.9\% & 77.6\% & 76.2\% & 83.3\% & 83.3\% & 83.8\% & 9.6\% & 15.3\% & 79.7\% & 75.7\% & 80.2\% & 83.6\% & 81.9\%\\ 
 OKHTTP-7 & 27.6\% & 36.5\% & 24.0\% & 39.6\% & 42.7\% & 26.0\% & 46.4\% & 10.1\% & 12.2\% & 11.6\% & 28.6\% & 34.4\% & 12.7\% & 28.0\%\\ 
-OKHTTP-8 &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 
+OKHTTP-8 & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\%\\
 RE2J-1 & 30.4\% & 50.7\% & 49.2\% & 51.4\% & 60.0\% & 60.5\% & 65.3\% & 19.7\% & 33.2\% & 32.0\% & 34.3\% & 43.8\% & 42.9\% & 39.9\%\\ 
@@
 RE2J-5 & 11.0\% & 22.7\% & 57.3\% & 61.2\% & 65.9\% & 58.0\% & 80.4\% & 2.9\% & 3.9\% & 31.1\% & 34.6\% & 36.9\% & 29.4\% & 42.7\%\\ 
-RE2J-6 &  0.0\% &  0.0\% &  55.1\% &  56.7\% &  83.7\% &  84.3\% &  86.8\% &  0.0\% &  0.0\% &  42.0\% &  51.0\% &  69.2\% &  68.9\% &  66.3\%\\ 
+RE2J-6 & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 55.1\% & 56.7\% & 83.7\% & 84.3\% & 86.8\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 42.0\% & 51.0\% & 69.2\% & 68.9\% & 66.3\%\\
 RE2J-7 & 15.4\% & 39.2\% & 40.3\% & 53.2\% & 48.2\% & 31.4\% & 51.5\% & 5.9\% & 17.0\% & 15.4\% & 40.1\% & 39.2\% & 27.5\% & 47.8\%\\ 

### 2017-02-20 papers/sbst17/paper_sbst17.tex
Acks
overall results

@@
 \usepackage{float}
-\usepackage{cite}
+\usepackage[numbers,sort&compress,square]{natbib}
 \usepackage{graphicx}
@@
 \usepackage[usenames,dvipsnames,table]{xcolor}
-%\usepackage{soul}
+\usepackage{soul}
 \usepackage{xspace}
@@
 \usepackage{balance}
+\definecolor{light-gray}{gray}{0.90}
 
@@
 
-%\documentstyle[times,art10,twocolumn,latex8]{article}
+\input{macros}
 
@@
 
-\author{\IEEEauthorblockN{Authors}}
+\author{\IEEEauthorblockN{Gordon Fraser\IEEEauthorrefmark{1}, Jos\'e
+    Miguel Rojas\IEEEauthorrefmark{2}, Jos\'e Campos\IEEEauthorrefmark{3}}
+  \IEEEauthorblockA{The University of Sheffield\\Sheffield, United Kingdom\\
+    \{\IEEEauthorrefmark{1}gordon.fraser,
+    \IEEEauthorrefmark{2}j.rojas, \IEEEauthorrefmark{3}jose.campos\}@sheffield.ac.uk} 
+\and
+\IEEEauthorblockN{Andrea Arcuri}
+  \IEEEauthorblockA{Westerdals Oslo ACT, Norway\\and University of Luxembourg, Luxembourg\\arcand@westerdals.no}
+}
 
@@
 
-The coverage results (line coverage and branch coverage) achieved by
-\EVOSUITE on the benchmark classes are listed in
-Table~\ref{table:coverage_results}. Coverage is generally in the
-expected range, with clear increases for higher time budgets. Coverage
-on several of the benchmarks from Closure is low, which matches
-previous findings~\cite{shamshiri2015automatically}.
+% overall results
+Table~\ref{table:results} lists the branch coverage and mutation
+analysis results achieved by \EVOSUITE on all benchmark classes in the
+contest. Coverage is generally in the expected range, with clear
+increases for higher time budgets as expected, except for
+$budget=300s$, where a decrease is observed, possibly due to crashes
+or \emph{out-of-memory} errors\TODO{confirm this conjecture}. With
+$budget=480s$, the average branch coverage achieved was \AvgCovG
+(slightly higher than last year's $65.6\%$) and the average mutation
+score was \AvgMutG (considerably higher than last year's $41.0\%$).
 
-Results in terms of mutation scores and fault detection ratio (i.e.,
-how many of the runs had at least one failing test on the
-corresponding bug) are showing in
-Table~\ref{table:fault_results}. Again the Closure results are
-generally worse than those of other projects, both in terms of
-mutation score and ratio of fault detection.
+% Coverage on several
+% of the benchmarks from Closure is low, which matches previous
+% findings~\cite{shamshiri2015automatically}.
 
-On average, \EVOSUITE generated 0.14 flaky tests per run, a value that
-is significantly lower than that of any of the competing tools. This
-is due to extensive efforts to isolate \EVOSUITE tests from the
-execution environment~\cite{arcuri2014automated}. A few of these flaky
-tests were introduced by recent changes to \EVOSUITE following
-experiments on Defects4J~\cite{shamshiri2015automatically}: \EVOSUITE
-now includes assertions on the source of exceptions, similar to
-commercial tools like Agitar One. %~\cite{agitarone}. 
-Unfortunately, there were several instances in the competition where these assertions
-lead to flaky tests. For example, the following is an excerpt from a
-test for the Defects4J bug Lang-41, generated by \EVOSUITE:
-\vspace{1em}
+% Results in terms of mutation scores and fault detection ratio (i.e.,
+% how many of the runs had at least one failing test on the
+% corresponding bug) are showing in
+% Table~\ref{table:fault_results}. Again the Closure results are
+% generally worse than those of other projects, both in terms of
+% mutation score and ratio of fault detection.
 
-\begin{lstlisting}
-@Test(timeout = 4000)
-public void test19()  throws Throwable  {
- Class<Double> class0 = Double.class;
- String string0 = ClassUtils.getPackageName(class0);
- try { 
-   ClassUtils.getClass(string0);
-   fail("Expecting exception: ClassNotFoundException"); 
- } catch(ClassNotFoundException e) {
-   assertThrownBy("java.net.URLClassLoader", e);
- }
-}
-\end{lstlisting}
+\EVOSUITE generated \FlakyEvosuite flaky tests per run on average,
+much lower than the number of flaky tests produced by the competing
+tools (\FlakyTthree by T3, \FlakyJtexpert by JTExpert, and
+\FlakyRandoop by Randoop). We attribute these results---also
+consistent with previous years' results---to the way \EVOSUITE handles
+execution environments during test generation (e.g., controlling the
+static state of the class under test, mocking interactions with the
+file system, system calls like \texttt{System.in} and
+\texttt{System.currentTimeMillis}, etc.)~\cite{arcuri2014automated}.
 
-While compiling and executing this test with JUnit works without
-problems, the mutation analysis step of the competition used Ant to
-run the tests; Ant uses a complex setup of classloaders that
-eventually leads to the \texttt{assertThrownBy} in the above example
-to fail, as the source of the exception is a different one.
+% A few of these flaky tests were introduced by recent changes to
+% \EVOSUITE following experiments on
+% Defects4J~\cite{shamshiri2015automatically}: \EVOSUITE now includes
+% assertions on the source of exceptions, similar to commercial tools
+% like Agitar One. %~\cite{agitarone}.
+% Unfortunately, there were several instances in the competition where
+% these assertions lead to flaky tests. For example, the following is an
+% excerpt from a test for the Defects4J bug Lang-41, generated by
+% \EVOSUITE: \vspace{1em}
 
-There are 15 runs in total where \EVOSUITE did not produce any test
-suites; these are only for higher time budgets (240s, 480s). The
-majority of these runs are due to \EVOSUITE not terminating before the
-hard timeout of the competition infrastructure. This may happen, for
-example, when test execution on the class under test takes long (e.g.,
-timeouts), and when resetting the static state of the classes under
-test takes a long time. However, this number is still lower than the
-number of erroneous runs compared to other tools, and in the remaining
-1617 runs of the competition \EVOSUITE terminated in time and produced
-at least two tests. In 13 of these, \EVOSUITE produced a test suite
-with a compilation error.
+% \begin{lstlisting}
+% @Test(timeout = 4000)
+% public void test19()  throws Throwable  {
+%  Class<Double> class0 = Double.class;
+%  String string0 = ClassUtils.getPackageName(class0);
+%  try { 
+%    ClassUtils.getClass(string0);
+%    fail("Expecting exception: ClassNotFoundException"); 
+%  } catch(ClassNotFoundException e) {
+%    assertThrownBy("java.net.URLClassLoader", e);
+%  }
+% }
+% \end{lstlisting}
+
+% While compiling and executing this test with JUnit works without
+% problems, the mutation analysis step of the competition used Ant to
+% run the tests; Ant uses a complex setup of classloaders that
+% eventually leads to the \texttt{assertThrownBy} in the above example
+% to fail, as the source of the exception is a different one.
+
+% There are 15 runs in total where \EVOSUITE did not produce any test
+% suites; these are only for higher time budgets (240s, 480s). The
+% majority of these runs are due to \EVOSUITE not terminating before the
+% hard timeout of the competition infrastructure. This may happen, for
+% example, when test execution on the class under test takes long (e.g.,
+% timeouts), and when resetting the static state of the classes under
+% test takes a long time. However, this number is still lower than the
+% number of erroneous runs compared to other tools, and in the remaining
+% 1617 runs of the competition \EVOSUITE terminated in time and produced
+% at least two tests. In 13 of these, \EVOSUITE produced a test suite
+% with a compilation error.
 
@@
 \textbf{Acknowledgments:} Many thanks to all the contributors to \EVOSUITE.
-This project has been funded by 
-%the EPSRC project ``EXOGEN'' (EP/K030353/1), a Google Focused Research Award on ``Test
-%Amplification'', and by 
-the National Research Fund, Luxembourg (FNR/P10/03).
+This project has been funded by the EPSRC
+project ``GREATEST'' (EP/N023978/1), and by the National Research
+Fund, Luxembourg (FNR/P10/03).
 

### 2017-02-20 papers/sbst17/r_files/analyze.R

@@ -3,232 +3,159 @@
 #conditionsTotal,conditionsCovered,conditionsCoverageRatio,mutantsTotal,mutantsCovered,mutantsCoverageRatio,
 #mutantsKilled,mutantsKillRatio,mutantsAlive,timeBudget,totalTestClasses
 
-FILE = "../data/single_transcript.csv";
+FILE <- "../data/single_transcript.csv";
 
 mainTable <- function(){
 
-	dt <- read.csv(FILE,sep=",",dec=".",header=T) #,colClasses=cols)
+  dt <- read.csv(FILE,sep=",",dec=".",header=T) #,colClasses=cols)
 
-	TABLE = paste("../mainTable.tex",sep="")
-	unlink(TABLE)
-	sink(TABLE, append=TRUE, split=TRUE)
+  TABLE = paste("../mainTable.tex",sep="")
+  unlink(TABLE)
+  sink(TABLE, append=TRUE, split=TRUE)
 
-	cat("\\begin{tabular}{ l rrrrrrr rrrrrrrr}\\toprule","\n")
-	cat(" Benchmark &  \\multicolumn{7}{c}{Branch Coverage} &  \\multicolumn{7}{c}{Mutation Score}\\\\ \n")
-	cat(" & 10s & 30s & 60s & 120s & 240s & 300s & 480s & 10s & 30s & 60s & 120s & 240s & 300s & 480s \\\\ \n" )
-	cat("\\midrule","\n")
+  cat("\\begin{tabular}{ l rrrrrrr rrrrrrrr}\\toprule","\n")
+  cat(" Benchmark &  \\multicolumn{7}{c}{Branch Coverage} &  \\multicolumn{7}{c}{Mutation Score}\\\\ \n")
+  cat(" & 10s & 30s & 60s & 120s & 240s & 300s & 480s & 10s & 30s & 60s & 120s & 240s & 300s & 480s \\\\ \n" )
+  cat("\\midrule","\n")
 
 
-	classes = sort(unique(dt$class))
-	times = sort(unique(dt$timeBudget))
-	benchmarks = sort(unique(dt$benchmark))
+  classes = sort(unique(dt$class))
+  times = sort(unique(dt$timeBudget))
+  benchmarks = sort(unique(dt$benchmark))
 
-        for(benchmark in benchmarks) {
-	#for(class in classes){
+  for(benchmark in benchmarks) {
+  #for(class in classes){
 
[…]

### 2017-02-21 papers/sbst17/paper_sbst17.tex
comparison with manual tests

@@
 competition, \EVOSUITE achieved a 1457.3 overall score, which was the
-highest among the competing tools.
+highest among the competing and baseline tools.
 
@@
 
-% overall results
+\subsection{Overall results}
+
 Table~\ref{table:results} lists the branch coverage and mutation
@@
 contest. Coverage is generally in the expected range, with clear
-increases for higher time budgets as expected, except for
-$budget=300s$, where a decrease is observed, possibly due to crashes
-or \emph{out-of-memory} errors\TODO{confirm this conjecture}. With
-$budget=480s$, the average branch coverage achieved was \AvgCovG
-(slightly higher than last year's $65.6\%$) and the average mutation
-score was \AvgMutG (considerably higher than last year's $41.0\%$).
+overall increases for higher time budgets. With $budget=480s$, the
+average branch coverage achieved was \AvgCovG (slightly higher than
+last year's $65.6\%$) and the average mutation score was \AvgMutG
+(considerably higher than last year's $41.0\%$).
+
+This year, the contest also included manually written test suites as
+baseline. \EVOSUITE significantly outperformed this manual baseline as
+well, both in terms of branch coverage (avg. \AvgCovEvosuite vs
+\AvgCovManual, with Vargha-Delaney's $A_{12}=\EvoManCovA$ and
+$p\EvoManCovPV$) and mutation scores (avg. \AvgMutEvosuite vs
+\AvgMutManual, with $A_{12}=\EvoManMutA$ and
+$p\EvoManMutPV$).\TODO{Does showing A12 make sense if there's only one
+  manual test suite per benchmark?}
 
@@
 much lower than the number of flaky tests produced by the competing
-tools (\FlakyTthree by T3, \FlakyJtexpert by JTExpert, and
+and baseline tools (\FlakyTthree by T3, \FlakyJtexpert by JTExpert, and
 \FlakyRandoop by Randoop). We attribute these results---also
@@
 \texttt{System.currentTimeMillis}, etc.)~\cite{arcuri2014automated}.
+
+\subsection{Challenges}
+
+% Look at benchmarks that always failed
+\EVOSUITE failed to produce any test suite for benchmarks JXPATH-7 and
+OKHTTP-8, and also struggled often for benchmarks LA4J-3, LA4J-7,
+BCEL-9 (highlighted in Table~\ref{table:results}).\TODO{look into details}
+
+% Look at benchmarks where coverage decreased with increased budget
+Although coverage generally increased with higher time budgets, there
+are instances where this expected behaviour was not observed,
+specially for $budget=300s$, where the average across benchmarks
+decreased. This is possibly due to crashes or out-of-memory
+runtime errors.\TODO{confirm this conjecture}\TODO{look into details}
+
+% Look at benchmarks with more flaky tests
+Flaky tests continue to be a challenge for test generation. Benchmarks
+FREEHEP-7 and JXPATH-10 were the ones with the highest number of flaky
+tests in one run (12 and 14, respectively).\TODO{look into details}
 
@@
 %\def\IEEEbibitemsep{6pt}
-
+\clearpage
 \bibliographystyle{IEEEtranS}

### 2017-02-21 papers/sbst17/r_files/analyze.R

@@ -3,7 +3,8 @@
 #conditionsTotal,conditionsCovered,conditionsCoverageRatio,mutantsTotal,mutantsCovered,mutantsCoverageRatio,
 #mutantsKilled,mutantsKillRatio,mutantsAlive,timeBudget,totalTestClasses
 
-FILE <- "../data/single_transcript.csv";
+FILE <- "../data/single_transcript.csv"
+FILE.MANUAL <- "../data/single_manual_transcript.csv"
 
 mainTable <- function(){
 
@@ -83,7 +84,8 @@ MacroFile <- function(){
       #mean(score))
     }
   }
-
+  ## Coverage and mutation scores per time budget
+  printComment(macro.file, "Coverage and Mutation per time budget")
   i <- 1
   for(t in times){
     printComment(macro.file, concat(toupper(letters[i]),concat("=",t)))
@@ -95,12 +97,37 @@ MacroFile <- function(){
     printMacro(macro.file, concat("AvgMut",toupper(letters[i])), asPercent(score))
     i <- i+1
   }
-  printComment(macro.file, "Overall")
+  ## Flakiness per tool
+  printComment(macro.file, "EvoSuite vs Manual")
   for(t in tools){
     flaky <- mean(dt$brokenTests[dt$tool==t])
     printMacro(macro.file, concat("Flaky",toolname(t)), formatC(flaky,digits=1,format="f"))
   }
-    
+  ## EvoSuite vs Manual
+  printComment(macro.file, "EvoSuite vs Manual")
+  dt.man <- read.csv(FILE.MANUAL,sep=",",dec=".",header=T)
+  evo.cov <- c()
+  evo.mut <- c()
+
+  for(benchmark in benchmarks) {
+    evo.mask = dt$tool=="evosuite" & dt$benchmark==benchmark
+    evo.cov <- c(mean(dt$conditionsCoverageRatio[evo.mask]), evo.cov)
+    evo.mut <- c(mean(dt$mutantsKillRatio[evo.mask]), evo.mut)
+  }
+
+  man.cov <- dt.man$conditionsCoverageRatio
+  man.mut <- dt.man$mutantsKillRatio
+  printMacro(macro.file, "AvgCovEvosuite", asPercent(mean(evo.cov)))
+  printMacro(macro.file, "AvgMutEvosuite", asPercent(mean(evo.mut)))
[…]

### 2017-02-21 papers/sbst17/paper_sbst17.tex
todo mocking
zero cov

@@
 OKHTTP-8, and also struggled often for benchmarks LA4J-3, LA4J-7,
-BCEL-9 (highlighted in Table~\ref{table:results}).\TODO{look into details}
+BCEL-9 (highlighted in Table~\ref{table:results}). All executions of
+\EVOSUITE for JXPATH-7 failed in the instrumentation phase as a result
+of exceeding Java's 64k limit on the size of methods. A trivial fix
+would be to stop instrumenting before the limit is reached, at the
+price of limited search guidance; a more effective solution would
+involve identifying parts of the code that are worth instrumenting. A
+missing dependency for OKHTTP-8 caused all executions---\emph{for all
+  tools}---to fail. For the other mentioned benchmarks, the failure
+reasons (in some cases related to sandboxing, mocking and timeouts)
+will require further investigation.
+
+% LA4J-3, LA4J-7: Phase INITIALIZATION lasted too long, Phase SEARCH lasted too long, 9 seconds more than allowed.
 
@@
 tests in one run (12 and 14, respectively).\TODO{look into details}
+
+% Mocking
+\TODO{Add some stats on mocking}
 

### 2017-02-21 papers/sbst17/paper_sbst17.tex
flaky

@@
 
-% LA4J-3, LA4J-7: Phase INITIALIZATION lasted too long, Phase SEARCH lasted too long, 9 seconds more than allowed.
-
 % Look at benchmarks where coverage decreased with increased budget
@@
 FREEHEP-7 and JXPATH-10 were the ones with the highest number of flaky
-tests in one run (12 and 14, respectively).\TODO{look into details}
+tests in one run (12 and 14, respectively). In both cases, the
+minimisation phase timed out and hence \EVOSUITE reverted the
+resulting test suite to the previous, unminimised one, which as
+mentioned before, is more likely to break. Partial minimisation might
+be worth investigating to alleviate this issue.
 

### 2017-02-21 papers/sbst17/paper_sbst17.tex
Repeated reference.

@@
 competition, in particular in relation to non-determinism and flaky
-tests~\cite{ase14_environment}.
+tests~\cite{arcuri2014automated}.
 

### 2017-02-21 papers/sbst17/paper_sbst17.tex
arguably not trivial

--- 2017-02-21 papers/sbst17/paper_sbst17.tex
@@
 \EVOSUITE for JXPATH-7 failed in the instrumentation phase as a result
-of exceeding Java's 64k limit on the size of methods. A trivial fix
+of exceeding Java's 64k limit on the size of methods. A viable fix
 would be to stop instrumenting before the limit is reached, at the

### 2017-02-21 papers/sbst17/paper_sbst17.tex
Added some examples to try to answer the question 'why coverage decreased in some cases with higher time budget?'.

--- 2017-02-21 papers/sbst17/paper_sbst17.tex
@@
 specially for $budget=300s$, where the average across benchmarks
-decreased. This is possibly due to crashes or out-of-memory
-runtime errors.\TODO{confirm this conjecture}\TODO{look into details}
+decreased. This is possibly due to crashes or out-of-memory runtime
+errors. For instance, \EVOSUITE failed to generate any test suite in
+one out of three runs of OKHTTP-2 and RE2J-7 due to an
+\textit{out-of-memory error}, and in all executions of LA4J-3 and
+LA4J-7 due to a \textit{state exception}. In order to evaluate a
+fitness function, each test case evolved by the underline GA of
+\EVOSUITE has to be executed. However, its execution could fail due to
+several reasons: state exception (if a test case tries to re-initalize
+EvoSuite's sanbox, LA4J-3 and LA4J-7), timeout (OKHTTP-2), etc. In
+case of a timeout, \EVOSUITE logs the stacktrace of the thread in
+which each test case is executed, which could cause an out-of-memory
+error if the stack trace message is to long. RE2J-7: \TODO{I do not
+understand how a java.lang.OutOfMemoryError could be throw by
+CBranchSuiteFitness.java:145}.
+%
+To avoid low coverage of final classes with private constructors (like
+the class under test of benchmark OKHTTP-7), \EVOSUITE uses reflection
+to call the default constructor of the class under test. However,
+\TODO{EvoSuite tries to access a field of the cut (which is public
+static final) by using an instance of cut. It's still not clear why}.
+For other benchmarks such for example BCEL-1, BCEL-5, BCEL-7,
+\EVOSUITE failed due to mocking related issues.
 

### 2017-02-21 papers/sbst17/paper_sbst17.tex
dd.

@@
 resulting test suite to the previous, unminimised one, which as
-mentioned before, is more likely to break. Partial minimisation might
-be worth investigating to alleviate this issue.
+mentioned before, is more likely to break. Techniques such as
+\textit{partial minimisation} to only select a few test cases to be
+minimised, rather than all test cases; or
+\textit{delta-debugging}~\cite{zellerdd}, which could isolate the
+relevant statements of each test case, might be worth investigating
+to alleviate this issue.
 

### 2017-02-21 papers/sbst17/paper_sbst17.tex
mocking

@@
 % Mocking
-\TODO{Add some stats on mocking}
+As mentioned in the previous section, \EVOSUITE now can use private
+API access and functional mocking in addition to environment
+mocking~\cite{ICST_Mocking17}. In the competition, a total of 20,921
+objects were mocked, 1,485 fields were set and 3,090 private methods
+were invoked using private API access, and environment classes were
+mocked 4,699 times, with \texttt{java.util.Random} and
+\texttt{java.io.File} being by far the most frequently mocked
+environment classes (resp. 1,286 and 1,121 times). Further
+investigation is needed to assess the impact of these mocking features
+on test generation effectiveness.
 

### 2017-02-21 papers/sbst17/paper_sbst17.tex
rm clearpage
omit env. mock

--- 2017-02-21 papers/sbst17/paper_sbst17.tex
@@
 % Mocking
-\TODO{Add some stats on mocking}
+As mentioned in the previous section, \EVOSUITE now uses private
+API access and functional mocking%  in addition to environment
+% mocking
+~\cite{ICST_Mocking17}. In the competition, a total of 20,921
+objects were mocked, 1,485 private fields were set and 3,090 private methods
+were invoked using mocked access% , and environment classes were
+% mocked 4,699 times, with \texttt{java.util.Random} and
+% \texttt{java.io.File} being by far the most frequently mocked
+% environment classes (resp. 1,286 and 1,121 times)
+. Further
+investigation is needed to assess the impact of these mocking features
+on test generation effectiveness for the benchmarks in the competition.
 
@@
 %\def\IEEEbibitemsep{6pt}
-\clearpage
+%\clearpage
 \bibliographystyle{IEEEtranS}

### 2017-02-21 papers/sbst17/paper_sbst17.tex
on vagueness

@@
 % Look at benchmarks where coverage decreased with increased budget
-Although coverage generally increased with higher time budgets, there
-are instances where this expected behaviour was not observed,
-specially for $budget=300s$, where the average across benchmarks
-decreased. This is possibly due to crashes or out-of-memory runtime
-errors. For instance, \EVOSUITE failed to generate any test suite in
-one out of three runs of OKHTTP-2 and RE2J-7 due to an
-\textit{out-of-memory error}, and in all executions of LA4J-3 and
-LA4J-7 due to a \textit{state exception}. In order to evaluate a
-fitness function, each test case evolved by the underline GA of
-\EVOSUITE has to be executed. However, its execution could fail due to
-several reasons: state exception (if a test case tries to re-initalize
-EvoSuite's sanbox, LA4J-3 and LA4J-7), timeout (OKHTTP-2), etc. In
-case of a timeout, \EVOSUITE logs the stacktrace of the thread in
-which each test case is executed, which could cause an out-of-memory
-error if the stack trace message is to long. RE2J-7: \TODO{I do not
-understand how a java.lang.OutOfMemoryError could be throw by
-CBranchSuiteFitness.java:145}.
-%
-To avoid low coverage of final classes with private constructors (like
-the class under test of benchmark OKHTTP-7), \EVOSUITE uses reflection
-to call the default constructor of the class under test. However,
-\TODO{EvoSuite tries to access a field of the cut (which is public
-static final) by using an instance of cut. It's still not clear why}.
-For other benchmarks such for example BCEL-1, BCEL-5, BCEL-7,
-\EVOSUITE failed due to mocking related issues.
+As expected, both branch coverage and mutation score generally
+increased with higher time budgets, although in some cases, specially
+at $budget=300s$, a decrease was observed for some benchmarks. Having
+run only three repetitions of the tool per time budget, it is fair to
+assume the decreases are due to bugs affecting executions with
+$budget=300s$ by chance. A preliminary investigation on the source of
+this loss of coverage revealed that out-of-memory errors (e.g., for
+OKHTTP-2 and RE2J-7), sandboxing problems (e.g., for LA4J-3 and
+LA4J-7), and mocking-related issues (e.g., for BCEL-1, BCEL-5, BCEL-7)
+are some of the problems in \EVOSUITE.
+
+% Although coverage generally increased with higher time budgets, there
+% are instances where this expected behaviour was not observed,
+% specially for $budget=300s$, where the average across benchmarks
+% decreased. This is possibly due to crashes or out-of-memory runtime
+% errors. For instance, \EVOSUITE failed to generate any test suite in
+% one out of three runs of OKHTTP-2 and RE2J-7 due to an
+% \textit{out-of-memory error}, and in all executions of LA4J-3 and
+% LA4J-7 due to a \textit{state exception}. In order to evaluate a
+% fitness function, each test case evolved by the underline GA of
+% \EVOSUITE has to be executed. However, its execution could fail due to
+% several reasons: state exception (if a test case tries to re-initalize
+% EvoSuite's sanbox, LA4J-3 and LA4J-7), timeout (OKHTTP-2), etc. In
+% case of a timeout, \EVOSUITE logs the stacktrace of the thread in
+% which each test case is executed, which could cause an out-of-memory
+% error if the stack trace message is to long. RE2J-7: \TODO{I do not
+% understand how a java.lang.OutOfMemoryError could be throw by
+% CBranchSuiteFitness.java:145}.
+% %
+% To avoid low coverage of final classes with private constructors (like
+% the class under test of benchmark OKHTTP-7), \EVOSUITE uses reflection
+% to call the default constructor of the class under test. However,
+% \TODO{EvoSuite tries to access a field of the cut (which is public
+% static final) by using an instance of cut. It's still not clear why}.
+% For other benchmarks such for example BCEL-1, BCEL-5, BCEL-7,
+% \EVOSUITE failed due to mocking related issues.
 
@@
 % environment classes (resp. 1,286 and 1,121 times)
-. Further
+, adding up to represent only 1.09\% of the total number of lines of code
+in the \EVOSUITE-generated test suites (2,329,361 LOC). Further
 investigation is needed to assess the impact of these mocking features
-on test generation effectiveness for the benchmarks in the competition.
+on test generation effectiveness for the benchmarks in the
+competition.
 

### 2017-02-21 papers/sbst17/paper_sbst17.tex
on vagueness 2

@@
 increased with higher time budgets, although in some cases, specially
-at $budget=300s$, a decrease was observed for some benchmarks. Having
-run only three repetitions of the tool per time budget, it is fair to
-assume the decreases are due to bugs affecting executions with
-$budget=300s$ by chance. A preliminary investigation on the source of
-this loss of coverage revealed that out-of-memory errors (e.g., for
-OKHTTP-2 and RE2J-7), sandboxing problems (e.g., for LA4J-3 and
-LA4J-7), and mocking-related issues (e.g., for BCEL-1, BCEL-5, BCEL-7)
-are some of the problems in \EVOSUITE.
+with $budget=300s$, a decrease was observed for some
+benchmarks. Having run only three repetitions of the tool per time
+budget, it is fair to assume the decreases are due to bugs affecting
+executions by chance. A preliminary investigation on the source of
+this loss of coverage revealed that memory management (e.g.,
+out-of-memory errors for OKHTTP-2 and RE2J-7), sandboxing (e.g.,
+affecting all executions for LA4J-3 and LA4J-7), and mocking
+(affecting BCEL-1, BCEL-5 and BCEL-7, for example) are some of the
+aspects that require attention and debugging in \EVOSUITE.
 

### 2017-02-21 papers/sbst17/paper_sbst17.tex
intro, bits and bobs

@@
 \newcommand{\EVOSUITE}{{\sc EvoSuite}\xspace}
+\newcommand{\JTEXPERT}{{\sc jTExpert}\xspace}
+\newcommand{\RANDOOP}{{\sc Randoop}\xspace}
+\newcommand{\TT}{{\sc T3}\xspace}
+
 \newcommand{\MUTEST}{{\sc $\mu$Test}\xspace}
@@
 competition at the International Workshop on Search-Based Software
-Testing (SBST) 2017, four tools competed on a set of open source Java
-classes. This paper describes the results of applying the \EVOSUITE
-test generation tool~\cite{FrA11c} in this competition. Details about
-the procedure of the competition, the technical framework, and the
-benchmark classes can be found in~\cite{sbst17competition}.  In this
-competition, \EVOSUITE achieved a 1457.3 overall score, which was the
-highest among the competing and baseline tools.
+Testing (SBST) 2017, two tools, \EVOSUITE and \JTEXPERT, competed on a
+set of 69 open-source Java classes. Two other tools, \RANDOOP and \TT,
+and existing open-source test suites were used as baseline. This paper
+describes the results obtained by the \EVOSUITE test generation
+tool~\cite{FrA11c} in this competition. Details about the procedure of
+the competition, the technical framework, and the benchmark classes
+can be found in~\cite{sbst17competition}.  In this competition,
+\EVOSUITE achieved a 1457.3 overall score, which was the highest among
+the competing and baseline tools.
 
@@
 \caption{Classification of the \EVOSUITE unit test generation
-  tool.}\label{tool-description}
+  tool}\label{tool-description}
 \resizebox{1.0\columnwidth}{!}{  
@@
   Interaction &  Through the command line, and plugins for IntelliJ, Maven and Eclipse\\
-  User guidance &  manual verification of assertions for functional faults\\
+  User guidance &  Manual verification of assertions for functional faults\\
   Source of information &  http://www.evosuite.org \\
@@
   \hline
-  Effectiveness and Scalability & See~\cite{GoA_TSE12,fraser2014large}. \\
+  Effectiveness and Scalability & See~\cite{GoA_TSE12,fraser2014large} \\
 %Completeness & \\
@@
 %------------------------------------------------------------------------- 
-\section{Benchmark results}
+\section{Benchmark Results}
 
@@
 
-\subsection{Overall results}
+\subsection{Overall Results}
 
@@
 much lower than the number of flaky tests produced by the competing
-and baseline tools (\FlakyTthree by T3, \FlakyJtexpert by JTExpert, and
-\FlakyRandoop by Randoop). We attribute these results---also
+and baseline tools (\FlakyTthree by \TT, \FlakyJtexpert by \JTEXPERT,
+and \FlakyRandoop by \RANDOOP). We attribute these results---also
 consistent with previous years' results---to the way \EVOSUITE handles

### 2017-02-21 papers/sbst17/paper_sbst17.tex
Edits

--- 2017-02-21 papers/sbst17/paper_sbst17.tex
@@
 benchmark classes can be found in~\cite{sbst17competition}.  In this
-competition, \EVOSUITE achieved a 1457.3 overall score, which was the
-highest among the competing and baseline tools.
+competition, \EVOSUITE achieved an overall score of 1457.3, which was
+the highest among the competing and baseline tools.
 
@@
 covered goals from the fitness function and stores the corresponding
-test cases is now enabled by default in \EVOSUITE.
+test cases, is now enabled by default in \EVOSUITE.
 
@@
 % Look at benchmarks that always failed
-\EVOSUITE failed to produce any test suite for benchmarks JXPATH-7 and
+\EVOSUITE failed to produce any test suites for benchmarks JXPATH-7 and
 OKHTTP-8, and also struggled often for benchmarks LA4J-3, LA4J-7,
 BCEL-9 (highlighted in Table~\ref{table:results}). All executions of
-\EVOSUITE for JXPATH-7 failed in the instrumentation phase as a result
-of exceeding Java's 64k limit on the size of methods. A viable fix
+\EVOSUITE for JXPATH-7 failed in the instrumentation phase, where
+Java's 64k limit on the size of methods was exceeded. A viable fix
 would be to stop instrumenting before the limit is reached, at the
@@
 As expected, both branch coverage and mutation score generally
-increased with higher time budgets, although in some cases, specially
+increased with higher time budgets, although in some cases, especially
 with $budget=300s$, a decrease was observed for some
@@
 \textit{partial minimisation} to only select a few test cases to be
-minimised, rather than all test cases; or
+minimised, rather than all test cases, or
 \textit{delta-debugging}~\cite{zellerdd}, which could isolate the

### 2017-02-21 papers/sbst17/paper_sbst17.tex
Edits edits edits

--- 2017-02-21 papers/sbst17/paper_sbst17.tex
@@
 can be found in~\cite{sbst17competition}.  In this competition,
-\EVOSUITE achieved a 1457.3 overall score, which was the highest among
-the competing and baseline tools.
+\EVOSUITE achieved an overall score of 1457.3, which was the highest
+among the competing and baseline tools.
 
@@
 \textit{partial minimisation} to only select a few test cases to be
-minimised, rather than all test cases; or
-\textit{delta-debugging}~\cite{zellerdd}, which could isolate the
-relevant statements of each test case, might be worth investigating
-to alleviate this issue.
+minimised, rather than all test cases, or more efficient minimisation
+based on \textit{delta-debugging}~\cite{LOZCM07}, might be worth
+investigating to alleviate this issue.
 
@@
 % environment classes (resp. 1,286 and 1,121 times)
-, adding up to represent only 1.09\% of the total number of lines of code
-in the \EVOSUITE-generated test suites (2,329,361 LOC). Further
-investigation is needed to assess the impact of these mocking features
-on test generation effectiveness for the benchmarks in the
+, adding up to represent only 1.09\% of the total number of lines of
+code in the \EVOSUITE-generated test suites (2,329,361 LOC). Further
+investigation would be needed to assess the impact of these mocking
+features on test generation effectiveness for the benchmarks in the
 competition.

### 2017-02-21 papers/sbst17/paper_sbst17.tex
BE

@@
   \EVOSUITE is a search-based tool that automatically generates unit
-  tests for Java code.  This paper summarizes the results and
+  tests for Java code.  This paper summarises the results and
   experiences of \EVOSUITE's participation at the fifth unit testing
@@
 competition~\cite{evosuiteAtSbst2016} to distribute the overall time
-budget onto the different phases of \EVOSUITE (e.g., initialization,
-search, minimization, assertion generation, compilation check, removal
+budget onto the different phases of \EVOSUITE (e.g., initialisation,
+search, minimisation, assertion generation, compilation check, removal
 of flaky tests). That is, 50\% of the time was allocated to the
@@
 % \EVOSUITE has to be executed. However, its execution could fail due to
-% several reasons: state exception (if a test case tries to re-initalize
+% several reasons: state exception (if a test case tries to re-initialise
 % EvoSuite's sanbox, LA4J-3 and LA4J-7), timeout (OKHTTP-2), etc. In

### 2017-02-21 papers/sbst17/paper_sbst17.tex
title
done

@@
 %\title{Unit Testing Tool competition: Results for EvoSuite}
-\title{EvoSuite at the SBST 2017 Tool Competition}
+\title{\EVOSUITE at the SBST 2017 Tool Competition}
 
@@
 Like in previous instances of the competition, we enabled the
-post-processing step of test minimisation (but not for efficiency
-reasons, but because minimised tests are less likely to break). To
+post-processing step of test minimisation---not for efficiency
+reasons, but because minimised tests are less likely to break. To
 reduce the overall time of test generation we included all assertions
@@
 contest. Coverage is generally in the expected range, with clear
-overall increases for higher time budgets. With $budget=480s$, the
+overall increases for higher time budgets. With the highest time
+budget of $480s$, the
 average branch coverage achieved was \AvgCovG (slightly higher than
@@
 
-With an overall score of 1126.7, \EVOSUITE achieved the highest score
-of all tools in the competition.
+This paper reports on the participation of the \EVOSUITE test
+generation tool in the 5th SBST Java Unit Testing Tool Contest. With
+an overall score of 1126.7, \EVOSUITE achieved the highest score of
+all tools in the competition.
 

### 2017-02-22 papers/sbst17/paper_sbst17.tex
TODO
new data for manual tests

@@
 		\mymarginpar{\raggedright\hbadness=10000\tiny\it #1\par}}
+	% TODO marker
+	\newcommand{\TODO}[1]{\sethlcolor{yellow}\textbf{\textcolor{ScarletRed}{\hl{TODO: #1}}}\xspace}
 \else
 	\newcommand\remark[1]	{}
+	\newcommand{\TODO}[1]{}
 \fi
@@
 \newcommand{\CS}{{\sc SF100}\xspace}
-
-% TODO marker
-\newcommand{\TODO}[1]{\sethlcolor{yellow}\textbf{\textcolor{ScarletRed}{\hl{TODO: #1}}}\xspace}
 
@@
 This year, the contest also included manually written test suites as
-baseline. \EVOSUITE significantly outperformed this manual baseline as
-well, both in terms of branch coverage (avg. \AvgCovEvosuite vs
-\AvgCovManual, with Vargha-Delaney's $A_{12}=\EvoManCovA$ and
-$p\EvoManCovPV$) and mutation scores (avg. \AvgMutEvosuite vs
-\AvgMutManual, with $A_{12}=\EvoManMutA$ and
-$p\EvoManMutPV$).\TODO{Does showing A12 make sense if there's only one
-  manual test suite per benchmark?}
+baseline (only for 63 out of the 69 benchmarks). The results indicate
+that there is no significant difference in branch coverage between
+\EVOSUITE-generated test suites (avg. \AvgCovEvosuite) and manually
+written ones (avg. \AvgCovManual), with Vargha-Delaney's
+$A_{12}=\EvoManCovA$ and $p=\EvoManCovPV$. In terms of mutation
+scores, however, the results show
+that---unsurprisingly---automatically generated assertions are weaker
+than manually written ones: the average \EVOSUITE mutation score for
+these 63 benchmarks is \AvgMutEvosuite, significantly lower than the
+average \AvgMutManual obtained by developer-written test suites, with
+$A_{12}=\EvoManMutA$ and $p\EvoManMutPV$.\TODO{Does showing A12 make
+  sense if there's only one manual test suite per benchmark?}
 
@@
 minimisation phase timed out and hence \EVOSUITE reverted the
-resulting test suite to the previous, unminimised one, which as
-mentioned before, is more likely to break. Techniques such as
-\textit{partial minimisation} to only select a few test cases to be
-minimised, rather than all test cases, or more efficient minimisation
-based on \textit{delta-debugging}~\cite{LOZCM07}, might be worth
-investigating to alleviate this issue.
+resulting test suite to its previous, unminimised version, which as
+mentioned before is more likely to break. A \textit{partial
+  minimisation} approach to select and minimise only a reduced subset
+of tests, or a more efficient minimisation approach based on
+\textit{delta-debugging}~\cite{LOZCM07}, might be worth exploring to
+alleviate this issue.
 

### 2017-02-22 papers/sbst17/paper_sbst17.tex
minor fix, and fixed score in conclusion

@@
 can be found in~\cite{sbst17competition}.  In this competition,
-\EVOSUITE achieved an overall score of 1457.3, which was the highest
+\EVOSUITE achieved an overall score of 1457, which was the highest
 among the competing and baseline tools.
@@
 under test and all its dependencies), \EVOSUITE automatically produces
-a set of JUnit test cases that maximise the achieved code
+a set of JUnit test cases aimed at maximising code
 coverage. \EVOSUITE can be used on the command line, or through
@@
 generation tool in the 5th SBST Java Unit Testing Tool Contest. With
-an overall score of 1126.7, \EVOSUITE achieved the highest score of
+an overall score of 1457, \EVOSUITE achieved the highest score of
 all tools in the competition.

### 2017-02-22 papers/sbst17/paper_sbst17.tex
drop todo

@@
 average \AvgMutManual obtained by developer-written test suites, with
-$A_{12}=\EvoManMutA$ and $p\EvoManMutPV$.\TODO{Does showing A12 make
-  sense if there's only one manual test suite per benchmark?}
+$A_{12}=\EvoManMutA$ and $p\EvoManMutPV$.
 

### 2018-01-30 papers/sbst18/mainTable.tex
2018

\begin{tabular}{ l rrrrrrr rrrrrrrr}\toprule 
 Benchmark &  \multicolumn{7}{c}{Branch Coverage} &  \multicolumn{7}{c}{Mutation Score}\\ 
 & 10s & 30s & 60s & 120s & 240s & 300s & 480s & 10s & 30s & 60s & 120s & 240s & 300s & 480s \\ 
\midrule 
BCEL-1 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                           \cellcolor{light-gray}
                                                           \textcolor{black}{0.0}\%
 & mocking\\ 
BCEL-10 & 63.9\% & 56.0\%\\ 
BCEL-2 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                           \cellcolor{light-gray}
                                                           \textcolor{black}{0.0}\%
 & \multicolumn{12}{l}{Failed to use Mockito on interface java.io.DataInput}\\ 
BCEL-3 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                           \cellcolor{light-gray}
                                                           \textcolor{black}{0.0}\%
 & \multicolumn{12}{l}{java.lang.ClassCastException: java.lang.Byte
   cannot be cast to java.lang.Short at org.evosuite.testcase.statements.FunctionalMockStatement\$1.fixBoxing(FunctionalMockStatement.java:849)}\\ 
BCEL-4 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                           \cellcolor{light-gray}
                                                           \textcolor{black}{0.0}\%
 & \multicolumn{13}{l}{Minimisation and junit check timeout; test
   suite's coverage: resulting coverage 74\% } \\ 
BCEL-5 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                           \cellcolor{light-gray}
                                                           \textcolor{black}{0.0}\%
 & \multicolumn{13}{l}{no error, evosuite reported coverage 42\%}\\ 
BCEL-6 & 72.2\% & 78.0\%\\ 
BCEL-7 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                           \cellcolor{light-gray} \textcolor{black}{0.0}\%& \multicolumn{13}{l}{ERROR FunctionalMockStatement - IAE on public java.lang.String org.apache.bcel.classfile.ConstantPool.getConstantString(int,byte) throws org.apache.bcel.classfile.ClassFormatException> when called with [0, null}\\ 
BCEL-8 & 95.8\% & 96.9\%\\ 
BCEL-9 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                           \cellcolor{light-gray}
                                                           \textcolor{black}{0.0}\%
 & \multicolumn{13}{l}{ERROR FunctionalMockStatement - Failed to use Mockito on interface java.io.DataInput: java.lang.Byte cannot be cast to java.lang.Short}\\ 
FREEHEP-1 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                              \cellcolor{light-gray}
                                                              \textcolor{black}{0.0}\%
 & \multicolumn{13}{l}{Resulting test suite's coverage: 98\%;
   minimisation timed out}\\ 
FREEHEP-10 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                               \cellcolor{light-gray}
                                                               \textcolor{black}{0.0}\%
 & \multicolumn{13}{l}{Resulting test suite's coverage: 83\%;
   JUNIT\_CHECK timed out}\\ 
FREEHEP-2 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                              \cellcolor{light-gray}
                                                              \textcolor{black}{0.0}\%
&  \multicolumn{13}{l}{Resulting test suite's coverage: 85\%; no error} \\ 
FREEHEP-3 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                              \cellcolor{light-gray}
                                                              \textcolor{black}{0.0}\%
 &  \multicolumn{13}{l}{Resulting test suite's coverage: 81\%; no
   error, flaky tests}\\ 
FREEHEP-4 & 60.3\% & 24.3\%\\ 
FREEHEP-5 & 69.1\% & 84.4\%\\ 
FREEHEP-6 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                              \cellcolor{light-gray}
                                                              \textcolor{black}{0.0}\%
  &  \multicolumn{13}{l}{Resulting test suite's coverage: 87\%; no
   error, flaky tests}\\
FREEHEP-7 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                              \cellcolor{light-gray} \textcolor{black}{0.0}\%   &  \multicolumn{13}{l}{Resulting test suite's coverage: 81\%; no
   error, flaky tests}\\ 
FREEHEP-8 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                              \cellcolor{light-gray}
                                                              \textcolor{black}{0.0}\%
 & \multicolumn{13}{l}{87\% coverage; Permissions denied during test execution:  java.lang.RuntimePermission: writeFileDescriptor: 7}\\ 
FREEHEP-9 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                              \cellcolor{light-gray}
                                                              \textcolor{black}{0.0}\% 
 & \multicolumn{13}{l}{57\% coverage; minimisation and junit\_check
   time out}\\ 
GSON-1 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                           \cellcolor{light-gray}
                                                           \textcolor{black}{0.0}\%

 & \multicolumn{13}{l}{test suite's coverage: 58\% .  Permissions denied during test execution:  java.lang.RuntimePermission: writeFileDescriptor: 1} \\ 
GSON-10 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                            \cellcolor{light-gray}
                                                            \textcolor{black}{0.0}\%
 &  \multicolumn{13}{l}{java.lang.RuntimeException: not implemented:
   class sun.reflect.generics.reflectiveObjects.TypeVariableImpl at com.googlecode.gentyref.GenericTypeReflector.isSuperType(GenericTypeReflector.java:218)} \\ 
GSON-2 & 33.5\% & 31.1\%\\ 
GSON-3 & 82.5\% & 83.9\%\\ 
GSON-4 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                           \cellcolor{light-gray}
                                                           \textcolor{black}{0.0}\%
 & \multicolumn{13}{l}{31\% coverage; no errors}\\ 
GSON-5 & 33.3\% & 36.5\%\\ 
GSON-6 & 90.7\% & 71.8\%\\ 
GSON-7 & 81.6\% & 94.0\%\\ 
GSON-8 & 90.7\% & 75.8\%\\ 
GSON-9 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                           \cellcolor{light-gray}
                                                           \textcolor{black}{0.0}\%
 & \multicolumn{13}{l}{java.lang.RuntimeException: not implemented: class sun.reflect.generics.reflectiveObjects.TypeVariableImpl}\\ 
IMAGE-1 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                            \cellcolor{light-gray}
                                                            \textcolor{black}{0.0}\%
 & \multicolumn{13}{l}{ERROR FunctionalMockStatement - Failed to use Mockito on class org.apache.commons.imaging.formats.tiff.write.TiffOutputDirectory}\\ 
IMAGE-2 & 85.0\% & 99.0\%\\ 
IMAGE-3 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                            \cellcolor{light-gray}
                                                            \textcolor{black}{0.0}\%
 & \multicolumn{13}{l}{Multiple errors like: ERROR ClassStateSupport - Could not initialize org.apache.commons.imaging.formats.tiff.TiffImageMetadata}\\ 
IMAGE-4 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                            \cellcolor{light-gray}
                                                            \textcolor{black}{0.0}\% 
& \multicolumn{13}{l}{coverage 76\%; JUNIT\_CHECK timed out; Permissions denied during test execution: java.lang.RuntimePermission: writeFileDescriptor: 3}
  \\ 
JXPATH-1 & 27.2\% & 25.4\%\\ 
JXPATH-10 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                              \cellcolor{light-gray}
                                                              \textcolor{black}{0.0}\%
 & \multicolumn{13}{l}{coverage 76\%; some errors (java.lang.ClassNotFoundException:
   Class not found: org/jdom/Element: java.lang.NullPointerException:
   Class not found org/jdom/Element); flaky tests}\\ 
JXPATH-2 & 81.4\% & 70.5\%\\ 
JXPATH-3 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                             \cellcolor{light-gray}
                                                             \textcolor{black}{0.0}\% 
 & \multicolumn{13}{l}{coverage 76\%; some errors (ERROR ClassStateSupport - Could not initialize org.apache.commons.jxpath.JXPathContextFactory); flaky tests}\\ 
JXPATH-4 & 81.4\% & 75.0\%\\ 
JXPATH-5 & 92.0\% & 92.9\%\\ 
JXPATH-6 & 93.5\% & 90.0\%\\ 
JXPATH-7 & 10.9\% & 7.7\%\\ 
JXPATH-8 & 53.3\% & 42.8\%\\ 
JXPATH-9 & 56.1\% & 27.9\%\\ 
LA4J-1 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                           \cellcolor{light-gray}
                                                           \textcolor{black}{0.0}\%
 & \multicolumn{13}{l}{coverage 75\%, JUNIT\_CHECK timed out}\\ 
LA4J-10 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                            \cellcolor{light-gray}
                                                            \textcolor{black}{0.0}\%
 & \multicolumn{13}{l}{Mocking problem: ERROR FunctionalMockStatement - Failed to use Mockito on class org.la4j.iterator.VectorIterator: tried to access class org.la4j.iterator.CursorIterator from class org.la4j.iterator.VectorIterator\$MockitoMock}\\ 
LA4J-2 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                           \cellcolor{light-gray} \textcolor{black}{0.0}\%
 & \multicolumn{13}{l}{same as above}\\ 
LA4J-3 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                           \cellcolor{light-gray}
                                                           \textcolor{black}{0.0}\%
 & \multicolumn{13}{l}{Coverage 73\%, minimisation and junit check
   timed out}\\ 
LA4J-4 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                           \cellcolor{light-gray}
                                                           \textcolor{black}{0.0}\%
 & \multicolumn{13}{l}{Coverage 88\%; minimisation timeout, errors compiling and checking tests(ERROR ClassStateSupport - Could not initialize org.la4j.iterator.JoinFunction)}\\ 
LA4J-5 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                           \cellcolor{light-gray}
                                                           \textcolor{black}{0.0}\%
 & \multicolumn{13}{l}{Coverage 55\%; search, minimisation and writing tests timed out}\\ 
LA4J-6 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                           \cellcolor{light-gray} \textcolor{black}{0.0}\%
 & \multicolumn{13}{l}{Mocking problem: ERROR FunctionalMockStatement - Failed to use Mockito on class org.la4j.iterator.VectorIterator: tried to access class org.la4j.iterator.CursorIterator from class org.la4j.iterator.VectorIterator\$MockitoMock}\\ 
LA4J-7 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                           \cellcolor{light-gray}
                                                           \textcolor{black}{0.0}\% 
& \multicolumn{13}{l}{Resulting test suite's coverage: 57\%; timeout when
  writing tests}\\ 
LA4J-8 & 75.0\% & 70.0\%\\ 
LA4J-9 & 85.1\% & 29.8\%\\ 
OKHTTP-1 & 7.7\% & 5.6\%\\ 
OKHTTP-2 & 50.0\% & 50.0\%\\ 
OKHTTP-3 & 75.8\% & 69.0\%\\ 
OKHTTP-4 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                             \cellcolor{light-gray} \textcolor{black}{0.0}\%
& \multicolumn{13}{l}{Coverage 62\%; Multiple errors (eg ERROR ConcreteClassAnalyzer - Problem for okhttp3.internal.http.HttpHeaders. Class not found: okhttp3.MultipartBody)}\\ 
OKHTTP-5 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                             \cellcolor{light-gray} \textcolor{black}{0.0}\%
& \multicolumn{13}{l}{Coverage 48\%; problem executing tests: java.security.SecurityPermission:  createAccessControlContext: 2 javax.security.auth.AuthPermission: getSubject: 21}\\ 
OKHTTP-6 & 84.3\% & 86.4\%\\ 
OKHTTP-7 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                             \cellcolor{light-gray} \textcolor{black}{0.0}\%
&  \multicolumn{13}{l}{Coverage 40\%; error Compiling and checking tests}\\ 
OKHTTP-8 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                             \cellcolor{light-gray} \textcolor{black}{0.0}\%
& \multicolumn{13}{l}{Classpath problem? Caused by: java.lang.ClassNotFoundException: Class 'okio/Buffer.class' should be in target project, but could not be found!}\\ 
RE2J-1 & 56.5\% & 39.4\%\\ 
RE2J-2 & 92.9\% & 66.7\%\\ 
RE2J-3 & 42.9\% & 39.7\%\\ 
RE2J-4 & 92.7\% & 88.0\%\\ 
RE2J-5 & 68.2\% & 41.7\%\\ 
RE2J-6 & 85.1\% & 68.3\%\\ 
RE2J-7 & 39.5\% & 35.2\%\\ 
RE2J-8 & 91.8\% & 82.6\%\\ 
\midrule 
Average  &  32.9\% &  29.1\%\\ 
\bottomrule 
\end{tabular}

### 2018-01-30 papers/sbst18/paper_sbst18.tex
2018

--- 2017-02-22 papers/sbst17/paper_sbst17.tex
@@
   experiences of \EVOSUITE's participation at the fifth unit testing
-  competition at SBST 2017, where \EVOSUITE achieved the highest
+  competition at SBST 2018, where \EVOSUITE achieved the highest
   overall score.
@@
   \caption{\label{table:results}Detailed results of \EVOSUITE on the SBST benchmark classes.}
-\resizebox{\textwidth}{!}{  
+\resizebox{0.7\textwidth}{!}{  
 \input{mainTable.tex}

### 2018-01-30 papers/sbst18/data/6thresults/collect.sh

@@ -1,0 +1,2 @@
+# creates single transcript file cointaining data from all transcript.csv files
+>single_transcript.csv;header="";for csv in $( find . -name "transcript.csv" ); do [[ -z $header ]] && header="first row" && head -n 1 "$csv" >> single_transcript.csv; awk '{$1=$1};1' "$csv" | grep . | tail -n +2 >> single_transcript.csv; done

### 2018-01-30 papers/sbst18/data/6thresults/process.sh

@@ -1,0 +1,3 @@
+# create error files for all subfolders
+for i in * ; do printf $i; find $i -type f -name *.log -exec grep -nH -e "ERROR" {} + > $i/errors.txt ; done
+

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/BCEL-10_1/temp/testcases/org/apache/bcel/verifier/structurals/Subroutines_ESTest_scaffolding.java

@@ -1,0 +1,459 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 19:59:18 GMT 2018
+ */
+
+package org.apache.bcel.verifier.structurals;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+@EvoSuiteClassExclude
+public class Subroutines_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "org.apache.bcel.verifier.structurals.Subroutines"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/BCEL-2_1/temp/testcases/org/apache/bcel/verifier/structurals/InstConstraintVisitor_ESTest.java

@@ -1,0 +1,4924 @@
+/*
+ * This file was automatically generated by EvoSuite
+ * Wed Jan 24 18:50:38 GMT 2018
+ */
+
+package org.apache.bcel.verifier.structurals;
+
+import org.junit.Test;
+import static org.junit.Assert.*;
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+import static org.evosuite.runtime.EvoAssertions.*;
+import org.apache.bcel.classfile.Constant;
+import org.apache.bcel.classfile.ConstantPool;
+import org.apache.bcel.generic.AALOAD;
+import org.apache.bcel.generic.AASTORE;
+import org.apache.bcel.generic.ACONST_NULL;
+import org.apache.bcel.generic.ALOAD;
+import org.apache.bcel.generic.ANEWARRAY;
+import org.apache.bcel.generic.ARETURN;
+import org.apache.bcel.generic.ARRAYLENGTH;
+import org.apache.bcel.generic.ASTORE;
+import org.apache.bcel.generic.ATHROW;
+import org.apache.bcel.generic.BALOAD;
+import org.apache.bcel.generic.BASTORE;
+import org.apache.bcel.generic.BIPUSH;
+import org.apache.bcel.generic.BREAKPOINT;
+import org.apache.bcel.generic.BasicType;
+import org.apache.bcel.generic.BranchHandle;
+import org.apache.bcel.generic.BranchInstruction;
+import org.apache.bcel.generic.CALOAD;
+import org.apache.bcel.generic.CASTORE;
+import org.apache.bcel.generic.CHECKCAST;
+import org.apache.bcel.generic.ConstantPoolGen;
+import org.apache.bcel.generic.D2F;
+import org.apache.bcel.generic.D2I;
+import org.apache.bcel.generic.D2L;
+import org.apache.bcel.generic.DADD;
+import org.apache.bcel.generic.DALOAD;
+import org.apache.bcel.generic.DASTORE;
+import org.apache.bcel.generic.DCMPG;
+import org.apache.bcel.generic.DCMPL;
+import org.apache.bcel.generic.DCONST;
+import org.apache.bcel.generic.DDIV;
+import org.apache.bcel.generic.DLOAD;
+import org.apache.bcel.generic.DMUL;
+import org.apache.bcel.generic.DNEG;
+import org.apache.bcel.generic.DREM;
+import org.apache.bcel.generic.DRETURN;
+import org.apache.bcel.generic.DSTORE;
+import org.apache.bcel.generic.DSUB;
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/BCEL-4_1/temp/testcases/org/apache/bcel/generic/InstructionList_ESTest_scaffolding.java

@@ -1,0 +1,472 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 18:53:37 GMT 2018
+ */
+
+package org.apache.bcel.generic;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+import java.util.concurrent.ExecutorService;
+import java.util.concurrent.Executors;
+import java.util.concurrent.Future;
+import java.util.concurrent.TimeUnit;
+
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+@EvoSuiteClassExclude
+public class InstructionList_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  protected static ExecutorService executor; 
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "org.apache.bcel.generic.InstructionList"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/BCEL-5_1/temp/testcases/org/apache/bcel/verifier/statics/Pass3aVerifier_ESTest.java

@@ -1,0 +1,803 @@
+/*
+ * This file was automatically generated by EvoSuite
+ * Wed Jan 24 18:25:42 GMT 2018
+ */
+
+package org.apache.bcel.verifier.statics;
+
+import org.junit.Test;
+import static org.junit.Assert.*;
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+import static org.evosuite.runtime.EvoAssertions.*;
+import org.apache.bcel.verifier.VerificationResult;
+import org.apache.bcel.verifier.Verifier;
+import org.apache.bcel.verifier.statics.Pass3aVerifier;
+import org.evosuite.runtime.EvoRunner;
+import org.evosuite.runtime.EvoRunnerParameters;
+import org.evosuite.runtime.ViolatedAssumptionAnswer;
+import org.junit.runner.RunWith;
+
+@RunWith(EvoRunner.class) @EvoRunnerParameters(mockJVMNonDeterminism = true, useVFS = true, useVNET = true, resetStaticState = true, separateClassLoader = true, useJEE = true) 
+public class Pass3aVerifier_ESTest extends Pass3aVerifier_ESTest_scaffolding {
+
+  @Test(timeout = 4000)
+  public void test00()  throws Throwable  {
+      VerificationResult verificationResult0 = VerificationResult.VR_NOTYET;
+      assertEquals(0, verificationResult0.getStatus());
+      assertEquals("Not yet verified.", verificationResult0.getMessage());
+      assertNotNull(verificationResult0);
+      assertEquals(0, VerificationResult.VERIFIED_NOTYET);
+      assertEquals(1, VerificationResult.VERIFIED_OK);
+      assertEquals(2, VerificationResult.VERIFIED_REJECTED);
+      
+      VerificationResult verificationResult1 = VerificationResult.VR_OK;
+      assertEquals(1, verificationResult1.getStatus());
+      assertEquals("Passed verification.", verificationResult1.getMessage());
+      assertNotNull(verificationResult1);
+      assertNotSame(verificationResult1, verificationResult0);
+      assertFalse(verificationResult1.equals((Object)verificationResult0));
+      assertEquals(1, VerificationResult.VERIFIED_OK);
+      assertEquals(0, VerificationResult.VERIFIED_NOTYET);
+      assertEquals(2, VerificationResult.VERIFIED_REJECTED);
+      
+      String string0 = "org.apache.bcel.classfile.Field";
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/BCEL-5_1/temp/testcases/org/apache/bcel/verifier/statics/Pass3aVerifier_ESTest_scaffolding.java

@@ -1,0 +1,451 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 18:25:42 GMT 2018
+ */
+
+package org.apache.bcel.verifier.statics;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+@EvoSuiteClassExclude
+public class Pass3aVerifier_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "org.apache.bcel.verifier.statics.Pass3aVerifier"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/BCEL-6_1/temp/testcases/org/apache/bcel/verifier/structurals/LocalVariables_ESTest.java

@@ -1,0 +1,1571 @@
+/*
+ * This file was automatically generated by EvoSuite
+ * Wed Jan 24 18:29:08 GMT 2018
+ */
+
+package org.apache.bcel.verifier.structurals;
+
+import org.junit.Test;
+import static org.junit.Assert.*;
+import static org.evosuite.runtime.EvoAssertions.*;
+import java.io.PipedInputStream;
+import java.io.PipedOutputStream;
+import org.apache.bcel.classfile.Constant;
+import org.apache.bcel.classfile.ConstantMethodHandle;
+import org.apache.bcel.generic.BIPUSH;
+import org.apache.bcel.generic.BasicType;
+import org.apache.bcel.generic.ConstantPoolGen;
+import org.apache.bcel.generic.ObjectType;
+import org.apache.bcel.generic.Type;
+import org.apache.bcel.verifier.structurals.LocalVariables;
+import org.apache.bcel.verifier.structurals.UninitializedObjectType;
+import org.evosuite.runtime.EvoRunner;
+import org.evosuite.runtime.EvoRunnerParameters;
+import org.evosuite.runtime.PrivateAccess;
+import org.evosuite.runtime.mock.java.io.MockFile;
+import org.evosuite.runtime.mock.java.io.MockRandomAccessFile;
+import org.evosuite.runtime.testdata.EvoSuiteFile;
+import org.evosuite.runtime.testdata.FileSystemHandling;
+import org.junit.runner.RunWith;
+
+@RunWith(EvoRunner.class) @EvoRunnerParameters(mockJVMNonDeterminism = true, useVFS = true, useVNET = true, resetStaticState = true, separateClassLoader = true, useJEE = true) 
+public class LocalVariables_ESTest extends LocalVariables_ESTest_scaffolding {
+
+  @Test(timeout = 4000)
+  public void test00()  throws Throwable  {
+      int int0 = 222;
+      LocalVariables localVariables0 = new LocalVariables(int0);
+      LocalVariables localVariables1 = localVariables0.getClone();
+      LocalVariables localVariables2 = localVariables1.getClone();
+      localVariables1.toString();
+      int int1 = 133;
+      BasicType basicType0 = Type.DOUBLE;
+      basicType0.toString();
+      localVariables1.set(int1, basicType0);
+      UninitializedObjectType uninitializedObjectType0 = null;
+      LocalVariables localVariables3 = localVariables2.getClone();
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/BCEL-6_1/temp/testcases/org/apache/bcel/verifier/structurals/LocalVariables_ESTest_scaffolding.java

@@ -1,0 +1,412 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 18:29:08 GMT 2018
+ */
+
+package org.apache.bcel.verifier.structurals;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+@EvoSuiteClassExclude
+public class LocalVariables_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "org.apache.bcel.verifier.structurals.LocalVariables"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
+    org.evosuite.runtime.Runtime.getInstance().resetRuntime(); 
+  } 
+
+  @AfterClass 
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/BCEL-8_1/temp/testcases/org/apache/bcel/generic/BranchInstruction_ESTest.java

@@ -1,0 +1,2138 @@
+/*
+ * This file was automatically generated by EvoSuite
+ * Wed Jan 24 18:35:53 GMT 2018
+ */
+
+package org.apache.bcel.generic;
+
+import org.junit.Test;
+import static org.junit.Assert.*;
+import static org.evosuite.runtime.EvoAssertions.*;
+import java.io.ByteArrayOutputStream;
+import java.io.DataOutputStream;
+import java.io.EOFException;
+import java.io.IOException;
+import java.io.PipedOutputStream;
+import org.apache.bcel.generic.BranchHandle;
+import org.apache.bcel.generic.BranchInstruction;
+import org.apache.bcel.generic.ConstantPoolGen;
+import org.apache.bcel.generic.DCONST;
+import org.apache.bcel.generic.DSTORE;
+import org.apache.bcel.generic.GOTO;
+import org.apache.bcel.generic.GOTO_W;
+import org.apache.bcel.generic.I2S;
+import org.apache.bcel.generic.IFGE;
+import org.apache.bcel.generic.IFGT;
+import org.apache.bcel.generic.IFLT;
+import org.apache.bcel.generic.IFNONNULL;
+import org.apache.bcel.generic.IFNULL;
+import org.apache.bcel.generic.IF_ACMPEQ;
+import org.apache.bcel.generic.IF_ACMPNE;
+import org.apache.bcel.generic.IF_ICMPGE;
+import org.apache.bcel.generic.IF_ICMPGT;
+import org.apache.bcel.generic.IF_ICMPLE;
+import org.apache.bcel.generic.IF_ICMPLT;
+import org.apache.bcel.generic.IF_ICMPNE;
+import org.apache.bcel.generic.INVOKEVIRTUAL;
+import org.apache.bcel.generic.IfInstruction;
+import org.apache.bcel.generic.Instruction;
+import org.apache.bcel.generic.InstructionComparator;
+import org.apache.bcel.generic.InstructionConstants;
+import org.apache.bcel.generic.InstructionHandle;
+import org.apache.bcel.generic.InstructionList;
+import org.apache.bcel.generic.JSR;
+import org.apache.bcel.generic.LAND;
+import org.apache.bcel.generic.LDIV;
+import org.apache.bcel.generic.LMUL;
+import org.apache.bcel.generic.LOOKUPSWITCH;
+import org.apache.bcel.generic.POP;
+import org.apache.bcel.generic.PUSH;
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/FREEHEP-10_1/temp/testcases/org/freehep/math/minuit/MnUserTransformation_ESTest_scaffolding.java

@@ -1,0 +1,111 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 18:46:28 GMT 2018
+ */
+
+package org.freehep.math.minuit;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+@EvoSuiteClassExclude
+public class MnUserTransformation_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "org.freehep.math.minuit.MnUserTransformation"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
+    org.evosuite.runtime.Runtime.getInstance().resetRuntime(); 
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/FREEHEP-1_1/temp/testcases/org/freehep/math/minuit/MnPlot_ESTest.java

@@ -1,0 +1,1394 @@
+/*
+ * This file was automatically generated by EvoSuite
+ * Wed Jan 24 19:02:43 GMT 2018
+ */
+
+package org.freehep.math.minuit;
+
+import org.junit.Test;
+import static org.junit.Assert.*;
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+import static org.evosuite.runtime.EvoAssertions.*;
+import java.util.Collection;
+import java.util.Iterator;
+import java.util.LinkedList;
+import java.util.List;
+import java.util.ListIterator;
+import org.evosuite.runtime.EvoRunner;
+import org.evosuite.runtime.EvoRunnerParameters;
+import org.evosuite.runtime.PrivateAccess;
+import org.evosuite.runtime.ViolatedAssumptionAnswer;
+import org.freehep.math.minuit.MnPlot;
+import org.freehep.math.minuit.Point;
+import org.junit.runner.RunWith;
+
+@RunWith(EvoRunner.class) @EvoRunnerParameters(mockJVMNonDeterminism = true, useVFS = true, useVNET = true, resetStaticState = true, separateClassLoader = true, useJEE = true) 
+public class MnPlot_ESTest extends MnPlot_ESTest_scaffolding {
+
+  @Test(timeout = 4000)
+  public void test00()  throws Throwable  {
+      int int0 = 0;
+      int int1 = 631;
+      MnPlot mnPlot0 = new MnPlot(int0, int1);
+      assertFalse(int0 == int1);
+      assertFalse(int1 == int0);
+      assertNotNull(mnPlot0);
+      
+      LinkedList<Point> linkedList0 = new LinkedList<Point>();
+      assertEquals(0, linkedList0.size());
+      assertNotNull(linkedList0);
+      
+      mnPlot0.plot((List<Point>) linkedList0);
+      assertFalse(int0 == int1);
+      assertFalse(int1 == int0);
+      assertEquals(0, linkedList0.size());
+      
+      double double0 = 1570.05;
+      Point point0 = new Point(double0, int0);
+      assertFalse(int0 == int1);
+      assertEquals(0.0, point0.second, 0.01);
+      assertEquals(1570.05, point0.first, 0.01);
+      assertNotNull(point0);
+      
+      boolean boolean0 = linkedList0.add(point0);
+      assertTrue(linkedList0.contains(point0));
+      assertFalse(int0 == int1);
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/FREEHEP-1_1/temp/testcases/org/freehep/math/minuit/MnPlot_ESTest_scaffolding.java

@@ -1,0 +1,100 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 19:02:43 GMT 2018
+ */
+
+package org.freehep.math.minuit;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+@EvoSuiteClassExclude
+public class MnPlot_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "org.freehep.math.minuit.MnPlot"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
+    org.evosuite.runtime.Runtime.getInstance().resetRuntime(); 
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/FREEHEP-2_1/temp/testcases/org/freehep/math/minuit/MnLineSearch_ESTest.java

@@ -1,0 +1,320 @@
+/*
+ * This file was automatically generated by EvoSuite
+ * Wed Jan 24 19:08:03 GMT 2018
+ */
+
+package org.freehep.math.minuit;
+
+import org.junit.Test;
+import static org.junit.Assert.*;
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+import static org.evosuite.runtime.EvoAssertions.*;
+import org.evosuite.runtime.EvoRunner;
+import org.evosuite.runtime.EvoRunnerParameters;
+import org.evosuite.runtime.ViolatedAssumptionAnswer;
+import org.freehep.math.minuit.FCNBase;
+import org.freehep.math.minuit.MinimumParameters;
+import org.freehep.math.minuit.MnAlgebraicVector;
+import org.freehep.math.minuit.MnFcn;
+import org.freehep.math.minuit.MnLineSearch;
+import org.freehep.math.minuit.MnMachinePrecision;
+import org.freehep.math.minuit.MnParabolaPoint;
+import org.junit.runner.RunWith;
+
+@RunWith(EvoRunner.class) @EvoRunnerParameters(mockJVMNonDeterminism = true, useVFS = true, useVNET = true, resetStaticState = true, separateClassLoader = true, useJEE = true) 
+public class MnLineSearch_ESTest extends MnLineSearch_ESTest_scaffolding {
+
+  @Test(timeout = 4000)
+  public void test00()  throws Throwable  {
+      FCNBase fCNBase0 = mock(FCNBase.class, new ViolatedAssumptionAnswer());
+      doReturn(0.0, 0.0, 0.0, 0.0, 0.0).when(fCNBase0).valueOf(any(double[].class));
+      double double0 = (-2475.50452131326);
+      MnFcn mnFcn0 = new MnFcn(fCNBase0, double0);
+      assertNotNull(mnFcn0);
+      
+      int int0 = 11;
+      MnAlgebraicVector mnAlgebraicVector0 = new MnAlgebraicVector(int0);
+      assertNotNull(mnAlgebraicVector0);
+      
+      MinimumParameters minimumParameters0 = new MinimumParameters(mnAlgebraicVector0, double0);
+      assertNotNull(minimumParameters0);
+      
+      MnMachinePrecision mnMachinePrecision0 = new MnMachinePrecision();
+      assertNotNull(mnMachinePrecision0);
+      
+      double double1 = 0.0;
+      mnMachinePrecision0.setPrecision(double1);
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/FREEHEP-2_1/temp/testcases/org/freehep/math/minuit/MnLineSearch_ESTest_scaffolding.java

@@ -1,0 +1,108 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 19:08:03 GMT 2018
+ */
+
+package org.freehep.math.minuit;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+@EvoSuiteClassExclude
+public class MnLineSearch_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "org.freehep.math.minuit.MnLineSearch"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
+    org.evosuite.runtime.Runtime.getInstance().resetRuntime(); 
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/FREEHEP-3_1/temp/testcases/org/freehep/math/minuit/MnFunctionCross_ESTest.java

@@ -1,0 +1,1489 @@
+/*
+ * This file was automatically generated by EvoSuite
+ * Wed Jan 24 19:09:33 GMT 2018
+ */
+
+package org.freehep.math.minuit;
+
+import org.junit.Test;
+import static org.junit.Assert.*;
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+import static org.evosuite.runtime.EvoAssertions.*;
+import org.evosuite.runtime.EvoRunner;
+import org.evosuite.runtime.EvoRunnerParameters;
+import org.evosuite.runtime.ViolatedAssumptionAnswer;
+import org.freehep.math.minuit.FCNBase;
+import org.freehep.math.minuit.MnCross;
+import org.freehep.math.minuit.MnFunctionCross;
+import org.freehep.math.minuit.MnStrategy;
+import org.freehep.math.minuit.MnUserCovariance;
+import org.freehep.math.minuit.MnUserParameterState;
+import org.freehep.math.minuit.MnUserParameters;
+import org.junit.runner.RunWith;
+
+@RunWith(EvoRunner.class) @EvoRunnerParameters(mockJVMNonDeterminism = true, useVFS = true, useVNET = true, resetStaticState = true, separateClassLoader = true, useJEE = true) 
+public class MnFunctionCross_ESTest extends MnFunctionCross_ESTest_scaffolding {
+
+  @Test(timeout = 4000)
+  public void test00()  throws Throwable  {
+      FCNBase fCNBase0 = mock(FCNBase.class, new ViolatedAssumptionAnswer());
+      doReturn(0.0, 0.0, 0.0, 0.0, 0.0).when(fCNBase0).valueOf(any(double[].class));
+      double[] doubleArray0 = new double[7];
+      MnUserParameters mnUserParameters0 = new MnUserParameters(doubleArray0, doubleArray0);
+      assertNotNull(mnUserParameters0);
+      assertArrayEquals(new double[] {0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0}, doubleArray0, 0.01);
+      assertEquals(7, doubleArray0.length);
+      assertEquals(7, mnUserParameters0.variableParameters());
+      
+      MnUserCovariance mnUserCovariance0 = new MnUserCovariance();
+      assertNotNull(mnUserCovariance0);
+      assertEquals(0, mnUserCovariance0.nrow());
+      assertEquals(0, mnUserCovariance0.ncol());
+      
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/FREEHEP-4_1/temp/testcases/org/freehep/math/minuit/MnAlgebraicSymMatrix_ESTest.java

@@ -1,0 +1,635 @@
+/*
+ * This file was automatically generated by EvoSuite
+ * Wed Jan 24 19:04:44 GMT 2018
+ */
+
+package org.freehep.math.minuit;
+
+import org.junit.Test;
+import static org.junit.Assert.*;
+import static org.evosuite.runtime.EvoAssertions.*;
+import org.evosuite.runtime.EvoRunner;
+import org.evosuite.runtime.EvoRunnerParameters;
+import org.evosuite.runtime.PrivateAccess;
+import org.freehep.math.minuit.MnAlgebraicSymMatrix;
+import org.freehep.math.minuit.MnAlgebraicVector;
+import org.junit.runner.RunWith;
+
+@RunWith(EvoRunner.class) @EvoRunnerParameters(mockJVMNonDeterminism = true, useVFS = true, useVNET = true, resetStaticState = true, separateClassLoader = true, useJEE = true) 
+public class MnAlgebraicSymMatrix_ESTest extends MnAlgebraicSymMatrix_ESTest_scaffolding {
+
+  @Test(timeout = 4000)
+  public void test00()  throws Throwable  {
+      int int0 = 1;
+      MnAlgebraicSymMatrix mnAlgebraicSymMatrix0 = new MnAlgebraicSymMatrix(int0);
+      int int1 = 338;
+      PrivateAccess.callMethod((Class<MnAlgebraicSymMatrix>) MnAlgebraicSymMatrix.class, mnAlgebraicSymMatrix0, "theIndex", (Object) int0, (Class<?>) int.class, (Object) int1, (Class<?>) int.class);
+      MnAlgebraicSymMatrix mnAlgebraicSymMatrix1 = mnAlgebraicSymMatrix0.clone();
+      mnAlgebraicSymMatrix1.eigenvalues();
+      double[] doubleArray0 = new double[0];
+      MnAlgebraicSymMatrix mnAlgebraicSymMatrix2 = mnAlgebraicSymMatrix0.clone();
+      PrivateAccess.setVariable((Class<MnAlgebraicSymMatrix>) MnAlgebraicSymMatrix.class, mnAlgebraicSymMatrix0, "theData", (Object) doubleArray0);
+      int int2 = (-1278);
+      int int3 = 0;
+      mnAlgebraicSymMatrix2.clone();
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/FREEHEP-5_1/temp/testcases/org/freehep/math/minuit/MnUserParameterState_ESTest_scaffolding.java

@@ -1,0 +1,125 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 19:06:31 GMT 2018
+ */
+
+package org.freehep.math.minuit;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+@EvoSuiteClassExclude
+public class MnUserParameterState_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "org.freehep.math.minuit.MnUserParameterState"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
+    org.evosuite.runtime.Runtime.getInstance().resetRuntime(); 
+  } 
+
+  @AfterClass 
+  public static void clearEvoSuiteFramework(){ 
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/FREEHEP-6_1/temp/testcases/org/freehep/math/minuit/SimplexBuilder_ESTest.java

@@ -1,0 +1,655 @@
+/*
+ * This file was automatically generated by EvoSuite
+ * Wed Jan 24 18:59:00 GMT 2018
+ */
+
+package org.freehep.math.minuit;
+
+import org.junit.Test;
+import static org.junit.Assert.*;
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+import static org.evosuite.runtime.EvoAssertions.*;
+import org.evosuite.runtime.EvoRunner;
+import org.evosuite.runtime.EvoRunnerParameters;
+import org.evosuite.runtime.ViolatedAssumptionAnswer;
+import org.freehep.math.minuit.FCNBase;
+import org.freehep.math.minuit.FunctionGradient;
+import org.freehep.math.minuit.FunctionMinimum;
+import org.freehep.math.minuit.HessianGradientCalculator;
+import org.freehep.math.minuit.MinimumError;
+import org.freehep.math.minuit.MinimumParameters;
+import org.freehep.math.minuit.MinimumSeed;
+import org.freehep.math.minuit.MinimumState;
+import org.freehep.math.minuit.MnAlgebraicVector;
+import org.freehep.math.minuit.MnFcn;
+import org.freehep.math.minuit.MnStrategy;
+import org.freehep.math.minuit.MnUserTransformation;
+import org.freehep.math.minuit.Numerical2PGradientCalculator;
+import org.freehep.math.minuit.SimplexBuilder;
+import org.junit.runner.RunWith;
+
+@RunWith(EvoRunner.class) @EvoRunnerParameters(mockJVMNonDeterminism = true, useVFS = true, useVNET = true, resetStaticState = true, separateClassLoader = true, useJEE = true) 
+public class SimplexBuilder_ESTest extends SimplexBuilder_ESTest_scaffolding {
+
+  @Test(timeout = 4000)
+  public void test0()  throws Throwable  {
+      SimplexBuilder simplexBuilder0 = new SimplexBuilder();
+      //  // Unstable assertion: assertNotNull(simplexBuilder0);
+      
+      double double0 = 1.0;
+      FCNBase fCNBase0 = mock(FCNBase.class, new ViolatedAssumptionAnswer());
+      doReturn(double0, double0, double0, double0).when(fCNBase0).valueOf(any(double[].class));
+      MnFcn mnFcn0 = new MnFcn(fCNBase0, double0);
+      //  // Unstable assertion: assertNotNull(mnFcn0);
+      
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/FREEHEP-6_1/temp/testcases/org/freehep/math/minuit/SimplexBuilder_ESTest_scaffolding.java

@@ -1,0 +1,143 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 18:59:00 GMT 2018
+ */
+
+package org.freehep.math.minuit;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+@EvoSuiteClassExclude
+public class SimplexBuilder_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "org.freehep.math.minuit.SimplexBuilder"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
+    org.evosuite.runtime.Runtime.getInstance().resetRuntime(); 
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/FREEHEP-7_1/temp/testcases/org/freehep/math/minuit/MnHesse_ESTest_scaffolding.java

@@ -1,0 +1,145 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 19:00:51 GMT 2018
+ */
+
+package org.freehep.math.minuit;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+@EvoSuiteClassExclude
+public class MnHesse_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "org.freehep.math.minuit.MnHesse"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
+    org.evosuite.runtime.Runtime.getInstance().resetRuntime(); 
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/FREEHEP-8_1/temp/testcases/org/freehep/math/minuit/MnPrint_ESTest_scaffolding.java

@@ -1,0 +1,147 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 18:55:34 GMT 2018
+ */
+
+package org.freehep.math.minuit;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+@EvoSuiteClassExclude
+public class MnPrint_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "org.freehep.math.minuit.MnPrint"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
+    org.evosuite.runtime.Runtime.getInstance().resetRuntime(); 
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/GSON-1_1/temp/testcases/com/google/gson/internal/bind/ReflectiveTypeAdapterFactory_ESTest.java

@@ -1,0 +1,352 @@
+/*
+ * This file was automatically generated by EvoSuite
+ * Wed Jan 24 19:54:08 GMT 2018
+ */
+
+package com.google.gson.internal.bind;
+
+import org.junit.Test;
+import static org.junit.Assert.*;
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+import static org.evosuite.runtime.EvoAssertions.*;
+import com.google.gson.FieldNamingPolicy;
+import com.google.gson.FieldNamingStrategy;
+import com.google.gson.Gson;
+import com.google.gson.JsonPrimitive;
+import com.google.gson.TypeAdapter;
+import com.google.gson.internal.ConstructorConstructor;
+import com.google.gson.internal.Excluder;
+import com.google.gson.internal.ObjectConstructor;
+import com.google.gson.internal.bind.JsonAdapterAnnotationTypeAdapterFactory;
+import com.google.gson.internal.bind.ReflectiveTypeAdapterFactory;
+import com.google.gson.reflect.TypeToken;
+import com.google.gson.stream.JsonReader;
+import com.google.gson.stream.JsonWriter;
+import java.io.FileDescriptor;
+import java.io.Reader;
+import java.io.Writer;
+import java.lang.reflect.Field;
+import java.lang.reflect.Type;
+import java.time.chrono.ChronoLocalDate;
+import java.util.HashMap;
+import java.util.Map;
+import org.evosuite.runtime.EvoRunner;
+import org.evosuite.runtime.EvoRunnerParameters;
+import org.evosuite.runtime.ViolatedAssumptionAnswer;
+import org.evosuite.runtime.mock.java.io.MockFileReader;
+import org.evosuite.runtime.mock.java.time.chrono.MockHijrahDate;
+import org.junit.runner.RunWith;
+
+@RunWith(EvoRunner.class) @EvoRunnerParameters(mockJVMNonDeterminism = true, useVFS = true, useVNET = true, resetStaticState = true, separateClassLoader = true, useJEE = true) 
+public class ReflectiveTypeAdapterFactory_ESTest extends ReflectiveTypeAdapterFactory_ESTest_scaffolding {
+
+  @Test(timeout = 4000)
+  public void test0()  throws Throwable  {
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/GSON-2_1/temp/testcases/com/google/gson/internal/LinkedHashTreeMap_ESTest_scaffolding.java

@@ -1,0 +1,114 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 19:46:58 GMT 2018
+ */
+
+package com.google.gson.internal;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+@EvoSuiteClassExclude
+public class LinkedHashTreeMap_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "com.google.gson.internal.LinkedHashTreeMap"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
+    org.evosuite.runtime.Runtime.getInstance().resetRuntime(); 
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/GSON-3_1/temp/testcases/com/google/gson/JsonPrimitive_ESTest.java

@@ -1,0 +1,3002 @@
+/*
+ * This file was automatically generated by EvoSuite
+ * Wed Jan 24 19:50:40 GMT 2018
+ */
+
+package com.google.gson;
+
+import org.junit.Test;
+import static org.junit.Assert.*;
+import static org.evosuite.runtime.EvoAssertions.*;
+import com.google.gson.JsonPrimitive;
+import java.math.BigDecimal;
+import java.math.BigInteger;
+import org.evosuite.runtime.EvoRunner;
+import org.evosuite.runtime.EvoRunnerParameters;
+import org.evosuite.runtime.PrivateAccess;
+import org.junit.runner.RunWith;
+
+@RunWith(EvoRunner.class) @EvoRunnerParameters(mockJVMNonDeterminism = true, useVFS = true, useVNET = true, resetStaticState = true, separateClassLoader = true, useJEE = true) 
+public class JsonPrimitive_ESTest extends JsonPrimitive_ESTest_scaffolding {
+
+  @Test(timeout = 4000)
+  public void test00()  throws Throwable  {
+      byte[] byteArray0 = new byte[6];
+      BigInteger bigInteger0 = new BigInteger(byteArray0);
+      assertNotNull(bigInteger0);
+      assertArrayEquals(new byte[] {(byte)0, (byte)0, (byte)0, (byte)0, (byte)0, (byte)0}, byteArray0);
+      assertEquals(6, byteArray0.length);
+      assertEquals((byte)0, bigInteger0.byteValue());
+      assertEquals((short)0, bigInteger0.shortValue());
+      
+      JsonPrimitive jsonPrimitive0 = new JsonPrimitive((Object) bigInteger0);
+      assertNotNull(jsonPrimitive0);
+      assertArrayEquals(new byte[] {(byte)0, (byte)0, (byte)0, (byte)0, (byte)0, (byte)0}, byteArray0);
+      assertEquals(6, byteArray0.length);
+      assertEquals((byte)0, bigInteger0.byteValue());
+      assertEquals((short)0, bigInteger0.shortValue());
+      assertFalse(jsonPrimitive0.isBoolean());
+      assertFalse(jsonPrimitive0.isJsonArray());
+      assertTrue(jsonPrimitive0.isNumber());
+      assertFalse(jsonPrimitive0.isJsonObject());
+      assertFalse(jsonPrimitive0.isString());
+      assertFalse(jsonPrimitive0.isJsonNull());
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/GSON-3_1/temp/testcases/com/google/gson/JsonPrimitive_ESTest_scaffolding.java

@@ -1,0 +1,170 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 19:50:40 GMT 2018
+ */
+
+package com.google.gson;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+@EvoSuiteClassExclude
+public class JsonPrimitive_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "com.google.gson.JsonPrimitive"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
+    org.evosuite.runtime.Runtime.getInstance().resetRuntime(); 
+  } 
+
+  @AfterClass 
+  public static void clearEvoSuiteFramework(){ 
+    Sandbox.resetDefaultSecurityManager(); 
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/GSON-4_1/temp/testcases/com/google/gson/stream/JsonReader_ESTest.java

@@ -1,0 +1,1247 @@
+/*
+ * This file was automatically generated by EvoSuite
+ * Wed Jan 24 19:41:03 GMT 2018
+ */
+
+package com.google.gson.stream;
+
+import org.junit.Test;
+import static org.junit.Assert.*;
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+import static org.evosuite.runtime.EvoAssertions.*;
+import com.google.gson.stream.JsonReader;
+import java.io.BufferedReader;
+import java.io.ByteArrayInputStream;
+import java.io.CharArrayReader;
+import java.io.EOFException;
+import java.io.FileDescriptor;
+import java.io.FileNotFoundException;
+import java.io.IOException;
+import java.io.InputStreamReader;
+import java.io.LineNumberReader;
+import java.io.PipedInputStream;
+import java.io.PipedReader;
+import java.io.PipedWriter;
+import java.io.PushbackReader;
+import java.io.Reader;
+import java.io.SequenceInputStream;
+import java.io.StringBufferInputStream;
+import java.io.StringReader;
+import java.nio.ByteBuffer;
+import java.nio.CharBuffer;
+import java.nio.charset.Charset;
+import java.nio.charset.CharsetDecoder;
+import java.nio.charset.MalformedInputException;
+import org.evosuite.runtime.EvoRunner;
+import org.evosuite.runtime.EvoRunnerParameters;
+import org.evosuite.runtime.PrivateAccess;
+import org.evosuite.runtime.ViolatedAssumptionAnswer;
+import org.evosuite.runtime.mock.java.io.MockFile;
+import org.evosuite.runtime.mock.java.io.MockFileInputStream;
+import org.evosuite.runtime.mock.java.io.MockFileReader;
+import org.evosuite.runtime.testdata.EvoSuiteFile;
+import org.evosuite.runtime.testdata.FileSystemHandling;
+import org.junit.runner.RunWith;
+
+@RunWith(EvoRunner.class) @EvoRunnerParameters(mockJVMNonDeterminism = true, useVFS = true, useVNET = true, resetStaticState = true, separateClassLoader = true, useJEE = true) 
+public class JsonReader_ESTest extends JsonReader_ESTest_scaffolding {
+
+  @Test(timeout = 4000)
+  public void test00()  throws Throwable  {
+      PipedWriter pipedWriter0 = new PipedWriter();
+      pipedWriter0.flush();
+      int int0 = 123;
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/GSON-4_1/temp/testcases/com/google/gson/stream/JsonReader_ESTest_scaffolding.java

@@ -1,0 +1,112 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 19:41:03 GMT 2018
+ */
+
+package com.google.gson.stream;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+@EvoSuiteClassExclude
+public class JsonReader_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "com.google.gson.stream.JsonReader"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
+    org.evosuite.runtime.Runtime.getInstance().resetRuntime(); 
+    try { initMocksToAvoidTimeoutsInTheTests(); } catch(ClassNotFoundException e) {} 
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/GSON-5_1/temp/testcases/com/google/gson/internal/LinkedTreeMap_ESTest.java

@@ -1,0 +1,854 @@
+/*
+ * This file was automatically generated by EvoSuite
+ * Wed Jan 24 19:44:38 GMT 2018
+ */
+
+package com.google.gson.internal;
+
+import org.junit.Test;
+import static org.junit.Assert.*;
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+import static org.evosuite.runtime.EvoAssertions.*;
+import com.google.gson.internal.LinkedTreeMap;
+import java.util.Comparator;
+import java.util.Iterator;
+import java.util.Map;
+import java.util.Set;
+import java.util.function.BinaryOperator;
+import org.evosuite.runtime.EvoRunner;
+import org.evosuite.runtime.EvoRunnerParameters;
+import org.evosuite.runtime.ViolatedAssumptionAnswer;
+import org.junit.runner.RunWith;
+
+@RunWith(EvoRunner.class) @EvoRunnerParameters(mockJVMNonDeterminism = true, useVFS = true, useVNET = true, resetStaticState = true, separateClassLoader = true, useJEE = true) 
+public class LinkedTreeMap_ESTest extends LinkedTreeMap_ESTest_scaffolding {
+
+  @Test(timeout = 4000)
+  public void test00()  throws Throwable  {
+      LinkedTreeMap.Node<String, String> linkedTreeMap_Node0 = new LinkedTreeMap.Node<String, String>();
+      assertNotNull(linkedTreeMap_Node0);
+      
+      String string0 = linkedTreeMap_Node0.getValue();
+      assertNull(string0);
+  }
+
+  @Test(timeout = 4000)
+  public void test01()  throws Throwable  {
+      Comparator<Object> comparator0 = (Comparator<Object>) mock(Comparator.class, new ViolatedAssumptionAnswer());
+      LinkedTreeMap<String, Object> linkedTreeMap0 = new LinkedTreeMap<String, Object>(comparator0);
+      assertEquals(0, linkedTreeMap0.size());
+      assertNotNull(linkedTreeMap0);
+      
+      String string0 = "}sJfDpJWwJ0+$";
+      boolean boolean0 = true;
+      LinkedTreeMap.Node<String, Object> linkedTreeMap_Node0 = linkedTreeMap0.find(string0, boolean0);
+      assertEquals(1, linkedTreeMap0.size());
+      assertNotNull(linkedTreeMap_Node0);
+      
+      String string1 = linkedTreeMap_Node0.getKey();
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/GSON-5_1/temp/testcases/com/google/gson/internal/LinkedTreeMap_ESTest_scaffolding.java

@@ -1,0 +1,111 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 19:44:38 GMT 2018
+ */
+
+package com.google.gson.internal;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+@EvoSuiteClassExclude
+public class LinkedTreeMap_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "com.google.gson.internal.LinkedTreeMap"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
+    org.evosuite.runtime.Runtime.getInstance().resetRuntime(); 
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/GSON-6_1/temp/testcases/com/google/gson/internal/bind/JsonTreeReader_ESTest_scaffolding.java

@@ -1,0 +1,178 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 19:34:07 GMT 2018
+ */
+
+package com.google.gson.internal.bind;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+@EvoSuiteClassExclude
+public class JsonTreeReader_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "com.google.gson.internal.bind.JsonTreeReader"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
+    org.evosuite.runtime.Runtime.getInstance().resetRuntime(); 
+  } 
+
+  @AfterClass 
+  public static void clearEvoSuiteFramework(){ 
+    Sandbox.resetDefaultSecurityManager(); 
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/GSON-7_1/temp/testcases/com/google/gson/GsonBuilder_ESTest.java

@@ -1,0 +1,1632 @@
+/*
+ * This file was automatically generated by EvoSuite
+ * Wed Jan 24 19:37:05 GMT 2018
+ */
+
+package com.google.gson;
+
+import org.junit.Test;
+import static org.junit.Assert.*;
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+import static org.evosuite.runtime.EvoAssertions.*;
+import com.google.gson.DefaultDateTypeAdapter;
+import com.google.gson.ExclusionStrategy;
+import com.google.gson.FieldNamingPolicy;
+import com.google.gson.FieldNamingStrategy;
+import com.google.gson.Gson;
+import com.google.gson.GsonBuilder;
+import com.google.gson.LongSerializationPolicy;
+import com.google.gson.TypeAdapter;
+import com.google.gson.TypeAdapterFactory;
+import com.google.gson.internal.Excluder;
+import com.google.gson.reflect.TypeToken;
+import java.time.chrono.ChronoLocalDate;
+import java.util.List;
+import java.util.Map;
+import org.evosuite.runtime.EvoRunner;
+import org.evosuite.runtime.EvoRunnerParameters;
+import org.evosuite.runtime.PrivateAccess;
+import org.evosuite.runtime.ViolatedAssumptionAnswer;
+import org.evosuite.runtime.mock.java.time.chrono.MockMinguoDate;
+import org.evosuite.runtime.testdata.EvoSuiteFile;
+import org.evosuite.runtime.testdata.FileSystemHandling;
+import org.junit.runner.RunWith;
+
+@RunWith(EvoRunner.class) @EvoRunnerParameters(mockJVMNonDeterminism = true, useVFS = true, useVNET = true, resetStaticState = true, separateClassLoader = true, useJEE = true) 
+public class GsonBuilder_ESTest extends GsonBuilder_ESTest_scaffolding {
+
+  @Test(timeout = 4000)
+  public void test00()  throws Throwable  {
+      GsonBuilder gsonBuilder0 = new GsonBuilder();
+      assertNotNull(gsonBuilder0);
+      
+      int int0 = 0;
+      int int1 = 1;
+      GsonBuilder gsonBuilder1 = gsonBuilder0.setDateFormat(int0, int1);
+      assertFalse(int0 == int1);
+      assertFalse(int1 == int0);
+      assertSame(gsonBuilder0, gsonBuilder1);
+      assertSame(gsonBuilder1, gsonBuilder0);
+      assertNotNull(gsonBuilder1);
+      
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/GSON-8_1/temp/testcases/com/google/gson/internal/bind/JsonTreeReader_ESTest.java

@@ -1,0 +1,2798 @@
+/*
+ * This file was automatically generated by EvoSuite
+ * Wed Jan 24 19:29:30 GMT 2018
+ */
+
+package com.google.gson.internal.bind;
+
+import org.junit.Test;
+import static org.junit.Assert.*;
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+import static org.evosuite.runtime.EvoAssertions.*;
+import com.google.gson.JsonArray;
+import com.google.gson.JsonElement;
+import com.google.gson.JsonNull;
+import com.google.gson.JsonObject;
+import com.google.gson.JsonPrimitive;
+import com.google.gson.internal.bind.JsonTreeReader;
+import com.google.gson.stream.JsonToken;
+import java.io.ObjectStreamConstants;
+import java.util.ConcurrentModificationException;
+import org.evosuite.runtime.EvoRunner;
+import org.evosuite.runtime.EvoRunnerParameters;
+import org.evosuite.runtime.PrivateAccess;
+import org.evosuite.runtime.ViolatedAssumptionAnswer;
+import org.junit.runner.RunWith;
+
+@RunWith(EvoRunner.class) @EvoRunnerParameters(mockJVMNonDeterminism = true, useVFS = true, useVNET = true, resetStaticState = true, separateClassLoader = true, useJEE = true) 
+public class JsonTreeReader_ESTest extends JsonTreeReader_ESTest_scaffolding {
+
+  @Test(timeout = 4000)
+  public void test00()  throws Throwable  {
+      JsonObject jsonObject0 = new JsonObject();
+      assertNotNull(jsonObject0);
+      assertTrue(jsonObject0.isJsonObject());
+      assertFalse(jsonObject0.isJsonPrimitive());
+      assertFalse(jsonObject0.isJsonArray());
+      assertFalse(jsonObject0.isJsonNull());
+      
+      String string0 = "";
+      Boolean boolean0 = Boolean.TRUE;
+      assertNotNull(boolean0);
+      assertTrue(boolean0);
+      
+      jsonObject0.addProperty(string0, boolean0);
+      assertTrue(jsonObject0.isJsonObject());
+      assertFalse(jsonObject0.isJsonPrimitive());
+      assertFalse(jsonObject0.isJsonArray());
+      assertFalse(jsonObject0.isJsonNull());
+      
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/IMAGE-2_1/temp/testcases/org/apache/commons/imaging/common/RationalNumber_ESTest_scaffolding.java

@@ -1,0 +1,100 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 19:17:32 GMT 2018
+ */
+
+package org.apache.commons.imaging.common;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+@EvoSuiteClassExclude
+public class RationalNumber_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "org.apache.commons.imaging.common.RationalNumber"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
+    org.evosuite.runtime.Runtime.getInstance().resetRuntime(); 
+  } 
+
+  @AfterClass 
+  public static void clearEvoSuiteFramework(){ 
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/IMAGE-4_1/temp/testcases/org/apache/commons/imaging/formats/tiff/TiffField_ESTest_scaffolding.java

@@ -1,0 +1,234 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 19:22:23 GMT 2018
+ */
+
+package org.apache.commons.imaging.formats.tiff;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+@EvoSuiteClassExclude
+public class TiffField_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "org.apache.commons.imaging.formats.tiff.TiffField"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
+    org.evosuite.runtime.Runtime.getInstance().resetRuntime(); 
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/JXPATH-1_1/temp/testcases/org/apache/commons/jxpath/util/BasicTypeConverter_ESTest.java

@@ -1,0 +1,673 @@
+/*
+ * This file was automatically generated by EvoSuite
+ * Wed Jan 24 18:47:52 GMT 2018
+ */
+
+package org.apache.commons.jxpath.util;
+
+import org.junit.Test;
+import static org.junit.Assert.*;
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+import static org.evosuite.runtime.EvoAssertions.*;
+import java.util.Collection;
+import java.util.LinkedHashSet;
+import java.util.LinkedList;
+import java.util.List;
+import java.util.TreeSet;
+import org.apache.commons.jxpath.BasicNodeSet;
+import org.apache.commons.jxpath.Pointer;
+import org.apache.commons.jxpath.util.BasicTypeConverter;
+import org.evosuite.runtime.EvoRunner;
+import org.evosuite.runtime.EvoRunnerParameters;
+import org.evosuite.runtime.ViolatedAssumptionAnswer;
+import org.junit.runner.RunWith;
+
+@RunWith(EvoRunner.class) @EvoRunnerParameters(mockJVMNonDeterminism = true, useVFS = true, useVNET = true, resetStaticState = true, separateClassLoader = true, useJEE = true) 
+public class BasicTypeConverter_ESTest extends BasicTypeConverter_ESTest_scaffolding {
+
+  @Test(timeout = 4000)
+  public void test00()  throws Throwable  {
+      int int0 = (-678);
+      List<BasicTypeConverter.ValuePointer> list0 = (List<BasicTypeConverter.ValuePointer>) mock(List.class, new ViolatedAssumptionAnswer());
+      doReturn(int0).when(list0).size();
+      BasicTypeConverter.ValueNodeSet basicTypeConverter_ValueNodeSet0 = new BasicTypeConverter.ValueNodeSet(list0);
+      assertNotNull(basicTypeConverter_ValueNodeSet0);
+      
+      List list1 = basicTypeConverter_ValueNodeSet0.getPointers();
+      assertNotNull(list1);
+      assertTrue(list1.isEmpty());
+      assertEquals(0, list1.size());
+  }
+
+  @Test(timeout = 4000)
+  public void test01()  throws Throwable  {
+      BasicTypeConverter basicTypeConverter0 = new BasicTypeConverter();
+      assertNotNull(basicTypeConverter0);
+      
+      Class<Object> class0 = null;
+      // Undeclared exception!
+      try { 
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/JXPATH-1_1/temp/testcases/org/apache/commons/jxpath/util/BasicTypeConverter_ESTest_scaffolding.java

@@ -1,0 +1,120 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 18:47:52 GMT 2018
+ */
+
+package org.apache.commons.jxpath.util;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+@EvoSuiteClassExclude
+public class BasicTypeConverter_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "org.apache.commons.jxpath.util.BasicTypeConverter"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
+    org.evosuite.runtime.Runtime.getInstance().resetRuntime(); 
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/JXPATH-2_1/temp/testcases/org/apache/commons/jxpath/ri/compiler/Path_ESTest.java

@@ -1,0 +1,2607 @@
+/*
+ * This file was automatically generated by EvoSuite
+ * Wed Jan 24 18:33:32 GMT 2018
+ */
+
+package org.apache.commons.jxpath.ri.compiler;
+
+import org.junit.Test;
+import static org.junit.Assert.*;
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+import static org.evosuite.runtime.EvoAssertions.*;
+import org.apache.commons.jxpath.BasicNodeSet;
+import org.apache.commons.jxpath.JXPathContext;
+import org.apache.commons.jxpath.NodeSet;
+import org.apache.commons.jxpath.Pointer;
+import org.apache.commons.jxpath.ri.EvalContext;
+import org.apache.commons.jxpath.ri.JXPathContextReferenceImpl;
+import org.apache.commons.jxpath.ri.QName;
+import org.apache.commons.jxpath.ri.axes.AttributeContext;
+import org.apache.commons.jxpath.ri.axes.ChildContext;
+import org.apache.commons.jxpath.ri.axes.DescendantContext;
+import org.apache.commons.jxpath.ri.axes.NamespaceContext;
+import org.apache.commons.jxpath.ri.axes.NodeSetContext;
+import org.apache.commons.jxpath.ri.axes.ParentContext;
+import org.apache.commons.jxpath.ri.axes.PrecedingOrFollowingContext;
+import org.apache.commons.jxpath.ri.axes.PredicateContext;
+import org.apache.commons.jxpath.ri.axes.RootContext;
+import org.apache.commons.jxpath.ri.axes.SelfContext;
+import org.apache.commons.jxpath.ri.axes.UnionContext;
+import org.apache.commons.jxpath.ri.compiler.Constant;
+import org.apache.commons.jxpath.ri.compiler.CoreFunction;
+import org.apache.commons.jxpath.ri.compiler.CoreOperation;
+import org.apache.commons.jxpath.ri.compiler.CoreOperationAdd;
+import org.apache.commons.jxpath.ri.compiler.CoreOperationAnd;
+import org.apache.commons.jxpath.ri.compiler.CoreOperationDivide;
+import org.apache.commons.jxpath.ri.compiler.CoreOperationEqual;
+import org.apache.commons.jxpath.ri.compiler.CoreOperationLessThan;
+import org.apache.commons.jxpath.ri.compiler.CoreOperationLessThanOrEqual;
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/JXPATH-2_1/temp/testcases/org/apache/commons/jxpath/ri/compiler/Path_ESTest_scaffolding.java

@@ -1,0 +1,268 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 18:33:32 GMT 2018
+ */
+
+package org.apache.commons.jxpath.ri.compiler;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+@EvoSuiteClassExclude
+public class Path_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "org.apache.commons.jxpath.ri.compiler.Path"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
+    org.evosuite.runtime.Runtime.getInstance().resetRuntime(); 
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/JXPATH-3_1/temp/testcases/org/apache/commons/jxpath/ri/compiler/CoreOperationCompare_ESTest.java

@@ -1,0 +1,1180 @@
+/*
+ * This file was automatically generated by EvoSuite
+ * Wed Jan 24 18:37:28 GMT 2018
+ */
+
+package org.apache.commons.jxpath.ri.compiler;
+
+import org.junit.Test;
+import static org.junit.Assert.*;
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+import static org.evosuite.runtime.EvoAssertions.*;
+import java.util.Iterator;
+import org.apache.commons.jxpath.BasicVariables;
+import org.apache.commons.jxpath.ri.EvalContext;
+import org.apache.commons.jxpath.ri.JXPathContextReferenceImpl;
+import org.apache.commons.jxpath.ri.NamespaceResolver;
+import org.apache.commons.jxpath.ri.QName;
+import org.apache.commons.jxpath.ri.axes.AttributeContext;
+import org.apache.commons.jxpath.ri.axes.ChildContext;
+import org.apache.commons.jxpath.ri.axes.NamespaceContext;
+import org.apache.commons.jxpath.ri.axes.PredicateContext;
+import org.apache.commons.jxpath.ri.axes.RootContext;
+import org.apache.commons.jxpath.ri.axes.UnionContext;
+import org.apache.commons.jxpath.ri.compiler.Constant;
+import org.apache.commons.jxpath.ri.compiler.CoreFunction;
+import org.apache.commons.jxpath.ri.compiler.CoreOperationAnd;
+import org.apache.commons.jxpath.ri.compiler.CoreOperationEqual;
+import org.apache.commons.jxpath.ri.compiler.CoreOperationGreaterThan;
+import org.apache.commons.jxpath.ri.compiler.CoreOperationGreaterThanOrEqual;
+import org.apache.commons.jxpath.ri.compiler.CoreOperationLessThan;
+import org.apache.commons.jxpath.ri.compiler.CoreOperationMod;
+import org.apache.commons.jxpath.ri.compiler.CoreOperationMultiply;
+import org.apache.commons.jxpath.ri.compiler.CoreOperationNotEqual;
+import org.apache.commons.jxpath.ri.compiler.CoreOperationOr;
+import org.apache.commons.jxpath.ri.compiler.Expression;
+import org.apache.commons.jxpath.ri.compiler.NameAttributeTest;
+import org.apache.commons.jxpath.ri.compiler.NodeTypeTest;
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/JXPATH-4_1/temp/testcases/org/apache/commons/jxpath/util/MethodLookupUtils_ESTest.java

@@ -1,0 +1,333 @@
+/*
+ * This file was automatically generated by EvoSuite
+ * Wed Jan 24 18:27:10 GMT 2018
+ */
+
+package org.apache.commons.jxpath.util;
+
+import org.junit.Test;
+import static org.junit.Assert.*;
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+import static org.evosuite.runtime.EvoAssertions.*;
+import java.lang.reflect.Array;
+import java.lang.reflect.Constructor;
+import java.lang.reflect.GenericDeclaration;
+import java.lang.reflect.Method;
+import org.apache.commons.jxpath.util.MethodLookupUtils;
+import org.apache.commons.jxpath.util.TypeConverter;
+import org.apache.commons.jxpath.util.TypeUtils;
+import org.evosuite.runtime.EvoRunner;
+import org.evosuite.runtime.EvoRunnerParameters;
+import org.evosuite.runtime.PrivateAccess;
+import org.evosuite.runtime.ViolatedAssumptionAnswer;
+import org.junit.runner.RunWith;
+
+@RunWith(EvoRunner.class) @EvoRunnerParameters(mockJVMNonDeterminism = true, useVFS = true, useVNET = true, resetStaticState = true, separateClassLoader = true, useJEE = true) 
+public class MethodLookupUtils_ESTest extends MethodLookupUtils_ESTest_scaffolding {
+
+  @Test(timeout = 4000)
+  public void test00()  throws Throwable  {
+      MethodLookupUtils methodLookupUtils0 = null;
+      Class<Object> class0 = Object.class;
+      Object object0 = PrivateAccess.callMethod((Class<MethodLookupUtils>) MethodLookupUtils.class, methodLookupUtils0, "matchType", (Object) class0, (Class<?>) Class.class, (Object) methodLookupUtils0, (Class<?>) Object.class);
+      assertEquals(1, object0);
+      assertNotNull(object0);
+      
+      Class<Object>[] classArray0 = (Class<Object>[]) Array.newInstance(Class.class, 7);
+      classArray0[0] = class0;
+      Class<Object> class1 = Object.class;
+      classArray0[1] = class1;
+      classArray0[2] = class0;
+      classArray0[3] = class0;
+      classArray0[4] = class0;
+      Class<Object> class2 = Object.class;
+      classArray0[5] = class2;
+      classArray0[6] = class0;
+      Object[] objectArray0 = null;
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/JXPATH-5_1/temp/testcases/org/apache/commons/jxpath/ri/compiler/Step_ESTest.java

@@ -1,0 +1,781 @@
+/*
+ * This file was automatically generated by EvoSuite
+ * Wed Jan 24 18:30:38 GMT 2018
+ */
+
+package org.apache.commons.jxpath.ri.compiler;
+
+import org.junit.Test;
+import static org.junit.Assert.*;
+import static org.evosuite.runtime.EvoAssertions.*;
+import org.apache.commons.jxpath.ri.QName;
+import org.apache.commons.jxpath.ri.compiler.CoreOperationAdd;
+import org.apache.commons.jxpath.ri.compiler.CoreOperationAnd;
+import org.apache.commons.jxpath.ri.compiler.Expression;
+import org.apache.commons.jxpath.ri.compiler.ExtensionFunction;
+import org.apache.commons.jxpath.ri.compiler.NodeNameTest;
+import org.apache.commons.jxpath.ri.compiler.NodeTest;
+import org.apache.commons.jxpath.ri.compiler.NodeTypeTest;
+import org.apache.commons.jxpath.ri.compiler.ProcessingInstructionTest;
+import org.apache.commons.jxpath.ri.compiler.Step;
+import org.evosuite.runtime.EvoRunner;
+import org.evosuite.runtime.EvoRunnerParameters;
+import org.junit.runner.RunWith;
+
+@RunWith(EvoRunner.class) @EvoRunnerParameters(mockJVMNonDeterminism = true, useVFS = true, useVNET = true, resetStaticState = true, separateClassLoader = true, useJEE = true) 
+public class Step_ESTest extends Step_ESTest_scaffolding {
+
+  @Test(timeout = 4000)
+  public void test00()  throws Throwable  {
+      int int0 = 1;
+      NodeTypeTest nodeTypeTest0 = new NodeTypeTest(int0);
+      assertEquals(1, nodeTypeTest0.getNodeType());
+      assertNotNull(nodeTypeTest0);
+      
+      Expression[] expressionArray0 = new Expression[4];
+      Step step0 = new Step(int0, nodeTypeTest0, expressionArray0);
+      assertEquals(1, nodeTypeTest0.getNodeType());
+      assertEquals(1, step0.getAxis());
+      assertNotNull(step0);
+      assertEquals(4, expressionArray0.length);
+      
+      Expression[] expressionArray1 = step0.getPredicates();
+      assertEquals(1, nodeTypeTest0.getNodeType());
+      assertEquals(1, step0.getAxis());
+      assertNotNull(expressionArray1);
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/JXPATH-5_1/temp/testcases/org/apache/commons/jxpath/ri/compiler/Step_ESTest_scaffolding.java

@@ -1,0 +1,215 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 18:30:38 GMT 2018
+ */
+
+package org.apache.commons.jxpath.ri.compiler;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+@EvoSuiteClassExclude
+public class Step_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "org.apache.commons.jxpath.ri.compiler.Step"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
+    org.evosuite.runtime.Runtime.getInstance().resetRuntime(); 
+  } 
+
+  @AfterClass 
+  public static void clearEvoSuiteFramework(){ 
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/JXPATH-6_1/temp/testcases/org/apache/commons/jxpath/JXPathContext_ESTest_scaffolding.java

@@ -1,0 +1,278 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 18:43:13 GMT 2018
+ */
+
+package org.apache.commons.jxpath;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+@EvoSuiteClassExclude
+public class JXPathContext_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "org.apache.commons.jxpath.JXPathContext"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
+    org.evosuite.runtime.Runtime.getInstance().resetRuntime(); 
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/JXPATH-7_1/temp/testcases/org/apache/commons/jxpath/ri/parser/XPathParserTokenManager_ESTest.java

@@ -1,0 +1,1312 @@
+/*
+ * This file was automatically generated by EvoSuite
+ * Wed Jan 24 18:44:44 GMT 2018
+ */
+
+package org.apache.commons.jxpath.ri.parser;
+
+import org.junit.Test;
+import static org.junit.Assert.*;
+import static org.evosuite.runtime.EvoAssertions.*;
+import java.io.ByteArrayInputStream;
+import java.io.CharArrayReader;
+import java.io.FileDescriptor;
+import java.io.PipedInputStream;
+import java.io.PipedReader;
+import java.io.PushbackReader;
+import java.io.Reader;
+import java.io.StringBufferInputStream;
+import java.io.StringReader;
+import org.apache.commons.jxpath.ri.parser.SimpleCharStream;
+import org.apache.commons.jxpath.ri.parser.Token;
+import org.apache.commons.jxpath.ri.parser.XPathParserTokenManager;
+import org.evosuite.runtime.EvoRunner;
+import org.evosuite.runtime.EvoRunnerParameters;
+import org.evosuite.runtime.PrivateAccess;
+import org.evosuite.runtime.mock.java.io.MockFileInputStream;
+import org.evosuite.runtime.mock.java.io.MockPrintStream;
+import org.junit.runner.RunWith;
+
+@RunWith(EvoRunner.class) @EvoRunnerParameters(mockJVMNonDeterminism = true, useVFS = true, useVNET = true, resetStaticState = true, separateClassLoader = true, useJEE = true) 
+public class XPathParserTokenManager_ESTest extends XPathParserTokenManager_ESTest_scaffolding {
+
+  @Test(timeout = 4000)
+  public void test00()  throws Throwable  {
+      String string0 = ". State unchanged.";
+      StringBufferInputStream stringBufferInputStream0 = new StringBufferInputStream(string0);
+      assertEquals(18, stringBufferInputStream0.available());
+      assertNotNull(stringBufferInputStream0);
+      
+      int int0 = (-1318);
+      SimpleCharStream simpleCharStream0 = new SimpleCharStream(stringBufferInputStream0, int0, int0);
+      assertFalse(SimpleCharStream.staticFlag);
+      assertEquals((-1), simpleCharStream0.bufpos);
+      assertEquals(18, stringBufferInputStream0.available());
+      assertEquals(0, simpleCharStream0.getBeginLine());
+      assertEquals(0, simpleCharStream0.getBeginColumn());
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/JXPATH-8_1/temp/testcases/org/apache/commons/jxpath/util/ValueUtils_ESTest_scaffolding.java

@@ -1,0 +1,124 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 18:39:38 GMT 2018
+ */
+
+package org.apache.commons.jxpath.util;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+@EvoSuiteClassExclude
+public class ValueUtils_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "org.apache.commons.jxpath.util.ValueUtils"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
+    org.evosuite.runtime.Runtime.getInstance().resetRuntime(); 
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/JXPATH-9_1/temp/testcases/org/apache/commons/jxpath/ri/model/beans/PropertyIterator_ESTest_scaffolding.java

@@ -1,0 +1,220 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 18:41:31 GMT 2018
+ */
+
+package org.apache.commons.jxpath.ri.model.beans;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+@EvoSuiteClassExclude
+public class PropertyIterator_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "org.apache.commons.jxpath.ri.model.beans.PropertyIterator"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
+    org.evosuite.runtime.Runtime.getInstance().resetRuntime(); 
+  } 
+
+  @AfterClass 
+  public static void clearEvoSuiteFramework(){ 
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/LA4J-1_1/temp/testcases/org/la4j/vector/sparse/CompressedVector_ESTest_scaffolding.java

@@ -1,0 +1,294 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 19:55:59 GMT 2018
+ */
+
+package org.la4j.vector.sparse;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+@EvoSuiteClassExclude
+public class CompressedVector_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "org.la4j.vector.sparse.CompressedVector"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/LA4J-2_1/temp/testcases/SBSTDummyForCoverageAndMutationCalculation.java

@@ -1,0 +1,7 @@
+import org.junit.Test;
+
+public class SBSTDummyForCoverageAndMutationCalculation{
+
+@org.junit.Test
+public void test(){}
+}

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/LA4J-3_1/temp/testcases/org/la4j/matrix/sparse/CRSMatrix_ESTest.java

@@ -1,0 +1,2535 @@
+/*
+ * This file was automatically generated by EvoSuite
+ * Wed Jan 24 19:43:10 GMT 2018
+ */
+
+package org.la4j.matrix.sparse;
+
+import org.junit.Test;
+import static org.junit.Assert.*;
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+import static org.evosuite.runtime.EvoAssertions.*;
+import java.nio.BufferUnderflowException;
+import java.text.DecimalFormat;
+import java.text.NumberFormat;
+import java.util.Iterator;
+import java.util.NoSuchElementException;
+import java.util.Random;
+import org.evosuite.runtime.EvoRunner;
+import org.evosuite.runtime.EvoRunnerParameters;
+import org.evosuite.runtime.PrivateAccess;
+import org.evosuite.runtime.ViolatedAssumptionAnswer;
+import org.evosuite.runtime.mock.java.util.MockRandom;
+import org.junit.runner.RunWith;
+import org.la4j.LinearAlgebra;
+import org.la4j.Matrix;
+import org.la4j.Vector;
+import org.la4j.linear.LeastSquaresSolver;
+import org.la4j.linear.SweepSolver;
+import org.la4j.matrix.MatrixFactory;
+import org.la4j.matrix.RowMajorSparseMatrix;
+import org.la4j.matrix.SparseMatrix;
+import org.la4j.matrix.functor.MatrixFunction;
+import org.la4j.matrix.functor.MatrixPredicate;
+import org.la4j.matrix.functor.MatrixProcedure;
+import org.la4j.matrix.sparse.CRSMatrix;
+import org.la4j.operation.MatrixOperation;
+import org.la4j.operation.MatrixVectorOperation;
+import org.la4j.vector.DenseVector;
+import org.la4j.vector.functor.VectorAccumulator;
+import org.la4j.vector.functor.VectorFunction;
+import org.la4j.vector.functor.VectorProcedure;
+
+@RunWith(EvoRunner.class) @EvoRunnerParameters(mockJVMNonDeterminism = true, useVFS = true, useVNET = true, resetStaticState = true, separateClassLoader = true, useJEE = true) 
+public class CRSMatrix_ESTest extends CRSMatrix_ESTest_scaffolding {
+
+  @Test(timeout = 4000)
+  public void test000()  throws Throwable  {
+      int int0 = 1857;
+      int int1 = 6;
+      int int2 = 947;
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/LA4J-3_1/temp/testcases/org/la4j/matrix/sparse/CRSMatrix_ESTest_scaffolding.java

@@ -1,0 +1,318 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 19:43:10 GMT 2018
+ */
+
+package org.la4j.matrix.sparse;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+@EvoSuiteClassExclude
+public class CRSMatrix_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "org.la4j.matrix.sparse.CRSMatrix"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/LA4J-4_1/temp/testcases/org/la4j/matrix/dense/Basic1DMatrix_ESTest.java

@@ -1,0 +1,3322 @@
+/*
+ * This file was automatically generated by EvoSuite
+ * Wed Jan 24 19:52:35 GMT 2018
+ */
+
+package org.la4j.matrix.dense;
+
+import org.junit.Test;
+import static org.junit.Assert.*;
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+import static org.evosuite.runtime.EvoAssertions.*;
+import java.math.RoundingMode;
+import java.nio.BufferOverflowException;
+import java.nio.BufferUnderflowException;
+import java.text.DecimalFormat;
+import java.text.DecimalFormatSymbols;
+import java.text.NumberFormat;
+import java.util.LinkedList;
+import java.util.Locale;
+import java.util.NoSuchElementException;
+import java.util.Spliterator;
+import java.util.stream.DoubleStream;
+import java.util.stream.LongStream;
+import org.evosuite.runtime.EvoRunner;
+import org.evosuite.runtime.EvoRunnerParameters;
+import org.evosuite.runtime.Random;
+import org.evosuite.runtime.ViolatedAssumptionAnswer;
+import org.evosuite.runtime.mock.java.util.MockRandom;
+import org.junit.runner.RunWith;
+import org.la4j.LinearAlgebra;
+import org.la4j.Matrix;
+import org.la4j.Vector;
+import org.la4j.decomposition.MatrixDecompositor;
+import org.la4j.inversion.MatrixInverter;
+import org.la4j.iterator.RowMajorMatrixIterator;
+import org.la4j.iterator.VectorIterator;
+import org.la4j.matrix.DenseMatrix;
+import org.la4j.matrix.MatrixFactory;
+import org.la4j.matrix.dense.Basic1DMatrix;
+import org.la4j.matrix.functor.MatrixAccumulator;
+import org.la4j.matrix.functor.MatrixPredicate;
+import org.la4j.matrix.sparse.CRSMatrix;
+import org.la4j.operation.ooplace.OoPlaceMatricesAddition;
+import org.la4j.vector.SparseVector;
+import org.la4j.vector.functor.VectorAccumulator;
+import org.la4j.vector.functor.VectorFunction;
+
+@RunWith(EvoRunner.class) @EvoRunnerParameters(mockJVMNonDeterminism = true, useVFS = true, useVNET = true, resetStaticState = true, separateClassLoader = true, useJEE = true) 
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/LA4J-5_1/temp/testcases/org/la4j/Matrix_ESTest_scaffolding.java

@@ -1,0 +1,348 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 19:49:06 GMT 2018
+ */
+
+package org.la4j;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+@EvoSuiteClassExclude
+public class Matrix_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "org.la4j.Matrix"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/LA4J-7_1/temp/testcases/org/la4j/matrix/sparse/CCSMatrix_ESTest.java

@@ -1,0 +1,2736 @@
+/*
+ * This file was automatically generated by EvoSuite
+ * Wed Jan 24 19:31:37 GMT 2018
+ */
+
+package org.la4j.matrix.sparse;
+
+import org.junit.Test;
+import static org.junit.Assert.*;
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+import static org.evosuite.runtime.EvoAssertions.*;
+import java.nio.BufferUnderflowException;
+import java.text.NumberFormat;
+import java.util.Locale;
+import java.util.NoSuchElementException;
+import java.util.Random;
+import java.util.stream.DoubleStream;
+import org.evosuite.runtime.EvoRunner;
+import org.evosuite.runtime.EvoRunnerParameters;
+import org.evosuite.runtime.PrivateAccess;
+import org.evosuite.runtime.ViolatedAssumptionAnswer;
+import org.evosuite.runtime.mock.java.util.MockRandom;
+import org.junit.runner.RunWith;
+import org.la4j.LinearAlgebra;
+import org.la4j.Matrix;
+import org.la4j.iterator.ColumnMajorMatrixIterator;
+import org.la4j.iterator.VectorIterator;
+import org.la4j.matrix.ColumnMajorSparseMatrix;
+import org.la4j.matrix.DenseMatrix;
+import org.la4j.matrix.MatrixFactory;
+import org.la4j.matrix.RowMajorSparseMatrix;
+import org.la4j.matrix.SparseMatrix;
+import org.la4j.matrix.functor.MatrixAccumulator;
+import org.la4j.matrix.functor.MatrixFunction;
+import org.la4j.matrix.functor.MatrixPredicate;
+import org.la4j.matrix.functor.MatrixProcedure;
+import org.la4j.matrix.sparse.CCSMatrix;
+import org.la4j.operation.MatrixOperation;
+import org.la4j.operation.inplace.InPlaceCopyMatrixToMatrix;
+import org.la4j.operation.ooplace.OoPlaceMatricesMultiplication;
+import org.la4j.vector.SparseVector;
+import org.la4j.vector.dense.BasicVector;
+import org.la4j.vector.functor.VectorAccumulator;
+import org.la4j.vector.functor.VectorFunction;
+import org.la4j.vector.functor.VectorProcedure;
+import org.la4j.vector.sparse.CompressedVector;
+
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/LA4J-7_1/temp/testcases/org/la4j/matrix/sparse/CCSMatrix_ESTest_scaffolding.java

@@ -1,0 +1,317 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 19:31:37 GMT 2018
+ */
+
+package org.la4j.matrix.sparse;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+@EvoSuiteClassExclude
+public class CCSMatrix_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "org.la4j.matrix.sparse.CCSMatrix"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/LA4J-8_1/temp/testcases/org/la4j/matrix/dense/Basic2DMatrix_ESTest.java

@@ -1,0 +1,3792 @@
+/*
+ * This file was automatically generated by EvoSuite
+ * Wed Jan 24 19:39:02 GMT 2018
+ */
+
+package org.la4j.matrix.dense;
+
+import org.junit.Test;
+import static org.junit.Assert.*;
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+import static org.evosuite.runtime.EvoAssertions.*;
+import java.math.RoundingMode;
+import java.nio.BufferOverflowException;
+import java.nio.BufferUnderflowException;
+import java.text.DecimalFormat;
+import java.text.NumberFormat;
+import java.util.NoSuchElementException;
+import java.util.Random;
+import java.util.function.Consumer;
+import java.util.stream.DoubleStream;
+import java.util.stream.IntStream;
+import org.evosuite.runtime.EvoRunner;
+import org.evosuite.runtime.EvoRunnerParameters;
+import org.evosuite.runtime.ViolatedAssumptionAnswer;
+import org.evosuite.runtime.mock.java.util.MockRandom;
+import org.junit.runner.RunWith;
+import org.la4j.LinearAlgebra;
+import org.la4j.Matrix;
+import org.la4j.Vector;
+import org.la4j.inversion.MatrixInverter;
+import org.la4j.iterator.ColumnMajorMatrixIterator;
+import org.la4j.iterator.VectorIterator;
+import org.la4j.linear.LinearSystemSolver;
+import org.la4j.matrix.ColumnMajorSparseMatrix;
+import org.la4j.matrix.DenseMatrix;
+import org.la4j.matrix.MatrixFactory;
+import org.la4j.matrix.RowMajorSparseMatrix;
+import org.la4j.matrix.dense.Basic2DMatrix;
+import org.la4j.matrix.functor.MatrixAccumulator;
+import org.la4j.matrix.functor.MatrixFunction;
+import org.la4j.matrix.functor.MatrixProcedure;
+import org.la4j.matrix.sparse.CCSMatrix;
+import org.la4j.matrix.sparse.CRSMatrix;
+import org.la4j.operation.MatrixMatrixOperation;
+import org.la4j.operation.MatrixOperation;
+import org.la4j.operation.ooplace.OoPlaceMatricesMultiplication;
+import org.la4j.operation.ooplace.OoPlaceMatrixHadamardProduct;
+import org.la4j.vector.functor.VectorAccumulator;
+import org.la4j.vector.functor.VectorFunction;
+
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/LA4J-8_1/temp/testcases/org/la4j/matrix/dense/Basic2DMatrix_ESTest_scaffolding.java

@@ -1,0 +1,316 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 19:39:02 GMT 2018
+ */
+
+package org.la4j.matrix.dense;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+@EvoSuiteClassExclude
+public class Basic2DMatrix_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "org.la4j.matrix.dense.Basic2DMatrix"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/LA4J-9_1/temp/testcases/org/la4j/decomposition/SingularValueDecompositor_ESTest.java

@@ -1,0 +1,279 @@
+/*
+ * This file was automatically generated by EvoSuite
+ * Wed Jan 24 19:35:36 GMT 2018
+ */
+
+package org.la4j.decomposition;
+
+import org.junit.Test;
+import static org.junit.Assert.*;
+import static org.evosuite.runtime.EvoAssertions.*;
+import java.util.Random;
+import org.evosuite.runtime.EvoRunner;
+import org.evosuite.runtime.EvoRunnerParameters;
+import org.evosuite.runtime.mock.java.util.MockRandom;
+import org.junit.runner.RunWith;
+import org.la4j.Matrix;
+import org.la4j.decomposition.SingularValueDecompositor;
+import org.la4j.matrix.ColumnMajorSparseMatrix;
+import org.la4j.matrix.DenseMatrix;
+import org.la4j.matrix.RowMajorSparseMatrix;
+import org.la4j.matrix.sparse.CRSMatrix;
+import org.la4j.vector.SparseVector;
+
+@RunWith(EvoRunner.class) @EvoRunnerParameters(mockJVMNonDeterminism = true, useVFS = true, useVNET = true, resetStaticState = true, separateClassLoader = true, useJEE = true) 
+public class SingularValueDecompositor_ESTest extends SingularValueDecompositor_ESTest_scaffolding {
+
+  @Test(timeout = 4000)
+  public void test0()  throws Throwable  {
+      int int0 = 292;
+      RowMajorSparseMatrix rowMajorSparseMatrix0 = RowMajorSparseMatrix.diagonal(int0, int0);
+      assertEquals(292, rowMajorSparseMatrix0.columns());
+      assertTrue(rowMajorSparseMatrix0.isRowMajor());
+      assertEquals(292.0, rowMajorSparseMatrix0.max(), 0.01);
+      assertEquals(292, rowMajorSparseMatrix0.rows());
+      assertEquals(0.003424657534246575, rowMajorSparseMatrix0.density(), 0.01);
+      assertEquals(292, rowMajorSparseMatrix0.cardinality());
+      assertEquals(0.0, rowMajorSparseMatrix0.min(), 0.01);
+      assertNotNull(rowMajorSparseMatrix0);
+      
+      SingularValueDecompositor singularValueDecompositor0 = new SingularValueDecompositor(rowMajorSparseMatrix0);
+      assertEquals(292, rowMajorSparseMatrix0.columns());
+      assertTrue(rowMajorSparseMatrix0.isRowMajor());
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/LA4J-9_1/temp/testcases/org/la4j/decomposition/SingularValueDecompositor_ESTest_scaffolding.java

@@ -1,0 +1,297 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 19:35:36 GMT 2018
+ */
+
+package org.la4j.decomposition;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+@EvoSuiteClassExclude
+public class SingularValueDecompositor_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "org.la4j.decomposition.SingularValueDecompositor"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/OKHTTP-1_1/temp/testcases/okhttp3/Cookie_ESTest.java

@@ -1,0 +1,563 @@
+/*
+ * This file was automatically generated by EvoSuite
+ * Wed Jan 24 18:19:33 GMT 2018
+ */
+
+package okhttp3;
+
+import org.junit.Test;
+import static org.junit.Assert.*;
+import static org.evosuite.runtime.EvoAssertions.*;
+import java.util.List;
+import okhttp3.Cookie;
+import okhttp3.Headers;
+import okhttp3.HttpUrl;
+import org.evosuite.runtime.EvoRunner;
+import org.evosuite.runtime.EvoRunnerParameters;
+import org.evosuite.runtime.PrivateAccess;
+import org.junit.runner.RunWith;
+
+@RunWith(EvoRunner.class) @EvoRunnerParameters(mockJVMNonDeterminism = true, useVFS = true, useVNET = true, resetStaticState = true, separateClassLoader = true, useJEE = true) 
+public class Cookie_ESTest extends Cookie_ESTest_scaffolding {
+
+  @Test(timeout = 4000)
+  public void test00()  throws Throwable  {
+      Cookie.Builder cookie_Builder0 = new Cookie.Builder();
+      assertNotNull(cookie_Builder0);
+      
+      long long0 = 0L;
+      Cookie.Builder cookie_Builder1 = cookie_Builder0.expiresAt(long0);
+      assertSame(cookie_Builder0, cookie_Builder1);
+      assertSame(cookie_Builder1, cookie_Builder0);
+      assertNotNull(cookie_Builder1);
+  }
+
+  @Test(timeout = 4000)
+  public void test01()  throws Throwable  {
+      Cookie cookie0 = null;
+      String string0 = ".3=~";
+      int int0 = 2147483641;
+      int int1 = (-2880);
+      try { 
+        PrivateAccess.callMethod((Class<Cookie>) Cookie.class, cookie0, "parseExpires", (Object) string0, (Class<?>) String.class, (Object) int0, (Class<?>) int.class, (Object) int1, (Class<?>) int.class);
+        fail("Expecting exception: IllegalArgumentException");
+      
+      } catch(IllegalArgumentException e) {
+         //
+         // no message in exception (getMessage() returned null)
+         //
+         verifyException("okhttp3.Cookie", e);
+      }
+  }
+
+  @Test(timeout = 4000)
+  public void test02()  throws Throwable  {
+      HttpUrl httpUrl0 = null;
+      String string0 = "";
+      Cookie cookie0 = null;
+      try { 
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/OKHTTP-1_1/temp/testcases/okhttp3/Cookie_ESTest_scaffolding.java

@@ -1,0 +1,113 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 18:19:33 GMT 2018
+ */
+
+package okhttp3;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+@EvoSuiteClassExclude
+public class Cookie_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "okhttp3.Cookie"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
+    org.evosuite.runtime.Runtime.getInstance().resetRuntime(); 
+  } 
+
+  @AfterClass 
+  public static void clearEvoSuiteFramework(){ 
+    Sandbox.resetDefaultSecurityManager(); 
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/OKHTTP-2_1/temp/testcases/okhttp3/internal/platform/AndroidPlatform_ESTest_scaffolding.java

@@ -1,0 +1,132 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 18:20:57 GMT 2018
+ */
+
+package okhttp3.internal.platform;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+@EvoSuiteClassExclude
+public class AndroidPlatform_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "okhttp3.internal.platform.AndroidPlatform"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
+    org.evosuite.runtime.Runtime.getInstance().resetRuntime(); 
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/OKHTTP-3_1/temp/testcases/okhttp3/ConnectionSpec_ESTest.java

@@ -1,0 +1,1246 @@
+/*
+ * This file was automatically generated by EvoSuite
+ * Wed Jan 24 18:22:25 GMT 2018
+ */
+
+package okhttp3;
+
+import org.junit.Test;
+import static org.junit.Assert.*;
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+import static org.evosuite.runtime.EvoAssertions.*;
+import java.util.List;
+import javax.net.ssl.SSLSocket;
+import okhttp3.CipherSuite;
+import okhttp3.ConnectionSpec;
+import okhttp3.TlsVersion;
+import org.evosuite.runtime.EvoRunner;
+import org.evosuite.runtime.EvoRunnerParameters;
+import org.evosuite.runtime.PrivateAccess;
+import org.evosuite.runtime.ViolatedAssumptionAnswer;
+import org.junit.runner.RunWith;
+
+@RunWith(EvoRunner.class) @EvoRunnerParameters(mockJVMNonDeterminism = true, useVFS = true, useVNET = true, resetStaticState = true, separateClassLoader = true, useJEE = true) 
+public class ConnectionSpec_ESTest extends ConnectionSpec_ESTest_scaffolding {
+
+  @Test(timeout = 4000)
+  public void test00()  throws Throwable  {
+      boolean boolean0 = true;
+      ConnectionSpec.Builder connectionSpec_Builder0 = new ConnectionSpec.Builder(boolean0);
+      assertNotNull(connectionSpec_Builder0);
+      
+      ConnectionSpec.Builder connectionSpec_Builder1 = connectionSpec_Builder0.supportsTlsExtensions(boolean0);
+      assertSame(connectionSpec_Builder0, connectionSpec_Builder1);
+      assertSame(connectionSpec_Builder1, connectionSpec_Builder0);
+      assertNotNull(connectionSpec_Builder1);
+  }
+
+  @Test(timeout = 4000)
+  public void test01()  throws Throwable  {
+      ConnectionSpec connectionSpec0 = ConnectionSpec.MODERN_TLS;
+      assertTrue(connectionSpec0.isTls());
+      assertTrue(connectionSpec0.supportsTlsExtensions());
+      assertNotNull(connectionSpec0);
+      
+      ConnectionSpec.Builder connectionSpec_Builder0 = new ConnectionSpec.Builder(connectionSpec0);
+      assertTrue(connectionSpec0.isTls());
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/OKHTTP-3_1/temp/testcases/okhttp3/ConnectionSpec_ESTest_scaffolding.java

@@ -1,0 +1,113 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 18:22:25 GMT 2018
+ */
+
+package okhttp3;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+@EvoSuiteClassExclude
+public class ConnectionSpec_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "okhttp3.ConnectionSpec"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
+    org.evosuite.runtime.Runtime.getInstance().resetRuntime(); 
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/OKHTTP-4_1/temp/testcases/okhttp3/internal/http/HttpHeaders_ESTest_scaffolding.java

@@ -1,0 +1,135 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 18:24:09 GMT 2018
+ */
+
+package okhttp3.internal.http;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+@EvoSuiteClassExclude
+public class HttpHeaders_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "okhttp3.internal.http.HttpHeaders"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
+    org.evosuite.runtime.Runtime.getInstance().resetRuntime(); 
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/OKHTTP-5_1/temp/testcases/okhttp3/internal/tls/DistinguishedNameParser_ESTest.java

@@ -1,0 +1,180 @@
+/*
+ * This file was automatically generated by EvoSuite
+ * Wed Jan 24 18:14:52 GMT 2018
+ */
+
+package okhttp3.internal.tls;
+
+import org.junit.Test;
+import static org.junit.Assert.*;
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+import static org.evosuite.runtime.EvoAssertions.*;
+import java.io.InputStream;
+import javax.security.auth.x500.X500Principal;
+import okhttp3.internal.tls.DistinguishedNameParser;
+import org.evosuite.runtime.EvoRunner;
+import org.evosuite.runtime.EvoRunnerParameters;
+import org.evosuite.runtime.PrivateAccess;
+import org.evosuite.runtime.ViolatedAssumptionAnswer;
+import org.junit.runner.RunWith;
+
+@RunWith(EvoRunner.class) @EvoRunnerParameters(mockJVMNonDeterminism = true, useVFS = true, useVNET = true, resetStaticState = true, separateClassLoader = true, useJEE = true) 
+public class DistinguishedNameParser_ESTest extends DistinguishedNameParser_ESTest_scaffolding {
+
+  @Test(timeout = 4000)
+  public void test0()  throws Throwable  {
+      X500Principal x500Principal0 = null;
+      DistinguishedNameParser distinguishedNameParser0 = null;
+      try {
+        distinguishedNameParser0 = new DistinguishedNameParser(x500Principal0);
+        fail("Expecting exception: NullPointerException");
+      
+      } catch(NullPointerException e) {
+         //
+         // no message in exception (getMessage() returned null)
+         //
+         verifyException("okhttp3.internal.tls.DistinguishedNameParser", e);
+      }
+  }
+
+  @Test(timeout = 4000)
+  public void test1()  throws Throwable  {
+      String string0 = "";
+      X500Principal x500Principal0 = new X500Principal(string0);
+      assertNotNull(x500Principal0);
+      
+      DistinguishedNameParser distinguishedNameParser0 = new DistinguishedNameParser(x500Principal0);
+      assertNotNull(distinguishedNameParser0);
+      
+      try { 
+        PrivateAccess.callMethod((Class<DistinguishedNameParser>) DistinguishedNameParser.class, distinguishedNameParser0, "getUTF8");
+        fail("Expecting exception: IllegalStateException");
+      
+      } catch(IllegalStateException e) {
+         //
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/OKHTTP-5_1/temp/testcases/okhttp3/internal/tls/DistinguishedNameParser_ESTest_scaffolding.java

@@ -1,0 +1,99 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 18:14:52 GMT 2018
+ */
+
+package okhttp3.internal.tls;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+@EvoSuiteClassExclude
+public class DistinguishedNameParser_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "okhttp3.internal.tls.DistinguishedNameParser"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
+    org.evosuite.runtime.Runtime.getInstance().resetRuntime(); 
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/OKHTTP-6_1/temp/testcases/okhttp3/CacheControl_ESTest_scaffolding.java

@@ -1,0 +1,123 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 18:16:27 GMT 2018
+ */
+
+package okhttp3;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+@EvoSuiteClassExclude
+public class CacheControl_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "okhttp3.CacheControl"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
+    org.evosuite.runtime.Runtime.getInstance().resetRuntime(); 
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/OKHTTP-7_1/temp/testcases/okhttp3/internal/tls/OkHostnameVerifier_ESTest.java

@@ -1,0 +1,363 @@
+/*
+ * This file was automatically generated by EvoSuite
+ * Wed Jan 24 18:17:49 GMT 2018
+ */
+
+package okhttp3.internal.tls;
+
+import org.junit.Test;
+import static org.junit.Assert.*;
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+import static org.evosuite.runtime.EvoAssertions.*;
+import java.security.cert.Certificate;
+import java.security.cert.X509Certificate;
+import java.util.Collection;
+import java.util.List;
+import javax.net.ssl.SSLSession;
+import javax.security.auth.x500.X500Principal;
+import okhttp3.internal.tls.OkHostnameVerifier;
+import org.evosuite.runtime.EvoRunner;
+import org.evosuite.runtime.EvoRunnerParameters;
+import org.evosuite.runtime.PrivateAccess;
+import org.evosuite.runtime.ViolatedAssumptionAnswer;
+import org.junit.runner.RunWith;
+
+@RunWith(EvoRunner.class) @EvoRunnerParameters(mockJVMNonDeterminism = true, useVFS = true, useVNET = true, resetStaticState = true, separateClassLoader = true, useJEE = true) 
+public class OkHostnameVerifier_ESTest extends OkHostnameVerifier_ESTest_scaffolding {
+
+  @Test(timeout = 4000)
+  public void test00()  throws Throwable  {
+      OkHostnameVerifier okHostnameVerifier0 = OkHostnameVerifier.INSTANCE;
+      assertNotNull(okHostnameVerifier0);
+      
+      String string0 = "]3_f";
+      Certificate[] certificateArray0 = new Certificate[6];
+      Certificate certificate0 = mock(Certificate.class, new ViolatedAssumptionAnswer());
+      certificateArray0[0] = certificate0;
+      SSLSession sSLSession0 = mock(SSLSession.class, new ViolatedAssumptionAnswer());
+      doReturn(certificateArray0).when(sSLSession0).getPeerCertificates();
+      // Undeclared exception!
+      try { 
+        okHostnameVerifier0.verify(string0, sSLSession0);
+        fail("Expecting exception: ClassCastException");
+      
+      } catch(ClassCastException e) {
+         //
+         // codegen.java.security.cert.Certificate$MockitoMock$1363551780 cannot be cast to java.security.cert.X509Certificate
+         //
+         verifyException("okhttp3.internal.tls.OkHostnameVerifier", e);
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/OKHTTP-7_1/temp/testcases/okhttp3/internal/tls/OkHostnameVerifier_ESTest_scaffolding.java

@@ -1,0 +1,112 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 18:17:49 GMT 2018
+ */
+
+package okhttp3.internal.tls;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+import static org.evosuite.shaded.org.mockito.Mockito.*;
+@EvoSuiteClassExclude
+public class OkHostnameVerifier_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "okhttp3.internal.tls.OkHostnameVerifier"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
+    org.evosuite.runtime.Runtime.getInstance().resetRuntime(); 
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/RE2J-1_1/temp/testcases/com/google/re2j/Parser_ESTest.java

@@ -1,0 +1,2604 @@
+/*
+ * This file was automatically generated by EvoSuite
+ * Wed Jan 24 20:01:09 GMT 2018
+ */
+
+package com.google.re2j;
+
+import org.junit.Test;
+import static org.junit.Assert.*;
+import static org.evosuite.runtime.EvoAssertions.*;
+import com.google.re2j.Parser;
+import com.google.re2j.Regexp;
+import org.evosuite.runtime.EvoRunner;
+import org.evosuite.runtime.EvoRunnerParameters;
+import org.evosuite.runtime.PrivateAccess;
+import org.junit.runner.RunWith;
+
+@RunWith(EvoRunner.class) @EvoRunnerParameters(mockJVMNonDeterminism = true, useVFS = true, useVNET = true, resetStaticState = true, separateClassLoader = true, useJEE = true) 
+public class Parser_ESTest extends Parser_ESTest_scaffolding {
+
+  @Test(timeout = 4000)
+  public void test00()  throws Throwable  {
+      String string0 = "B7P~j.<ye/cfjrT(Y";
+      int int0 = 1077;
+      Regexp.Op regexp_Op0 = Regexp.Op.PLUS;
+      Regexp regexp0 = new Regexp(regexp_Op0);
+      assertNotNull(regexp0);
+      
+      String string1 = "&m?##LuoiED7nwE&&";
+      int int1 = 2615;
+      Parser parser0 = new Parser(string1, int1);
+      assertNotNull(parser0);
+      assertFalse(string1.equals((Object)string0));
+      assertFalse(int1 == int0);
+      
+      boolean boolean0 = false;
+      Object object0 = PrivateAccess.callMethod((Class<Parser>) Parser.class, parser0, "removeLeadingRegexp", (Object) regexp0, (Class<?>) Regexp.class, (Object) boolean0, (Class<?>) boolean.class);
+      assertNotNull(object0);
+      assertFalse(string1.equals((Object)string0));
+      assertFalse(int1 == int0);
+      assertFalse(object0.equals((Object)regexp0));
+      assertNotSame(regexp0, object0);
+      assertNotSame(string1, string0);
+      assertNotSame(object0, regexp0);
+      
+      Regexp regexp1 = new Regexp(regexp_Op0);
+      assertNotNull(regexp1);
+      assertFalse(regexp1.equals((Object)object0));
+      
+      int int2 = (-1696);
+      try { 
+        Parser.parse(string0, int0);
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/RE2J-1_1/temp/testcases/com/google/re2j/Parser_ESTest_scaffolding.java

@@ -1,0 +1,122 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 20:01:09 GMT 2018
+ */
+
+package com.google.re2j;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+@EvoSuiteClassExclude
+public class Parser_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "com.google.re2j.Parser"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
+    org.evosuite.runtime.Runtime.getInstance().resetRuntime(); 
+  } 
+
+  @AfterClass 
+  public static void clearEvoSuiteFramework(){ 
+    Sandbox.resetDefaultSecurityManager(); 
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/RE2J-2_1/temp/testcases/com/google/re2j/CharClass_ESTest.java

@@ -1,0 +1,2201 @@
+/*
+ * This file was automatically generated by EvoSuite
+ * Wed Jan 24 19:15:40 GMT 2018
+ */
+
+package com.google.re2j;
+
+import org.junit.Test;
+import static org.junit.Assert.*;
+import static org.evosuite.runtime.EvoAssertions.*;
+import com.google.re2j.CharClass;
+import com.google.re2j.CharGroup;
+import org.evosuite.runtime.EvoRunner;
+import org.evosuite.runtime.EvoRunnerParameters;
+import org.junit.runner.RunWith;
+
+@RunWith(EvoRunner.class) @EvoRunnerParameters(mockJVMNonDeterminism = true, useVFS = true, useVNET = true, resetStaticState = true, separateClassLoader = true, useJEE = true) 
+public class CharClass_ESTest extends CharClass_ESTest_scaffolding {
+
+  @Test(timeout = 4000)
+  public void test00()  throws Throwable  {
+      int[] intArray0 = new int[6];
+      int int0 = (-187);
+      intArray0[0] = int0;
+      int int1 = 1;
+      intArray0[1] = int1;
+      int int2 = 0;
+      intArray0[2] = int2;
+      int int3 = 964;
+      intArray0[3] = int3;
+      int int4 = (-2722);
+      intArray0[4] = int4;
+      int int5 = 0;
+      intArray0[5] = int5;
+      CharClass charClass0 = new CharClass(intArray0);
+      CharClass charClass1 = charClass0.cleanClass();
+      CharClass charClass2 = charClass1.appendFoldedClass(intArray0);
+      int int6 = 2;
+      CharClass charClass3 = charClass2.appendLiteral(int6, int5);
+      int[][] intArrayArray0 = null;
+      // Undeclared exception!
+      try { 
+        charClass3.appendTable(intArrayArray0);
+        fail("Expecting exception: NullPointerException");
+      
+      } catch(NullPointerException e) {
+         //
+         // no message in exception (getMessage() returned null)
+         //
+         verifyException("com.google.re2j.CharClass", e);
+      }
+  }
+
+  @Test(timeout = 4000)
+  public void test01()  throws Throwable  {
+      int[] intArray0 = new int[4];
+      int int0 = 0;
+      intArray0[0] = int0;
+      int int1 = (-3377);
+      intArray0[1] = int1;
+      int int2 = (-4193);
+      intArray0[2] = int2;
+      int int3 = 0;
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/RE2J-2_1/temp/testcases/com/google/re2j/CharClass_ESTest_scaffolding.java

@@ -1,0 +1,105 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 19:15:41 GMT 2018
+ */
+
+package com.google.re2j;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+@EvoSuiteClassExclude
+public class CharClass_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "com.google.re2j.CharClass"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
+    org.evosuite.runtime.Runtime.getInstance().resetRuntime(); 
+  } 
+
+  @AfterClass 
+  public static void clearEvoSuiteFramework(){ 
+    Sandbox.resetDefaultSecurityManager(); 
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/RE2J-3_1/temp/testcases/com/google/re2j/Simplify_ESTest_scaffolding.java

@@ -1,0 +1,112 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 19:11:44 GMT 2018
+ */
+
+package com.google.re2j;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+@EvoSuiteClassExclude
+public class Simplify_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "com.google.re2j.Simplify"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
+    org.evosuite.runtime.Runtime.getInstance().resetRuntime(); 
+  } 
+
+  @AfterClass 
+  public static void clearEvoSuiteFramework(){ 
+    Sandbox.resetDefaultSecurityManager(); 
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/RE2J-4_1/temp/testcases/com/google/re2j/Utils_ESTest.java

@@ -1,0 +1,872 @@
+/*
+ * This file was automatically generated by EvoSuite
+ * Wed Jan 24 19:20:35 GMT 2018
+ */
+
+package com.google.re2j;
+
+import org.junit.Test;
+import static org.junit.Assert.*;
+import static org.evosuite.runtime.EvoAssertions.*;
+import com.google.re2j.Utils;
+import org.evosuite.runtime.EvoRunner;
+import org.evosuite.runtime.EvoRunnerParameters;
+import org.junit.runner.RunWith;
+
+@RunWith(EvoRunner.class) @EvoRunnerParameters(mockJVMNonDeterminism = true, useVFS = true, useVNET = true, resetStaticState = true, separateClassLoader = true, useJEE = true) 
+public class Utils_ESTest extends Utils_ESTest_scaffolding {
+
+  @Test(timeout = 4000)
+  public void test00()  throws Throwable  {
+      byte[] byteArray0 = new byte[2];
+      int int0 = 0;
+      int int1 = Utils.emptyOpContext(int0, byteArray0[1]);
+      assertEquals(32, int1);
+      assertFalse(int1 == int0);
+      assertArrayEquals(new byte[] {(byte)0, (byte)0}, byteArray0);
+      assertEquals(2, byteArray0.length);
+  }
+
+  @Test(timeout = 4000)
+  public void test01()  throws Throwable  {
+      int int0 = 57;
+      int int1 = Utils.emptyOpContext(int0, int0);
+      assertEquals(32, int1);
+      assertFalse(int1 == int0);
+  }
+
+  @Test(timeout = 4000)
+  public void test02()  throws Throwable  {
+      int int0 = 97;
+      int int1 = Utils.emptyOpContext(int0, int0);
+      assertEquals(32, int1);
+      assertFalse(int1 == int0);
+  }
+
+  @Test(timeout = 4000)
+  public void test03()  throws Throwable  {
+      int int0 = 65;
+      boolean boolean0 = Utils.isWordRune(int0);
+      assertTrue(boolean0);
+  }
+
+  @Test(timeout = 4000)
+  public void test04()  throws Throwable  {
+      byte[] byteArray0 = new byte[8];
+      byte byte0 = (byte) (-80);
+      byte[] byteArray1 = new byte[4];
+      assertFalse(byteArray1.equals((Object)byteArray0));
+      
+      byteArray1[1] = byte0;
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/RE2J-4_1/temp/testcases/com/google/re2j/Utils_ESTest_scaffolding.java

@@ -1,0 +1,103 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 19:20:35 GMT 2018
+ */
+
+package com.google.re2j;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+@EvoSuiteClassExclude
+public class Utils_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "com.google.re2j.Utils"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
+    org.evosuite.runtime.Runtime.getInstance().resetRuntime(); 
+  } 
+
+  @AfterClass 
+  public static void clearEvoSuiteFramework(){ 
+    Sandbox.resetDefaultSecurityManager(); 
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/RE2J-5_1/temp/testcases/com/google/re2j/Compiler_ESTest.java

@@ -1,0 +1,433 @@
+/*
+ * This file was automatically generated by EvoSuite
+ * Wed Jan 24 19:19:08 GMT 2018
+ */
+
+package com.google.re2j;
+
+import org.junit.Test;
+import static org.junit.Assert.*;
+import static org.evosuite.runtime.EvoAssertions.*;
+import com.google.re2j.Compiler;
+import com.google.re2j.Prog;
+import com.google.re2j.Regexp;
+import org.evosuite.runtime.EvoRunner;
+import org.evosuite.runtime.EvoRunnerParameters;
+import org.junit.runner.RunWith;
+
+@RunWith(EvoRunner.class) @EvoRunnerParameters(mockJVMNonDeterminism = true, useVFS = true, useVNET = true, resetStaticState = true, separateClassLoader = true, useJEE = true) 
+public class Compiler_ESTest extends Compiler_ESTest_scaffolding {
+
+  @Test(timeout = 4000)
+  public void test00()  throws Throwable  {
+      Regexp.Op regexp_Op0 = Regexp.Op.CHAR_CLASS;
+      Regexp regexp0 = new Regexp(regexp_Op0);
+      assertNotNull(regexp0);
+      
+      int[] intArray0 = new int[6];
+      regexp0.runes = intArray0;
+      Prog prog0 = Compiler.compileRegexp(regexp0);
+      assertNotNull(prog0);
+  }
+
+  @Test(timeout = 4000)
+  public void test01()  throws Throwable  {
+      Regexp.Op regexp_Op0 = Regexp.Op.ANY_CHAR;
+      Regexp regexp0 = new Regexp(regexp_Op0);
+      assertNotNull(regexp0);
+      
+      Regexp regexp1 = new Regexp(regexp0);
+      assertNotNull(regexp1);
+      assertTrue(regexp1.equals((Object)regexp0));
+      
+      Regexp[] regexpArray0 = new Regexp[5];
+      Regexp regexp2 = new Regexp(regexp0);
+      assertNotNull(regexp2);
+      assertTrue(regexp0.equals((Object)regexp1));
+      assertTrue(regexp2.equals((Object)regexp0));
+      assertTrue(regexp2.equals((Object)regexp1));
+      
+      regexpArray0[0] = regexp2;
+      regexp1.subs = regexpArray0;
+      Regexp.Op regexp_Op1 = Regexp.Op.CAPTURE;
+      regexp1.op = regexp_Op1;
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/RE2J-5_1/temp/testcases/com/google/re2j/Compiler_ESTest_scaffolding.java

@@ -1,0 +1,120 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 19:19:08 GMT 2018
+ */
+
+package com.google.re2j;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+@EvoSuiteClassExclude
+public class Compiler_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "com.google.re2j.Compiler"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
+    org.evosuite.runtime.Runtime.getInstance().resetRuntime(); 
+  } 
+
+  @AfterClass 
+  public static void clearEvoSuiteFramework(){ 
+    Sandbox.resetDefaultSecurityManager(); 
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/RE2J-6_1/temp/testcases/com/google/re2j/Machine_ESTest.java

@@ -1,0 +1,598 @@
+/*
+ * This file was automatically generated by EvoSuite
+ * Wed Jan 24 19:26:07 GMT 2018
+ */
+
+package com.google.re2j;
+
+import org.junit.Test;
+import static org.junit.Assert.*;
+import static org.evosuite.runtime.EvoAssertions.*;
+import com.google.re2j.Machine;
+import com.google.re2j.MachineInput;
+import com.google.re2j.Prog;
+import com.google.re2j.RE2;
+import java.util.List;
+import org.evosuite.runtime.EvoRunner;
+import org.evosuite.runtime.EvoRunnerParameters;
+import org.evosuite.runtime.PrivateAccess;
+import org.junit.runner.RunWith;
+
+@RunWith(EvoRunner.class) @EvoRunnerParameters(mockJVMNonDeterminism = true, useVFS = true, useVNET = true, resetStaticState = true, separateClassLoader = true, useJEE = true) 
+public class Machine_ESTest extends Machine_ESTest_scaffolding {
+
+  @Test(timeout = 4000)
+  public void test00()  throws Throwable  {
+      String string0 = "";
+      RE2 rE2_0 = RE2.compilePOSIX(string0);
+      assertEquals("", rE2_0.toString());
+      assertNotNull(rE2_0);
+      
+      int int0 = 0;
+      int int1 = 97;
+      int[] intArray0 = new int[2];
+      // Undeclared exception!
+      try { 
+        rE2_0.match(string0, int0, int0, int1, intArray0, int1);
+        fail("Expecting exception: ArrayIndexOutOfBoundsException");
+      
+      } catch(ArrayIndexOutOfBoundsException e) {
+      }
+  }
+
+  @Test(timeout = 4000)
+  public void test01()  throws Throwable  {
+      String string0 = "phP<^J^";
+      RE2 rE2_0 = RE2.compilePOSIX(string0);
+      assertEquals("phP<^J^", rE2_0.toString());
+      assertNotNull(rE2_0);
+      
+      int int0 = 1;
+      Machine machine0 = new Machine(rE2_0);
+      assertEquals("phP<^J^", rE2_0.toString());
+      assertNotNull(machine0);
+      
+      byte[] byteArray0 = new byte[1];
+      int int1 = 601;
+      MachineInput machineInput0 = MachineInput.fromUTF8(byteArray0, int1, int0);
+      assertEquals(1, byteArray0.length);
+      assertFalse(int0 == int1);
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/RE2J-6_1/temp/testcases/com/google/re2j/Machine_ESTest_scaffolding.java

@@ -1,0 +1,155 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 19:26:07 GMT 2018
+ */
+
+package com.google.re2j;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+@EvoSuiteClassExclude
+public class Machine_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "com.google.re2j.Machine"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
+    org.evosuite.runtime.Runtime.getInstance().resetRuntime(); 
+  } 
+
+  @AfterClass 
+  public static void clearEvoSuiteFramework(){ 
+    Sandbox.resetDefaultSecurityManager(); 
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/RE2J-7_1/temp/testcases/com/google/re2j/Regexp_ESTest.java

@@ -1,0 +1,1717 @@
+/*
+ * This file was automatically generated by EvoSuite
+ * Wed Jan 24 19:24:21 GMT 2018
+ */
+
+package com.google.re2j;
+
+import org.junit.Test;
+import static org.junit.Assert.*;
+import static org.evosuite.runtime.EvoAssertions.*;
+import com.google.re2j.Regexp;
+import org.evosuite.runtime.EvoRunner;
+import org.evosuite.runtime.EvoRunnerParameters;
+import org.evosuite.runtime.PrivateAccess;
+import org.junit.runner.RunWith;
+
+@RunWith(EvoRunner.class) @EvoRunnerParameters(mockJVMNonDeterminism = true, useVFS = true, useVNET = true, resetStaticState = true, separateClassLoader = true, useJEE = true) 
+public class Regexp_ESTest extends Regexp_ESTest_scaffolding {
+
+  @Test(timeout = 4000)
+  public void test00()  throws Throwable  {
+      Regexp.Op regexp_Op0 = Regexp.Op.LITERAL;
+      Regexp regexp0 = new Regexp(regexp_Op0);
+      String string0 = "";
+      Regexp[] regexpArray0 = null;
+      regexp0.subs = regexpArray0;
+      StringBuilder stringBuilder0 = null;
+      int int0 = 17;
+      PrivateAccess.callMethod((Class<Regexp>) Regexp.class, regexp0, "quoteIfHyphen", (Object) stringBuilder0, (Class<?>) StringBuilder.class, (Object) int0, (Class<?>) int.class);
+      regexp0.name = string0;
+      // Undeclared exception!
+      try { 
+        regexp0.toString();
+        fail("Expecting exception: NullPointerException");
+      
+      } catch(NullPointerException e) {
+         //
+         // no message in exception (getMessage() returned null)
+         //
+         verifyException("com.google.re2j.Regexp", e);
+      }
+  }
+
+  @Test(timeout = 4000)
+  public void test01()  throws Throwable  {
+      Regexp.Op regexp_Op0 = Regexp.Op.BEGIN_LINE;
+      Regexp regexp0 = new Regexp(regexp_Op0);
+      Object object0 = new Object();
+      regexp0.equals(object0);
+      Regexp regexp1 = new Regexp(regexp0);
+      int int0 = 68;
+      regexp0.min = int0;
+      Regexp regexp2 = new Regexp(regexp1);
+      regexp2.reinit();
[…]

### 2018-01-30 papers/sbst18/data/6thresults/results_evosuite_120/RE2J-7_1/temp/testcases/com/google/re2j/Regexp_ESTest_scaffolding.java

@@ -1,0 +1,109 @@
+/**
+ * Scaffolding file used to store all the setups needed to run 
+ * tests automatically generated by EvoSuite
+ * Wed Jan 24 19:24:21 GMT 2018
+ */
+
+package com.google.re2j;
+
+import org.evosuite.runtime.annotation.EvoSuiteClassExclude;
+import org.junit.BeforeClass;
+import org.junit.Before;
+import org.junit.After;
+import org.junit.AfterClass;
+import org.evosuite.runtime.sandbox.Sandbox;
+import org.evosuite.runtime.sandbox.Sandbox.SandboxMode;
+
+@EvoSuiteClassExclude
+public class Regexp_ESTest_scaffolding {
+
+  @org.junit.Rule 
+  public org.evosuite.runtime.vnet.NonFunctionalRequirementRule nfr = new org.evosuite.runtime.vnet.NonFunctionalRequirementRule();
+
+  private static final java.util.Properties defaultProperties = (java.util.Properties) java.lang.System.getProperties().clone(); 
+
+  private org.evosuite.runtime.thread.ThreadStopper threadStopper =  new org.evosuite.runtime.thread.ThreadStopper (org.evosuite.runtime.thread.KillSwitchHandler.getInstance(), 3000);
+
+
+  @BeforeClass 
+  public static void initEvoSuiteFramework() { 
+    org.evosuite.runtime.RuntimeSettings.className = "com.google.re2j.Regexp"; 
+    org.evosuite.runtime.GuiSupport.initialize(); 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfThreads = 100; 
+    org.evosuite.runtime.RuntimeSettings.maxNumberOfIterationsPerLoop = 10000; 
+    org.evosuite.runtime.RuntimeSettings.mockSystemIn = true; 
+    org.evosuite.runtime.RuntimeSettings.sandboxMode = org.evosuite.runtime.sandbox.Sandbox.SandboxMode.RECOMMENDED; 
+    org.evosuite.runtime.sandbox.Sandbox.initializeSecurityManagerForSUT(); 
+    org.evosuite.runtime.classhandling.JDKClassResetter.init();
+    setSystemProperties();
+    initializeClasses();
+    org.evosuite.runtime.Runtime.getInstance().resetRuntime(); 
+  } 
+
+  @AfterClass 
+  public static void clearEvoSuiteFramework(){ 
+    Sandbox.resetDefaultSecurityManager(); 
[…]

### 2018-01-30 papers/sbst18/r_files/analyze.R

@@ -1,0 +1,237 @@
+#tool,benchmark,class,run,preparationTime,generationTime,executionTime,testcaseNumber,
+#uncompilableNumber,brokenTests,failTests,linesTotal,linesCovered,linesCoverageRatio,
+#conditionsTotal,conditionsCovered,conditionsCoverageRatio,mutantsTotal,mutantsCovered,mutantsCoverageRatio,
+#mutantsKilled,mutantsKillRatio,mutantsAlive,timeBudget,totalTestClasses
+
+library(stringr)
+
+FILE <- "../data/single_transcript.csv"
+# FILE.MANUAL <- "../data/single_manual_transcript.csv"
+
+mainTable <- function(){
+
+  dt <- read.csv(FILE,sep=",",dec=".",header=T) #,colClasses=cols)
+
+  TABLE = paste("../mainTable.tex",sep="")
+  unlink(TABLE)
+  sink(TABLE, append=TRUE, split=TRUE)
+
+  cat("\\begin{tabular}{ l rrrrrrr rrrrrrrr}\\toprule","\n")
+  cat(" Benchmark &  \\multicolumn{7}{c}{Branch Coverage} &  \\multicolumn{7}{c}{Mutation Score}\\\\ \n")
+  cat(" & 10s & 30s & 60s & 120s & 240s & 300s & 480s & 10s & 30s & 60s & 120s & 240s & 300s & 480s \\\\ \n" )
+  cat("\\midrule","\n")
+
+
+  classes = sort(unique(dt$class))
+  times = sort(unique(dt$timeBudget))
+  benchmarks = sort(unique(dt$benchmark))
+
+  for(benchmark in benchmarks) {
+  #for(class in classes){
+
+    mask = dt$tool=="evosuite" & dt$benchmark==benchmark
+
+    cat(benchmark)
+
+    #cat(class)
+
+    for(t in times){
+      cov <- dt$conditionsCoverageRatio[mask & dt$timeBudget==t]
+      cat(" & ", getColouredCell(mean(cov)),"\\%",sep="")
+
+      score <- dt$mutantsKillRatio[mask & dt$timeBudget==t]
+      cat(" & ", getColouredCell(mean(score)),"\\%",sep="")
+    }
+
+    cat("\\\\ \n")
+  }
+  cat("\\midrule","\n")
+  cat("Average ")
+  for(t in times){
+    cov <- dt$conditionsCoverageRatio[dt$tool=="evosuite" & dt$timeBudget==t]
[…]

### 2018-01-31 papers/sbst18/mainTable.tex
updated table

@@
 \midrule 
-BCEL-1 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
+BCEL-1 & 54.7\% & 47.9\%\\ 
+BCEL-10 & 62.5\% & 56.0\%\\ 
+BCEL-2 & 1.2\% & 0.8\% & \multicolumn{13}{l}{Resulting test suite's coverage: 34\% (average coverage for all fitness functions)}\\ 
+BCEL-3 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
+                                                           \cellcolor{light-gray} \textcolor{black}{0.0}\%
+& \multicolumn{13}{l}{org.evosuite.shaded.org.mockito.exceptions.misusing.InvalidUseOfMatchersException: 
+Misplaced or misused argument matcher detected here}\\ 
+BCEL-4 & 80.8\% & 80.5\%\\ 
+BCEL-5 & 37.5\% & 63.8\%\\ 
+BCEL-6 & 59.3\% & 76.0\%\\ 
+BCEL-7 & 60.0\% & 50.0\%\\ 
+BCEL-8 & 95.8\% & 90.6\%\\ 
+BCEL-9 & 81.1\% & 67.5\%\\ 
+FREEHEP-1 & 93.1\% & 42.2\%\\ 
+FREEHEP-10 & 95.8\% & 69.6\%\\ 
+FREEHEP-2 & 76.6\% & 5.7\%\\ 
+FREEHEP-3 & 55.6\% & 62.1\%\\ 
+FREEHEP-4 & 46.8\% & 22.2\%\\ 
+FREEHEP-5 & 70.9\% & 54.1\%\\ 
+FREEHEP-6 & 59.3\% & 27.0\%\\ 
+FREEHEP-7 & 81.2\% & 77.2\%\\ 
+FREEHEP-8 & 93.1\% & 74.7\%\\ 
+FREEHEP-9 & 29.7\% & \cellcolor{light-gray} \textcolor{black}{0.0}\%
+& \multicolumn{13}{l}{Resulting test suite's coverage: 36\%; ERROR ClassStateSupport - Could not initialize org.freehep.math.minuit.ModularFunctionMinimizer}\\ 
+GSON-1 & 63.9\% & 41.7\%\\ 
+GSON-10 & 58.5\% & 39.0\%\\ 
+GSON-2 & 33.5\% & 34.8\%\\ 
+GSON-3 & 77.5\% & 81.6\%\\ 
+GSON-4 & 31.4\% & 24.2\%\\ 
+GSON-5 & 29.3\% & 34.8\%\\ 
+GSON-6 & 86.0\% & 72.6\%\\ 
+GSON-7 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                            \cellcolor{light-gray}
                                                            \textcolor{black}{0.0}\%
- & mocking\\ 
-BCEL-10 & 63.9\% & 56.0\%\\ 
-BCEL-2 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
-                                                           \cellcolor{light-gray}
-                                                           \textcolor{black}{0.0}\%
- & \multicolumn{12}{l}{Failed to use Mockito on interface java.io.DataInput}\\ 
-BCEL-3 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
-                                                           \cellcolor{light-gray}
-                                                           \textcolor{black}{0.0}\%
- & \multicolumn{12}{l}{java.lang.ClassCastException: java.lang.Byte
-   cannot be cast to java.lang.Short at org.evosuite.testcase.statements.FunctionalMockStatement\$1.fixBoxing(FunctionalMockStatement.java:849)}\\ 
-BCEL-4 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
-                                                           \cellcolor{light-gray}
-                                                           \textcolor{black}{0.0}\%
- & \multicolumn{13}{l}{Minimisation and junit check timeout; test
-   suite's coverage: resulting coverage 74\% } \\ 
-BCEL-5 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
-                                                           \cellcolor{light-gray}
-                                                           \textcolor{black}{0.0}\%
- & \multicolumn{13}{l}{no error, evosuite reported coverage 42\%}\\ 
-BCEL-6 & 72.2\% & 78.0\%\\ 
-BCEL-7 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
-                                                           \cellcolor{light-gray} \textcolor{black}{0.0}\%& \multicolumn{13}{l}{ERROR FunctionalMockStatement - IAE on public java.lang.String org.apache.bcel.classfile.ConstantPool.getConstantString(int,byte) throws org.apache.bcel.classfile.ClassFormatException> when called with [0, null}\\
-BCEL-8 & 95.8\% & 96.9\%\\ 
-BCEL-9 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
-                                                           \cellcolor{light-gray}
-                                                           \textcolor{black}{0.0}\%
- & \multicolumn{13}{l}{ERROR FunctionalMockStatement - Failed to use Mockito on interface java.io.DataInput: java.lang.Byte cannot be cast to java.lang.Short}\\ 
-FREEHEP-1 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
-                                                              \cellcolor{light-gray}
-                                                              \textcolor{black}{0.0}\%
- & \multicolumn{13}{l}{Resulting test suite's coverage: 98\%;
-   minimisation timed out}\\ 
-FREEHEP-10 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
-                                                               \cellcolor{light-gray}
-                                                               \textcolor{black}{0.0}\%
- & \multicolumn{13}{l}{Resulting test suite's coverage: 83\%;
-   JUNIT\_CHECK timed out}\\ 
-FREEHEP-2 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
-                                                              \cellcolor{light-gray}
-                                                              \textcolor{black}{0.0}\%
-&  \multicolumn{13}{l}{Resulting test suite's coverage: 85\%; no error} \\ 
-FREEHEP-3 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
-                                                              \cellcolor{light-gray}
-                                                              \textcolor{black}{0.0}\%
- &  \multicolumn{13}{l}{Resulting test suite's coverage: 81\%; no
-   error, flaky tests}\\ 
-FREEHEP-4 & 60.3\% & 24.3\%\\ 
-FREEHEP-5 & 69.1\% & 84.4\%\\ 
-FREEHEP-6 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
-                                                              \cellcolor{light-gray}
-                                                              \textcolor{black}{0.0}\%
-  &  \multicolumn{13}{l}{Resulting test suite's coverage: 87\%; no
-   error, flaky tests}\\
-FREEHEP-7 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
-                                                              \cellcolor{light-gray} \textcolor{black}{0.0}\%   &  \multicolumn{13}{l}{Resulting test suite's coverage: 81\%; no
-   error, flaky tests}\\ 
-FREEHEP-8 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
-                                                              \cellcolor{light-gray}
-                                                              \textcolor{black}{0.0}\%
- & \multicolumn{13}{l}{87\% coverage; Permissions denied during test execution:  java.lang.RuntimePermission: writeFileDescriptor: 7}\\ 
-FREEHEP-9 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
-                                                              \cellcolor{light-gray}
-                                                              \textcolor{black}{0.0}\% 
- & \multicolumn{13}{l}{57\% coverage; minimisation and junit\_check
-   time out}\\ 
-GSON-1 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
-                                                           \cellcolor{light-gray}
-                                                           \textcolor{black}{0.0}\%
-
- & \multicolumn{13}{l}{test suite's coverage: 58\% .  Permissions denied during test execution:  java.lang.RuntimePermission: writeFileDescriptor: 1} \\ 
-GSON-10 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
-                                                            \cellcolor{light-gray}
-                                                            \textcolor{black}{0.0}\%
- &  \multicolumn{13}{l}{java.lang.RuntimeException: not implemented:
-   class sun.reflect.generics.reflectiveObjects.TypeVariableImpl at com.googlecode.gentyref.GenericTypeReflector.isSuperType(GenericTypeReflector.java:218)} \\ 
-GSON-2 & 33.5\% & 31.1\%\\ 
-GSON-3 & 82.5\% & 83.9\%\\ 
-GSON-4 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
-                                                           \cellcolor{light-gray}
-                                                           \textcolor{black}{0.0}\%
- & \multicolumn{13}{l}{31\% coverage; no errors}\\ 
-GSON-5 & 33.3\% & 36.5\%\\ 
-GSON-6 & 90.7\% & 71.8\%\\ 
-GSON-7 & 81.6\% & 94.0\%\\ 
-GSON-8 & 90.7\% & 75.8\%\\ 
+ & \multicolumn{13}{l}{java.lang.RuntimeException: not implemented: class sun.reflect.generics.reflectiveObjects.TypeVariableImpl}\\ 
+GSON-8 & 86.0\% & 70.2\%\\ 
 GSON-9 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
-                                                           \cellcolor{light-gray}
-                                                           \textcolor{black}{0.0}\%
+                                                           \cellcolor{light-gray} \textcolor{black}{0.0}\%
  & \multicolumn{13}{l}{java.lang.RuntimeException: not implemented: class sun.reflect.generics.reflectiveObjects.TypeVariableImpl}\\ 
@@
                                                             \textcolor{black}{0.0}\%
- & \multicolumn{13}{l}{ERROR FunctionalMockStatement - Failed to use Mockito on class org.apache.commons.imaging.formats.tiff.write.TiffOutputDirectory}\\ 
-IMAGE-2 & 85.0\% & 99.0\%\\ 
-IMAGE-3 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
+ & \multicolumn{13}{l}{ERROR FunctionalMockStatement - Failed to use Mockito on class org.apache.commons.imaging.formats.tiff.write.TiffOutputDirectory: tried to access class org.apache.commons.imaging.formats.tiff.write.TiffOutputItem}\\
+IMAGE-2 & 88.3\% & 99.0\%\\ 
+IMAGE-3 & 57.0\% & 32.5\%\\ 
+IMAGE-4 & 80.6\% & 73.9\%\\ 
+JXPATH-1 & 27.5\% & 25.4\%\\ 
+JXPATH-10 & 40.8\% & 33.5\%\\ 
+JXPATH-2 & 82.6\% & 72.7\%\\ 
+JXPATH-3 & 73.4\% & 83.7\%\\ 
+JXPATH-4 & 78.4\% & 72.8\%\\ 
+JXPATH-5 & 90.0\% & 92.9\%\\ 
+JXPATH-6 & 93.5\% & 96.0\%\\ 
+JXPATH-7 & 24.5\% & 10.8\%\\ 
+JXPATH-8 & 52.7\% & 42.8\%\\ 
+JXPATH-9 & 68.4\% & 27.9\%\\ 
+LA4J-1 & 75.4\% & 81.4\%\\ 
+LA4J-10 & 86.4\% & 67.9\%\\ 
+LA4J-2 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                            \cellcolor{light-gray}
                                                            \textcolor{black}{0.0}\%
- & \multicolumn{13}{l}{Multiple errors like: ERROR ClassStateSupport - Could not initialize org.apache.commons.imaging.formats.tiff.TiffImageMetadata}\\ 
-IMAGE-4 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
+                                                           & \multicolumn{13}{l}{ERROR FunctionalMockStatement - Failed to use Mockito on class org.la4j.iterator.RowMajorMatrixIterator}\\ 
+LA4J-3 & 67.1\% & 37.6\%\\ 
+LA4J-4 & 84.8\% & 74.7\%\\ 
+LA4J-5 & 52.9\% & 34.5\%\\ 
+LA4J-6 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                            \cellcolor{light-gray}
                                                            \textcolor{black}{0.0}\%
-& \multicolumn{13}{l}{coverage 76\%; JUNIT\_CHECK timed out; Permissions denied during test execution: java.lang.RuntimePermission: writeFileDescriptor: 3}
-  \\ 
-JXPATH-1 & 27.2\% & 25.4\%\\ 
-JXPATH-10 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
+ & \multicolumn{13}{l}{ERROR FunctionalMockStatement - Failed to use Mockito on class org.la4j.iterator.VectorIterator}\\ 
+LA4J-7 & 64.3\% & 40.6\%\\ 
+LA4J-8 & 76.5\% & 93.6\%\\ 
+LA4J-9 & 94.3\% & 30.4\%\\ 
+OKHTTP-1 & 7.2\% & 5.6\%\\ 
+OKHTTP-2 & 50.0\% & 44.1\%\\ 
+OKHTTP-3 & 74.2\% & 67.6\%\\ 
+OKHTTP-4 & 58.1\% & 53.5\%\\ 
+OKHTTP-5 & 3.0\% & 4.0\%\\ 
+OKHTTP-6 & 77.1\% & 76.3\%\\ 
+OKHTTP-7 & 46.9\% & 27.0\%\\ 
+OKHTTP-8 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                              \cellcolor{light-gray}
                                                              \textcolor{black}{0.0}\%
- & \multicolumn{13}{l}{coverage 76\%; some errors (java.lang.ClassNotFoundException:
-   Class not found: org/jdom/Element: java.lang.NullPointerException:
-   Class not found org/jdom/Element); flaky tests}\\ 
-JXPATH-2 & 81.4\% & 70.5\%\\ 
-JXPATH-3 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
-                                                             \cellcolor{light-gray}
-                                                             \textcolor{black}{0.0}\% 
- & \multicolumn{13}{l}{coverage 76\%; some errors (ERROR ClassStateSupport - Could not initialize org.apache.commons.jxpath.JXPathContextFactory); flaky tests}\\ 
-JXPATH-4 & 81.4\% & 75.0\%\\ 
-JXPATH-5 & 92.0\% & 92.9\%\\ 
-JXPATH-6 & 93.5\% & 90.0\%\\ 
-JXPATH-7 & 10.9\% & 7.7\%\\ 
-JXPATH-8 & 53.3\% & 42.8\%\\ 
-JXPATH-9 & 56.1\% & 27.9\%\\ 
-LA4J-1 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
-                                                           \cellcolor{light-gray}
-                                                           \textcolor{black}{0.0}\%
- & \multicolumn{13}{l}{coverage 75\%, JUNIT\_CHECK timed out}\\ 
-LA4J-10 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
-                                                            \cellcolor{light-gray}
-                                                            \textcolor{black}{0.0}\%
- & \multicolumn{13}{l}{Mocking problem: ERROR FunctionalMockStatement - Failed to use Mockito on class org.la4j.iterator.VectorIterator: tried to access class org.la4j.iterator.CursorIterator from class org.la4j.iterator.VectorIterator\$MockitoMock}\\
-LA4J-2 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
-                                                           \cellcolor{light-gray} \textcolor{black}{0.0}\%
- & \multicolumn{13}{l}{same as above}\\ 
-LA4J-3 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
-                                                           \cellcolor{light-gray}
-                                                           \textcolor{black}{0.0}\%
- & \multicolumn{13}{l}{Coverage 73\%, minimisation and junit check
-   timed out}\\ 
-LA4J-4 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
-                                                           \cellcolor{light-gray}
-                                                           \textcolor{black}{0.0}\%
- & \multicolumn{13}{l}{Coverage 88\%; minimisation timeout, errors compiling and checking tests(ERROR ClassStateSupport - Could not initialize org.la4j.iterator.JoinFunction)}\\ 
-LA4J-5 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
-                                                           \cellcolor{light-gray}
-                                                           \textcolor{black}{0.0}\%
- & \multicolumn{13}{l}{Coverage 55\%; search, minimisation and writing tests timed out}\\ 
-LA4J-6 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
-                                                           \cellcolor{light-gray} \textcolor{black}{0.0}\%
- & \multicolumn{13}{l}{Mocking problem: ERROR FunctionalMockStatement - Failed to use Mockito on class org.la4j.iterator.VectorIterator: tried to access class org.la4j.iterator.CursorIterator from class org.la4j.iterator.VectorIterator\$MockitoMock}\\
-LA4J-7 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
-                                                           \cellcolor{light-gray}
-                                                           \textcolor{black}{0.0}\% 
-& \multicolumn{13}{l}{Resulting test suite's coverage: 57\%; timeout when
-  writing tests}\\ 
-LA4J-8 & 75.0\% & 70.0\%\\ 
-LA4J-9 & 85.1\% & 29.8\%\\ 
-OKHTTP-1 & 7.7\% & 5.6\%\\ 
-OKHTTP-2 & 50.0\% & 50.0\%\\ 
-OKHTTP-3 & 75.8\% & 69.0\%\\ 
-OKHTTP-4 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
-                                                             \cellcolor{light-gray} \textcolor{black}{0.0}\%
-& \multicolumn{13}{l}{Coverage 62\%; Multiple errors (eg ERROR ConcreteClassAnalyzer - Problem for okhttp3.internal.http.HttpHeaders. Class not found: okhttp3.MultipartBody)}\\ 
-OKHTTP-5 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
-                                                             \cellcolor{light-gray} \textcolor{black}{0.0}\%
-& \multicolumn{13}{l}{Coverage 48\%; problem executing tests: java.security.SecurityPermission:  createAccessControlContext: 2 javax.security.auth.AuthPermission: getSubject: 21}\\ 
-OKHTTP-6 & 84.3\% & 86.4\%\\ 
-OKHTTP-7 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
-                                                             \cellcolor{light-gray} \textcolor{black}{0.0}\%
-&  \multicolumn{13}{l}{Coverage 40\%; error Compiling and checking tests}\\ 
-OKHTTP-8 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
-                                                             \cellcolor{light-gray} \textcolor{black}{0.0}\%
-& \multicolumn{13}{l}{Classpath problem? Caused by: java.lang.ClassNotFoundException: Class 'okio/Buffer.class' should be in target project, but could not be found!}\\ 
-RE2J-1 & 56.5\% & 39.4\%\\ 
-RE2J-2 & 92.9\% & 66.7\%\\ 
-RE2J-3 & 42.9\% & 39.7\%\\ 
-RE2J-4 & 92.7\% & 88.0\%\\ 
-RE2J-5 & 68.2\% & 41.7\%\\ 
-RE2J-6 & 85.1\% & 68.3\%\\ 
-RE2J-7 & 39.5\% & 35.2\%\\ 
-RE2J-8 & 91.8\% & 82.6\%\\ 
+ & \multicolumn{13}{l}{Caused by: java.lang.ClassNotFoundException:
+   Class okio/Buffer.class should be in target project, but could not be found!}\\ 
+RE2J-1 & 54.5\% & 36.9\%\\ 
+RE2J-2 & 93.8\% & 71.6\%\\ 
+RE2J-3 & 50.0\% & 37.9\%\\ 
+RE2J-4 & 97.9\% & 90.6\%\\ 
+RE2J-5 & 57.6\% & 29.1\%\\ 
+RE2J-6 & 83.5\% & 71.2\%\\ 
+RE2J-7 & 47.1\% & 27.8\%\\ 
+RE2J-8 & 91.8\% & 79.0\%\\ 
 \midrule 
-Average  &  32.9\% &  29.1\%\\ 
+Average  &  57.9\% &  47.3\%\\ 
 \bottomrule 

### 2018-02-28 papers/sbst18/mainTable.tex
updated scripts and paper

@@
-\begin{tabular}{ l rrrrrrr rrrrrrrr}\toprule 
- Benchmark &  \multicolumn{7}{c}{Branch Coverage} &  \multicolumn{7}{c}{Mutation Score}\\ 
- & 10s & 30s & 60s & 120s & 240s & 300s & 480s & 10s & 30s & 60s & 120s & 240s & 300s & 480s \\ 
+\begin{tabular}{ ll rrrr rrrr}\toprule 
+ \multirow{2}{1in}{Benchmark} & \multirow{2}{1in}{Java Class} &  \multicolumn{4}{c}{Branch Coverage} &  \multicolumn{4}{c}{Mutation Score}\\\cmidrule(lr){3-6}\cmidrule(lr){7-10} 
+ & & 10s & 60s & 120s & 240s & 10s & 60s & 120s & 240s \\ 
 \midrule 
-BCEL-1 & 54.7\% & 47.9\%\\ 
-BCEL-10 & 62.5\% & 56.0\%\\ 
-BCEL-2 & 1.2\% & 0.8\% & \multicolumn{13}{l}{Resulting test suite's coverage: 34\% (average coverage for all fitness functions)}\\ 
-BCEL-3 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
-                                                           \cellcolor{light-gray} \textcolor{black}{0.0}\%
-& \multicolumn{13}{l}{org.evosuite.shaded.org.mockito.exceptions.misusing.InvalidUseOfMatchersException: 
-Misplaced or misused argument matcher detected here}\\ 
-BCEL-4 & 80.8\% & 80.5\%\\ 
-BCEL-5 & 37.5\% & 63.8\%\\ 
-BCEL-6 & 59.3\% & 76.0\%\\ 
-BCEL-7 & 60.0\% & 50.0\%\\ 
-BCEL-8 & 95.8\% & 90.6\%\\ 
-BCEL-9 & 81.1\% & 67.5\%\\ 
-FREEHEP-1 & 93.1\% & 42.2\%\\ 
-FREEHEP-10 & 95.8\% & 69.6\%\\ 
-FREEHEP-2 & 76.6\% & 5.7\%\\ 
-FREEHEP-3 & 55.6\% & 62.1\%\\ 
-FREEHEP-4 & 46.8\% & 22.2\%\\ 
-FREEHEP-5 & 70.9\% & 54.1\%\\ 
-FREEHEP-6 & 59.3\% & 27.0\%\\ 
-FREEHEP-7 & 81.2\% & 77.2\%\\ 
-FREEHEP-8 & 93.1\% & 74.7\%\\ 
-FREEHEP-9 & 29.7\% & \cellcolor{light-gray} \textcolor{black}{0.0}\%
-& \multicolumn{13}{l}{Resulting test suite's coverage: 36\%; ERROR ClassStateSupport - Could not initialize org.freehep.math.minuit.ModularFunctionMinimizer}\\ 
-GSON-1 & 63.9\% & 41.7\%\\ 
-GSON-10 & 58.5\% & 39.0\%\\ 
-GSON-2 & 33.5\% & 34.8\%\\ 
-GSON-3 & 77.5\% & 81.6\%\\ 
-GSON-4 & 31.4\% & 24.2\%\\ 
-GSON-5 & 29.3\% & 34.8\%\\ 
-GSON-6 & 86.0\% & 72.6\%\\ 
-GSON-7 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
-                                                           \cellcolor{light-gray}
-                                                           \textcolor{black}{0.0}\%
- & \multicolumn{13}{l}{java.lang.RuntimeException: not implemented: class sun.reflect.generics.reflectiveObjects.TypeVariableImpl}\\ 
-GSON-8 & 86.0\% & 70.2\%\\ 
-GSON-9 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
-                                                           \cellcolor{light-gray} \textcolor{black}{0.0}\%
- & \multicolumn{13}{l}{java.lang.RuntimeException: not implemented: class sun.reflect.generics.reflectiveObjects.TypeVariableImpl}\\ 
-IMAGE-1 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
-                                                            \cellcolor{light-gray}
-                                                            \textcolor{black}{0.0}\%
- & \multicolumn{13}{l}{ERROR FunctionalMockStatement - Failed to use Mockito on class org.apache.commons.imaging.formats.tiff.write.TiffOutputDirectory: tried to access class org.apache.commons.imaging.formats.tiff.write.TiffOutputItem}\\
-IMAGE-2 & 88.3\% & 99.0\%\\ 
-IMAGE-3 & 57.0\% & 32.5\%\\ 
-IMAGE-4 & 80.6\% & 73.9\%\\ 
-JXPATH-1 & 27.5\% & 25.4\%\\ 
-JXPATH-10 & 40.8\% & 33.5\%\\ 
-JXPATH-2 & 82.6\% & 72.7\%\\ 
-JXPATH-3 & 73.4\% & 83.7\%\\ 
-JXPATH-4 & 78.4\% & 72.8\%\\ 
-JXPATH-5 & 90.0\% & 92.9\%\\ 
-JXPATH-6 & 93.5\% & 96.0\%\\ 
-JXPATH-7 & 24.5\% & 10.8\%\\ 
-JXPATH-8 & 52.7\% & 42.8\%\\ 
-JXPATH-9 & 68.4\% & 27.9\%\\ 
-LA4J-1 & 75.4\% & 81.4\%\\ 
-LA4J-10 & 86.4\% & 67.9\%\\ 
-LA4J-2 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
-                                                           \cellcolor{light-gray}
-                                                           \textcolor{black}{0.0}\%
-                                                           & \multicolumn{13}{l}{ERROR FunctionalMockStatement - Failed to use Mockito on class org.la4j.iterator.RowMajorMatrixIterator}\\ 
-LA4J-3 & 67.1\% & 37.6\%\\ 
-LA4J-4 & 84.8\% & 74.7\%\\ 
-LA4J-5 & 52.9\% & 34.5\%\\ 
-LA4J-6 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
-                                                           \cellcolor{light-gray}
-                                                           \textcolor{black}{0.0}\%
- & \multicolumn{13}{l}{ERROR FunctionalMockStatement - Failed to use Mockito on class org.la4j.iterator.VectorIterator}\\ 
-LA4J-7 & 64.3\% & 40.6\%\\ 
-LA4J-8 & 76.5\% & 93.6\%\\ 
-LA4J-9 & 94.3\% & 30.4\%\\ 
-OKHTTP-1 & 7.2\% & 5.6\%\\ 
-OKHTTP-2 & 50.0\% & 44.1\%\\ 
-OKHTTP-3 & 74.2\% & 67.6\%\\ 
-OKHTTP-4 & 58.1\% & 53.5\%\\ 
-OKHTTP-5 & 3.0\% & 4.0\%\\ 
-OKHTTP-6 & 77.1\% & 76.3\%\\ 
-OKHTTP-7 & 46.9\% & 27.0\%\\ 
-OKHTTP-8 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
-                                                             \cellcolor{light-gray}
-                                                             \textcolor{black}{0.0}\%
- & \multicolumn{13}{l}{Caused by: java.lang.ClassNotFoundException:
-   Class okio/Buffer.class should be in target project, but could not be found!}\\ 
-RE2J-1 & 54.5\% & 36.9\%\\ 
-RE2J-2 & 93.8\% & 71.6\%\\ 
-RE2J-3 & 50.0\% & 37.9\%\\ 
-RE2J-4 & 97.9\% & 90.6\%\\ 
-RE2J-5 & 57.6\% & 29.1\%\\ 
-RE2J-6 & 83.5\% & 71.2\%\\ 
-RE2J-7 & 47.1\% & 27.8\%\\ 
-RE2J-8 & 91.8\% & 79.0\%\\ 
+DUBBO-10  &  com.alibaba.dubbo.common.bytecode.Wrapper & 24.1\% & 24.5\% & 25.3\% & 28.2\% & 11.5\% & 20.9\% & 21.3\% & 20.9\%\\ 
+DUBBO-2  &  com.alibaba.dubbo.common.utils.ReflectUtils & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\
+DUBBO-3  &  com.alibaba.dubbo.common.utils.StringUtils & 87.1\% & 94.6\% & 96.8\% & 97.1\% & 93.9\% & 87.3\% & 81.8\% & 85.8\%\\ 
+DUBBO-4  &  com.alibaba.dubbo.common.utils.ClassHelper & 92.4\% & 94.4\% & 95.8\% & 95.1\% & 66.7\% & 91.4\% & 93.8\% & 92.6\%\\ 
+DUBBO-5  &  com.alibaba.dubbo.common.io.UnsafeByteArrayOutputStream & 94.4\% & 94.4\% & 94.4\% & 94.4\% & 68.3\% & 77.8\% & 79.4\% & 78.9\%\\ 
+DUBBO-6  &  com.alibaba.dubbo.common.utils.CompatibleTypeUtils & 4.7\% & 3.9\% & 4.7\% & 4.7\% & 3.1\% & 2.9\% & 3.1\% & 2.3\%\\ 
+DUBBO-7  &  com.alibaba.dubbo.common.beanutil.JavaBeanDescriptor & 80.2\% & 92.4\% & 95.1\% & 97.9\% & 77.9\% & 96.2\% & 97.4\% & 99.0\%\\ 
+DUBBO-8  &  com.alibaba.dubbo.common.Parameters & 61.1\% & 66.1\% & 77.6\% & 77.6\% & 49.5\% & 74.8\% & 76.9\% & 78.4\%\\ 
+DUBBO-9  &  com.alibaba.dubbo.common.io.Bytes & 67.8\% & 71.9\% & 79.5\% & 77.1\% & 38.1\% & 65.2\% & 71.8\% & 70.4\%\\ 
+FASTJSON-1  &  com.alibaba.fastjson.parser.JSONLexerBase & \cellcolor{light-gray} \textcolor{black}{-} & 15.9\% & 15.2\% & 20.4\% & \cellcolor{light-gray} \textcolor{black}{-} & 3.7\% & 6.8\% & 10.2\%\\
+FASTJSON-10  &  com.alibaba.fastjson.serializer.StringCodec & 40.0\% & 44.2\% & 46.7\% & 50.0\% & 21.8\% & 42.0\% & 44.3\% & 45.4\%\\ 
+FASTJSON-2  &  com.alibaba.fastjson.util.TypeUtils & 6.8\% & 28.7\% & 31.2\% & 40.4\% & 8.6\% & 30.3\% & 32.9\% & 43.5\%\\ 
+FASTJSON-3  &  com.alibaba.fastjson.parser.DefaultJSONParser & 5.3\% & 9.3\% & 16.2\% & 18.5\% & 2.9\% & 6.8\% & 13.4\% & 16.9\%\\ 
+FASTJSON-4  &  com.alibaba.fastjson.JSONArray & 20.0\% & 32.2\% & 21.1\% & 30.6\% & 34.2\% & 52.3\% & 38.7\% & 54.0\%\\ 
+FASTJSON-5  &  com.alibaba.fastjson.util.JavaBeanInfo & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 15.7\% & 17.6\% & 21.0\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 12.2\% & 15.2\% & 17.6\%\\
+FASTJSON-6  &  com.alibaba.fastjson.serializer.DateCodec & 18.5\% & 39.2\% & 48.0\% & 34.5\% & 8.8\% & 20.9\% & 25.9\% & 19.1\%\\ 
+FASTJSON-7  &  com.alibaba.fastjson.util.IOUtils & 52.4\% & 63.6\% & 66.6\% & 71.6\% & 18.9\% & 40.2\% & 46.8\% & 49.8\%\\ 
+FASTJSON-8  &  com.alibaba.fastjson.parser.JSONReaderScanner & 69.6\% & 70.1\% & 73.1\% & 77.3\% & 74.7\% & 70.6\% & 71.0\% & 73.1\%\\ 
+FASTJSON-9  &  com.alibaba.fastjson.util.ASMUtils & 38.5\% & 39.1\% & 39.1\% & 39.1\% & 27.6\% & 38.6\% & 39.0\% & 39.5\%\\ 
+JSOUP-1  &  org.jsoup.parser.TokenQueue & 85.8\% & 90.0\% & 90.6\% & 94.9\% & 59.3\% & 81.8\% & 85.6\% & 87.5\%\\ 
+JSOUP-2  &  org.jsoup.select.QueryParser & 49.8\% & 24.9\% & 21.9\% & 55.8\% & 36.4\% & 12.8\% & 11.3\% & 40.8\%\\ 
+JSOUP-3  &  org.jsoup.helper.DataUtil & 39.6\% & 38.7\% & 44.8\% & 52.0\% & 28.3\% & 28.1\% & 41.0\% & 49.8\%\\ 
+JSOUP-4  &  org.jsoup.parser.Parser & 48.3\% & 95.0\% & 98.3\% & 98.0\% & 31.7\% & 80.6\% & 85.6\% & 87.3\%\\ 
+JSOUP-5  &  org.jsoup.parser.Tokeniser & 35.6\% & 53.3\% & 54.8\% & 56.5\% & 23.4\% & 44.0\% & 47.3\% & 50.0\%\\ 
+OKIO-1  &  okio.Buffer & 44.6\% & 42.1\% & 58.3\% & 56.1\% & 9.8\% & 21.0\% & 34.1\% & 23.9\%\\ 
+OKIO-10  &  okio.Timeout & 83.3\% & 80.0\% & 85.6\% & 83.3\% & 76.8\% & 78.1\% & 82.5\% & 80.7\%\\ 
+OKIO-2  &  okio.ByteString & 81.7\% & 72.3\% & 89.8\% & 95.0\% & 40.9\% & 59.2\% & 84.5\% & 78.7\%\\ 
+OKIO-3  &  okio.SegmentedByteString & 56.1\% & 72.5\% & 88.9\% & 87.8\% & 28.0\% & 61.4\% & 67.6\% & 69.2\%\\ 
+OKIO-4  &  okio.RealBufferedSource & 12.7\% & 27.4\% & 40.1\% & 49.9\% & 12.3\% & 17.9\% & 30.5\% & 51.1\%\\ 
+OKIO-5  &  okio.RealBufferedSink & 61.4\% & 79.5\% & 89.1\% & 93.4\% & 45.7\% & 76.9\% & 86.5\% & 88.4\%\\ 
+OKIO-6  &  okio.Okio & 73.2\% & 81.5\% & 82.1\% & 85.7\% & 80.6\% & 83.3\% & 83.9\% & 86.7\%\\ 
+OKIO-7  &  okio.Segment & 85.4\% & 96.5\% & 97.2\% & 97.2\% & 54.5\% & 77.6\% & 78.0\% & 79.3\%\\ 
+OKIO-8  &  okio.AsyncTimeout & 40.9\% & 58.0\% & 55.7\% & 59.5\% & 20.6\% & 46.1\% & 58.2\% & 60.5\%\\ 
+OKIO-9  &  okio.Utf8 & 42.3\% & 42.3\% & 42.3\% & 42.3\% & 25.6\% & 35.9\% & 35.9\% & 35.9\%\\ 
+REDISSON-1  &  org.redisson.RedissonSetMultimapValues & 13.3\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{-} & 1.1\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{-}\\
+REDISSON-10  &  org.redisson.config.Config & 63.8\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 97.8\% & \cellcolor{light-gray} \textcolor{black}{-} & 17.1\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 20.9\% & \cellcolor{light-gray} \textcolor{black}{-}\\
+REDISSON-2  &  org.redisson.RedissonQueue & 39.6\% & 25.0\% & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{-}\\
+REDISSON-3  &  org.redisson.jcache.JCacheManager & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\
+REDISSON-4  &  org.redisson.RedissonSetMultimap & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{-}\\
+REDISSON-5  &  org.redisson.RedissonBloomFilter & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{-}\\
+REDISSON-6  &  org.redisson.reactive.RedissonMapReactive & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{-}\\
+REDISSON-7  &  org.redisson.RedissonBaseMapIterator & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{-}\\
+REDISSON-8  &  org.redisson.jcache.JCachingProvider & 58.3\% & 61.1\% & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{-} & 80.6\% & 79.0\% & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{-}\\
+REDISSON-9  &  org.redisson.cluster.ClusterPartition & 68.2\% & 92.4\% & 99.2\% & 99.2\% & 30.1\% & 69.9\% & 75.5\% & 74.5\%\\ 
+WEBMAGIC-1  &  us.codecraft.webmagic.model.PageModelExtractor & 10.3\% & 17.9\% & 21.5\% & 22.4\% & 24.6\% & 34.0\% & 41.0\% & 42.0\%\\ 
+WEBMAGIC-2  &  us.codecraft.webmagic.Spider & 25.9\% & 36.1\% & 40.7\% & 41.5\% & 52.1\% & 60.8\% & 60.2\% & 53.6\%\\ 
+WEBMAGIC-3  &  us.codecraft.webmagic.Site & 55.2\% & 65.4\% & 79.9\% & 84.1\% & 33.9\% & 90.7\% & 79.5\% & 83.2\%\\ 
+WEBMAGIC-4  &  us.codecraft.webmagic.Page & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\
+WEBMAGIC-5  &  us.codecraft.webmagic.utils.DoubleKeyMap & 50.0\% & 26.0\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 68.8\% & 30.0\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\
+ZXING-1  &  com.google.zxing.qrcode.detector.FinderPatternFinder & 29.8\% & 32.8\% & 36.3\% & 39.3\% & 4.4\% & 16.2\% & 22.8\% & 16.7\%\\ 
+ZXING-10  &  com.google.zxing.qrcode.encoder.Encoder & 68.4\% & 79.6\% & 80.4\% & 81.7\% & 54.1\% & 73.7\% & 76.3\% & 73.2\%\\ 
+ZXING-2  &  com.google.zxing.pdf417.decoder.PDF417ScanningDecoder & 24.3\% & 25.6\% & 27.5\% & 30.3\% & 6.8\% & 17.9\% & 27.1\% & 32.9\%\\ 
+ZXING-3  &  com.google.zxing.common.StringUtils & 87.6\% & 90.8\% & 91.5\% & 91.7\% & 3.9\% & 65.5\% & 65.9\% & 68.6\%\\ 
+ZXING-4  &  com.google.zxing.client.result.ResultParser & 86.2\% & 81.9\% & 89.2\% & 95.3\% & 82.0\% & 75.7\% & 83.2\% & 84.3\%\\ 
+ZXING-5  &  com.google.zxing.qrcode.encoder.MatrixUtil & 46.0\% & 77.9\% & 80.0\% & 89.0\% & 53.4\% & 53.5\% & 56.8\% & 52.6\%\\ 
+ZXING-6  &  com.google.zxing.datamatrix.decoder.BitMatrixParser & 36.3\% & 56.5\% & 60.5\% & 61.5\% & 45.3\% & 33.1\% & 34.4\% & 37.7\%\\ 
+ZXING-7  &  com.google.zxing.pdf417.decoder.ec.ModulusPoly & 96.1\% & 97.4\% & 96.5\% & 97.4\% & 72.7\% & 87.0\% & 92.4\% & 92.4\%\\ 
+ZXING-8  &  com.google.zxing.maxicode.decoder.DecodedBitStreamParser & 54.4\% & 67.2\% & 77.8\% & 82.2\% & 31.1\% & 36.9\% & 42.3\% & 46.8\%\\ 
+ZXING-9  &  com.google.zxing.oned.CodaBarWriter & 89.8\% & 91.5\% & 92.5\% & 96.9\% & 52.5\% & 57.1\% & 61.0\% & 63.5\%\\ 
 \midrule 
-Average  &  57.9\% &  47.3\%\\ 
+Average &  &  47.8\% &  53.3\% &  58.9\% &  61.6\% &  34.8\% &  46.6\% &  51.4\% &  53.5\%\\ 
 \bottomrule 

### 2018-02-28 papers/sbst18/paper_sbst18.tex
updated scripts and paper

@@
 %\documentclass[10pt,conference,compsocconf]{IEEEtran}
-\documentclass[10pt,conference]{IEEEtran}
+%\documentclass[10pt,conference]{IEEEtran} 
+\documentclass[sigconf,table]{acmart}
 
@@
 \usepackage{float}
-\usepackage[numbers,sort&compress,square]{natbib}
+%\usepackage[numbers,sort&compress,square]{natbib}
 \usepackage{graphicx}
@@
 \usepackage{color}
-\usepackage[usenames,dvipsnames,table]{xcolor}
-\usepackage{soul}
+%\usepackage[usenames,dvipsnames,]{xcolor}
+%\usepackage{soul}
 \usepackage{xspace}
@@
 
+\setcopyright{rightsretained}
+
 % in draft mode we put \remarks into the margins and do other stuff
@@
 \draftfalse
+\drafttrue
 
@@
 	% TODO marker
-	\newcommand{\TODO}[1]{\sethlcolor{yellow}\textbf{\textcolor{ScarletRed}{\hl{TODO: #1}}}\xspace}
+	\newcommand{\TODO}[1]{\textbf{\textcolor{ScarletRed}{[TODO: #1]}}\xspace}
 \else
@@
 
+\newcommand{\TOTALPOINTS}{{686.91}\xspace}
+
 \DeclareMathSymbol{,}{\mathpunct}{letters}{"3B}
@@
 %\title{Unit Testing Tool competition: Results for EvoSuite}
-\title{\EVOSUITE at the SBST 2017 Tool Competition}
+\title{\EVOSUITE at the SBST 2018 Tool Competition}
 
-\author{\IEEEauthorblockN{Gordon Fraser\IEEEauthorrefmark{1}, Jos\'e
-    Miguel Rojas\IEEEauthorrefmark{2}, Jos\'e Campos\IEEEauthorrefmark{3}}
-  \IEEEauthorblockA{The University of Sheffield\\Sheffield, United Kingdom\\
-    \{\IEEEauthorrefmark{1}gordon.fraser,
-    \IEEEauthorrefmark{2}j.rojas, \IEEEauthorrefmark{3}jose.campos\}@sheffield.ac.uk} 
-\and
-\IEEEauthorblockN{Andrea Arcuri}
-  \IEEEauthorblockA{Westerdals Oslo ACT, Norway\\and University of Luxembourg, Luxembourg\\arcand@westerdals.no}
+\author{Gordon Fraser}
+\affiliation{%
+  \institution{Chair of Software Engineering II, University of Passau}
+  \city{Passau}
+  \country{Germany}
 }
+\email{gordon.fraser@uni-passau.de}
+
+\author{Jos\'e Miguel Rojas}
+\affiliation{%
+  \institution{Department of Informatics, University of Leicester}
+  \city{Leicester}
+  \country{United Kingdom}
+}
+\email{j.rojas@leicester.ac.uk}
+
+% \affil\IEEEauthorrefmark{1}, \IEEEauthorrefmark{2}, Jos\'e Campos\IEEEauthorrefmark{3}}
+%   \IEEEauthorblockA{The University of Sheffield\\Sheffield, United Kingdom\\
+%     \{\IEEEauthorrefmark{1}gordon.fraser,
+%     \IEEEauthorrefmark{2}j.rojas, \IEEEauthorrefmark{3}jose.campos\}@sheffield.ac.uk} 
+% \and
+% \IEEEauthorblockN{Andrea Arcuri}
+%   \IEEEauthorblockA{Westerdals Oslo ACT, Norway\\and University of Luxembourg, Luxembourg\\arcand@westerdals.no}
+% }
+
+% The default list of authors is too long for headers.
+\renewcommand{\shortauthors}{B. Trovato et al.}
+
+\begin{abstract}
+  \EVOSUITE is a search-based tool that automatically generates
+  executable unit tests for Java code (JUnit tests).  This paper
+  summarises the results and experiences of \EVOSUITE's participation
+  at the sixth unit testing competition at SBST 2018, where \EVOSUITE
+  achieved the highest overall score (\TOTALPOINTS points) for the
+  fifth time in six editions of the competition.
+\end{abstract}
 
@@
 
-\begin{abstract}
-  \EVOSUITE is a search-based tool that automatically generates unit
-  tests for Java code.  This paper summarises the results and
-  experiences of \EVOSUITE's participation at the fifth unit testing
-  competition at SBST 2018, where \EVOSUITE achieved the highest
-  overall score.
-\end{abstract}
-
 %------------------------------------------------------------------------- 
@@
 The annual unit test generation competition aims to drive and evaluate
-progress on unit test generation tools. In the 5th instance of the
+progress on unit test generation tools. In the 6th instance of the
 competition at the International Workshop on Search-Based Software
-Testing (SBST) 2017, two tools, \EVOSUITE and \JTEXPERT, competed on a
-set of 69 open-source Java classes. Two other tools, \RANDOOP and \TT,
-and existing open-source test suites were used as baseline. This paper
-describes the results obtained by the \EVOSUITE test generation
-tool~\cite{FrA11c} in this competition. Details about the procedure of
-the competition, the technical framework, and the benchmark classes
-can be found in~\cite{sbst17competition}.  In this competition,
-\EVOSUITE achieved an overall score of 1457, which was the highest
-among the competing and baseline tools.
+Testing (SBST) 2018, two tools, \EVOSUITE and \JTEXPERT\TODO{confirm},
+competed on a set of 59 open-source Java classes. Two other tools,
+\RANDOOP and \TT, and existing open-source test suites were used as
+baseline. This paper describes the results obtained by the \EVOSUITE
+test generation tool~\cite{FrA11c} in this competition. Details about
+the procedure of the competition, the technical framework, and the
+benchmark classes can be found in~\cite{sbst18competition}.  In this
+competition, \EVOSUITE achieved an overall score of \TOTALPOINTS,
+which was the highest among the competing and baseline
+tools\TODO{confirm baseline}.
 
@@
 under test and all its dependencies), \EVOSUITE automatically produces
-a set of JUnit test cases aimed at maximising code
-coverage. \EVOSUITE can be used on the command line, or through
-plugins for popular development tools such as IntelliJ, Eclipse, or Maven~\cite{ICST16_Tool}.
+a set of JUnit test cases aimed at maximising code coverage. \EVOSUITE
+can be used on the command line, or through plugins for popular
+development tools such as IntelliJ, Eclipse, or
+Maven~\cite{ICST16_Tool}.
 
@@
 effectiveness~\cite{shamshiri2015automatically,moein2017}, and effects
-on developer productivity~\cite{TOSEM_userstudy,ISSTA15_Study}.
+on developer
+productivity~\cite{TOSEM_userstudy,ISSTA15_Study} and software
+maintenance~\cite{ICST2018_Maintenance}.
 
-In the first two and the fourth editions of the unit testing tool
-competition, \EVOSUITE ranked
-first~\cite{evosuiteAtSbst2013,evosuiteAtFittest2013,evosuiteAtSbst2016},
-whereas it ranked second in the third one.
+\EVOSUITE has a longstanding record of success at the unit testing
+tool competition, having ranked second the third edition of the
+competition~\cite{evosuiteAtSbst2015} and first in all the other
+editions~\cite{evosuiteAtSbst2013,evosuiteAtFittest2013,evosuiteAtSbst2016,evosuiteAtSbst2017}.
 
@@
 branch coverage, branch coverage by direct method invocation, weak
-mutation testing, output coverage, exception coverage). The use of an
-archive of solutions~\cite{emse_archive}, which iteratively removes
-covered goals from the fitness function and stores the corresponding
-test cases, is now enabled by default in \EVOSUITE.
-
-A new feature in \EVOSUITE is the use of Mockito mock
-classes~\cite{ICST_Mocking17}. After a certain percentage of the
-search budget has passed, \EVOSUITE starts considering the use of mock
-objects instead of real classes. Only branches that cannot be covered
-without mocks will result in tests with mock objects in the end. We
-further added frequency based weighting to constants for
-seeding~\cite{sakti2015instance}, and included extensions to support
-Java Enterprise Edition features~\cite{arcuri2016java}. Besides these
-changes, several bug fixes were applied since the last instance of the
-competition, in particular in relation to non-determinism and flaky
-tests~\cite{arcuri2014automated}.
+mutation testing, output coverage, exception coverage). \EVOSUITE uses
+an archive of solutions~\cite{emse_archive} to keep the search focused
+on uncovered goals, iteratively discarding covered goals and storing
+the tests that covered them. After a certain percentage of the search
+budget has passed and with a certain probability, \EVOSUITE starts
+using mock objects (relying on Mockito) instead of actual class
+instances~\cite{ICST_Mocking17}; only branches that cannot be covered
+without mocks lead to tests with mock objects. As in the previous
+instance of the competition, we continue to use frequency-based
+weighted constants for seeding~\cite{sakti2015instance} and support
+Java Enterprise Edition features~\cite{arcuri2016java}. \TODO{any
+  other noteworthy change?} \EVOSUITE is being actively developed,
+therefore several improvements and bug fixes were applied since the
+last instance of the competition, in particular in relation to
+non-determinism and flaky tests~\cite{arcuri2014automated}.
 
@@
 
-Like in the 2016 competition, tools were called with different time
-budgets. We used the same strategy as for the previous
-competition~\cite{evosuiteAtSbst2016} to distribute the overall time
+Like in previous editions of the competition, tools were called with
+different time budgets. We used the same strategy used in previous
+competition (e.g.,~\cite{evosuiteAtSbst2016}) to distribute the overall time
 budget onto the different phases of \EVOSUITE (e.g., initialisation,
@@
 of flaky tests). That is, 50\% of the time was allocated to the
-search, and the rest was distributed equally to the remaining
-phases.
+search, and the rest was distributed equally to the remaining phases.
 
@@
 overall increases for higher time budgets. With the highest time
-budget of $480s$, the
-average branch coverage achieved was \AvgCovG (slightly higher than
-last year's $65.6\%$) and the average mutation score was \AvgMutG
-(considerably higher than last year's $41.0\%$).
+budget of $240s$, the average branch coverage achieved was \AvgCovD,
+lower that last year's 64.6\% for the same time budget, but the
+average mutation score was \AvgMutD, higher than last year's 49.6\%
+for the same time budget.
 
 This year, the contest also included manually written test suites as
-baseline (only for 63 out of the 69 benchmarks). The results indicate
-that there is no significant difference in branch coverage between
+baseline (for 49 out of 59 benchmarks). The results indicate that
+there is no significant difference in branch coverage between
 \EVOSUITE-generated test suites (avg. \AvgCovEvosuite) and manually
@@
 $A_{12}=\EvoManCovA$ and $p=\EvoManCovPV$. In terms of mutation
-scores, however, the results show
-that---unsurprisingly---automatically generated assertions are weaker
-than manually written ones: the average \EVOSUITE mutation score for
-these 63 benchmarks is \AvgMutEvosuite, significantly lower than the
-average \AvgMutManual obtained by developer-written test suites, with
-$A_{12}=\EvoManMutA$ and $p\EvoManMutPV$.
+scores, surprisingly, the results show that automatically generated
+assertions are competitive with manually written ones: the average
+\EVOSUITE mutation score for these 49 benchmarks is \AvgMutEvosuite
+and the average mutation score obtained by developer-written test
+suites is \AvgMutManual ($A_{12}=\EvoManMutA$ and
+$p=\EvoManMutPV$).
 
@@
 % Look at benchmarks that always failed
-\EVOSUITE failed to produce any test suites for benchmarks JXPATH-7 and
-OKHTTP-8, and also struggled often for benchmarks LA4J-3, LA4J-7,
-BCEL-9 (highlighted in Table~\ref{table:results}). All executions of
-\EVOSUITE for JXPATH-7 failed in the instrumentation phase, where
-Java's 64k limit on the size of methods was exceeded. A viable fix
-would be to stop instrumenting before the limit is reached, at the
-price of limited search guidance; a more effective solution would
-involve identifying parts of the code that are worth instrumenting. A
-missing dependency for OKHTTP-8 caused all executions---\emph{for all
-  tools}---to fail. For the other mentioned benchmarks, the failure
-reasons (in some cases related to sandboxing, mocking and timeouts)
-will require further investigation.
+\EVOSUITE failed to produce any test suites for benchmarks DUBBO-2 and
+WEBMAGIC-4, and generally struggled with most REDISSON benchmarks
+(highlighted in grey in Table~\ref{table:results}).\TODO{Investigate}
+
+% All executions of \EVOSUITE for JXPATH-7 failed in the instrumentation
+% phase, where Java's 64k limit on the size of methods was exceeded. A
+% viable fix would be to stop instrumenting before the limit is reached,
+% at the price of limited search guidance; a more effective solution
+% would involve identifying parts of the code that are worth
+% instrumenting. A missing dependency for OKHTTP-8 caused all
+% executions---\emph{for all tools}---to fail. For the other mentioned
+% benchmarks, the failure reasons (in some cases related to sandboxing,
+% mocking and timeouts) will require further investigation.
 
@@
 As expected, both branch coverage and mutation score generally
-increased with higher time budgets, although in some cases, especially
-with $budget=300s$, a decrease was observed for some
-benchmarks. Having run only three repetitions of the tool per time
-budget, it is fair to assume the decreases are due to bugs affecting
-executions by chance. A preliminary investigation on the source of
-this loss of coverage revealed that memory management (e.g.,
-out-of-memory errors for OKHTTP-2 and RE2J-7), sandboxing (e.g.,
-affecting all executions for LA4J-3 and LA4J-7), and mocking
-(affecting BCEL-1, BCEL-5 and BCEL-7, for example) are some of the
-aspects that require attention and debugging in \EVOSUITE.
+increased with higher time budgets.
+
+% A preliminary investigation on the source of this loss of coverage
+% revealed that memory management (e.g., out-of-memory errors for
+% OKHTTP-2 and RE2J-7), sandboxing (e.g., affecting all executions for
+% LA4J-3 and LA4J-7), and mocking (affecting BCEL-1, BCEL-5 and BCEL-7,
+% for example) are some of the aspects that require attention and
+% debugging in \EVOSUITE.
 
@@
 
-% Look at benchmarks with more flaky tests
-Flaky tests continue to be a challenge for test generation. Benchmarks
-FREEHEP-7 and JXPATH-10 were the ones with the highest number of flaky
-tests in one run (12 and 14, respectively). In both cases, the
-minimisation phase timed out and hence \EVOSUITE reverted the
-resulting test suite to its previous, unminimised version, which as
-mentioned before is more likely to break. A \textit{partial
-  minimisation} approach to select and minimise only a reduced subset
-of tests, or a more efficient minimisation approach based on
-\textit{delta-debugging}~\cite{LOZCM07}, might be worth exploring to
-alleviate this issue.
+\TODO{Look at benchmarks with more flaky tests}
+% Flaky tests continue to be a challenge for test generation. Benchmarks
+% FREEHEP-7 and JXPATH-10 were the ones with the highest number of flaky
+% tests in one run (12 and 14, respectively). In both cases, the
+% minimisation phase timed out and hence \EVOSUITE reverted the
+% resulting test suite to its previous, unminimised version, which as
+% mentioned before is more likely to break. A \textit{partial
+%   minimisation} approach to select and minimise only a reduced subset
+% of tests, or a more efficient minimisation approach based on
+% \textit{delta-debugging}~\cite{LOZCM07}, might be worth exploring to
+% alleviate this issue.
 
 % Mocking
-As mentioned in the previous section, \EVOSUITE now uses private
-API access and functional mocking%  in addition to environment
+As mentioned in the previous section, \EVOSUITE uses private API
+access and functional mocking% in addition to environment
 % mocking
-~\cite{ICST_Mocking17}. In the competition, a total of 20,921
+~\cite{ICST_Mocking17}. In the competition, a total of 20,921\TODO{Update}
 objects were mocked, 1,485 private fields were set and 3,090 private methods
@@
 This paper reports on the participation of the \EVOSUITE test
-generation tool in the 5th SBST Java Unit Testing Tool Contest. With
-an overall score of 1457, \EVOSUITE achieved the highest score of
-all tools in the competition.
+generation tool in the 6th SBST Java Unit Testing Tool Contest. With
+an overall score of \TOTALPOINTS, \EVOSUITE achieved the highest score
+of all tools in the competition.
 
@@
 project ``GREATEST'' (EP/N023978/1), and by the National Research
-Fund, Luxembourg (FNR/P10/03).
+Fund, Luxembourg (FNR/P10/03)\TODO{remove?}.
 

### 2018-02-28 papers/sbst18/r_files/analyze.R

@@ -5,8 +5,10 @@
 
 library(stringr)
 
-FILE <- "../data/single_transcript.csv"
+FILE <- "../data/6runs_budgets-10-60-120-240_single_transcript-without_ANTLR4_n_DUBBO-1.csv"
 # FILE.MANUAL <- "../data/single_manual_transcript.csv"
+FILE.COMBINED <- "../data/6runs_budgets-10-60-120-240_single_transcript-without_ANTLR4_n_DUBBO-1.csv"
+FILE.MANUAL <- "../data/results_manual_10_single_transcript-without_ANTLR4_n_DUBBO-1.csv"
 
 mainTable <- function(){
 
@@ -16,45 +18,45 @@ mainTable <- function(){
   unlink(TABLE)
   sink(TABLE, append=TRUE, split=TRUE)
 
-  cat("\\begin{tabular}{ l rrrrrrr rrrrrrrr}\\toprule","\n")
-  cat(" Benchmark &  \\multicolumn{7}{c}{Branch Coverage} &  \\multicolumn{7}{c}{Mutation Score}\\\\ \n")
-  cat(" & 10s & 30s & 60s & 120s & 240s & 300s & 480s & 10s & 30s & 60s & 120s & 240s & 300s & 480s \\\\ \n" )
+  cat("\\begin{tabular}{ ll rrrr rrrr}\\toprule","\n")
+  cat(" \\multirow{2}{1in}{Benchmark} & \\multirow{2}{1in}{Java Class} &  \\multicolumn{4}{c}{Branch Coverage} &  \\multicolumn{4}{c}{Mutation Score}\\\\\\cmidrule(lr){3-6}\\cmidrule(lr){7-10} \n")
+  cat(" & & 10s & 60s & 120s & 240s & 10s & 60s & 120s & 240s \\\\ \n" )
   cat("\\midrule","\n")
 
-
-  classes = sort(unique(dt$class))
-  times = sort(unique(dt$timeBudget))
-  benchmarks = sort(unique(dt$benchmark))
+  times <- c(10, 60, 120, 240) # sort(unique(dt$timeBudget))
+  classes <- sort(unique(dt$class))
+  benchmarks <- sort(unique(dt$benchmark))
 
   for(benchmark in benchmarks) {
   #for(class in classes){
 
-    mask = dt$tool=="evosuite" & dt$benchmark==benchmark
+    mask = dt$tool=="evosuite" & dt$benchmark==benchmark & dt$preparationTime != "?"
 
-    cat(benchmark)
[…]

### 2018-03-07 papers/sbst18/paper_sbst18.tex
andrea
Minor edits

@@
 
+\author{Andrea Arcuri}
+\affiliation{%
+  \institution{Westerdals Oslo ACT}
+  \city{Oslo}
+  \country{Norway}
+}
+\email{arcand@westerdals.no}
+
 % \affil\IEEEauthorrefmark{1}, \IEEEauthorrefmark{2}, Jos\'e Campos\IEEEauthorrefmark{3}}
@@
 competition at the International Workshop on Search-Based Software
-Testing (SBST) 2018, two tools, \EVOSUITE and \JTEXPERT\TODO{confirm},
-competed on a set of 59 open-source Java classes. Two other tools,
-\RANDOOP and \TT, and existing open-source test suites were used as
+Testing (SBST) 2018, several JUnit test generation tools
+%two tools, \EVOSUITE and \JTEXPERT\TODO{confirm},
+competed on a set of 59 open-source Java classes, and 
+% Two other tools,
+%\RANDOOP and \TT, and 
+existing open-source test suites were used as
 baseline. This paper describes the results obtained by the \EVOSUITE
@@
 which was the highest among the competing and baseline
-tools\TODO{confirm baseline}.
+tools.
 
@@
 \EVOSUITE has a longstanding record of success at the unit testing
-tool competition, having ranked second the third edition of the
+tool competition, having ranked second in the third edition of the
 competition~\cite{evosuiteAtSbst2015} and first in all the other
@@
 
-The configuration of \EVOSUITE for the competition is largely based on
-its default values, since these have been tuned
+The configuration of \EVOSUITE for the 2018 competition is largely
+based on its default values, since these have been tuned
 extensively~\cite{arcuri2013parameter}. We used the default set of
@@
 using mock objects (relying on Mockito) instead of actual class
-instances~\cite{ICST_Mocking17}; only branches that cannot be covered
-without mocks lead to tests with mock objects. As in the previous
-instance of the competition, we continue to use frequency-based
-weighted constants for seeding~\cite{sakti2015instance} and support
-Java Enterprise Edition features~\cite{arcuri2016java}. \TODO{any
-  other noteworthy change?} \EVOSUITE is being actively developed,
-therefore several improvements and bug fixes were applied since the
-last instance of the competition, in particular in relation to
-non-determinism and flaky tests~\cite{arcuri2014automated}.
+instances~\cite{ICST_Mocking17} for dependencies; only branches that
+cannot be covered without mocks lead to tests with mock objects. As in
+the previous instance of the competition, we continue to use
+frequency-based weighted constants for
+seeding~\cite{sakti2015instance} and support Java Enterprise Edition
+features~\cite{arcuri2016java}. %\TODO{any other noteworthy change?} No.
+\EVOSUITE is actively maintained, therefore several bug fixes and
+minor improvements have been applied since the last instance of the
+competition, in particular in relation to non-determinism and flaky
+tests~\cite{arcuri2014automated}, as well as new types of test
+assertions (e.g., related to arrays and standard contained classes).
 
@@
 This project has been funded by the EPSRC
-project ``GREATEST'' (EP/N023978/1), and by the National Research
-Fund, Luxembourg (FNR/P10/03)\TODO{remove?}.
+project ``GREATEST'' (EP/N023978/1).
+%, and by the National Research
+%Fund, Luxembourg (FNR/P10/03)\TODO{remove?}.
 

### 2018-03-14 papers/sbst18/paper_sbst18.tex
discussion of results

@@
 
-\newcommand{\TOTALPOINTS}{{686.91}\xspace}
+\newcommand{\TOTALPOINTS}{{687}\xspace}
 
@@
 
-%------------------------------------------------------------------------- 
+%------------------------------------------------------------------------- g
 % take the % away on next line to produce the final camera-ready version 
@@
 
-Like in previous editions of the competition, tools were called with
-different time budgets. We used the same strategy used in previous
-competition (e.g.,~\cite{evosuiteAtSbst2016}) to distribute the overall time
+Four time budgets were used to call each tool: 10, 60, 120 and 240
+seconds. We used the same strategy used in previous competition
+(e.g.,~\cite{evosuiteAtSbst2016}) to distribute the overall time
 budget onto the different phases of \EVOSUITE (e.g., initialisation,
@@
 
-\subsection{Overall Results}
+\paragraph{Overall Results}
 
@@
 analysis results achieved by \EVOSUITE on all benchmark classes in the
-contest. Coverage is generally in the expected range, with clear
-overall increases for higher time budgets. With the highest time
-budget of $240s$, the average branch coverage achieved was \AvgCovD,
-lower that last year's 64.6\% for the same time budget, but the
-average mutation score was \AvgMutD, higher than last year's 49.6\%
-for the same time budget.
+contest. Coverage and mutation scores are generally in the expected
+ranges, with clear overall increases for higher time budgets. With the
+highest time budget of $240s$, the average branch coverage achieved
+was \AvgCovD, lower that last year's 64.6\% for the same time budget,
+but the average mutation score was \AvgMutD, higher than last year's
+49.6\% for the same time budget.
+
+\paragraph{Manually Written Tests}
 
@@
 
-\EVOSUITE generated \FlakyEvosuite flaky tests per run on average,
+\paragraph{Flaky Tests}
+
+~\EVOSUITE generated \FlakyEvosuite flaky tests per run on average,
 much lower than the number of flaky tests produced by the competing
 and baseline tools (\FlakyTthree by \TT, \FlakyJtexpert by \JTEXPERT,
-and \FlakyRandoop by \RANDOOP). We attribute these results---also
-consistent with previous years' results---to the way \EVOSUITE handles
-execution environments during test generation (e.g., controlling the
-static state of the class under test, mocking interactions with the
-file system, system calls like \texttt{System.in} and
-\texttt{System.currentTimeMillis}, etc.)~\cite{arcuri2014automated}.
+and \FlakyRandoop by \RANDOOP). We attribute these relatively positive 
+results---also consistent with previous years' results---to the way
+\EVOSUITE handles execution environments during test generation (e.g.,
+controlling the static state of the class under test, mocking
+interactions with the file system, system calls like
+\texttt{System.in} and \texttt{System.currentTimeMillis},
+etc.)~\cite{arcuri2014automated}.
 
-\subsection{Challenges}
+Overall, no flaky tests were generated for the vast majority of
+subjects in the competition. Amongst those benchmarks for which
+\EVOSUITE struggled with flakiness, FASTJSON-4 is a notable example:
+in the worst case, 90 flaky tests were generated in one single run. An
+analysis of the execution logs indicates several possible sources for
+this flakiness: a) a non-final static constant that is not properly
+reset in between executions; b) an possibly incorrect handling of enum
+types; and c) global property not being reset in between
+executions. Further investigation will be needed to confirm these
+conjectures and act upon them.
 
-% Look at benchmarks that always failed
-\EVOSUITE failed to produce any test suites for benchmarks DUBBO-2 and
-WEBMAGIC-4, and generally struggled with most REDISSON benchmarks
-(highlighted in grey in Table~\ref{table:results}).\TODO{Investigate}
+\paragraph{Mocking}
 
-% All executions of \EVOSUITE for JXPATH-7 failed in the instrumentation
-% phase, where Java's 64k limit on the size of methods was exceeded. A
-% viable fix would be to stop instrumenting before the limit is reached,
-% at the price of limited search guidance; a more effective solution
-% would involve identifying parts of the code that are worth
-% instrumenting. A missing dependency for OKHTTP-8 caused all
-% executions---\emph{for all tools}---to fail. For the other mentioned
-% benchmarks, the failure reasons (in some cases related to sandboxing,
-% mocking and timeouts) will require further investigation.
-
-% Look at benchmarks where coverage decreased with increased budget
-As expected, both branch coverage and mutation score generally
-increased with higher time budgets.
-
-% A preliminary investigation on the source of this loss of coverage
-% revealed that memory management (e.g., out-of-memory errors for
-% OKHTTP-2 and RE2J-7), sandboxing (e.g., affecting all executions for
-% LA4J-3 and LA4J-7), and mocking (affecting BCEL-1, BCEL-5 and BCEL-7,
-% for example) are some of the aspects that require attention and
-% debugging in \EVOSUITE.
-
-% Although coverage generally increased with higher time budgets, there
-% are instances where this expected behaviour was not observed,
-% specially for $budget=300s$, where the average across benchmarks
-% decreased. This is possibly due to crashes or out-of-memory runtime
-% errors. For instance, \EVOSUITE failed to generate any test suite in
-% one out of three runs of OKHTTP-2 and RE2J-7 due to an
-% \textit{out-of-memory error}, and in all executions of LA4J-3 and
-% LA4J-7 due to a \textit{state exception}. In order to evaluate a
-% fitness function, each test case evolved by the underline GA of
-% \EVOSUITE has to be executed. However, its execution could fail due to
-% several reasons: state exception (if a test case tries to re-initialise
-% EvoSuite's sanbox, LA4J-3 and LA4J-7), timeout (OKHTTP-2), etc. In
-% case of a timeout, \EVOSUITE logs the stacktrace of the thread in
-% which each test case is executed, which could cause an out-of-memory
-% error if the stack trace message is to long. RE2J-7: \TODO{I do not
-% understand how a java.lang.OutOfMemoryError could be throw by
-% CBranchSuiteFitness.java:145}.
-% %
-% To avoid low coverage of final classes with private constructors (like
-% the class under test of benchmark OKHTTP-7), \EVOSUITE uses reflection
-% to call the default constructor of the class under test. However,
-% \TODO{EvoSuite tries to access a field of the cut (which is public
-% static final) by using an instance of cut. It's still not clear why}.
-% For other benchmarks such for example BCEL-1, BCEL-5, BCEL-7,
-% \EVOSUITE failed due to mocking related issues.
-
-\TODO{Look at benchmarks with more flaky tests}
-% Flaky tests continue to be a challenge for test generation. Benchmarks
-% FREEHEP-7 and JXPATH-10 were the ones with the highest number of flaky
-% tests in one run (12 and 14, respectively). In both cases, the
-% minimisation phase timed out and hence \EVOSUITE reverted the
-% resulting test suite to its previous, unminimised version, which as
-% mentioned before is more likely to break. A \textit{partial
-%   minimisation} approach to select and minimise only a reduced subset
-% of tests, or a more efficient minimisation approach based on
-% \textit{delta-debugging}~\cite{LOZCM07}, might be worth exploring to
-% alleviate this issue.
-
-% Mocking
 As mentioned in the previous section, \EVOSUITE uses private API
@@
 % mocking
-~\cite{ICST_Mocking17}. In the competition, a total of 20,921\TODO{Update}
-objects were mocked, 1,485 private fields were set and 3,090 private methods
-were invoked using mocked access% , and environment classes were
-% mocked 4,699 times, with \texttt{java.util.Random} and
-% \texttt{java.io.File} being by far the most frequently mocked
-% environment classes (resp. 1,286 and 1,121 times)
-, adding up to represent only 1.09\% of the total number of lines of
-code in the \EVOSUITE-generated test suites (2,329,361 LOC). Further
-investigation would be needed to assess the impact of these mocking
-features on test generation effectiveness for the benchmarks in the
-competition.
+~\cite{ICST_Mocking17}. In this competition, a total of 2,766 mock
+instances were created, 1,339 private fields were set and 2,409
+private methods were invoked using mocked access. Some of the Java
+classes most frequently used for mocking across benchmarks are
+\texttt{File} (849 instances in total), \texttt{Throwable} (284),
+\texttt{PrintStream} (210) and \texttt{Thread} (114). Mocking was
+particularly useful for \EVOSUITE to generate tests for the FASTJSON
+benchmarks, where multiple calendar systems are necessary (e.g.,
+classes \texttt{HijrahDate}, \texttt{MinguoDate},
+\texttt{JapaneseDate}, \texttt{ThaiBuddhistDate} were mocked 719 times
+altogether).
 
-% A few of these flaky tests were introduced by recent changes to
-% \EVOSUITE following experiments on
-% Defects4J~\cite{shamshiri2015automatically}: \EVOSUITE now includes
-% assertions on the source of exceptions, similar to commercial tools
-% like Agitar One. %~\cite{agitarone}.
-% Unfortunately, there were several instances in the competition where
-% these assertions lead to flaky tests. For example, the following is an
-% excerpt from a test for the Defects4J bug Lang-41, generated by
-% \EVOSUITE: \vspace{1em}
+% . Further
+% investigation would be needed to assess the impact of these mocking
+% features on test generation effectiveness for the benchmarks in the
+% competition.
 
-% \begin{lstlisting}
-% @Test(timeout = 4000)
-% public void test19()  throws Throwable  {
-%  Class<Double> class0 = Double.class;
-%  String string0 = ClassUtils.getPackageName(class0);
-%  try { 
-%    ClassUtils.getClass(string0);
-%    fail("Expecting exception: ClassNotFoundException"); 
-%  } catch(ClassNotFoundException e) {
-%    assertThrownBy("java.net.URLClassLoader", e);
-%  }
-% }
-% \end{lstlisting}
+\paragraph{Problematic benchmarks}
 
-% While compiling and executing this test with JUnit works without
-% problems, the mutation analysis step of the competition used Ant to
-% run the tests; Ant uses a complex setup of classloaders that
-% eventually leads to the \texttt{assertThrownBy} in the above example
-% to fail, as the source of the exception is a different one.
-
-% There are 15 runs in total where \EVOSUITE did not produce any test
-% suites; these are only for higher time budgets (240s, 480s). The
-% majority of these runs are due to \EVOSUITE not terminating before the
-% hard timeout of the competition infrastructure. This may happen, for
-% example, when test execution on the class under test takes long (e.g.,
-% timeouts), and when resetting the static state of the classes under
-% test takes a long time. However, this number is still lower than the
-% number of erroneous runs compared to other tools, and in the remaining
-% 1617 runs of the competition \EVOSUITE terminated in time and produced
-% at least two tests. In 13 of these, \EVOSUITE produced a test suite
-% with a compilation error.
+~\EVOSUITE failed to produce any test suites for benchmarks DUBBO-2 and
+WEBMAGIC-4, and generally struggled with most REDISSON benchmarks
+(highlighted in grey in Table~\ref{table:results}). The former two
+benchmarks had missing dependencies in the competition
+setup~\cite{sbst18competition}, which explains why \EVOSUITE was
+incapable of generating any test. For the REDISSON benchmarks, most
+executions ended with a timeout; unfortunately, we have not been able
+to reproduce this behaviour locally, hence we can only conjecture that
+the timeouts (reported during the initialisation phase) are due to the
+large number of dependency classes (>7000) that need to be loaded for
+these benchmarks to start off the test generation.
 
@@
 generation tool in the 6th SBST Java Unit Testing Tool Contest. With
-an overall score of \TOTALPOINTS, \EVOSUITE achieved the highest score
+an overall score of \TOTALPOINTS points, \EVOSUITE achieved the highest score
 of all tools in the competition.

### 2018-03-15 papers/sbst18/paper_sbst18.tex
Edits

@@
 rather than filtering them with mutation
-analysis~\cite{10.1109/TSE.2011.93}, which is a computationally
-expensive process. The use of all assertions has a negative impact on
+analysis~\cite{10.1109/TSE.2011.93}, which is computationally
+expensive. The use of all assertions has a negative impact on
 readability, but this is not evaluated as part of the SBST contest.
@@
   \centering
-  \caption{\label{table:results}Detailed results of \EVOSUITE on the SBST benchmark classes.}
-\resizebox{0.7\textwidth}{!}{  
+  \caption{\label{table:results}Detailed results of \EVOSUITE on the
+    SBST benchmark classes.}
+\vspace{-1em}
+\resizebox{0.71\textwidth}{!}{  
 \input{mainTable.tex}
@@
 \texttt{System.in} and \texttt{System.currentTimeMillis},
-etc.)~\cite{arcuri2014automated}.
+etc.)~\cite{arcuri2014automated}.  \EVOSUITE provides deterministic
+replacement classes for many classes with known non-determinism,
+(e.g., those related to date and time), and in particular the FASTJSON
+benchmarks made heavy use of these. For example, multiple calendar
+systems are necessary (e.g., classes \texttt{HijrahDate},
+\texttt{MinguoDate}, \texttt{JapaneseDate},
+\texttt{ThaiBuddhistDate}), and \EVOSUITE instantiated its own
+replacement versions of these classes 719 times altogether, thus
+potentially avoiding many flaky tests. Overall, no flaky tests were
+generated for the vast majority of subjects in the competition.
 
-Overall, no flaky tests were generated for the vast majority of
-subjects in the competition. Amongst those benchmarks for which
+Amongst those benchmarks for which
 \EVOSUITE struggled with flakiness, FASTJSON-4 is a notable example:
@@
 types; and c) global property not being reset in between
-executions. Further investigation will be needed to confirm these
+executions.Considering that there were still remaining flaky tests, further investigation will be needed to confirm these
 conjectures and act upon them.
@@
 % mocking
-~\cite{ICST_Mocking17}. In this competition, a total of 2,766 mock
-instances were created, 1,339 private fields were set and 2,409
-private methods were invoked using mocked access. Some of the Java
-classes most frequently used for mocking across benchmarks are
-\texttt{File} (849 instances in total), \texttt{Throwable} (284),
-\texttt{PrintStream} (210) and \texttt{Thread} (114). Mocking was
-particularly useful for \EVOSUITE to generate tests for the FASTJSON
-benchmarks, where multiple calendar systems are necessary (e.g.,
-classes \texttt{HijrahDate}, \texttt{MinguoDate},
-\texttt{JapaneseDate}, \texttt{ThaiBuddhistDate} were mocked 719 times
-altogether).
+~\cite{ICST_Mocking17}. Overall, in all tests generated in this
+competition, 1,339 private fields were set and 2,409
+private methods were invoked using reflection, and 15,369 Mockito mock
+instances were created and configured using another 9,553 statements
+(e.g., using the \text{doReturn} method). Considering the 1,804,932 overall test
+statements, this means that only 1.4\% of the tests were devoted to
+mocking. Amongst the 331 distinct classes for which mocks were
+generated at least once there are some classes for which EvoSuite can
+instantiate regular objects (e.g., \texttt{List}). This suggests that
+EvoSuite sometimes struggles to generate and set up complex objects
+correctly, and there is potential for future improvements.
+
+%a total of 2,766 mock
+%instances were created, using mocked access. Some of the Java
+%classes most frequently used for mocking across benchmarks are
+%\texttt{File} (849 instances in total), \texttt{Throwable} (284),
+%\texttt{PrintStream} (210) and \texttt{Thread} (114).
 
@@
 setup~\cite{sbst18competition}, which explains why \EVOSUITE was
-incapable of generating any test. For the REDISSON benchmarks, most
+incapable of generating any test: When a dependency of the class under
+test is missing, then \EVOSUITE intentionally aborts with an error to
+inform the user of the configuration error. While this is desirable
+behavior during regular usage, arguably in the scope of the
+competition \EVOSUITE could try to ignore such errors and try to
+generate tests nevertheless, as it might still be possible to cover
+code even with some missing dependencies.
+
+For the REDISSON benchmarks, most
 executions ended with a timeout; unfortunately, we have not been able

### 2018-03-15 papers/sbst18/paper_sbst18.tex
minors

@@
 (chromosomes). Each test suite consists of a variable number of test
-cases, each of which is represented as a variable length sequence of
+cases, each of which is represented as a variable-length sequence of
 Java statements (e.g., calls on the class under test). A population of
@@
 tests~\cite{arcuri2014automated}, as well as new types of test
-assertions (e.g., related to arrays and standard contained classes).
+assertions (e.g., related to arrays and standard container classes).
 
@@
 reset in between executions; b) an possibly incorrect handling of enum
-types; and c) global property not being reset in between
-executions.Considering that there were still remaining flaky tests, further investigation will be needed to confirm these
+types; and c) a global property not being reset in between
+executions. Considering that there were still remaining flaky tests, further investigation will be needed to confirm these
 conjectures and act upon them.

### 2018-03-16 papers/sbst18/paper_sbst18.tex
Add ACM copyright
Update Andreas affiliation, and typo

@@
 
+\copyrightyear{2018} 
+\acmYear{2018} 
+\setcopyright{acmcopyright}
+\acmConference[SBST'18]{SBST'18:IEEE/ACM 11th International Workshop on Search-Based Software Testing }{May 28--29, 2018}{Gothenburg, Sweden}
+\acmBooktitle{SBST'18: SBST'18:IEEE/ACM 11th International Workshop on Search-Based Software Testing , May 28--29, 2018, Gothenburg, Sweden}
+\acmPrice{15.00}
+\acmDOI{10.1145/3194718.3194729}
+\acmISBN{978-1-4503-5741-8/18/05}
+
 %
@@
 \affiliation{%
-  \institution{Westerdals Oslo ACT}
-  \city{Oslo}
-  \country{Norway}
+  \institution{Westerdals Oslo ACT, Norway  and University of
+    Luxembourg, Luxembourg}
+%  \city{Oslo}
+%  \country{Norway}
 }
@@
 this flakiness: a) a non-final static constant that is not properly
-reset in between executions; b) an possibly incorrect handling of enum
+reset in between executions; b) a possibly incorrect handling of enum
 types; and c) a global property not being reset in between
@@
 %\noindent
-\textbf{Acknowledgments:} Many thanks to all the contributors to \EVOSUITE.
-This project has been funded by the EPSRC
-project ``GREATEST'' (EP/N023978/1).
-%, and by the National Research
-%Fund, Luxembourg (FNR/P10/03)\TODO{remove?}.
+\textbf{Acknowledgments:} Many thanks to all the contributors to
+\EVOSUITE.  This project has been funded by the EPSRC project
+``GREATEST'' (EP/N023978/1), and by the National Research Fund,
+Luxembourg (FNR/P10/03).
 

### 2019-03-16 papers/sbst19/mainTable.tex
SBST'19 init commit.

\begin{tabular}{ ll rrrr rrrr}\toprule 
 \multirow{2}{1in}{Benchmark} & \multirow{2}{1in}{Java Class} &  \multicolumn{4}{c}{Branch Coverage} &  \multicolumn{4}{c}{Mutation Score}\\\cmidrule(lr){3-6}\cmidrule(lr){7-10} 
 & & 10s & 60s & 120s & 240s & 10s & 60s & 120s & 240s \\ 
\midrule 
AUTHZFORCE-1  &  org.ow2.authzforce.core.pdp.impl.PdpBean & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 16.7\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 14.4\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
AUTHZFORCE-11  &  org.ow2.authzforce.core.pdp.impl.func.LogicalNOfFunction & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 4.8\% & 4.8\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
AUTHZFORCE-27  &  org.ow2.authzforce.core.pdp.impl.func.MapFunctionFactory & 75.0\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 75.0\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
AUTHZFORCE-32  &  org.ow2.authzforce.core.pdp.impl.func.SubstringFunction & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 7.7\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
AUTHZFORCE-33  &  org.ow2.authzforce.core.pdp.impl.SchemaHandler & 55.6\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 57.6\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
AUTHZFORCE-48  &  org.ow2.authzforce.core.pdp.impl.policy.PolicyVersions & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 12.1\% & 34.8\% & 60.6\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 16.7\% & 37.3\% & 69.6\%\\ 
AUTHZFORCE-5  &  org.ow2.authzforce.core.pdp.impl.CloseableAttributeProvider & 20.5\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 27.4\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
AUTHZFORCE-52  &  org.ow2.authzforce.core.pdp.impl.PepActionExpression & 91.7\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 100.0\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
AUTHZFORCE-63  &  org.ow2.authzforce.core.pdp.impl.combining.DPUnlessPDCombiningAlg & 10.0\% & 3.3\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 5.6\% & 1.9\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
AUTHZFORCE-65  &  org.ow2.authzforce.core.pdp.impl.combining.FirstApplicableCombiningAlg & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
DUBBO-2  &  com.alibaba.dubbo.common.utils.ReflectUtils & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
FASTJSON-1  &  com.alibaba.fastjson.parser.JSONLexerBase & \cellcolor{light-gray} \textcolor{black}{-} & 23.0\% & 24.9\% & 31.6\% & \cellcolor{light-gray} \textcolor{black}{-} & 7.7\% & 8.8\% & 6.5\%\\ 
FASTJSON-3  &  com.alibaba.fastjson.parser.DefaultJSONParser & \cellcolor{light-gray} \textcolor{black}{-} & 13.4\% & 20.5\% & 25.7\% & \cellcolor{light-gray} \textcolor{black}{-} & 9.4\% & 14.1\% & 19.1\%\\ 
FESCAR-1  &  com.alibaba.fescar.core.protocol.transaction.BranchReportRequest & 97.9\% & 95.8\% & 96.9\% & 99.0\% & 97.7\% & 97.7\% & 98.5\% & 100.0\%\\ 
FESCAR-12  &  com.alibaba.fescar.core.rpc.netty.RpcServerHandler & 12.5\% & 87.5\% & 87.5\% & 87.5\% & 50.0\% & 100.0\% & 100.0\% & 100.0\%\\ 
FESCAR-18  &  com.alibaba.fescar.core.protocol.MergedWarpMessage & 61.9\% & 48.8\% & 56.0\% & 42.9\% & 81.2\% & 60.9\% & 68.1\% & 51.4\%\\ 
FESCAR-23  &  com.alibaba.fescar.core.protocol.MergeResultMessage & 63.1\% & 78.6\% & 64.3\% & 83.3\% & 78.6\% & 97.0\% & 79.2\% & 98.8\%\\ 
FESCAR-25  &  com.alibaba.fescar.core.rpc.netty.RmMessageListener & 37.5\% & 62.5\% & 62.5\% & 50.0\% & 22.2\% & 22.2\% & 22.2\% & 18.5\%\\ 
FESCAR-36  &  com.alibaba.fescar.core.protocol.RegisterRMRequest & 100.0\% & 92.9\% & 80.1\% & 83.3\% & 100.0\% & 93.8\% & 81.2\% & 83.0\%\\ 
FESCAR-37  &  com.alibaba.fescar.core.rpc.RpcContext & 52.9\% & 89.2\% & 91.2\% & 91.2\% & 71.9\% & 96.4\% & 94.8\% & 95.8\%\\ 
FESCAR-41  &  com.alibaba.fescar.core.rpc.netty.RmRpcClient & \cellcolor{light-gray} \textcolor{black}{-} & 2.0\% & 2.0\% & 2.0\% & \cellcolor{light-gray} \textcolor{black}{-} & 2.4\% & 2.4\% & 2.4\%\\ 
FESCAR-42  &  com.alibaba.fescar.core.rpc.DefaultServerMessageListenerImpl & \cellcolor{light-gray} \textcolor{black}{-} & 16.1\% & 27.4\% & 27.9\% & \cellcolor{light-gray} \textcolor{black}{-} & 16.7\% & 27.8\% & 29.2\%\\ 
FESCAR-7  &  com.alibaba.fescar.core.rpc.netty.MessageCodecHandler & 37.8\% & 78.4\% & 82.8\% & 87.1\% & 37.9\% & 92.8\% & 95.2\% & 98.3\%\\ 
OKIO-1  &  okio.Buffer & 27.4\% & 57.0\% & 62.3\% & 67.9\% & 13.2\% & 20.2\% & 16.3\% & 18.5\%\\ 
OKIO-4  &  okio.RealBufferedSource & 19.2\% & 37.6\% & 51.3\% & 76.2\% & 13.1\% & 28.8\% & 40.1\% & 45.3\%\\ 
SPOON-105  &  spoon.support.compiler.jdt.PositionBuilder & \cellcolor{light-gray} \textcolor{black}{-} & 22.1\% & 16.4\% & 3.8\% & \cellcolor{light-gray} \textcolor{black}{-} & 27.7\% & 23.1\% & 5.4\%\\ 
SPOON-155  &  spoon.reflect.visitor.filter.AllMethodsSameSignatureFunction & 12.0\% & 4.2\% & 2.5\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 19.0\% & 10.7\% & 4.3\% & 5.0\%\\ 
SPOON-16  &  spoon.reflect.path.CtElementPathBuilder & 34.0\% & 34.3\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 2.0\% & 45.5\% & 43.9\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 4.0\%\\ 
SPOON-169  &  spoon.reflect.visitor.ImportScannerImpl & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
SPOON-20  &  spoon.support.reflect.reference.CtLocalVariableReferenceImpl & 33.3\% & 20.0\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 40.3\% & 33.3\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
SPOON-211  &  spoon.reflect.path.impl.CtRolePathElement & 8.1\% & 19.2\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 5.1\% & 27.8\% & 36.8\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 17.7\%\\ 
SPOON-25  &  spoon.pattern.internal.ValueConvertorImpl & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
SPOON-253  &  spoon.pattern.internal.parameter.MapParameterInfo & 29.7\% & 50.0\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 34.8\% & 50.0\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
SPOON-32  &  spoon.MavenLauncher & 12.5\% & 10.4\% & 10.4\% & 12.5\% & 6.7\% & 5.6\% & 5.6\% & 6.7\%\\ 
SPOON-65  &  spoon.support.DefaultCoreFactory & 9.0\% & 49.8\% & 20.0\% & 5.7\% & 1.2\% & 2.3\% & 1.2\% & 2.0\%\\ 
WEBMAGIC-1  &  us.codecraft.webmagic.model.PageModelExtractor & 28.0\% & 27.6\% & 28.8\% & 31.3\% & 50.4\% & 50.0\% & 51.3\% & 54.3\%\\ 
WEBMAGIC-4  &  us.codecraft.webmagic.Page & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
ZXING-10  &  com.google.zxing.qrcode.encoder.Encoder & 70.1\% & 82.3\% & 82.9\% & 84.0\% & 63.0\% & 76.1\% & 72.6\% & 72.8\%\\ 
\midrule 
Average &  &  17.3\% &  17.2\% &  14.8\% &  15.5\% &  19.9\% &  16.9\% &  13.9\% &  14.6\%\\ 
\bottomrule 
\end{tabular}

### 2019-03-16 papers/sbst19/paper_sbst19.tex
SBST'19 init commit.

--- 2018-03-16 papers/sbst18/paper_sbst18.tex
@@
 % Competition paper
-% SBST 2013
+% SBST 2019
 % Page limit: 4 pages
@@
 
-\newcommand{\TOTALPOINTS}{{687}\xspace}
+\newcommand{\TOTALPOINTS}{{255.43}\xspace}
 
@@
 
+\newcommand{\NumCUTS}{{38}\xspace}
+
 %------------------------------------------------------------------------- g
@@
 
-\copyrightyear{2018} 
-\acmYear{2018} 
+\copyrightyear{2019} 
+\acmYear{2019} 
 \setcopyright{acmcopyright}
-\acmConference[SBST'18]{SBST'18:IEEE/ACM 11th International Workshop on Search-Based Software Testing }{May 28--29, 2018}{Gothenburg, Sweden}
-\acmBooktitle{SBST'18: SBST'18:IEEE/ACM 11th International Workshop on Search-Based Software Testing , May 28--29, 2018, Gothenburg, Sweden}
+\acmConference[SBST'19]{SBST'19: IEEE/ACM 12th International Workshop on Search-Based Software Testing}{May 27, 2019}{Montreal, Canada}
+\acmBooktitle{SBST'19: SBST'19: IEEE/ACM 12th International Workshop on Search-Based Software Testing, May 27, 2019, Montreal, Canada}
 \acmPrice{15.00}
-\acmDOI{10.1145/3194718.3194729}
-\acmISBN{978-1-4503-5741-8/18/05}
+\acmDOI{}
+\acmISBN{}
 
@@
 %\title{Unit Testing Tool competition: Results for EvoSuite}
-\title{\EVOSUITE at the SBST 2018 Tool Competition}
+\title{\EVOSUITE at the SBST 2019 Tool Competition}
+
+\author{Annibale Panichella}
+\affiliation{%
+  \institution{Delft University of Technology}
+  \city{Delft}
+  \country{Netherlands}
+}
+\email{a.panichella@tudelft.nl}
+
+\author{Jos\'e Campos}
+\affiliation{%
+  \institution{University of Washington}
+  \city{Seattle}
+  \country{USA}
+}
+\email{jmcampos@uw.edu}
 
@@
 \email{gordon.fraser@uni-passau.de}
-
-\author{Jos\'e Miguel Rojas}
-\affiliation{%
-  \institution{Department of Informatics, University of Leicester}
-  \city{Leicester}
-  \country{United Kingdom}
-}
-\email{j.rojas@leicester.ac.uk}
-
-\author{Andrea Arcuri}
-\affiliation{%
-  \institution{Westerdals Oslo ACT, Norway  and University of
-    Luxembourg, Luxembourg}
-%  \city{Oslo}
-%  \country{Norway}
-}
-\email{arcand@westerdals.no}
 
@@
   summarises the results and experiences of \EVOSUITE's participation
-  at the sixth unit testing competition at SBST 2018, where \EVOSUITE
+  at the seventh unit testing competition at SBST 2019, where \EVOSUITE
   achieved the highest overall score (\TOTALPOINTS points) for the
-  fifth time in six editions of the competition.
+  sixth time in seven editions of the competition.
 \end{abstract}
@@
 The annual unit test generation competition aims to drive and evaluate
-progress on unit test generation tools. In the 6th instance of the
+progress on unit test generation tools. In the 7th instance of the
 competition at the International Workshop on Search-Based Software
-Testing (SBST) 2018, several JUnit test generation tools
+Testing (SBST) 2019, several JUnit test generation tools
 %two tools, \EVOSUITE and \JTEXPERT\TODO{confirm},
-competed on a set of 59 open-source Java classes, and 
+competed on a set of \NumCUTS open-source Java classes. %, and 
 % Two other tools,
 %\RANDOOP and \TT, and 
-existing open-source test suites were used as
-baseline. This paper describes the results obtained by the \EVOSUITE
+%existing open-source test suites were used as
+%baseline.
+This paper describes the results obtained by the \EVOSUITE
 test generation tool~\cite{FrA11c} in this competition. Details about
 the procedure of the competition, the technical framework, and the
-benchmark classes can be found in~\cite{sbst18competition}.  In this
+benchmark classes can be found in~\cite{sbst19competition}.  In this
 competition, \EVOSUITE achieved an overall score of \TOTALPOINTS,
@@
   Maturity&  Mature research prototype, under development\\
-  Technology behind the tool & Search-based testing / whole test suite generation\\
+  Technology behind the tool & Search-based testing / whole test suite generation \TODO{not whole test suite anymore}\\
 \hline
@@
 
+\TODO{introduce DynaMOSA}
 The underlying genetic algorithm uses test suites as representation
@@
 well as industrial software in terms of code
-coverage~\cite{fraser2014large,emse_archive}, fault finding
+coverage~\cite{fraser2014large,emse_archive,ea_evaluation}, fault finding
 effectiveness~\cite{shamshiri2015automatically,moein2017}, and effects
@@
 competition~\cite{evosuiteAtSbst2015} and first in all the other
-editions~\cite{evosuiteAtSbst2013,evosuiteAtFittest2013,evosuiteAtSbst2016,evosuiteAtSbst2017}.
+editions~\cite{evosuiteAtSbst2013,evosuiteAtFittest2013,evosuiteAtSbst2016,evosuiteAtSbst2017,evosuiteAtSbst2018}.
 
@@
 
-The configuration of \EVOSUITE for the 2018 competition is largely
+The configuration of \EVOSUITE for the 2019 competition is largely
 based on its default values, since these have been tuned
@@
 \vspace{-1em}
-\resizebox{0.71\textwidth}{!}{  
+\resizebox{\textwidth}{!}{  
 \input{mainTable.tex}
@@
 
-Table~\ref{table:results} lists the branch coverage and mutation
-analysis results achieved by \EVOSUITE on all benchmark classes in the
-contest. Coverage and mutation scores are generally in the expected
-ranges, with clear overall increases for higher time budgets. With the
-highest time budget of $240s$, the average branch coverage achieved
-was \AvgCovD, lower that last year's 64.6\% for the same time budget,
-but the average mutation score was \AvgMutD, higher than last year's
-49.6\% for the same time budget.
+\TODO{}
 
-\paragraph{Manually Written Tests}
+%Table~\ref{table:results} lists the branch coverage and mutation
+%analysis results achieved by \EVOSUITE on all benchmark classes in the
+%contest. Coverage and mutation scores are generally in the expected
+%ranges, with clear overall increases for higher time budgets. With the
+%highest time budget of $240s$, the average branch coverage achieved
+%was \AvgCovD, lower that last year's 64.6\% for the same time budget,
+%but the average mutation score was \AvgMutD, higher than last year's
+%49.6\% for the same time budget.
 
-This year, the contest also included manually written test suites as
-baseline (for 49 out of 59 benchmarks). The results indicate that
-there is no significant difference in branch coverage between
-\EVOSUITE-generated test suites (avg. \AvgCovEvosuite) and manually
-written ones (avg. \AvgCovManual), with Vargha-Delaney's
-$A_{12}=\EvoManCovA$ and $p=\EvoManCovPV$. In terms of mutation
-scores, surprisingly, the results show that automatically generated
-assertions are competitive with manually written ones: the average
-\EVOSUITE mutation score for these 49 benchmarks is \AvgMutEvosuite
-and the average mutation score obtained by developer-written test
-suites is \AvgMutManual ($A_{12}=\EvoManMutA$ and
-$p=\EvoManMutPV$).
+%\paragraph{Manually Written Tests}
+
+%This year, the contest also included manually written test suites as
+%baseline (for 49 out of 59 benchmarks). The results indicate that
+%there is no significant difference in branch coverage between
+%\EVOSUITE-generated test suites (avg. \AvgCovEvosuite) and manually
+%written ones (avg. \AvgCovManual), with Vargha-Delaney's
+%$A_{12}=\EvoManCovA$ and $p=\EvoManCovPV$. In terms of mutation
+%scores, surprisingly, the results show that automatically generated
+%assertions are competitive with manually written ones: the average
+%\EVOSUITE mutation score for these 49 benchmarks is \AvgMutEvosuite
+%and the average mutation score obtained by developer-written test
+%suites is \AvgMutManual ($A_{12}=\EvoManMutA$ and
+%$p=\EvoManMutPV$).
 
@@
 
-~\EVOSUITE generated \FlakyEvosuite flaky tests per run on average,
-much lower than the number of flaky tests produced by the competing
-and baseline tools (\FlakyTthree by \TT, \FlakyJtexpert by \JTEXPERT,
-and \FlakyRandoop by \RANDOOP). We attribute these relatively positive
-results---also consistent with previous years' results---to the way
-\EVOSUITE handles execution environments during test generation (e.g.,
-controlling the static state of the class under test, mocking
-interactions with the file system, system calls like
-\texttt{System.in} and \texttt{System.currentTimeMillis},
-etc.)~\cite{arcuri2014automated}.  \EVOSUITE provides deterministic
-replacement classes for many classes with known non-determinism,
-(e.g., those related to date and time), and in particular the FASTJSON
-benchmarks made heavy use of these. For example, multiple calendar
-systems are necessary (e.g., classes \texttt{HijrahDate},
-\texttt{MinguoDate}, \texttt{JapaneseDate},
-\texttt{ThaiBuddhistDate}), and \EVOSUITE instantiated its own
-replacement versions of these classes 719 times altogether, thus
-potentially avoiding many flaky tests. Overall, no flaky tests were
-generated for the vast majority of subjects in the competition.
+\TODO{}
 
-Amongst those benchmarks for which
-\EVOSUITE struggled with flakiness, FASTJSON-4 is a notable example:
-in the worst case, 90 flaky tests were generated in one single run. An
-analysis of the execution logs indicates several possible sources for
-this flakiness: a) a non-final static constant that is not properly
-reset in between executions; b) a possibly incorrect handling of enum
-types; and c) a global property not being reset in between
-executions. Considering that there were still remaining flaky tests, further investigation will be needed to confirm these
-conjectures and act upon them.
+%~\EVOSUITE generated \FlakyEvosuite flaky tests per run on average,
+%much lower than the number of flaky tests produced by the competing
+%and baseline tools (\FlakyTthree by \TT, \FlakyJtexpert by \JTEXPERT,
+%and \FlakyRandoop by \RANDOOP). We attribute these relatively positive
+%results---also consistent with previous years' results---to the way
+%\EVOSUITE handles execution environments during test generation (e.g.,
+%controlling the static state of the class under test, mocking
+%interactions with the file system, system calls like
+%\texttt{System.in} and \texttt{System.currentTimeMillis},
+%etc.)~\cite{arcuri2014automated}.  \EVOSUITE provides deterministic
+%replacement classes for many classes with known non-determinism,
+%(e.g., those related to date and time), and in particular the FASTJSON
+%benchmarks made heavy use of these. For example, multiple calendar
+%systems are necessary (e.g., classes \texttt{HijrahDate},
+%\texttt{MinguoDate}, \texttt{JapaneseDate},
+%\texttt{ThaiBuddhistDate}), and \EVOSUITE instantiated its own
+%replacement versions of these classes 719 times altogether, thus
+%potentially avoiding many flaky tests. Overall, no flaky tests were
+%generated for the vast majority of subjects in the competition.
 
-\paragraph{Mocking}
+%Amongst those benchmarks for which
+%\EVOSUITE struggled with flakiness, FASTJSON-4 is a notable example:
+%in the worst case, 90 flaky tests were generated in one single run. An
+%analysis of the execution logs indicates several possible sources for
+%this flakiness: a) a non-final static constant that is not properly
+%reset in between executions; b) a possibly incorrect handling of enum
+%types; and c) a global property not being reset in between
+%executions. Considering that there were still remaining flaky tests, further investigation will be needed to confirm these
+%conjectures and act upon them.
 
-As mentioned in the previous section, \EVOSUITE uses private API
-access and functional mocking% in addition to environment
-% mocking
-~\cite{ICST_Mocking17}. Overall, in all tests generated in this
-competition, 1,339 private fields were set and 2,409
-private methods were invoked using reflection, and 15,369 Mockito mock
-instances were created and configured using another 9,553 statements
-(e.g., using the \text{doReturn} method). Considering the 1,804,932 overall test
-statements, this means that only 1.4\% of the tests were devoted to
-mocking. Amongst the 331 distinct classes for which mocks were
-generated at least once there are some classes for which EvoSuite can
-instantiate regular objects (e.g., \texttt{List}). This suggests that
-EvoSuite sometimes struggles to generate and set up complex objects
-correctly, and there is potential for future improvements.
+%\paragraph{Mocking}
 
-%a total of 2,766 mock
-%instances were created, using mocked access. Some of the Java
-%classes most frequently used for mocking across benchmarks are
-%\texttt{File} (849 instances in total), \texttt{Throwable} (284),
-%\texttt{PrintStream} (210) and \texttt{Thread} (114).
+%As mentioned in the previous section, \EVOSUITE uses private API
+%access and functional mocking% in addition to environment
+%% mocking
+%~\cite{ICST_Mocking17}. Overall, in all tests generated in this
+%competition, 1,339 private fields were set and 2,409
+%private methods were invoked using reflection, and 15,369 Mockito mock
+%instances were created and configured using another 9,553 statements
+%(e.g., using the \text{doReturn} method). Considering the 1,804,932 overall test
+%statements, this means that only 1.4\% of the tests were devoted to
+%mocking. Amongst the 331 distinct classes for which mocks were
+%generated at least once there are some classes for which EvoSuite can
+%instantiate regular objects (e.g., \texttt{List}). This suggests that
+%EvoSuite sometimes struggles to generate and set up complex objects
+%correctly, and there is potential for future improvements.
 
-% . Further
-% investigation would be needed to assess the impact of these mocking
-% features on test generation effectiveness for the benchmarks in the
-% competition.
+%%a total of 2,766 mock
+%%instances were created, using mocked access. Some of the Java
+%%classes most frequently used for mocking across benchmarks are
+%%\texttt{File} (849 instances in total), \texttt{Throwable} (284),
+%%\texttt{PrintStream} (210) and \texttt{Thread} (114).
+
+%% . Further
+%% investigation would be needed to assess the impact of these mocking
+%% features on test generation effectiveness for the benchmarks in the
+%% competition.
 
@@
 
-~\EVOSUITE failed to produce any test suites for benchmarks DUBBO-2 and
-WEBMAGIC-4, and generally struggled with most REDISSON benchmarks
-(highlighted in grey in Table~\ref{table:results}). The former two
-benchmarks had missing dependencies in the competition
-setup~\cite{sbst18competition}, which explains why \EVOSUITE was
-incapable of generating any test: When a dependency of the class under
-test is missing, then \EVOSUITE intentionally aborts with an error to
-inform the user of the configuration error. While this is desirable
-behavior during regular usage, arguably in the scope of the
-competition \EVOSUITE could try to ignore such errors and try to
-generate tests nevertheless, as it might still be possible to cover
-code even with some missing dependencies.
+\TODO{why did we get 0\% coverage on most AUTHZFORCE benchmarks? and SPOON-169,
+SPOON-25?}
 
-For the REDISSON benchmarks, most
-executions ended with a timeout; unfortunately, we have not been able
-to reproduce this behaviour locally, hence we can only conjecture that
-the timeouts (reported during the initialisation phase) are due to the
-large number of dependency classes (>7000) that need to be loaded for
-these benchmarks to start off the test generation.
+\TODO{why did we get 0\% coverage on DUBBO-2 and WEBMAGIC-4? classpath was
+incorrect.}
+
+\TODO{what did we get 0\% coverage on SPOON-253, SPOON-20, SPOON-16, SPOON-155
+for larger search budgets?}
+
+\TODO{why did not we get data for FASTJSON-1, FASTJSON-3, FESCAR-41, FESCAR-42,
+SPOON-105 for a search budget of 10 seconds?}
+
+%~\EVOSUITE failed to produce any test suites for benchmarks DUBBO-2 and
+%WEBMAGIC-4, and generally struggled with most REDISSON benchmarks
+%(highlighted in grey in Table~\ref{table:results}). The former two
+%benchmarks had missing dependencies in the competition
+%setup~\cite{sbst18competition}, which explains why \EVOSUITE was
+%incapable of generating any test: When a dependency of the class under
+%test is missing, then \EVOSUITE intentionally aborts with an error to
+%inform the user of the configuration error. While this is desirable
+%behavior during regular usage, arguably in the scope of the
+%competition \EVOSUITE could try to ignore such errors and try to
+%generate tests nevertheless, as it might still be possible to cover
+%code even with some missing dependencies.
+
+%For the REDISSON benchmarks, most
+%executions ended with a timeout; unfortunately, we have not been able
+%to reproduce this behaviour locally, hence we can only conjecture that
+%the timeouts (reported during the initialisation phase) are due to the
+%large number of dependency classes (>7000) that need to be loaded for
+%these benchmarks to start off the test generation.
 
@@
 This paper reports on the participation of the \EVOSUITE test
-generation tool in the 6th SBST Java Unit Testing Tool Contest. With
+generation tool in the 7th SBST Java Unit Testing Tool Contest. With
 an overall score of \TOTALPOINTS points, \EVOSUITE achieved the highest score
@@
 ``GREATEST'' (EP/N023978/1), and by the National Research Fund,
-Luxembourg (FNR/P10/03).
+Luxembourg (FNR/P10/03). \TODO{update}
 

### 2019-03-16 papers/sbst19/r_files/analyze.R

@@ -1,0 +1,259 @@
+#tool,benchmark,class,run,preparationTime,generationTime,executionTime,testcaseNumber,
+#uncompilableNumber,brokenTests,failTests,linesTotal,linesCovered,linesCoverageRatio,
+#conditionsTotal,conditionsCovered,conditionsCoverageRatio,mutantsTotal,mutantsCovered,
+#mutantsCoverageRatio,mutantsKilled,mutantsKillRatio,mutantsAlive,timeBudget,totalTestClasses
+
+library(stringr)
+
+FILE <- "../data/single_transcript_without_question_mark.csv"
+
+benchmarks <- sort(unique(read.csv("../data/benchmarks.txt", header=T)$benchmark))
+
+mainTable <- function(){
+
+  dt <- read.csv(FILE,sep=",",dec=".",header=T) #,colClasses=cols)
+
+  TABLE = paste("../mainTable.tex",sep="")
+  unlink(TABLE)
+  sink(TABLE, append=TRUE, split=TRUE)
+
+  cat("\\begin{tabular}{ ll rrrr rrrr}\\toprule","\n")
+  cat(" \\multirow{2}{1in}{Benchmark} & \\multirow{2}{1in}{Java Class} &  \\multicolumn{4}{c}{Branch Coverage} &  \\multicolumn{4}{c}{Mutation Score}\\\\\\cmidrule(lr){3-6}\\cmidrule(lr){7-10} \n")
+  cat(" & & 10s & 60s & 120s & 240s & 10s & 60s & 120s & 240s \\\\ \n" )
+  cat("\\midrule","\n")
+
+  times <- c(10, 60, 120, 240) # sort(unique(dt$timeBudget))
+  classes <- sort(unique(dt$class))
+
+  for(benchmark in benchmarks) {
+  #for(class in classes){
+
+    mask = dt$tool=="evosuite" & dt$benchmark==benchmark & dt$preparationTime != "?"
+
+    cat(benchmark, " & ", as.character(unique(dt$class[ dt$benchmark==benchmark ])))
+
+    #cat(class)
+
+    for(t in times){
+      cov <-  as.numeric(as.character(dt$conditionsCoverageRatio[mask & dt$timeBudget==t]))
+      cat(" & ", getColouredCell(mean(cov)),sep="")
+    }
+    for(t in times){
+      score <- as.numeric(as.character(dt$mutantsKillRatio[mask & dt$timeBudget==t]))
[…]

### 2019-03-21 papers/sbst19/mainTable-t3.tex
T3 results.

\begin{tabular}{ ll rrrr rrrr}\toprule 
 \multirow{2}{1in}{Benchmark} & \multirow{2}{1in}{Java Class} &  \multicolumn{4}{c}{Branch Coverage} &  \multicolumn{4}{c}{Mutation Score}\\\cmidrule(lr){3-6}\cmidrule(lr){7-10} 
 & & 10s & 60s & 120s & 240s & 10s & 60s & 120s & 240s \\ 
\midrule 
AUTHZFORCE-1  &  org.ow2.authzforce.core.pdp.impl.PdpBean & 100.0\% & 100.0\% & 100.0\% & 100.0\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
AUTHZFORCE-11  &  org.ow2.authzforce.core.pdp.impl.func.LogicalNOfFunction & 10.0\% & 10.0\% & 10.0\% & 10.0\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
AUTHZFORCE-27  &  org.ow2.authzforce.core.pdp.impl.func.MapFunctionFactory & 25.0\% & 25.0\% & 25.0\% & 25.0\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
AUTHZFORCE-32  &  org.ow2.authzforce.core.pdp.impl.func.SubstringFunction & 20.0\% & 20.0\% & 20.0\% & 20.0\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
AUTHZFORCE-33  &  org.ow2.authzforce.core.pdp.impl.SchemaHandler & 94.4\% & 100.0\% & 100.0\% & 100.0\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
AUTHZFORCE-48  &  org.ow2.authzforce.core.pdp.impl.policy.PolicyVersions & 62.9\% & 58.3\% & 63.6\% & 58.3\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
AUTHZFORCE-5  &  org.ow2.authzforce.core.pdp.impl.CloseableAttributeProvider & 53.8\% & 54.5\% & 54.5\% & 54.5\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
AUTHZFORCE-52  &  org.ow2.authzforce.core.pdp.impl.PepActionExpression & 83.3\% & 83.3\% & 83.3\% & 83.3\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
AUTHZFORCE-63  &  org.ow2.authzforce.core.pdp.impl.combining.DPUnlessPDCombiningAlg & 30.0\% & 30.0\% & 30.0\% & 30.0\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
AUTHZFORCE-65  &  org.ow2.authzforce.core.pdp.impl.combining.FirstApplicableCombiningAlg & 41.7\% & 41.7\% & 41.7\% & 41.7\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
DUBBO-2  &  com.alibaba.dubbo.common.utils.ReflectUtils & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
FASTJSON-1  &  com.alibaba.fastjson.parser.JSONLexerBase & 0.6\% & 0.8\% & 2.3\% & 4.3\% & 0.4\% & 0.6\% & 1.6\% & 1.3\%\\ 
FASTJSON-3  &  com.alibaba.fastjson.parser.DefaultJSONParser & 5.0\% & 15.0\% & 16.0\% & 16.7\% & 6.4\% & 12.9\% & 12.9\% & 11.6\%\\ 
FESCAR-1  &  com.alibaba.fescar.core.protocol.transaction.BranchReportRequest & 60.4\% & 64.6\% & 61.5\% & 68.8\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
FESCAR-12  &  com.alibaba.fescar.core.rpc.netty.RpcServerHandler & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
FESCAR-18  &  com.alibaba.fescar.core.protocol.MergedWarpMessage & 35.7\% & 35.7\% & 35.7\% & 35.7\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
FESCAR-23  &  com.alibaba.fescar.core.protocol.MergeResultMessage & 28.6\% & 28.6\% & 28.6\% & 28.6\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
FESCAR-25  &  com.alibaba.fescar.core.rpc.netty.RmMessageListener & 37.5\% & 37.5\% & 37.5\% & 37.5\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
FESCAR-36  &  com.alibaba.fescar.core.protocol.RegisterRMRequest & 14.7\% & 14.1\% & 12.8\% & 12.8\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
FESCAR-37  &  com.alibaba.fescar.core.rpc.RpcContext & 35.3\% & 35.3\% & 35.3\% & 35.3\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
FESCAR-41  &  com.alibaba.fescar.core.rpc.netty.RmRpcClient & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 0.7\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
FESCAR-42  &  com.alibaba.fescar.core.rpc.DefaultServerMessageListenerImpl & 7.1\% & 7.1\% & 7.1\% & 7.1\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
FESCAR-7  &  com.alibaba.fescar.core.rpc.netty.MessageCodecHandler & 18.8\% & 18.8\% & 18.8\% & 18.8\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
OKIO-1  &  okio.Buffer & 22.9\% & 10.2\% & 18.3\% & 21.4\% & 8.5\% & 5.2\% & 1.6\% & 8.1\%\\ 
OKIO-4  &  okio.RealBufferedSource & 0.6\% & 0.6\% & 0.6\% & 0.6\% & 0.9\% & 0.9\% & 0.9\% & 0.9\%\\ 
SPOON-105  &  spoon.support.compiler.jdt.PositionBuilder & 17.3\% & 16.7\% & 16.7\% & 16.8\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
SPOON-155  &  spoon.reflect.visitor.filter.AllMethodsSameSignatureFunction & 6.2\% & 6.2\% & 6.2\% & 6.2\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
SPOON-16  &  spoon.reflect.path.CtElementPathBuilder & 7.8\% & 7.8\% & 7.8\% & 7.8\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
SPOON-169  &  spoon.reflect.visitor.ImportScannerImpl & 3.3\% & 4.3\% & 5.2\% & 4.1\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
SPOON-20  &  spoon.support.reflect.reference.CtLocalVariableReferenceImpl & 20.0\% & 20.0\% & 20.0\% & 20.0\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
SPOON-211  &  spoon.reflect.path.impl.CtRolePathElement & 15.4\% & 15.4\% & 15.4\% & 15.4\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
SPOON-25  &  spoon.pattern.internal.ValueConvertorImpl & 21.2\% & 20.8\% & 21.2\% & 21.2\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
SPOON-253  &  spoon.pattern.internal.parameter.MapParameterInfo & 54.7\% & 52.6\% & 53.1\% & 52.1\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
SPOON-32  &  spoon.MavenLauncher & 12.5\% & 12.5\% & 12.5\% & 12.5\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
SPOON-65  &  spoon.support.DefaultCoreFactory & 50.0\% & 50.0\% & 50.0\% & 50.0\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
WEBMAGIC-1  &  us.codecraft.webmagic.model.PageModelExtractor & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
WEBMAGIC-4  &  us.codecraft.webmagic.Page & 2.1\% & 6.3\% & 5.6\% & 5.6\% & 9.8\% & 22.4\% & 31.6\% & 14.9\%\\ 
ZXING-10  &  com.google.zxing.qrcode.encoder.Encoder & 62.0\% & 64.0\% & 63.9\% & 64.7\% & 33.8\% & 28.6\% & 34.1\% & 33.6\%\\ 
\midrule 
Average &  &  17.3\% &  17.2\% &  14.8\% &  15.5\% &  19.9\% &  16.9\% &  13.9\% &  14.6\%\\ 
\bottomrule 
\end{tabular}

### 2019-03-22 papers/sbst19/paper_sbst19.tex
Added commands for the other tools.
T3 results.
Draft problematic challenges.

@@
 \newcommand{\TT}{{\sc T3}\xspace}
+\newcommand{\SUSHI}{{\sc Sushi}\xspace}
+\newcommand{\TARDIS}{{\sc Tardis}\xspace}
 
@@
 
+\begin{table*}[t]
+  \centering
+  \caption{\label{table:t3_results}Detailed results of \TT on the
+    SBST benchmark classes.}
+\vspace{-1em}
+\resizebox{\textwidth}{!}{  
+\input{mainTable-t3.tex}
+}	
+\end{table*}
+
 % \begin{table*}[t]
@@
 
-\TODO{why did we get 0\% coverage on most AUTHZFORCE benchmarks? and SPOON-169,
-SPOON-25?}
+\EVOSUITE failed to produce any test suites for benchmarks DUBBO-2, SPOON-169,
+SPOON-25, and WEBMAGIC-4, and generally struggled with most AUTHZFORCE
+benchmarks (highlighted in grey in Table~\ref{table:results}).
 
-\TODO{why did we get 0\% coverage on DUBBO-2 and WEBMAGIC-4? classpath was
-incorrect.}
+The benchmarks DUBBO-2 and WEBMAGIC-4 had missing dependencies in the
+competition setup~\cite{sbst19competition} (something we reported last
+year~\cite{evosuiteAtSbst2018}), which explains why \EVOSUITE was incapable of
+generating any test: When a dependency of the class under test is missing, then
+\EVOSUITE intentionally aborts with an error to inform the user of the
+configuration error. While this is desirable behavior during regular usage,
+arguably in the scope of the competition \EVOSUITE could try to ignore such
+errors and try to generate tests nevertheless, as it might still be possible to
+cover code even with some missing dependencies. For the benchmark FASTJSON-3 and
+a 10s time budget, \EVOSUITE generated some test suites but due to a bug in the
+competition infrastructure, no data was collected. % FileNotFoundException in the infrastructure
 
-\TODO{what did we get 0\% coverage on SPOON-253, SPOON-20, SPOON-16, SPOON-155
-for larger search budgets?}
+For the benchmarks SPOON-169 and SPOON-25, \EVOSUITE either failed to generated
+a compilable test suite or crashed due to a bug in DynaMOSA. Although \EVOSUITE's
+minimization could help at reducing the number of uncompilable / flaky test cases,
+for SPOON-169 all minimizations attempts ran out of time.
+% SPOON-169
+% Minimization timeout. Roll back to original test suite
+% and therefore the test suite
 
-\TODO{why did not we get data for FASTJSON-1, FASTJSON-3, FESCAR-41, FESCAR-42,
-SPOON-105 for a search budget of 10 seconds?}
+For the AUTHZFORCE benchmarks, although \EVOSUITE managed to generate some test
+suites, most executions ended with a failure, unfortunately, we have not been
+able to reproduce this behaviour locally, hence we cannot conjecture the reason
+of such failures. \TODO{exact the same happened for SPOON-253 (120s and 240s).
+Some sort of java.lang.SecurityException: Security manager blocks ("java.lang.RuntimePermission" "setSecurityManager").}
 
-%~\EVOSUITE failed to produce any test suites for benchmarks DUBBO-2 and
-%WEBMAGIC-4, and generally struggled with most REDISSON benchmarks
-%(highlighted in grey in Table~\ref{table:results}). The former two
-%benchmarks had missing dependencies in the competition
-%setup~\cite{sbst18competition}, which explains why \EVOSUITE was
-%incapable of generating any test: When a dependency of the class under
-%test is missing, then \EVOSUITE intentionally aborts with an error to
-%inform the user of the configuration error. While this is desirable
-%behavior during regular usage, arguably in the scope of the
-%competition \EVOSUITE could try to ignore such errors and try to
-%generate tests nevertheless, as it might still be possible to cover
-%code even with some missing dependencies.
-
-%For the REDISSON benchmarks, most
-%executions ended with a timeout; unfortunately, we have not been able
-%to reproduce this behaviour locally, hence we can only conjecture that
-%the timeouts (reported during the initialisation phase) are due to the
-%large number of dependency classes (>7000) that need to be loaded for
-%these benchmarks to start off the test generation.
+For a 10 seconds time budget, Table~\ref{table:results} reports ``-'' for
+benchmarks FASTJSON-1, FASTJSON-3, FESCAR-41, FESCAR-42, and SPOON-105.
+% last message in the log files was * Initial Number of Goals in DynMOSA = 942 / 10337
+\TODO{either infinite loop, took much time to start evolving, or DynaMOSA can't
+be used in this benchmarks with a time budget of 10s.}
+%
+On the other hand, and surprisingly, for benchmarks SPOON-155, SPOON-16,
+SPOON-20, and SPOON-211, \EVOSUITE successfully generated test suites for small
+time budgets but it failed to do it for large time budgets. For all, \EVOSUITE
+crashed due to a bug in the DynaMOSA algorithm.
+%% SPOON-155 (240s), SPOON-16 (120s), SPOON-20 (120s and 240s), SPOON-211 (120s)
+%java.lang.NullPointerException: null
+%	at org.evosuite.ga.operators.ranking.RankBasedPreferenceSorting.getNumberOfSubfronts(RankBasedPreferenceSorting.java:158) ~[evosuite-master-1.0.7-SNAPSHOT.jar:1.0.7-SNAPSHOT]
+%	at org.evosuite.ga.metaheuristics.mosa.DynaMOSA.generateSolution(DynaMOSA.java:152) ~[evosuite-master-1.0.7-SNAPSHOT.jar:1.0.7-SNAPSHOT]
+%	at org.evosuite.strategy.MOSuiteStrategy.generateTests(MOSuiteStrategy.java:115) ~[evosuite-master-1.0.7-SNAPSHOT.jar:1.0.7-SNAPSHOT]
 

### 2019-03-23 papers/sbst19/paper_sbst19.tex
Add text on infrastructure problem

@@
 
-For the AUTHZFORCE benchmarks, although \EVOSUITE managed to generate some test
-suites, most executions ended with a failure, unfortunately, we have not been
-able to reproduce this behaviour locally, hence we cannot conjecture the reason
-of such failures. \TODO{exact the same happened for SPOON-253 (120s and 240s).
-Some sort of java.lang.SecurityException: Security manager blocks ("java.lang.RuntimePermission" "setSecurityManager").}
+For the AUTHZFORCE benchmarks, although \EVOSUITE managed to generate
+some test suites, most executions for data collection ended with a
+failure. Specifically, for these classes an exception was raised for
+test execution for \emph{all} tools in the competition. However,
+while this exception was not problematic for other tools, it caused
+an inconsistent state of the JVM which led to the \texttt{@Before}
+setup methods of \EVOSUITE to fail (the \texttt{@Before} method was
+not able to configure \EVOSUITE's custom security manager because it
+was never correctly removed). As a consequence, all test executions
+failed. We were not able to reproduce the error in the competition
+infrastructure, and thus cannot conjecture about the causes. The same
+problem also occurred for SPOON-253. While in principle it would be
+possible to extend \EVOSUITE to try to ignore such errors and keep on
+executing tests, as explained it is \EVOSUITE's philosophy that the
+user should be made aware of configuration errors, and hence such an
+extension would only serve to tune \EVOSUITE for the competition.
 
@@
 \EVOSUITE.  This project has been funded by the EPSRC project
-``GREATEST'' (EP/N023978/1), and by the National Research Fund,
+``GREATEST'' (EP/N023978/2), and by the National Research Fund,
 Luxembourg (FNR/P10/03). \TODO{update}

### 2019-03-25 papers/sbst19/paper_sbst19.tex
Adding a short description of DynaMOSA

@@
 
-\TODO{introduce DynaMOSA}
-The underlying genetic algorithm uses test suites as representation
-(chromosomes). Each test suite consists of a variable number of test
-cases, each of which is represented as a variable-length sequence of
-Java statements (e.g., calls on the class under test). A population of
-randomly generated individuals is evolved using suitable search
-operators (e.g., selection, crossover and mutation), such that
-iteratively better solutions with respect to the optimisation target
-are produced. The optimisation target is to maximise code coverage. To
-achieve this, the fitness function uses standard heuristics such as
-the branch distance; see~\cite{GoA_TSE12} for more details. \EVOSUITE
-can be configured to optimise for multiple coverage criteria at the
-same time, and the default configuration combines branch coverage with
+For this edition of the competition, \EVOSUITE was configured with \textit{Dynamic Many-Objective Sorting Algorithm} (DynaMOSA) as a search algorithm.
+DynMOSA~\cite{dynamosa, panichella:ssbse2018} is a recently developed many-objective algorithm that incrementally optimizes multiple coverage criteria at the same time.
+More specifically, different testing coverage requirements (e.g., branches) are treated as distinct, contrasting search objectives in a many-objective paradigm.
+Search objectives are computed using standard heuristics for code coverage, such as the branch distance and the approach level (see~\cite{GoA_TSE12} for more details).
+Coverage requirements are prioritized during the search according to their structural dependencies in the control dependency graph.
+The search is initialized with the coverage requirements (e.g., branches) positioned higher in the hierarchy; then, the remaining requirements are incrementally inserted in later generations when their dominator requirements are covered.
+
+DynaMOSA evolves test cases~\cite{dynamosa}, which correspond to the chromosomes for the search.
+Each test case consists of variable-length sequences of Java statements (e.g., primitive statements and calls on the class under test).
+A population of randomly generated test cases is evolved using search operators (e.g., selection, crossover and mutation) to iteratively produce test cases that are closer to satisfy the target coverage requirements.
+The final test suite is formed by the shorter test cases encountered during the search, and that satisfy the coverage requirements.
+These tests are stored in an external data structure, called \textit{archive}~\cite{mosa,dynamosa}.
+
+\EVOSUITE can be configured to satisfy for multiple coverage criteria at the same time, and the default configuration combines branch coverage with
 mutation testing~\cite{emse14_mutation} and other basic
-criteria~\cite{rojas2015combining}. Once the search is completed,
-\EVOSUITE applies various optimisations to improve the readability of
-the generated tests. For example, tests are minimised, and a
-minimised set of effective test assertions is selected using mutation
-analysis~\cite{10.1109/TSE.2011.93}. For more details on the tool and
-its abilities we refer to~\cite{FrA11c,FrA13a}.
+criteria~\cite{rojas2015combining}. Once the search is completed, \EVOSUITE applies various post-search optimizations aimed to improve the readability of
+the generated tests.
+For example, tests are minimised and test assertions are selected using mutation analysis~\cite{10.1109/TSE.2011.93}.
+For more details on post-process optimization we refer to~\cite{FrA11c,FrA13a}.
 
-The effectiveness of \EVOSUITE has been evaluated on open source as
-well as industrial software in terms of code
-coverage~\cite{fraser2014large,emse_archive,ea_evaluation}, fault finding
-effectiveness~\cite{shamshiri2015automatically,moein2017}, and effects
-on developer
-productivity~\cite{TOSEM_userstudy,ISSTA15_Study} and software
-maintenance~\cite{ICST2018_Maintenance}.
+The effectiveness of \EVOSUITE has been evaluated on open source as well as industrial software in terms of code coverage~\cite{fraser2014large,emse_archive,ea_evaluation,dynamosa}, fault finding
+effectiveness~\cite{shamshiri2015automatically,moein2017}, and effects on developer productivity~\cite{TOSEM_userstudy,ISSTA15_Study} and software maintenance~\cite{ICST2018_Maintenance}.
 

### 2019-03-26 papers/sbst19/paper_sbst19.tex
Update text

@@
 
-The effectiveness of \EVOSUITE has been evaluated on open source as well as industrial software in terms of code coverage~\cite{fraser2014large,emse_archive,ea_evaluation,dynamosa}, fault finding
-effectiveness~\cite{shamshiri2015automatically,moein2017}, and effects on developer productivity~\cite{TOSEM_userstudy,ISSTA15_Study} and software maintenance~\cite{ICST2018_Maintenance}.
-
+In the past, the effectiveness of \EVOSUITE has been evaluated on open
+source as well as industrial software in terms of code
+coverage~\cite{fraser2014large,emse_archive,ea_evaluation,dynamosa},
+fault finding
+effectiveness~\cite{shamshiri2015automatically,moein2017}, and effects
+on developer productivity~\cite{TOSEM_userstudy,ISSTA15_Study} and
+software maintenance~\cite{ICST2018_Maintenance}.
+%
 \EVOSUITE has a longstanding record of success at the unit testing
@@
 
-\begin{table*}[t]
-  \centering
-  \caption{\label{table:t3_results}Detailed results of \TT on the
-    SBST benchmark classes.}
-\vspace{-1em}
-\resizebox{\textwidth}{!}{  
-\input{mainTable-t3.tex}
-}	
-\end{table*}
+%\begin{table*}[t]
+%  \centering
+%  \caption{\label{table:t3_results}Detailed results of \TT on the
+%    SBST benchmark classes.}
+%\vspace{-1em}
+%\resizebox{\textwidth}{!}{  
+%\input{mainTable-t3.tex}
+%}	
+%\end{table*}
 
@@
 
-\paragraph{Overall Results}
-
-\TODO{}
+%\paragraph{Overall Results}
 
@@
 % mutation score and ratio of fault detection.
-
-\paragraph{Flaky Tests}
-
-\TODO{}
 
@@
 
-\paragraph{Problematic benchmarks}
+On the whole, the performance of \EVOSUITE was in line with previous
+results, although \EVOSUITE seemed to fail on a notably large number
+of classes. In particular, \EVOSUITE failed to produce any test
+suites for benchmarks DUBBO-2, SPOON-169, SPOON-25, and WEBMAGIC-4,
+and generally struggled with most AUTHZFORCE benchmarks (highlighted
+in grey in Table~\ref{table:results}).
 
-\EVOSUITE failed to produce any test suites for benchmarks DUBBO-2, SPOON-169,
-SPOON-25, and WEBMAGIC-4, and generally struggled with most AUTHZFORCE
-benchmarks (highlighted in grey in Table~\ref{table:results}).
-
-The benchmarks DUBBO-2 and WEBMAGIC-4 had missing dependencies in the
-competition setup~\cite{sbst19competition} (something we reported last
-year~\cite{evosuiteAtSbst2018}), which explains why \EVOSUITE was incapable of
-generating any test: When a dependency of the class under test is missing, then
-\EVOSUITE intentionally aborts with an error to inform the user of the
-configuration error. While this is desirable behavior during regular usage,
-arguably in the scope of the competition \EVOSUITE could try to ignore such
-errors and try to generate tests nevertheless, as it might still be possible to
-cover code even with some missing dependencies. For the benchmark FASTJSON-3 and
-a 10s time budget, \EVOSUITE generated some test suites but due to a bug in the
+A closer look at the benchmarks DUBBO-2 and WEBMAGIC-4 reveals that
+there were missing dependencies in the competition
+setup~\cite{sbst19competition} (similar to cases in previous
+years~\cite{evosuiteAtSbst2018}), which explains why \EVOSUITE was
+incapable of generating any test: When a dependency of the class
+under test is missing, then \EVOSUITE intentionally aborts with an
+error to inform the user of the configuration error. While this is
+desirable behavior during regular usage, arguably in the scope of the
+competition \EVOSUITE could try to ignore such errors and try to
+generate tests nevertheless, as it might still be possible to cover
+code even with some missing dependencies. For the benchmark
+FASTJSON-3 and a 10s time budget, \EVOSUITE generated some test
+suites but due to a bug in the
 competition infrastructure, no data was collected. % FileNotFoundException in the infrastructure
@@
 
-For a 10 seconds time budget, Table~\ref{table:results} reports ``-'' for
-benchmarks FASTJSON-1, FASTJSON-3, FESCAR-41, FESCAR-42, and SPOON-105.
+In general, \EVOSUITE often struggles with a time budget as low as 10
+seonds. For example, Table~\ref{table:results} reports ``-'' for
+benchmarks FASTJSON-1, FASTJSON-3, FESCAR-41, FESCAR-42, and
+SPOON-105.
 % last message in the log files was * Initial Number of Goals in DynMOSA = 942 / 10337
-\TODO{either infinite loop, took much time to start evolving, or DynaMOSA can't
-be used in this benchmarks with a time budget of 10s.}
+%\TODO{either infinite loop, took much time to start evolving, or DynaMOSA can't
+%be used in this benchmarks with a time budget of 10s.}
 %
-On the other hand, and surprisingly, for benchmarks SPOON-155, SPOON-16,
-SPOON-20, and SPOON-211, \EVOSUITE successfully generated test suites for small
-time budgets but it failed to do it for large time budgets. For all, \EVOSUITE
-crashed due to a bug in the DynaMOSA algorithm.
+Surprisingly, for benchmarks SPOON-155, SPOON-16, SPOON-20, and
+SPOON-211, \EVOSUITE successfully generated test suites for small
+time budgets but it failed to do it for large time budgets. For all,
+\EVOSUITE crashed due to a bug in the DynaMOSA algorithm which had
+not been revealed by our previous experiments. Consequently, even
+though DynaMOSA is known to increase the coverage \EVOSUITE achieves
+subtantially in general, this increase was countered with some
+missing datapoints. As always, the competition was helpful in
+improving the robustness of the tool, by revealing this and other
+bugs.
 %% SPOON-155 (240s), SPOON-16 (120s), SPOON-20 (120s and 240s), SPOON-211 (120s)
@@
 generation tool in the 7th SBST Java Unit Testing Tool Contest. With
-an overall score of \TOTALPOINTS points, \EVOSUITE achieved the highest score
-of all tools in the competition.
+an overall score of \TOTALPOINTS points, \EVOSUITE achieved the
+highest score of all tools in the competition.
 
@@
 ``GREATEST'' (EP/N023978/2), and by the National Research Fund,
-Luxembourg (FNR/P10/03). \TODO{update}
+Luxembourg (FNR/P10/03).
 

### 2019-03-26 papers/sbst19/paper_sbst19.tex
Typo.
US.

@@
 the generated tests.
-For example, tests are minimised and test assertions are selected using mutation analysis~\cite{10.1109/TSE.2011.93}.
+For example, tests are minimized and test assertions are selected using mutation analysis~\cite{10.1109/TSE.2011.93}.
 For more details on post-process optimization we refer to~\cite{FrA11c,FrA13a}.
@@
 Like in previous instances of the competition, we enabled the
-post-processing step of test minimisation---not for efficiency
-reasons, but because minimised tests are less likely to break. To
+post-processing step of test minimization---not for efficiency
+reasons, but because minimized tests are less likely to break. To
 reduce the overall time of test generation we included all assertions
@@
 budget onto the different phases of \EVOSUITE (e.g., initialisation,
-search, minimisation, assertion generation, compilation check, removal
+search, minimization, assertion generation, compilation check, removal
 of flaky tests). That is, 50\% of the time was allocated to the
@@
 In general, \EVOSUITE often struggles with a time budget as low as 10
-seonds. For example, Table~\ref{table:results} reports ``-'' for
+seconds. For example, Table~\ref{table:results} reports ``-'' for
 benchmarks FASTJSON-1, FASTJSON-3, FESCAR-41, FESCAR-42, and

### 2019-03-26 papers/sbst19/paper_sbst19.tex
Removed todo.

@@
   Maturity&  Mature research prototype, under development\\
-  Technology behind the tool & Search-based testing / whole test suite generation \TODO{not whole test suite anymore}\\
+  Technology behind the tool & Search-based testing / whole test suite generation \\
 \hline

### 2019-03-27 papers/sbst19/paper_sbst19.tex
Minor

@@
 \acmConference[SBST'19]{SBST'19: IEEE/ACM 12th International Workshop on Search-Based Software Testing}{May 27, 2019}{Montreal, Canada}
-\acmBooktitle{SBST'19: SBST'19: IEEE/ACM 12th International Workshop on Search-Based Software Testing, May 27, 2019, Montreal, Canada}
+\acmBooktitle{SBST'19: IEEE/ACM 12th International Workshop on Search-Based Software Testing, May 27, 2019, Montreal, Canada}
 \acmPrice{15.00}
@@
   Maturity&  Mature research prototype, under development\\
-  Technology behind the tool & Search-based testing / whole test suite generation \\
+  Technology behind the tool & Search-based testing / many-objective optimization \\
 \hline

### 2019-03-27 papers/sbst19/paper_sbst19.tex
Few minor changes

@@
 mutation testing~\cite{emse14_mutation} and other basic
-criteria~\cite{rojas2015combining}. Once the search is completed, \EVOSUITE applies various post-search optimizations aimed to improve the readability of
+criteria~\cite{rojas2015combining}. Once the search is completed, \EVOSUITE applies various post-search optimisations aimed to improve the readability of
 the generated tests.
-For example, tests are minimized and test assertions are selected using mutation analysis~\cite{10.1109/TSE.2011.93}.
-For more details on post-process optimization we refer to~\cite{FrA11c,FrA13a}.
+For example, tests are minimised and test assertions are selected using mutation analysis~\cite{10.1109/TSE.2011.93}.
+For more details on post-process optimisation we refer to~\cite{FrA11c,FrA13a}.
 
@@
 The configuration of \EVOSUITE for the 2019 competition is largely
-based on its default values, since these have been tuned
+based on its default values since these have been tuned
 extensively~\cite{arcuri2013parameter}. We used the default set of
 coverage criteria~\cite{rojas2015combining} (e.g., line coverage,
-branch coverage, branch coverage by direct method invocation, weak
+branch coverage, branch coverage by direct method invocations, weak
 mutation testing, output coverage, exception coverage). \EVOSUITE uses
@@
 minor improvements have been applied since the last instance of the
-competition, in particular in relation to non-determinism and flaky
+competition, in particular regarging non-determinism and flaky
 tests~\cite{arcuri2014automated}, as well as new types of test
@@
 desirable behavior during regular usage, arguably in the scope of the
-competition \EVOSUITE could try to ignore such errors and try to
+competition, \EVOSUITE could try to ignore such errors and try to
 generate tests nevertheless, as it might still be possible to cover
@@
 FASTJSON-3 and a 10s time budget, \EVOSUITE generated some test
-suites but due to a bug in the
+suites, but due to a bug in the
 competition infrastructure, no data was collected. % FileNotFoundException in the infrastructure
 
-For the benchmarks SPOON-169 and SPOON-25, \EVOSUITE either failed to generated
+For the benchmarks SPOON-169 and SPOON-25, \EVOSUITE either failed to generate
 a compilable test suite or crashed due to a bug in DynaMOSA. Although \EVOSUITE's
@@
 some test suites, most executions for data collection ended with a
-failure. Specifically, for these classes an exception was raised for
+failure. Specifically, for these classes, an exception was raised for
 test execution for \emph{all} tools in the competition. However,
@@
 Surprisingly, for benchmarks SPOON-155, SPOON-16, SPOON-20, and
-SPOON-211, \EVOSUITE successfully generated test suites for small
-time budgets but it failed to do it for large time budgets. For all,
+SPOON-211, \EVOSUITE successfully generated test suites for small-time 
+budgets, but it failed to do it for large time budgets. For all,
 \EVOSUITE crashed due to a bug in the DynaMOSA algorithm which had
 not been revealed by our previous experiments. Consequently, even
-though DynaMOSA is known to increase the coverage \EVOSUITE achieves
-subtantially in general, this increase was countered with some
+though DynaMOSA is known to increase the coverage, \EVOSUITE achieves
+substantially in general, this increase was countered with some
 missing datapoints. As always, the competition was helpful in

### 2019-03-27 papers/sbst19/paper_sbst19.tex
Author order and AE

@@
 
+\author{Jos\'e Campos}
+\affiliation{%
+  \institution{University of Washington}
+  \city{Seattle}
+  \country{USA}
+}
+\email{jmcampos@uw.edu}
 \author{Annibale Panichella}
@@
 \email{a.panichella@tudelft.nl}
-
-\author{Jos\'e Campos}
-\affiliation{%
-  \institution{University of Washington}
-  \city{Seattle}
-  \country{USA}
-}
-\email{jmcampos@uw.edu}
 
@@
 under test and all its dependencies), \EVOSUITE automatically produces
-a set of JUnit test cases aimed at maximising code coverage. \EVOSUITE
+a set of JUnit test cases aimed at maximizing code coverage. \EVOSUITE
 can be used on the command line, or through plugins for popular
@@
 mutation testing~\cite{emse14_mutation} and other basic
-criteria~\cite{rojas2015combining}. Once the search is completed, \EVOSUITE applies various post-search optimisations aimed to improve the readability of
+criteria~\cite{rojas2015combining}. Once the search is completed, \EVOSUITE applies various post-search optimizations aimed to improve the readability of
 the generated tests.
-For example, tests are minimised and test assertions are selected using mutation analysis~\cite{10.1109/TSE.2011.93}.
-For more details on post-process optimisation we refer to~\cite{FrA11c,FrA13a}.
+For example, tests are minimized and test assertions are selected using mutation analysis~\cite{10.1109/TSE.2011.93}.
+For more details on post-process optimization we refer to~\cite{FrA11c,FrA13a}.
 

### 2020-03-11 papers/sbst20/main.tex
Template for sbst20

\documentclass[sigconf]{acmart}
\usepackage{amsfonts}
\usepackage[latin1]{inputenc}
\usepackage[english]{babel}
\usepackage{listings}
\usepackage{algorithmic}
\usepackage{float}
%\usepackage[numbers,sort&compress,square]{natbib}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{subfigure}
%\usepackage{hyperref}
\usepackage{color}
%\usepackage[usenames,dvipsnames,]{xcolor}
%\usepackage{soul}
\usepackage{xspace}
\usepackage{boxedminipage}
\usepackage{alltt}
\usepackage{multirow}
\usepackage{paralist}
\usepackage{amsmath}
\usepackage{balance}
\definecolor{light-gray}{gray}{0.90}

\newcommand{\EVOSUITE}{{\sc EvoSuite}\xspace}
\newcommand{\RANDOOP}{{\sc Randoop}\xspace}
\newcommand{\MUTEST}{{\sc $\mu$Test}\xspace}
\newcommand{\CS}{{\sc SF100}\xspace}
\newcommand{\TOTALPOINTS}{{255.43}\xspace}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmcopyright}
\copyrightyear{2018}
\acmYear{2018}
\acmDOI{10.1145/1122445.1122456}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[SBST '20]{SBST'20: IEEE/ACM 13th International Workshop on Search-Based Software Testing}{October 2020}{Seoul, South Korea}
\acmBooktitle{SBST'20: IEEE/ACM 13th International Workshop on Search-Based Software Testing,
  October 2020, Seoul, South Korea}
\acmPrice{15.00}
\acmISBN{978-1-4503-9999-9/18/06}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.

\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{\EVOSUITE at the SBST 2020 Tool Competition}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Annibale Panichella}
%\orcid{0000-0002-5385-7695}
%\author{G.K.M. Tobin}
%\authornotemark[1]
%\email{webmaster@marysville-ohio.com}
\affiliation{%
  \institution{Delft University of Technology}
  \state{The Netherlands}
}
\email{a.panichella@tudelft.nl}

\author{Jose Campos}
%\email{a.panichella@tudelft.nl}
%\orcid{0000-0002-5385-7695}
%\author{G.K.M. Tobin}
%\authornotemark[1]
\affiliation{%
  \institution{LASIGE, Faculdade de Ci\^encias \\ Universidade de Lisboa}
  \state{Portugal}
}
%\email{webmaster@marysville-ohio.com}

\author{Gordon Fraser}
\affiliation{%
  \institution{Chair of Software Engineering II, University of Passau}
  \city{Passau}
  \country{Germany}
}
\email{gordon.fraser@uni-passau.de}

%\begin{teaserfigure}

%\end{teaserfigure}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
%\renewcommand{\shortauthors}{Anonymous et al.}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
TBD
\end{abstract}

\maketitle

\section{Introduction}

\section{\EVOSUITE}

\section{Tool Setup}

\section{Benchmark Results}

\section{Conclusion}

\bibliographystyle{ACM-Reference-Format}
\bibliography{papers}

\end{document}

### 2020-03-24 papers/sbst20/main.tex
Fix José name
Updated Jose's affliation and email.
Add table

@@
 %\usepackage{hyperref}
-\usepackage{color}
+\usepackage{xspace}
+\usepackage{xcolor,colortbl}
 %\usepackage[usenames,dvipsnames,]{xcolor}
 %\usepackage{soul}
-\usepackage{xspace}
-\usepackage{boxedminipage}
-\usepackage{alltt}
+%\usepackage{boxedminipage}
+%\usepackage{alltt}
 \usepackage{multirow}
-\usepackage{paralist}
-\usepackage{amsmath}
+%\usepackage{paralist}
+%\usepackage{amsmath}
 \usepackage{balance}
@@
 
-\author{Jose Campos}
+\author{Jos\'e Campos}
 %\email{a.panichella@tudelft.nl}
@@
   \institution{LASIGE, Faculdade de Ci\^encias \\ Universidade de Lisboa}
-  \state{Portugal}
+  \city{Lisboa}
+  \country{Portugal}
 }
-%\email{webmaster@marysville-ohio.com}
+\email{jcmcampos@fc.ul.pt}
 
@@
 
+\begin{table}[!h]
+\renewcommand{\arraystretch}{1.3}
+\caption{Classification of the \EVOSUITE unit test generation
+  tool}\label{tool-description}
+\resizebox{1.0\columnwidth}{!}{  
+\begin{tabular}{|l|p{5cm}|}
+  \hline
+  \multicolumn{2}{|l|}{Prerequisites} \\
+  \hline
+  Static or dynamic &  Dynamic testing at the Java class level\\
+  Software Type &  Java classes\\
+  Lifecycle phase&  Unit testing for Java programs\\
+  Environment&  All Java development environments \\
+  Knowledge required & JUnit unit testing for Java\\
+  Experience required &  Basic unit testing knowledge\\
+ \hline
+  \multicolumn{2}{|l|}{Input and Output of the tool} \\
+  \hline
+ Input & Bytecode of the target class and dependencies \\
+\hline
+Output&  JUnit 4 test cases\\
+
+  \hline
+  \multicolumn{2}{|l|}{Operation} \\
+  \hline
+  Interaction &  Through the command line, and plugins for IntelliJ, Maven and Eclipse\\
+  User guidance &  Manual verification of assertions for functional faults\\
+  Source of information &  http://www.evosuite.org \\
+  Maturity&  Mature research prototype, under development\\
+  Technology behind the tool & Search-based testing / many-objective optimization \\
+\hline
+  \multicolumn{2}{|l|}{Obtaining the tool and information} \\
+  \hline
+License & Lesser GPL V.3\\
+Cost & Open source\\
+Support & None \\
+\hline
+\hline
+  \multicolumn{2}{|l|}{Does there exist empirical evidence about} \\
+  \hline
+  Effectiveness and Scalability & See~\cite{GoA_TSE12,fraser2014large} \\
+%Completeness & \\
+%Effectiveness & \\
+%Efficiency & \\
+%Defect types & \\
+%Scalability & \\
+%Comprehensibility & \\
+%Learnability & \\
+%Subjective satisfaction & \\
+%Other & \\
+\hline
+\end{tabular}\vspace{-1em}
+}
+\end{table}
+
 \section{Tool Setup}
@@
 
-\section{Conclusion}
+\begin{table*}[t]
+  \centering
+  \caption{\label{table:results}Detailed results of \EVOSUITE on the
+    SBST benchmark classes.}
+\vspace{-1em}
+\resizebox{0.8\textwidth}{!}{  
+\input{mainTable.tex}
+}	
+\end{table*}
+
+\section{Conclusions}
 

### 2020-03-24 papers/sbst20/mainTable.tex
Add table

\begin{tabular}{ ll rr rr}\toprule 
 \multirow{2}{1in}{Benchmark} & \multirow{2}{1in}{Java Class} &  \multicolumn{2}{c}{Branch Coverage} &  \multicolumn{2}{c}{Mutation Score}\\\cmidrule(lr){3-4}\cmidrule(lr){5-6} 
 & & 60s & 180s & 60s & 180s \\ 
\midrule 
FESCAR-10  &  com.alibaba.fescar.core.model.BranchType & 80.0\% & 90.0\% & 80.0\% & 90.0\%\\ 
FESCAR-12  &  com.alibaba.fescar.core.rpc.netty.RpcServerHandler & 87.5\% & 87.5\% & 100.0\% & 100.0\%\\ 
FESCAR-13  &  com.alibaba.fescar.core.exception.TransactionExceptionCode & 100.0\% & 100.0\% & 100.0\% & 100.0\%\\ 
FESCAR-15  &  com.alibaba.fescar.core.rpc.netty.RpcServer & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
FESCAR-17  &  com.alibaba.fescar.core.protocol.transaction.GlobalBeginResponse & 100.0\% & 100.0\% & 90.0\% & 90.0\%\\ 
FESCAR-2  &  com.alibaba.fescar.core.service.ServiceManagerStaticConfigImpl & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
FESCAR-23  &  com.alibaba.fescar.core.protocol.MergeResultMessage & 76.4\% & 50.0\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
FESCAR-25  &  com.alibaba.fescar.core.rpc.netty.RmMessageListener & 62.5\% & 48.8\% & 22.2\% & 17.8\%\\ 
FESCAR-28  &  com.alibaba.fescar.core.rpc.ClientType & 90.0\% & 100.0\% & 90.0\% & 100.0\%\\ 
FESCAR-32  &  com.alibaba.fescar.core.protocol.transaction.BranchRegisterRequest & 94.4\% & 87.5\% & 95.2\% & 78.3\%\\ 
FESCAR-33  &  com.alibaba.fescar.core.model.GlobalStatus & 100.0\% & 100.0\% & 100.0\% & 100.0\%\\ 
FESCAR-34  &  com.alibaba.fescar.core.protocol.ResultCode & 90.0\% & 100.0\% & 90.0\% & 100.0\%\\ 
FESCAR-37  &  com.alibaba.fescar.core.rpc.RpcContext & 86.8\% & 91.2\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
FESCAR-41  &  com.alibaba.fescar.core.rpc.netty.RmRpcClient & 2.0\% & 2.0\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 2.4\%\\ 
FESCAR-42  &  com.alibaba.fescar.core.rpc.DefaultServerMessageListenerImpl & 11.8\% & 27.1\% & 12.1\% & 25.4\%\\ 
FESCAR-5  &  com.alibaba.fescar.core.protocol.MessageFuture & 96.0\% & 98.0\% & 99.2\% & 100.0\%\\ 
FESCAR-6  &  com.alibaba.fescar.core.rpc.netty.TmRpcClient & 2.7\% & 2.7\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 2.7\%\\ 
FESCAR-7  &  com.alibaba.fescar.core.rpc.netty.MessageCodecHandler & 73.3\% & 77.2\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
FESCAR-8  &  com.alibaba.fescar.core.rpc.netty.NettyPoolableFactory & 50.8\% & 57.5\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
FESCAR-9  &  com.alibaba.fescar.core.protocol.transaction.GlobalBeginRequest & 100.0\% & 100.0\% & 99.1\% & 98.2\%\\ 
GUAVA-102  &  com.google.common.collect.LinkedListMultimap & 12.9\% & 11.6\% & 19.2\% & 14.8\%\\ 
GUAVA-110  &  com.google.common.collect.LexicographicalOrdering & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 7.5\% & 0.6\% & 15.0\%\\ 
GUAVA-128  &  com.google.common.base.Throwables & 75.8\% & 25.3\% & 81.0\% & 26.8\%\\ 
GUAVA-129  &  com.google.common.collect.SparseImmutableTable & 37.5\% & 42.5\% & 35.0\% & 43.8\%\\ 
GUAVA-159  &  com.google.common.primitives.ParseRequest & 100.0\% & 100.0\% & 50.0\% & 50.0\%\\ 
GUAVA-169  &  com.google.common.math.LongMath & 94.2\% & 85.3\% & 99.2\% & 89.3\%\\ 
GUAVA-177  &  com.google.common.primitives.Doubles & 99.3\% & 99.3\% & 100.0\% & 100.0\%\\ 
GUAVA-181  &  com.google.common.primitives.SignedBytes & 100.0\% & 100.0\% & 100.0\% & 100.0\%\\ 
GUAVA-184  &  com.google.thirdparty.publicsuffix.PublicSuffixType & 100.0\% & 100.0\% & 100.0\% & 100.0\%\\ 
GUAVA-196  &  com.google.common.io.Closeables & 77.5\% & 75.0\% & 88.0\% & 88.0\%\\ 
GUAVA-2  &  com.google.common.collect.MinMaxPriorityQueue & 6.4\% & 11.1\% & 16.5\% & 19.2\%\\ 
GUAVA-206  &  com.google.common.collect.ImmutableEnumSet & 23.6\% & 24.5\% & 7.1\% & 7.6\%\\ 
GUAVA-212  &  com.google.common.net.MediaType & 77.6\% & 83.0\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
GUAVA-22  &  com.google.common.graph.Graphs & 51.8\% & 47.3\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
GUAVA-224  &  com.google.common.primitives.UnsignedLongs & 100.0\% & 90.0\% & 100.0\% & 90.0\%\\ 
GUAVA-240  &  com.google.common.collect.FilteredMultimapValues & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 5.0\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
GUAVA-39  &  com.google.common.collect.TreeMultiset & 18.6\% & 27.9\% & 19.5\% & 31.3\%\\ 
GUAVA-47  &  com.google.common.collect.FilteredEntryMultimap & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 0.7\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 0.4\%\\ 
GUAVA-90  &  com.google.common.io.FileBackedOutputStream & 98.1\% & 90.0\% & 98.0\% & 89.3\%\\ 
GUAVA-95  &  com.google.common.collect.ComparatorOrdering & 12.5\% & 30.0\% & 18.8\% & 31.2\%\\ 
PDFBOX-117  &  org.apache.pdfbox.filter.Predictor & 83.9\% & 91.0\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 28.6\%\\ 
PDFBOX-127  &  org.apache.pdfbox.pdfparser.PDFObjectStreamParser & 37.1\% & 43.6\% & 44.4\% & 50.6\%\\ 
PDFBOX-130  &  org.apache.pdfbox.pdmodel.interactive.digitalsignature.visible.PDVisibleSignDesigner & 1.7\% & 1.7\% & 1.5\% & 2.5\%\\ 
PDFBOX-157  &  org.apache.pdfbox.pdmodel.font.PDType1Font & 0.4\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
PDFBOX-198  &  org.apache.pdfbox.pdmodel.fdf.FDFAnnotationLine & 32.4\% & 32.7\% & 5.5\% & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
PDFBOX-214  &  org.apache.pdfbox.pdfparser.EndstreamOutputStream & 99.2\% & 90.0\% & 48.0\% & 40.0\%\\ 
PDFBOX-22  &  org.apache.pdfbox.pdmodel.fdf.FDFAnnotationCaret & 64.3\% & 64.3\% & 10.5\% & 31.4\%\\ 
PDFBOX-220  &  org.apache.pdfbox.filter.JPXFilter & 7.7\% & 7.3\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
PDFBOX-229  &  org.apache.pdfbox.util.XMLUtil & 52.5\% & 60.0\% & 10.7\% & 13.6\%\\ 
PDFBOX-234  &  org.apache.pdfbox.pdmodel.interactive.action.PDActionSound & 88.9\% & 87.8\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 20.0\%\\ 
PDFBOX-235  &  org.apache.pdfbox.pdmodel.font.PDTrueTypeFontEmbedder & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
PDFBOX-26  &  org.apache.pdfbox.pdmodel.encryption.SecurityProvider & 100.0\% & 100.0\% & 100.0\% & 90.0\%\\ 
PDFBOX-265  &  org.apache.pdfbox.pdmodel.font.PDType3Font & 42.3\% & 52.0\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
PDFBOX-278  &  org.apache.pdfbox.pdfwriter.ContentStreamWriter & 96.7\% & 96.3\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
PDFBOX-285  &  org.apache.pdfbox.pdmodel.interactive.digitalsignature.PDSignature & 89.5\% & 95.5\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
PDFBOX-40  &  org.apache.pdfbox.pdmodel.font.PDCIDFontType2 & 45.1\% & 46.6\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
PDFBOX-62  &  org.apache.pdfbox.rendering.PageDrawer & 1.2\% & 4.2\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
PDFBOX-8  &  org.apache.pdfbox.pdmodel.font.FileSystemFontProvider & 34.2\% & 35.8\% & 41.9\% & 52.2\%\\ 
PDFBOX-83  &  org.apache.pdfbox.contentstream.operator.text.SetTextRenderingMode & 92.5\% & 100.0\% & 82.5\% & 87.5\%\\ 
PDFBOX-91  &  org.apache.pdfbox.pdmodel.documentinterchange.taggedpdf.PDArtifactMarkedContent & 71.2\% & 92.5\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
SPOON-105  &  spoon.support.compiler.jdt.PositionBuilder & 7.8\% & 3.9\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
SPOON-155  &  spoon.reflect.visitor.filter.AllMethodsSameSignatureFunction & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 1.2\% & 0.7\% & 3.2\%\\ 
SPOON-16  &  spoon.reflect.path.CtElementPathBuilder & 8.0\% & 9.0\% & 10.3\% & 6.4\%\\ 
SPOON-169  &  spoon.reflect.visitor.ImportScannerImpl & 0.1\% & 4.7\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 1.3\%\\ 
SPOON-20  &  spoon.support.reflect.reference.CtLocalVariableReferenceImpl & 14.0\% & 18.0\% & 3.3\% & 13.3\%\\ 
SPOON-211  &  spoon.reflect.path.impl.CtRolePathElement & 6.2\% & 10.3\% & 6.2\% & 11.2\%\\ 
SPOON-25  &  spoon.pattern.internal.ValueConvertorImpl & 1.2\% & 3.1\% & 0.7\% & 4.3\%\\ 
SPOON-253  &  spoon.pattern.internal.parameter.MapParameterInfo & 72.5\% & 73.8\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
SPOON-32  &  spoon.MavenLauncher & 11.2\% & 12.5\% & 6.0\% & 6.7\%\\ 
SPOON-65  &  spoon.support.DefaultCoreFactory & 5.9\% & 8.9\% & 0.1\% & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
\midrule 
Average &  &  50.8\% &  51.7\% &  32.6\% &  33.8\%\\ 
\bottomrule 
\end{tabular}

### 2020-03-24 papers/sbst20/r_files/analyze.R

@@ -1,0 +1,261 @@
+#tool,benchmark,class,run,preparationTime,generationTime,executionTime,testcaseNumber,
+#uncompilableNumber,brokenTests,failTests,linesTotal,linesCovered,linesCoverageRatio,
+#conditionsTotal,conditionsCovered,conditionsCoverageRatio,mutantsTotal,mutantsCovered,
+#mutantsCoverageRatio,mutantsKilled,mutantsKillRatio,mutantsAlive,timeBudget,totalTestClasses
+
+library(stringr)
+
+FILE <- "../data/single_transcript_without_question_mark.csv"
+
+benchmarks <- sort(unique(read.csv("../data/benchmarks.txt", header=T)$benchmark))
+
+mainTable <- function(){
+
+  dt <- read.csv(FILE,sep=",",dec=".",header=T) #,colClasses=cols)
+
+  TABLE = paste("../mainTable.tex",sep="")
+  unlink(TABLE)
+  sink(TABLE, append=TRUE, split=TRUE)
+
+  cat("\\begin{tabular}{ ll rr rr}\\toprule","\n")
+  cat(" \\multirow{2}{1in}{Benchmark} & \\multirow{2}{1in}{Java Class} &  \\multicolumn{2}{c}{Branch Coverage} &  \\multicolumn{2}{c}{Mutation Score}\\\\\\cmidrule(lr){3-4}\\cmidrule(lr){5-6} \n")
+  cat(" & & 60s & 180s & 60s & 180s \\\\ \n" )
+  cat("\\midrule","\n")
+
+  times <- c(60, 180) # sort(unique(dt$timeBudget))
+  classes <- sort(unique(dt$class))
+
+  for(benchmark in benchmarks) {
+  #for(class in classes){
+
+    mask = dt$tool=="evosuite" & dt$benchmark==benchmark & dt$preparationTime != "?"
+
+    cat(benchmark, " & ", as.character(unique(dt$class[ dt$benchmark==benchmark ])))
+
+    #cat(class)
+
+    for(t in times){
+      cov <-  as.numeric(as.character(dt$conditionsCoverageRatio[mask & dt$timeBudget==t]))
+      cat(" & ", getColouredCell(mean(cov)),sep="")
+    }
+    for(t in times){
+      score <- as.numeric(as.character(dt$mutantsKillRatio[mask & dt$timeBudget==t]))
[…]

### 2020-03-25 papers/sbst20/main.tex
Attempt to explain 0% coverage and 0% mutation score.

@@
 
+%% FESCAR-15 0% coverage 0% mutation score
+
+\subsubsection*{FESCAR-15} According to the \texttt{transcript.csv} file, it
+seems that the generated test cases do cover some lines of code but no
+branches/conditions.  Looking at the \texttt{logs.log}, \EVOSUITE also reported
+0\% coverage, however there are not any issues in any log file.
+
+%% FESCAR-2 0% coverage 0% mutation score
+
+\subsubsection*{FESCAR-2} No clue.  \EVOSUITE does report some coverage at the
+end of the \texttt{logs.log} file, but somehow (and according to JaCoCo) the
+generated test suite does not cover any branch.
+
+%% FESCAR-37 86.8% coverage 0% mutation score
+
+\subsubsection*{FESCAR-37} The classpath is incomplete as there is a
+\texttt{java.lang.ClassNotFoundException: io.netty.channel.Channel}.
+
+%% GUAVA-110 0% coverage 0.6% mutation score
+
+\subsubsection*{GUAVA-110} No clue.
+
+%% FESCAR-7 73.3% coverage 0% mutation score
+%% GUAVA-212 77.6% coverage 0% mutation score
+%% GUAVA-22 51.8% coverage 0% mutation score
+%% PDFBOX-265 51.8% coverage 0% mutation score
+
+\subsubsection*{GUAVA-212, GUAVA-22, PDFBOX-265, PDFBOX-278, PDFBOX-285,
+PDFBOX-40, PDFBOX-91} The mutation analysis failed due to a
+\texttt{java.util.concurrent.ExecutionException} thrown by the experimental
+infrastructure.
+
+%% PDFBOX-62 1.2% coverage 0% mutation score
+
+\subsubsection*{PDFBOX-62} \EVOSUITE crashed due to some Mocking stuff.
+
+%% SPOON
+
+\subsubsection*{SPOON} There is no \texttt{logs.log} file to check \EVOSUITE's
+log messages.  There is any test suite for any SPOON
+class.  The reason might be due to
+\texttt{java.io.IOException: Not a valid directory name: /var/benchmarks/projects/spoon-core-7.2.0/src/main/java}.
+in the \texttt{log\_detailed.txt} file.  Also, all \texttt{transcript.csv} are
+empty.  Thus, it seems the experimental infrastructure do not even attempt to
+generate test cases for any SPOON class.  Question: how did \EVOSUITE achieved
+a 72.5\% coverage for, e.g., SPOON-253 if there is no test suite or even a valid
+attempt?
+
 \section{Conclusions}

### 2020-03-25 papers/sbst20/main.tex
Fix.

@@
 \subsubsection*{GUAVA-212, GUAVA-22, PDFBOX-265, PDFBOX-278, PDFBOX-285,
-PDFBOX-40, PDFBOX-91} The mutation analysis failed due to a
+PDFBOX-40, PDFBOX-91, PDFBOX-62} The mutation analysis failed due to a
 \texttt{java.util.concurrent.ExecutionException} thrown by the experimental
@@
 
-%% PDFBOX-62 1.2% coverage 0% mutation score
+%% PDFBOX-235 0% coverage 0% mutation score
 
-\subsubsection*{PDFBOX-62} \EVOSUITE crashed due to some Mocking stuff.
+\subsubsection*{PDFBOX-235} \EVOSUITE crashed due to some Mocking stuff.
 

### 2020-03-25 papers/sbst20/main.tex
Spoon results are in another zip file.

@@
 \subsubsection*{GUAVA-212, GUAVA-22, PDFBOX-265, PDFBOX-278, PDFBOX-285,
-PDFBOX-40, PDFBOX-91, PDFBOX-62} The mutation analysis failed due to a
-\texttt{java.util.concurrent.ExecutionException} thrown by the experimental
-infrastructure.
+PDFBOX-40, PDFBOX-91, PDFBOX-62, SPOON-105, SPOON-253} The mutation analysis
+failed due to a \texttt{java.util.concurrent.ExecutionException} thrown by the
+experimental infrastructure.
 
 %% PDFBOX-235 0% coverage 0% mutation score
+%% SPOON-155 0% coverage 0% mutation score
 
-\subsubsection*{PDFBOX-235} \EVOSUITE crashed due to some Mocking stuff.
-
-%% SPOON
-
-\subsubsection*{SPOON} There is no \texttt{logs.log} file to check \EVOSUITE's
-log messages.  There is any test suite for any SPOON
-class.  The reason might be due to
-\texttt{java.io.IOException: Not a valid directory name: /var/benchmarks/projects/spoon-core-7.2.0/src/main/java}.
-in the \texttt{log\_detailed.txt} file.  Also, all \texttt{transcript.csv} are
-empty.  Thus, it seems the experimental infrastructure do not even attempt to
-generate test cases for any SPOON class.  Question: how did \EVOSUITE achieved
-a 72.5\% coverage for, e.g., SPOON-253 if there is no test suite or even a valid
-attempt?
+\subsubsection*{PDFBOX-235, SPOON-105} \EVOSUITE crashed due to some Mocking stuff.
 

### 2020-03-29 papers/sbst20/main.tex
Fixed id.
Extending the explanatioon for Fescar 15

@@
 branches/conditions.  Looking at the \texttt{logs.log}, \EVOSUITE also reported
-0\% coverage, however there are not any issues in any log file.
+0\% coverage and we could not find any issues in any log file. 
+For further investigation, we ran \EVOSUITE as stand-alone tool (i.e., wot using the benchmark infrastructure but it was still not capable of covering any line.
+Through manual investigation, we notice that the CUT manage objects of the class \texttt{ScheduledExecutorService} and \textit{threads}.
+Generating tests for CUTs that produce or manage threads is challenging and a well-known open problem in the literature~\cite{FrA13a}.
+\textcolor{red}{Annibale: does EvoSuite allow to generate threads within the scope of the generated tests? If I am not mistaken, it does not for security reasons. Should we mention it?
+}
 
@@
 
-\subsubsection*{PDFBOX-235, SPOON-105} \EVOSUITE crashed due to some Mocking stuff.
+\subsubsection*{PDFBOX-235, SPOON-155} \EVOSUITE crashed due to some Mocking stuff.
 

### 2020-03-29 papers/sbst20/mainTable.tex
Adding line coverage

@@
-\begin{tabular}{ ll rr rr}\toprule 
- \multirow{2}{1in}{Benchmark} & \multirow{2}{1in}{Java Class} &  \multicolumn{2}{c}{Branch Coverage} &  \multicolumn{2}{c}{Mutation Score}\\\cmidrule(lr){3-4}\cmidrule(lr){5-6} 
- & & 60s & 180s & 60s & 180s \\ 
+\begin{tabular}{ ll rr rr rr}\toprule 
+ \multirow{2}{1in}{Benchmark} & \multirow{2}{1in}{Java Class} &  \multicolumn{2}{c}{Line Coverage} &  \multicolumn{2}{c}{Branch Coverage} &  \multicolumn{2}{c}{Mutation Score}\\\cmidrule(lr){3-4}\cmidrule(lr){5-6} \cmidrule(lr){7-8}
+ & & 60s & 180s & 60s & 180s & 60s & 180s \\ 
 \midrule 
-FESCAR-10  &  com.alibaba.fescar.core.model.BranchType & 80.0\% & 90.0\% & 80.0\% & 90.0\%\\ 
-FESCAR-12  &  com.alibaba.fescar.core.rpc.netty.RpcServerHandler & 87.5\% & 87.5\% & 100.0\% & 100.0\%\\ 
-FESCAR-13  &  com.alibaba.fescar.core.exception.TransactionExceptionCode & 100.0\% & 100.0\% & 100.0\% & 100.0\%\\ 
-FESCAR-15  &  com.alibaba.fescar.core.rpc.netty.RpcServer & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\
-FESCAR-17  &  com.alibaba.fescar.core.protocol.transaction.GlobalBeginResponse & 100.0\% & 100.0\% & 90.0\% & 90.0\%\\ 
-FESCAR-2  &  com.alibaba.fescar.core.service.ServiceManagerStaticConfigImpl & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\
-FESCAR-23  &  com.alibaba.fescar.core.protocol.MergeResultMessage & 76.4\% & 50.0\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
-FESCAR-25  &  com.alibaba.fescar.core.rpc.netty.RmMessageListener & 62.5\% & 48.8\% & 22.2\% & 17.8\%\\ 
-FESCAR-28  &  com.alibaba.fescar.core.rpc.ClientType & 90.0\% & 100.0\% & 90.0\% & 100.0\%\\ 
-FESCAR-32  &  com.alibaba.fescar.core.protocol.transaction.BranchRegisterRequest & 94.4\% & 87.5\% & 95.2\% & 78.3\%\\ 
-FESCAR-33  &  com.alibaba.fescar.core.model.GlobalStatus & 100.0\% & 100.0\% & 100.0\% & 100.0\%\\ 
-FESCAR-34  &  com.alibaba.fescar.core.protocol.ResultCode & 90.0\% & 100.0\% & 90.0\% & 100.0\%\\ 
-FESCAR-37  &  com.alibaba.fescar.core.rpc.RpcContext & 86.8\% & 91.2\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
-FESCAR-41  &  com.alibaba.fescar.core.rpc.netty.RmRpcClient & 2.0\% & 2.0\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 2.4\%\\ 
-FESCAR-42  &  com.alibaba.fescar.core.rpc.DefaultServerMessageListenerImpl & 11.8\% & 27.1\% & 12.1\% & 25.4\%\\ 
-FESCAR-5  &  com.alibaba.fescar.core.protocol.MessageFuture & 96.0\% & 98.0\% & 99.2\% & 100.0\%\\ 
-FESCAR-6  &  com.alibaba.fescar.core.rpc.netty.TmRpcClient & 2.7\% & 2.7\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 2.7\%\\ 
-FESCAR-7  &  com.alibaba.fescar.core.rpc.netty.MessageCodecHandler & 73.3\% & 77.2\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
-FESCAR-8  &  com.alibaba.fescar.core.rpc.netty.NettyPoolableFactory & 50.8\% & 57.5\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
-FESCAR-9  &  com.alibaba.fescar.core.protocol.transaction.GlobalBeginRequest & 100.0\% & 100.0\% & 99.1\% & 98.2\%\\ 
-GUAVA-102  &  com.google.common.collect.LinkedListMultimap & 12.9\% & 11.6\% & 19.2\% & 14.8\%\\ 
-GUAVA-110  &  com.google.common.collect.LexicographicalOrdering & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 7.5\% & 0.6\% & 15.0\%\\ 
-GUAVA-128  &  com.google.common.base.Throwables & 75.8\% & 25.3\% & 81.0\% & 26.8\%\\ 
-GUAVA-129  &  com.google.common.collect.SparseImmutableTable & 37.5\% & 42.5\% & 35.0\% & 43.8\%\\ 
-GUAVA-159  &  com.google.common.primitives.ParseRequest & 100.0\% & 100.0\% & 50.0\% & 50.0\%\\ 
-GUAVA-169  &  com.google.common.math.LongMath & 94.2\% & 85.3\% & 99.2\% & 89.3\%\\ 
-GUAVA-177  &  com.google.common.primitives.Doubles & 99.3\% & 99.3\% & 100.0\% & 100.0\%\\ 
-GUAVA-181  &  com.google.common.primitives.SignedBytes & 100.0\% & 100.0\% & 100.0\% & 100.0\%\\ 
-GUAVA-184  &  com.google.thirdparty.publicsuffix.PublicSuffixType & 100.0\% & 100.0\% & 100.0\% & 100.0\%\\ 
-GUAVA-196  &  com.google.common.io.Closeables & 77.5\% & 75.0\% & 88.0\% & 88.0\%\\ 
-GUAVA-2  &  com.google.common.collect.MinMaxPriorityQueue & 6.4\% & 11.1\% & 16.5\% & 19.2\%\\ 
-GUAVA-206  &  com.google.common.collect.ImmutableEnumSet & 23.6\% & 24.5\% & 7.1\% & 7.6\%\\ 
-GUAVA-212  &  com.google.common.net.MediaType & 77.6\% & 83.0\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
-GUAVA-22  &  com.google.common.graph.Graphs & 51.8\% & 47.3\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
-GUAVA-224  &  com.google.common.primitives.UnsignedLongs & 100.0\% & 90.0\% & 100.0\% & 90.0\%\\ 
-GUAVA-240  &  com.google.common.collect.FilteredMultimapValues & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 5.0\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\
-GUAVA-39  &  com.google.common.collect.TreeMultiset & 18.6\% & 27.9\% & 19.5\% & 31.3\%\\ 
-GUAVA-47  &  com.google.common.collect.FilteredEntryMultimap & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 0.7\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 0.4\%\\ 
-GUAVA-90  &  com.google.common.io.FileBackedOutputStream & 98.1\% & 90.0\% & 98.0\% & 89.3\%\\ 
-GUAVA-95  &  com.google.common.collect.ComparatorOrdering & 12.5\% & 30.0\% & 18.8\% & 31.2\%\\ 
-PDFBOX-117  &  org.apache.pdfbox.filter.Predictor & 83.9\% & 91.0\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 28.6\%\\ 
-PDFBOX-127  &  org.apache.pdfbox.pdfparser.PDFObjectStreamParser & 37.1\% & 43.6\% & 44.4\% & 50.6\%\\ 
-PDFBOX-130  &  org.apache.pdfbox.pdmodel.interactive.digitalsignature.visible.PDVisibleSignDesigner & 1.7\% & 1.7\% & 1.5\% & 2.5\%\\ 
-PDFBOX-157  &  org.apache.pdfbox.pdmodel.font.PDType1Font & 0.4\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\
-PDFBOX-198  &  org.apache.pdfbox.pdmodel.fdf.FDFAnnotationLine & 32.4\% & 32.7\% & 5.5\% & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
-PDFBOX-214  &  org.apache.pdfbox.pdfparser.EndstreamOutputStream & 99.2\% & 90.0\% & 48.0\% & 40.0\%\\ 
-PDFBOX-22  &  org.apache.pdfbox.pdmodel.fdf.FDFAnnotationCaret & 64.3\% & 64.3\% & 10.5\% & 31.4\%\\ 
-PDFBOX-220  &  org.apache.pdfbox.filter.JPXFilter & 7.7\% & 7.3\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
-PDFBOX-229  &  org.apache.pdfbox.util.XMLUtil & 52.5\% & 60.0\% & 10.7\% & 13.6\%\\ 
-PDFBOX-234  &  org.apache.pdfbox.pdmodel.interactive.action.PDActionSound & 88.9\% & 87.8\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 20.0\%\\ 
-PDFBOX-235  &  org.apache.pdfbox.pdmodel.font.PDTrueTypeFontEmbedder & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\
-PDFBOX-26  &  org.apache.pdfbox.pdmodel.encryption.SecurityProvider & 100.0\% & 100.0\% & 100.0\% & 90.0\%\\ 
-PDFBOX-265  &  org.apache.pdfbox.pdmodel.font.PDType3Font & 42.3\% & 52.0\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
-PDFBOX-278  &  org.apache.pdfbox.pdfwriter.ContentStreamWriter & 96.7\% & 96.3\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
-PDFBOX-285  &  org.apache.pdfbox.pdmodel.interactive.digitalsignature.PDSignature & 89.5\% & 95.5\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\
-PDFBOX-40  &  org.apache.pdfbox.pdmodel.font.PDCIDFontType2 & 45.1\% & 46.6\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
-PDFBOX-62  &  org.apache.pdfbox.rendering.PageDrawer & 1.2\% & 4.2\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
-PDFBOX-8  &  org.apache.pdfbox.pdmodel.font.FileSystemFontProvider & 34.2\% & 35.8\% & 41.9\% & 52.2\%\\ 
-PDFBOX-83  &  org.apache.pdfbox.contentstream.operator.text.SetTextRenderingMode & 92.5\% & 100.0\% & 82.5\% & 87.5\%\\ 
-PDFBOX-91  &  org.apache.pdfbox.pdmodel.documentinterchange.taggedpdf.PDArtifactMarkedContent & 71.2\% & 92.5\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\
-SPOON-105  &  spoon.support.compiler.jdt.PositionBuilder & 7.8\% & 3.9\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
-SPOON-155  &  spoon.reflect.visitor.filter.AllMethodsSameSignatureFunction & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 1.2\% & 0.7\% & 3.2\%\\ 
-SPOON-16  &  spoon.reflect.path.CtElementPathBuilder & 8.0\% & 9.0\% & 10.3\% & 6.4\%\\ 
-SPOON-169  &  spoon.reflect.visitor.ImportScannerImpl & 0.1\% & 4.7\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 1.3\%\\ 
-SPOON-20  &  spoon.support.reflect.reference.CtLocalVariableReferenceImpl & 14.0\% & 18.0\% & 3.3\% & 13.3\%\\ 
-SPOON-211  &  spoon.reflect.path.impl.CtRolePathElement & 6.2\% & 10.3\% & 6.2\% & 11.2\%\\ 
-SPOON-25  &  spoon.pattern.internal.ValueConvertorImpl & 1.2\% & 3.1\% & 0.7\% & 4.3\%\\ 
-SPOON-253  &  spoon.pattern.internal.parameter.MapParameterInfo & 72.5\% & 73.8\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
-SPOON-32  &  spoon.MavenLauncher & 11.2\% & 12.5\% & 6.0\% & 6.7\%\\ 
-SPOON-65  &  spoon.support.DefaultCoreFactory & 5.9\% & 8.9\% & 0.1\% & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
+FESCAR-10  &  com.alibaba.fescar.core.model.BranchType & 80.0\% & 90.0\% & 80.0\% & 90.0\% & 80.0\% & 90.0\%\\ 
+FESCAR-12  &  com.alibaba.fescar.core.rpc.netty.RpcServerHandler & 100.0\% & 100.0\% & 87.5\% & 87.5\% & 100.0\% & 100.0\%\\ 
+FESCAR-13  &  com.alibaba.fescar.core.exception.TransactionExceptionCode & 100.0\% & 100.0\% & 100.0\% & 100.0\% & 100.0\% & 100.0\%\\ 
+FESCAR-15  &  com.alibaba.fescar.core.rpc.netty.RpcServer & 0.8\% & 0.7\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\
+FESCAR-17  &  com.alibaba.fescar.core.protocol.transaction.GlobalBeginResponse & 99.4\% & 99.4\% & 100.0\% & 100.0\% & 90.0\% & 90.0\%\\ 
+FESCAR-2  &  com.alibaba.fescar.core.service.ServiceManagerStaticConfigImpl & 20.5\% & 25.8\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\
+FESCAR-23  &  com.alibaba.fescar.core.protocol.MergeResultMessage & 90.5\% & 60.5\% & 76.4\% & 50.0\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\
+FESCAR-25  &  com.alibaba.fescar.core.rpc.netty.RmMessageListener & 46.9\% & 37.5\% & 62.5\% & 48.8\% & 22.2\% & 17.8\%\\ 
+FESCAR-28  &  com.alibaba.fescar.core.rpc.ClientType & 90.0\% & 100.0\% & 90.0\% & 100.0\% & 90.0\% & 100.0\%\\ 
+FESCAR-32  &  com.alibaba.fescar.core.protocol.transaction.BranchRegisterRequest & 97.7\% & 89.2\% & 94.4\% & 87.5\% & 95.2\% & 78.3\%\\ 
+FESCAR-33  &  com.alibaba.fescar.core.model.GlobalStatus & 100.0\% & 100.0\% & 100.0\% & 100.0\% & 100.0\% & 100.0\%\\ 
+FESCAR-34  &  com.alibaba.fescar.core.protocol.ResultCode & 90.0\% & 100.0\% & 90.0\% & 100.0\% & 90.0\% & 100.0\%\\ 
+FESCAR-37  &  com.alibaba.fescar.core.rpc.RpcContext & 92.4\% & 94.6\% & 86.8\% & 91.2\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
+FESCAR-41  &  com.alibaba.fescar.core.rpc.netty.RmRpcClient & 1.7\% & 1.7\% & 2.0\% & 2.0\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 2.4\%\\ 
+FESCAR-42  &  com.alibaba.fescar.core.rpc.DefaultServerMessageListenerImpl & 24.3\% & 42.6\% & 11.8\% & 27.1\% & 12.1\% & 25.4\%\\ 
+FESCAR-5  &  com.alibaba.fescar.core.protocol.MessageFuture & 98.6\% & 99.1\% & 96.0\% & 98.0\% & 99.2\% & 100.0\%\\ 
+FESCAR-6  &  com.alibaba.fescar.core.rpc.netty.TmRpcClient & 3.4\% & 3.4\% & 2.7\% & 2.7\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 2.7\%\\ 
+FESCAR-7  &  com.alibaba.fescar.core.rpc.netty.MessageCodecHandler & 76.1\% & 78.2\% & 73.3\% & 77.2\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\
+FESCAR-8  &  com.alibaba.fescar.core.rpc.netty.NettyPoolableFactory & 57.3\% & 62.0\% & 50.8\% & 57.5\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\
+FESCAR-9  &  com.alibaba.fescar.core.protocol.transaction.GlobalBeginRequest & 99.0\% & 98.3\% & 100.0\% & 100.0\% & 99.1\% & 98.2\%\\ 
+GUAVA-102  &  com.google.common.collect.LinkedListMultimap & 29.4\% & 32.3\% & 12.9\% & 11.6\% & 19.2\% & 14.8\%\\ 
+GUAVA-110  &  com.google.common.collect.LexicographicalOrdering & 3.0\% & 22.2\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 7.5\% & 0.6\% & 15.0\%\\ 
+GUAVA-128  &  com.google.common.base.Throwables & 75.1\% & 25.0\% & 75.8\% & 25.3\% & 81.0\% & 26.8\%\\ 
+GUAVA-129  &  com.google.common.collect.SparseImmutableTable & 31.9\% & 35.8\% & 37.5\% & 42.5\% & 35.0\% & 43.8\%\\ 
+GUAVA-159  &  com.google.common.primitives.ParseRequest & 100.0\% & 100.0\% & 100.0\% & 100.0\% & 50.0\% & 50.0\%\\ 
+GUAVA-169  &  com.google.common.math.LongMath & 96.2\% & 86.7\% & 94.2\% & 85.3\% & 99.2\% & 89.3\%\\ 
+GUAVA-177  &  com.google.common.primitives.Doubles & 98.7\% & 98.5\% & 99.3\% & 99.3\% & 100.0\% & 100.0\%\\ 
+GUAVA-181  &  com.google.common.primitives.SignedBytes & 100.0\% & 100.0\% & 100.0\% & 100.0\% & 100.0\% & 100.0\%\\ 
+GUAVA-184  &  com.google.thirdparty.publicsuffix.PublicSuffixType & 100.0\% & 100.0\% & 100.0\% & 100.0\% & 100.0\% & 100.0\%\\ 
+GUAVA-196  &  com.google.common.io.Closeables & 71.5\% & 70.0\% & 77.5\% & 75.0\% & 88.0\% & 88.0\%\\ 
+GUAVA-2  &  com.google.common.collect.MinMaxPriorityQueue & 13.9\% & 22.5\% & 6.4\% & 11.1\% & 16.5\% & 19.2\%\\ 
+GUAVA-206  &  com.google.common.collect.ImmutableEnumSet & 25.4\% & 26.1\% & 23.6\% & 24.5\% & 7.1\% & 7.6\%\\ 
+GUAVA-212  &  com.google.common.net.MediaType & 92.6\% & 94.3\% & 77.6\% & 83.0\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
+GUAVA-22  &  com.google.common.graph.Graphs & 53.9\% & 49.7\% & 51.8\% & 47.3\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
+GUAVA-224  &  com.google.common.primitives.UnsignedLongs & 99.3\% & 89.6\% & 100.0\% & 90.0\% & 100.0\% & 90.0\%\\ 
+GUAVA-240  &  com.google.common.collect.FilteredMultimapValues & 12.3\% & 22.7\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 5.0\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\
+GUAVA-39  &  com.google.common.collect.TreeMultiset & 30.2\% & 43.1\% & 18.6\% & 27.9\% & 19.5\% & 31.3\%\\ 
+GUAVA-47  &  com.google.common.collect.FilteredEntryMultimap & 2.6\% & 11.3\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 0.7\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 0.4\%\\ 
+GUAVA-90  &  com.google.common.io.FileBackedOutputStream & 98.9\% & 89.6\% & 98.1\% & 90.0\% & 98.0\% & 89.3\%\\ 
+GUAVA-95  &  com.google.common.collect.ComparatorOrdering & 27.5\% & 51.7\% & 12.5\% & 30.0\% & 18.8\% & 31.2\%\\ 
+PDFBOX-117  &  org.apache.pdfbox.filter.Predictor & 89.0\% & 93.5\% & 83.9\% & 91.0\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 28.6\%\\ 
+PDFBOX-127  &  org.apache.pdfbox.pdfparser.PDFObjectStreamParser & 57.5\% & 65.6\% & 37.1\% & 43.6\% & 44.4\% & 50.6\%\\ 
+PDFBOX-130  &  org.apache.pdfbox.pdmodel.interactive.digitalsignature.visible.PDVisibleSignDesigner & 7.1\% & 14.3\% & 1.7\% & 1.7\% & 1.5\% & 2.5\%\\ 
+PDFBOX-157  &  org.apache.pdfbox.pdmodel.font.PDType1Font & 2.1\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 0.4\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\
+PDFBOX-198  &  org.apache.pdfbox.pdmodel.fdf.FDFAnnotationLine & 66.4\% & 66.5\% & 32.4\% & 32.7\% & 5.5\% & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
+PDFBOX-214  &  org.apache.pdfbox.pdfparser.EndstreamOutputStream & 99.5\% & 90.0\% & 99.2\% & 90.0\% & 48.0\% & 40.0\%\\ 
+PDFBOX-22  &  org.apache.pdfbox.pdmodel.fdf.FDFAnnotationCaret & 63.9\% & 63.9\% & 64.3\% & 64.3\% & 10.5\% & 31.4\%\\ 
+PDFBOX-220  &  org.apache.pdfbox.filter.JPXFilter & 32.7\% & 32.7\% & 7.7\% & 7.3\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
+PDFBOX-229  &  org.apache.pdfbox.util.XMLUtil & 62.4\% & 69.6\% & 52.5\% & 60.0\% & 10.7\% & 13.6\%\\ 
+PDFBOX-234  &  org.apache.pdfbox.pdmodel.interactive.action.PDActionSound & 97.7\% & 96.7\% & 88.9\% & 87.8\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 20.0\%\\ 
+PDFBOX-235  &  org.apache.pdfbox.pdmodel.font.PDTrueTypeFontEmbedder & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\
+PDFBOX-26  &  org.apache.pdfbox.pdmodel.encryption.SecurityProvider & 55.8\% & 56.8\% & 100.0\% & 100.0\% & 100.0\% & 90.0\%\\ 
+PDFBOX-265  &  org.apache.pdfbox.pdmodel.font.PDType3Font & 62.4\% & 70.2\% & 42.3\% & 52.0\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
+PDFBOX-278  &  org.apache.pdfbox.pdfwriter.ContentStreamWriter & 96.8\% & 98.3\% & 96.7\% & 96.3\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\
+PDFBOX-285  &  org.apache.pdfbox.pdmodel.interactive.digitalsignature.PDSignature & 98.9\% & 99.7\% & 89.5\% & 95.5\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\
+PDFBOX-40  &  org.apache.pdfbox.pdmodel.font.PDCIDFontType2 & 57.2\% & 54.9\% & 45.1\% & 46.6\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
+PDFBOX-62  &  org.apache.pdfbox.rendering.PageDrawer & 2.3\% & 6.8\% & 1.2\% & 4.2\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
+PDFBOX-8  &  org.apache.pdfbox.pdmodel.font.FileSystemFontProvider & 45.2\% & 48.4\% & 34.2\% & 35.8\% & 41.9\% & 52.2\%\\ 
+PDFBOX-83  &  org.apache.pdfbox.contentstream.operator.text.SetTextRenderingMode & 89.3\% & 85.7\% & 92.5\% & 100.0\% & 82.5\% & 87.5\%\\ 
+PDFBOX-91  &  org.apache.pdfbox.pdmodel.documentinterchange.taggedpdf.PDArtifactMarkedContent & 91.6\% & 97.9\% & 71.2\% & 92.5\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\
+SPOON-105  &  spoon.support.compiler.jdt.PositionBuilder & 9.6\% & 5.5\% & 7.8\% & 3.9\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
+SPOON-155  &  spoon.reflect.visitor.filter.AllMethodsSameSignatureFunction & 13.0\% & 12.7\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 1.2\% & 0.7\% & 3.2\%\\ 
+SPOON-16  &  spoon.reflect.path.CtElementPathBuilder & 15.9\% & 16.1\% & 8.0\% & 9.0\% & 10.3\% & 6.4\%\\ 
+SPOON-169  &  spoon.reflect.visitor.ImportScannerImpl & 1.2\% & 10.6\% & 0.1\% & 4.7\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 1.3\%\\ 
+SPOON-20  &  spoon.support.reflect.reference.CtLocalVariableReferenceImpl & 30.0\% & 38.6\% & 14.0\% & 18.0\% & 3.3\% & 13.3\%\\ 
+SPOON-211  &  spoon.reflect.path.impl.CtRolePathElement & 16.3\% & 18.3\% & 6.2\% & 10.3\% & 6.2\% & 11.2\%\\ 
+SPOON-25  &  spoon.pattern.internal.ValueConvertorImpl & 3.0\% & 7.1\% & 1.2\% & 3.1\% & 0.7\% & 4.3\%\\ 
+SPOON-253  &  spoon.pattern.internal.parameter.MapParameterInfo & 76.8\% & 73.9\% & 72.5\% & 73.8\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\
+SPOON-32  &  spoon.MavenLauncher & 27.0\% & 30.0\% & 11.2\% & 12.5\% & 6.0\% & 6.7\%\\ 
+SPOON-65  &  spoon.support.DefaultCoreFactory & 10.7\% & 9.7\% & 5.9\% & 8.9\% & 0.1\% & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
 \midrule 
-Average &  &  50.8\% &  51.7\% &  32.6\% &  33.8\%\\ 
+Average &  &  55.9\% &  57.0\% &  50.8\% &  51.7\% &  32.6\% &  33.8\%\\ 
 \bottomrule 

### 2020-03-29 papers/sbst20/r_files/analyze.R

@@ -17,9 +17,9 @@ mainTable <- function(){
   unlink(TABLE)
   sink(TABLE, append=TRUE, split=TRUE)
 
-  cat("\\begin{tabular}{ ll rr rr}\\toprule","\n")
-  cat(" \\multirow{2}{1in}{Benchmark} & \\multirow{2}{1in}{Java Class} &  \\multicolumn{2}{c}{Branch Coverage} &  \\multicolumn{2}{c}{Mutation Score}\\\\\\cmidrule(lr){3-4}\\cmidrule(lr){5-6} \n")
-  cat(" & & 60s & 180s & 60s & 180s \\\\ \n" )
+  cat("\\begin{tabular}{ ll rr rr rr}\\toprule","\n")
+  cat(" \\multirow{2}{1in}{Benchmark} & \\multirow{2}{1in}{Java Class} &  \\multicolumn{2}{c}{Line Coverage} &  \\multicolumn{2}{c}{Branch Coverage} &  \\multicolumn{2}{c}{Mutation Score}\\\\\\cmidrule(lr){3-4}\\cmidrule(lr){5-6} \n")
+  cat(" & & 60s & 180s & 60s & 180s & 60s & 180s \\\\ \n" )
   cat("\\midrule","\n")
 
   times <- c(60, 180) # sort(unique(dt$timeBudget))
@@ -35,6 +35,11 @@ mainTable <- function(){
     #cat(class)
 
     for(t in times){
+      cov <-  as.numeric(as.character(dt$linesCoverageRatio[mask & dt$timeBudget==t]))
+      cat(" & ", getColouredCell(mean(cov)),sep="")
+    }
+    
+    for(t in times){
       cov <-  as.numeric(as.character(dt$conditionsCoverageRatio[mask & dt$timeBudget==t]))
       cat(" & ", getColouredCell(mean(cov)),sep="")
     }
@@ -47,6 +52,11 @@ mainTable <- function(){
   }
   cat("\\midrule","\n")
   cat("Average & ")
+  for(t in times){
+    cov <- as.numeric(as.character(dt$linesCoverageRatio[dt$tool=="evosuite" & dt$timeBudget==t]))
+    cat(" & ", getColouredCell(mean(cov, na.rm = TRUE)))
+  }
+  
   for(t in times){
     cov <- as.numeric(as.character(dt$conditionsCoverageRatio[dt$tool=="evosuite" & dt$timeBudget==t]))
     cat(" & ", getColouredCell(mean(cov, na.rm = TRUE)))
[…]

### 2020-03-29 papers/sbst20/main.tex
Explaining more cases

@@
 seems that the generated test cases do cover some lines of code but no
-branches/conditions.  Looking at the \texttt{logs.log}, \EVOSUITE also reported
-0\% coverage and we could not find any issues in any log file. 
+branches/conditions.  
+%Looking at the \texttt{logs.log}, \EVOSUITE also reported
+%0\% coverage and we could not find any issues in any %log file. 
 For further investigation, we ran \EVOSUITE as stand-alone tool (i.e., wot using the benchmark infrastructure but it was still not capable of covering any line.
-Through manual investigation, we notice that the CUT manage objects of the class \texttt{ScheduledExecutorService} and \textit{threads}.
+Through manual investigation, we notice that the CUT manages objects of the class \texttt{ScheduledExecutorService} and \textit{threads}.
 Generating tests for CUTs that produce or manage threads is challenging and a well-known open problem in the literature~\cite{FrA13a}.
@@
 
-\subsubsection*{FESCAR-2} No clue.  \EVOSUITE does report some coverage at the
-end of the \texttt{logs.log} file, but somehow (and according to JaCoCo) the
-generated test suite does not cover any branch.
+\subsubsection*{FESCAR-2} This CUT contains only a few branches (i.e., 14) and lines (i.e., 19).
+\EVOSUITE could generate test cases that could cover around 20\%-25\% of lines but 0\% of condition coverage.
+The generated tests cover branchless methods and the root branch of the method \texttt{lookup}, which is the only method with some conditions.
+It is worth noticing that \EVOSUITE could not complete a single generation, even with a search budget of 180s.
+The CUT is particularly expensive, and each generated test requires seconds for its execution.
+Low search budgets are thus not feasible nor recommended for this CUT.
+
+\subsubsection*{FESCAR-41, FESCAR-6} \EVOSUITE reached a very low line and branch coverage for these two CUTs, independently from the search budget.
+These CUT also manage threads, and more precisely objects of the classes \texttt{ThreadPoolExecutor} and \texttt{NamedThreadFactory}.
 
 %% FESCAR-37 86.8% coverage 0% mutation score
-
-\subsubsection*{FESCAR-37} The classpath is incomplete as there is a
-\texttt{java.lang.ClassNotFoundException: io.netty.channel.Channel}.
+%% Annibale: from the logs, I see a \texttt{java.util.concurrent.ExecutionException}.
+%% \subsubsection*{FESCAR-37} The classpath is incomplete as there is a
+%% \texttt{java.lang.}-\texttt{ClassNotFoundException:  io.netty.channel.Channel}.
 
@@
 
-\subsubsection*{GUAVA-110} No clue.
+\subsubsection*{GUAVA-110, GUAVA-240} Both classes make use of the annotation \texttt{@Nullable}.
+GUAVA-110 uses the annotation for the input parameter of the method \texttt{equals(...)}, while GUAVA-240 uses it for the methods \texttt{contains(...)} and \texttt{remove(...)}.
+The static analyzer implemented in \EVOSUITE does not handle the annotation \texttt{@Nullable} and triggers the error \textit{``Cannot find symbol''}.
+
+\subsubsection*{GUAVA-47} For this class, \EVOSUITE reached very low coverage (both line and branch) and mutation score.
+To have a better understanding of the underlying issue, we ran \EVOSUITE stand-alone.
+We notice that our tool could not generate any single test cases, never completing the initialization process (and the generation of the initial population, in particular) even with a search budget of 180s.
+A more in-depth analysis is needed to discover the root cause of the issue.
+
+\subsubsection*{PDFBOX-157} \EVOSUITE crashed in 9 out ten times with a search budget of 60s, and in 10 out of 10 runs for larger budgets.
 
@@
 
-\subsubsection*{GUAVA-212, GUAVA-22, PDFBOX-265, PDFBOX-278, PDFBOX-285,
-PDFBOX-40, PDFBOX-91, PDFBOX-62, SPOON-105, SPOON-253} The mutation analysis
+\subsubsection*{FESCAR-23, FESCAR-37, FESCAR-7, FESCAR-8, GUAVA-212, GUAVA-22, PDFBOX-265, PDFBOX-278, PDFBOX-285, PDFBOX-40, PDFBOX-91, PDFBOX-62, SPOON-105, SPOON-253} The mutation analysis
 failed due to a \texttt{java.util.concurrent.ExecutionException} thrown by the

### 2020-04-04 papers/sbst20/main.tex
Add text

@@
 \begin{abstract}
-TBD
+%
+  \EVOSUITE is a search-based tool that automatically generates
+  executable unit tests for Java code (JUnit tests).  This paper
+  summarizes the results and experiences of \EVOSUITE's participation
+  at the eighth unit testing competition at SBST 2020, where \EVOSUITE
+  achieved the highest overall score (\TOTALPOINTS points) for the
+  seventh time in eight editions of the competition.
+  %
 \end{abstract}
@@
 \section{Introduction}
+
+Automated unit test generation can support developers and testers, produce
+regression test suites, and is an enabler for dynamic program analyses. The
+annual unit test generation aims to foster research and development of
+automated unit test generators. This paper describes the results obtained by
+the \EVOSUITE test generation tool~\cite{FrA11c} in this competition. \EVOSUITE
+uses meta-heuristic search in order to evolve unit test suites with high
+coverage, and automatically produces regression oracles in the form of test
+assertions. In the 8th instance of the competition at the International
+Workshop on Search-Based Software Testing (SBST) 2020, \EVOSUITE achieved an
+overall score of \TOTALPOINTS, which was the highest among the competing and
+baseline tools. This paper describes the results obtained by the \EVOSUITE test
+generation tool in this competition.
 
@@
 
+\EVOSUITE~\cite{FrA11c} is a search-based unit test generation
+tool~\cite{GoA_TSE12}. Table~\ref{tool-description} summarizes the features of
+\EVOSUITE in the standard format of the SBST unit testing competition: Given
+just the Java classpath containing all compiled dependencies and the name of a
+class under test, \EVOSUITE automatically generates a set of JUnit test cases
+aimed at maximinizing code coverage. \EVOSUITE can be used on the command line,
+as a Maven plugin, or using plugins for the Eclipse and IntelliJ development
+environments~\cite{ICST16_Tool}.
+
+Over the course of its development, several different search algorithms have
+been evaluated, starting with a basic genetic algorithm.
+\EVOSUITE's encoding of test cases for the evolutionary search (i.e., its chromosomes) consists of variable-length sequences of Java statements (e.g., primitive statements and calls on the class under test).
+The usual search operators used in evolutionary search (e.g., selection, crossover, mutation) are adapted for this particular representation.
+%
+In the original approach, individuals of the genetic algorithm were whole test
+suites, with the optimization goal of finding a test suite that maximizes code
+coverage. This was later improved by adding an archive of
+solutions~\cite{emse_archive} to keep the search focused on uncovered goals,
+iteratively discarding covered goals and storing the tests that covered them.
+
+Recently, the \textit{Dynamic Many-Objective Sorting Algorithm} (DynaMOSA) search algorithm~\cite{dynamosa, panichella:ssbse2018}  has been shown to be the most effective approach of all the algorithms evaluated so far.
+DynaMOSA is a many-objective algorithm, where individuals of the search population are test cases, rather than test suites, and the optimization is driven by a collection of individual fitness functions, one for each coverage objective (e.g., line or branch).
+
+The fitness functions in \EVOSUITE are based on traditional heuristics for code
+coverage, such as the branch distance and the approach level
+(see~\cite{GoA_TSE12} for more details).
+%
+\EVOSUITE supports multiple different coverage criteria, which can be optimized
+for at the same time. The default configuration combines branch coverage with
+mutation testing~\cite{emse14_mutation} and other basic
+criteria~\cite{rojas2015combining}.
+%
+In order to cope with the potentially large number of coverage objectives,
+DynaMOSA prioritizes them during the search according to their structural
+dependencies in the control dependency graph. Initially the search focuses on
+coverage objectives positioned higher in the hierarchy, and the remaining
+objectives are incrementally inserted in later generations when their dominator
+requirements are covered.
+
+After the search has used up the available search budget (or alternatively, has
+achieved 100\% coverage of all coverage objectives), \EVOSUITE applies various
+post-search optimizations aimed to improve the readability of the generated
+tests~\cite{FrA11c,FrA13a}, such as minimization and addition of test assertions using mutation
+analysis~\cite{10.1109/TSE.2011.93}.
+It also checks all generated tests for compile errors (which may be the result of bugs in \EVOSUITE) or flakiness caused by non-determinism in the class under test, not covered by \EVOSUITE's extensive instrumentation.
+
+\EVOSUITE has been evaluated on open
+source as well as industrial software in terms of code
+coverage~\cite{fraser2014large,emse_archive,ea_evaluation,dynamosa},
+fault finding
+effectiveness~\cite{shamshiri2015automatically,moein2017}, and effects
+on developer productivity~\cite{TOSEM_userstudy,ISSTA15_Study} and
+software maintenance~\cite{ICST2018_Maintenance}.
+%
+\EVOSUITE has a longstanding record of success at the unit testing tool
+competition, having ranked second in the third edition of the
+competition~\cite{evosuiteAtSbst2015} and first in all the other
+editions~\cite{evosuiteAtSbst2013,evosuiteAtFittest2013,evosuiteAtSbst2016,evosuiteAtSbst2017,evosuiteAtSbst2018}. In the 2019 SBST contest, \EVOSUITE
+achieved the highest overall score of all participating tools~\cite{evosuiteAtSbst2019}, although the
+performance was inhibited by some bugs.
+
 \section{Tool Setup}
+
+Similar to the previous years, the configuration of \EVOSUITE for the 2020
+competition is largely based on its default values since these have been tuned
+extensively~\cite{arcuri2013parameter}. 
+%
+The search algorithm used was DynaMOSA~\cite{dynamosa}, optimizing for the
+default set of coverage criteria~\cite{rojas2015combining} (i.e., line
+coverage, branch coverage, branch coverage by direct method invocations, weak
+mutation testing, output coverage, exception coverage).
+%
+Other features enabled by default include the use of frequency-based weighted
+constants for seeding~\cite{sakti2015instance} as well as support for Java
+Enterprise Edition features~\cite{arcuri2016java}.
+In the case of difficult dependencies and branches that cannot be covered, \EVOSUITE can start using mock objectes once a certain percentage of the search
+budget has passed~\cite{ICST_Mocking17} .
+
+No major new features have been introduced in \EVOSUITE since the 2019 competition, but several bugs that affected \EVOSUITE's performance during the previous competition have been fixed.
+In particular, there were several problematic cases when \EVOSUITE was run using very small search budgets.
+
+The test minimization step used by \EVOSUITE is computationally expensive and
+sometimes omitted for empirical studies; in the competition we always enable
+the post-processing step of test minimization, because minimized tests are less
+likely to break or expose flakiness. However, we aimed to reduce the
+post-processing time by including all regression assertions rather than
+filtering them with mutation analysis~\cite{10.1109/TSE.2011.93}. While this
+makes test cases less readable and potentially more brittle with respect to
+future changes in the software under test, neither of these aspects is
+evaluated as part of the SBST contest.
+
+\EVOSUITE uses different phases (e.g., initialisation, search, minimization,
+assertion generation, compilation check, removal of flaky tests). Like in
+previous competitions (e.g.,~\cite{evosuiteAtSbst2016}) we allocated 50\% of
+the overall time set by the competition organisers for the search, and
+distributed the other 50\% equally to the remaining phases.
 
@@
 
+\balance
 \bibliographystyle{ACM-Reference-Format}

### 2020-04-04 papers/sbst20/main.tex
Update discussion and conclusion

@@
 
-\begin{table*}[t]
+\begin{table*}[t!]
   \centering
@@
     SBST benchmark classes.}
-\vspace{-1em}
-\resizebox{0.8\textwidth}{!}{  
+%\vspace{-1em}
+\resizebox{0.9\textwidth}{!}{  
 \input{mainTable.tex}
@@
 
+Table~\ref{table:results} summarizes the results achieved by \EVOSUITE on the competition classes and search budgets. In general, the performance of \EVOSUITE was in line with previous
+results.
+As usual, there are some noteable cases where \EVOSUITE did not perform well.
+In the following, we discuss these cases, such that future work can address open problems in automated unit test generation.
+
 %% FESCAR-15 0% coverage 0% mutation score
 
-\subsubsection*{FESCAR-15} According to the \texttt{transcript.csv} file, it
-seems that the generated test cases do cover some lines of code but no
-branches/conditions.  
+\subsubsection*{FESCAR-15} According to the results provided by the competition
+organizers, it seems that the generated test cases do cover some lines of code
+but no branches/conditions.
 %Looking at the \texttt{logs.log}, \EVOSUITE also reported
 %0\% coverage and we could not find any issues in any %log file. 
-For further investigation, we ran \EVOSUITE as stand-alone tool (i.e., wot using the benchmark infrastructure but it was still not capable of covering any line.
+For further investigation, we ran \EVOSUITE as stand-alone tool (i.e., not using the benchmark infrastructure but it was still not capable of covering any line.
 Through manual investigation, we notice that the CUT manages objects of the class \texttt{ScheduledExecutorService} and \textit{threads}.
 Generating tests for CUTs that produce or manage threads is challenging and a well-known open problem in the literature~\cite{FrA13a}.
-\textcolor{red}{Annibale: does EvoSuite allow to generate threads within the scope of the generated tests? If I am not mistaken, it does not for security reasons. Should we mention it?
-}
+\EVOSUITE does not prevent the CUT to spawn new threads, but it (1) forces the use of a wrapper class that leads to deterministic stack traces and thread names, and (2) any spawned threads are joined and removed after a test execution to ensure a clean state for successive test executions, which may consume a substantial amount of time.
 
@@
 \subsubsection*{FESCAR-2} This CUT contains only a few branches (i.e., 14) and lines (i.e., 19).
-\EVOSUITE could generate test cases that could cover around 20\%-25\% of lines but 0\% of condition coverage.
+\EVOSUITE was only able to generate test cases that cover around 20\%-25\% of lines but 0\% of condition coverage.
 The generated tests cover branchless methods and the root branch of the method \texttt{lookup}, which is the only method with some conditions.
@@
 The static analyzer implemented in \EVOSUITE does not handle the annotation \texttt{@Nullable} and triggers the error \textit{``Cannot find symbol''}.
+This, in retrospect, would have been easy to avoid.
 
@@
 \subsubsection*{PDFBOX-157} \EVOSUITE crashed in 9 out ten times with a search budget of 60s, and in 10 out of 10 runs for larger budgets.
+The exact reasons are not yet clear, and will require further debugging.
 
@@
 
-\subsubsection*{FESCAR-23, FESCAR-37, FESCAR-7, FESCAR-8, GUAVA-212, GUAVA-22, PDFBOX-265, PDFBOX-278, PDFBOX-285, PDFBOX-40, PDFBOX-91, PDFBOX-62, SPOON-105, SPOON-253} The mutation analysis
-failed due to a \texttt{java.util.concurrent.ExecutionException} thrown by the
-experimental infrastructure.
+\subsubsection*{FESCAR-23, FESCAR-37, FESCAR-7, FESCAR-8, GUAVA-212, GUAVA-22,
+PDFBOX-265, PDFBOX-278, PDFBOX-285, PDFBOX-40, PDFBOX-91, PDFBOX-62, SPOON-105,
+SPOON-253} For all these classes the mutation analysis failed due to a
+\texttt{java.util.concurrent.\\ExecutionException} thrown by the experimental
+infrastructure, rather than by \EVOSUITE.
 
@@
 
-\subsubsection*{PDFBOX-235, SPOON-155} \EVOSUITE crashed due to some Mocking stuff.
+\subsubsection*{PDFBOX-235, SPOON-155} In these two cases, \EVOSUITE crashed while attempting to set up mock objects; these are bugs in \EVOSUITE.
 
 \section{Conclusions}
+
+This paper reports on the participation of the \EVOSUITE test
+generation tool in the 8th SBST Java Unit Testing Tool Contest. With
+an overall score of \TOTALPOINTS points, \EVOSUITE achieved the
+highest score of all tools in the competition.
+Despite the many years of development, the benchmark used in the competition points out several opportunities for improvement, which we discussed in this paper.
+
+To learn more about \EVOSUITE, visit our Web site:
+\begin{center}
+%\url{http://evosuite.org/}
+\texttt{http://www.evosuite.org}
+\end{center}
 

### 2020-04-04 papers/sbst20/main.tex
Update score
Add acks and fix refs
My pass on the paper

@@
 \newcommand{\CS}{{\sc SF100}\xspace}
-\newcommand{\TOTALPOINTS}{{255.43}\xspace}
+\newcommand{\TOTALPOINTS}{{406.14}\xspace}
 
@@
 the \EVOSUITE test generation tool~\cite{FrA11c} in this competition. \EVOSUITE
-uses meta-heuristic search in order to evolve unit test suites with high
+uses meta-heuristic search to evolve unit test suites with high
 coverage, and automatically produces regression oracles in the form of test
@@
 class under test, \EVOSUITE automatically generates a set of JUnit test cases
-aimed at maximinizing code coverage. \EVOSUITE can be used on the command line,
+aimed at maximizing code coverage. \EVOSUITE can be used on the command line,
 as a Maven plugin, or using plugins for the Eclipse and IntelliJ development
@@
 
-Over the course of its development, several different search algorithms have
+Throughout its development, several different search algorithms have
 been evaluated, starting with a basic genetic algorithm.
@@
 
-Recently, the \textit{Dynamic Many-Objective Sorting Algorithm} (DynaMOSA) search algorithm~\cite{dynamosa, panichella:ssbse2018}  has been shown to be the most effective approach of all the algorithms evaluated so far.
+Recently, the \textit{Dynamic Many-Objective Sorting Algorithm} (DynaMOSA) search algorithm~\cite{dynamosa, panichella:ssbse2018, panichella2018large}  has been shown to be the most effective approach of all the algorithms evaluated so far.
 DynaMOSA is a many-objective algorithm, where individuals of the search population are test cases, rather than test suites, and the optimization is driven by a collection of individual fitness functions, one for each coverage objective (e.g., line or branch).
@@
 \EVOSUITE supports multiple different coverage criteria, which can be optimized
-for at the same time. The default configuration combines branch coverage with
+at the same time. The default configuration combines branch coverage with
 mutation testing~\cite{emse14_mutation} and other basic
@@
 %
-In order to cope with the potentially large number of coverage objectives,
+To cope with the potentially large number of coverage objectives,
 DynaMOSA prioritizes them during the search according to their structural
-dependencies in the control dependency graph. Initially the search focuses on
+dependencies in the control dependency graph. Initially, the search focuses on
 coverage objectives positioned higher in the hierarchy, and the remaining
@@
 coverage~\cite{fraser2014large,emse_archive,ea_evaluation,dynamosa},
-fault finding
+fault-finding
 effectiveness~\cite{shamshiri2015automatically,moein2017}, and effects
@@
 editions~\cite{evosuiteAtSbst2013,evosuiteAtFittest2013,evosuiteAtSbst2016,evosuiteAtSbst2017,evosuiteAtSbst2018}. In the 2019 SBST contest, \EVOSUITE
-achieved the highest overall score of all participating tools~\cite{evosuiteAtSbst2019}, although the
-performance was inhibited by some bugs.
+achieved the highest overall score of all participating tools~\cite{evosuiteAtSbst2019}, 
+although some bugs inhibited its performance.
 
@@
 Enterprise Edition features~\cite{arcuri2016java}.
-In the case of difficult dependencies and branches that cannot be covered, \EVOSUITE can start using mock objectes once a certain percentage of the search
+In the case of difficult dependencies and branches that cannot be covered, \EVOSUITE can start using mock objects once a certain percentage of the search
 budget has passed~\cite{ICST_Mocking17} .
@@
 The test minimization step used by \EVOSUITE is computationally expensive and
-sometimes omitted for empirical studies; in the competition we always enable
+sometimes omitted for empirical studies; in the competition, we always enable
 the post-processing step of test minimization, because minimized tests are less
@@
 
-\EVOSUITE uses different phases (e.g., initialisation, search, minimization,
+\EVOSUITE uses different phases (e.g., initialization, search, minimization,
 assertion generation, compilation check, removal of flaky tests). Like in
-previous competitions (e.g.,~\cite{evosuiteAtSbst2016}) we allocated 50\% of
-the overall time set by the competition organisers for the search, and
+previous competitions (e.g.,~\cite{evosuiteAtSbst2016}), we allocated 50\% of
+the overall time set by the competition organizers for the search, and
 distributed the other 50\% equally to the remaining phases.
@@
 results.
-As usual, there are some noteable cases where \EVOSUITE did not perform well.
+As usual, there are some notable cases where \EVOSUITE did not perform well.
 In the following, we discuss these cases, such that future work can address open problems in automated unit test generation.
@@
 %0\% coverage and we could not find any issues in any %log file. 
-For further investigation, we ran \EVOSUITE as stand-alone tool (i.e., not using the benchmark infrastructure but it was still not capable of covering any line.
+For further investigation, we ran \EVOSUITE as a stand-alone tool (i.e., not using the benchmark infrastructure) but it was still not capable of covering any line.
 Through manual investigation, we notice that the CUT manages objects of the class \texttt{ScheduledExecutorService} and \textit{threads}.
 Generating tests for CUTs that produce or manage threads is challenging and a well-known open problem in the literature~\cite{FrA13a}.
-\EVOSUITE does not prevent the CUT to spawn new threads, but it (1) forces the use of a wrapper class that leads to deterministic stack traces and thread names, and (2) any spawned threads are joined and removed after a test execution to ensure a clean state for successive test executions, which may consume a substantial amount of time.
+\EVOSUITE does not prevent the CUT from spawning new threads, but it (1) forces the use of a wrapper class that leads to deterministic stack traces and thread names, and (2) any spawned threads are joined and removed after a test execution to ensure a clean state for successive test executions, which may consume a substantial amount of time.
 
@@
 
+\textbf{Acknowledgments:} Many thanks to all the contributors to
+\EVOSUITE.  This project has been funded by the EPSRC project
+``GREATEST'' (EP/N023978/2).
+
 \balance
